### 2013-04-13 doc/paper.tex
first commit

%\IfFileExists{revtex4-1.cls}{\documentclass[prd, twocolumn, lengthcheck, superscriptaddress, showpacs, letterpaper, footinbib]{revtex4-1}}{ 
%\IfFileExists{revtex4.cls}{\documentclass[prd, twocolumn, lengthcheck, superscriptaddress, showpacs, letterpaper]{revtex4}}{}}
\documentclass{emulateapj}

%\documentclass[prd, twocolumn, lengthcheck,superscriptaddress, showpacs, letterpaper, footinbib]{revtex4}
%\documentclass[lengthcheck,superscriptaddress,showpacs,letterpaper,nofootinbib]{article}
\usepackage{ifpdf}
\usepackage[bookmarks=false]{hyperref}
\pdfoutput=1
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx}
\usepackage{graphics}  
  \usepackage{float}
%\restylefloat{table}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{acronym}
\usepackage{multirow}
\usepackage{xspace}
%\restylefloat{figure}
\usepackage{units}
\usepackage{dcolumn}
\usepackage{ulem}

\def\aj{Astron. J.}                 % Astronomical Journal
\def\apj{Astrophys. J.}                % Astrophysical Journal
\def\apjl{Astrophys. J. Lett.}             % Astrophysical Journal, Letters
\def\pasj{PASJ}
\def\apjs{Astrophys. J., Suppl. Ser.}              % Astrophysical Journal, Supplement
\def\mnras{Mon. Not. R. Astron. Soc.}            % Monthly Notices of the RAS
\def\prd{Phys. Rev. D}       % Physical Review D
\def\prl{Phys. Rev. Lett.}    % Physical Review Letters
\def\cqg{Class. Quant. Grav.}%Classical and Quantum Gravity
\def\araa{Annu. Rev. Astron. Astrophys.}             % Annual Review of Astron and Astrophys
\def\nat{Nature}              % Nature
\def\aap{Astron. Astrophys.}                % Astronomy and
                                % Astrophysics
\def\jasa{J. Am. Stat. Assoc.}
\def\pccp{Phys. Chem. Chem. Phys.}
\def\jrssb{J. R. Stat. Soc. B}
\def\aipcs{AIP Conf. Ser.}
\def\jcp{J. Chem. Phys.}

\newcommand{\carl}[1]{{\color{red}  #1}}
\newcommand{\ilya}[1]{{\color{blue} #1}}
\newcommand{\ben}[1]{{\color{green} #1}}
\newcommand{\will}[1]{{\color{cyan} #1}}

\begin{document}
\title{Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/VIRGO Network}
\author{Carl L. Rodriguez}
\email{carlrodriguez2015@u.northwestern.edu}
\affiliation{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) \& Dept.~of Physics and Astronomy, Northwestern University, 2145 Sheridan Rd, Evanston, IL 60208, USA}

\begin{abstract}
\end{abstract}

\maketitle
\section{Introduction}

 By 2016 (\carl{?}), the field of gravitational-wave astrophysics will mature from a speculative scientific genre into an ideal tool for exploring the gravitational side of the universe.
 Within the next few years, the first generation of gravitational-wave detectors capable of regularly resolving astrophysical sources will come online \carl{cite}.   The Advanced LIGO and VIRGO detectors will provide  the first insights into the final moment of binary compact object mergers, including the merger of binary neutron star systems.  Intense preparations are currently underway to prepare to characterize and extract as much physical information as possible from these signals.

The mergers of binary neutron stars are expected to be the most ubiquitous source in the advanced detector era \carl{cite}.   Models from stellar evolution suggest that the number of binary neutron star mergers within Advanced LIGO/VIRGO's detection horizon could reach into the hundreds per year \carl{cite}.  Although the peak sensitivity of ground-based detectors is not focused on the frequency at which BNS systems merge, it should still be possible to extract information about both strong field gravitational physics \carl{cite} and the hydrodynamics of dense matter (e.g. the equation of state of nuclear matter) \carl{cite}.  As such, BNS systems will likely form the ``bread and butter'' of the compact object efforts in the coming years \carl{the high-mass folks might not like this, but fuck 'em}.

Of course, in this context, one must distinguish between the detection of such events, and the precision measurement of the relevant physical parameters.   There are two separate issues to consider in this context: the detection of BNS systems will be performed with a matched filtering approach, which allows one to search the time domain data at a sufficiently fast rate \carl{[yeah that phrasing sucks]} by comparing the data stream to a bank of theoretical templates.  When the overlap between one of the template waveforms and the detector output is sufficiently large (97\%), a detection is claimed.  However, the parameter space of our signals can be highly degenerate, with several locations in parameter space corresponding to near identical waveforms.  In order to fully realize the science potential of these instruments, we must perform a full exploration of the parameter space for each detection.  By analyzing each candidate's parameter space with fully Bayesian techniques and proper sampling, we will be able to make precise, scientifically meaningful statements about the composition and formation of these objections.  To this end, we employ a Markov-Chain Monte Carlo sampling algorithm, included in the LIGO Application Library parameter estimation code, \texttt{LALInferenceMCMC}.

By employing the full parameter estimation machinery that will eventually be used in the Advanced Detector era, our results give the first estimate at the realistic capabilities of Advanced ground-based detectors.  Until recently, the majority of studies have employed the Fisher matrix formalism as it was first adapted for gravitational-wave parameter estimation by \cite{FinnDetection}.  While each of these studies (\cite{PoissonWill,CutlerFlanagan,ArunPE}, among many others) have done their due diligence in pointing out the limitations and flaws of the Fisher Information Matrix, there has been no study which states the BNS parameter estimation capabilities of Advanced LIGO/VIRGO via the techniques that will eventually be employed.  The recent work of \cite{Vallisneri} and our own work \citep{Inadequacies} has demonstrated that the Fisher matrix cannot even be treated as a lower bound on the standard deviations about certain parameters (particularly the masses) measurable in advanced detectors.

In this paper, we perform a systematic study of the statistical uncertainty with which the Advanced LIGO network will be able to measure the basic parameters of binary neutron stars.  In section \ref{BNSsection}, we review some of the basic physics of gravitational waves from binary neutron stars, including the potential science case to be made with Advanced LIGO.  In section \ref{PEsection}, we describe the machinery of our parameter estimation code, \texttt{LALInferenceMCMC}, as well as the gravitational-wave template used for signal extraction.   In section \ref{ResultsSection}, we

\begin{itemize}
 \item BNS source
\item PE vs detection
\item Why not FIM
\item Overview
\end{itemize}

\section{BNS systems}
\label{BNSsection}
\begin{itemize}
\item expected rates
\item interesting physics
\item Expected parameters (non spinning, SNR distribution, etc)
\item waveform issues
\end{itemize}

\section{Parameter Estimation}
\label{PEsection}

\begin{itemize}
\item parameter estimation setup
\item MCMC
\item Waveform model
\end{itemize}
\label{peSection}

We begin by introducing a Bayesian formalism for parameter estimation. 
%Before offering a brief derivation of the FIM, a few preliminary
%techniques must be introduced.  First,
We assume that the time-domain signal in our gravitational wave
network can be written as a combination of a gravitational
waveform $h_0$ and the noise of the detector $n$.  We further assume
that this noise is stationary and Gaussian with mean zero.  Therefore,
the detector output is simply
\begin{equation}
s = n + h_0 .
\label{SignalAddition}
\end{equation}
Since our noise is assumed to be Gaussian, we can write the
probability of a specific signal realization $s$ as the probability
that our signal is Gaussian once the waveform has been subtracted
\begin{align}
  p(s | \boldsymbol{\theta}) &\propto \exp\left[-\frac{1}{2}\left<n|n
    \right>\right] \nonumber \\ &= \exp\left[-\frac{1}{2}\left < s -
    h(\boldsymbol{\theta}) | s-h(\boldsymbol{\theta})\right >\right] ,
  \label{likelihood}
\end{align}
where $\boldsymbol{\theta}$ is the set of parameters for our template
waveforms.The inner product, $\left< ~|~ \right> $, is defined using the noise
spectrum of the detectors as
\begin{equation}
  \left<a|b\right> \equiv 4 \Re \int \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df ,
  \label{innerProduct}
\end{equation}
where $S_n(f)$ is the one-sided power spectral density as a function
of frequency, and $\tilde{a}(f)$ and $\tilde{b}(f)$ are the Fourier
transforms of the time-domain signals $a(t)$ and $b(t)$.

Once we have the likelihood of the signal \eqref{likelihood}, we
employ Bayes Rule to obtain the posterior probability of the system
parameters $\boldsymbol{\theta}$ given the signal $s$ as
\begin{align}
  p(\boldsymbol{\theta} | s) &= \frac{p(\boldsymbol{\theta})p(s | \boldsymbol{\theta})}{p(s)} \nonumber\\
  & \propto p(\boldsymbol{\theta}) \exp\left[-\frac{1}{2}\big < s - h(\boldsymbol{\theta}) | s-h(\boldsymbol{\theta}) \big > \right] ,
  \label{posterior}
\end{align}
where $p(\boldsymbol{\theta})$ are the prior probabilities on our
source parameters and $p(s)$ is a normalization constant.  Our prior
information can come from physics limits in the parameter space, or
from our \textit{a priori} knowledge of astrophysical systems. If we
pick a set of parameters $\boldsymbol{\theta}$ such that
$h(\boldsymbol{\theta}) = h_0$, then our posterior \eqref{posterior}
will be near a global maximum; however, the presence of noise will in
general deflect the maximum of our posterior away from the value at
$\boldsymbol{\theta}_0$. That is, in the presence of noise, there is
no guarantee that the maximum-likelihood of our signal corresponds to
the true parameters of the system.  Hence our use of the term
``best-fit parameters'' (\citep{CutlerFlanagan}), particularly when
discussing the point in parameter space where the FIM is evaluated.
The goal of parameter estimation is to sample the available parameter
space, considering all areas of posterior support, to determine best
estimates on the parameters of the signal and their uncertainties.  We
will discuss one such sampling technique, Markov-Chain Monte Carlo, in
\ref{MCMCSection}.

\subsection{Parameter estimation via Markov-Chain Monte Carlo}
\label{MCMCSection}

Our parameter estimation code, \texttt{LALInferenceMCMC}, is an
enhancement of the previously described MCMC parameter estimation code
\texttt{SpinSpiral} \citep{spinspiral2009, spinspiral2010}.  The basic
description of the Markov-Chain Monte Carlo via the
Metropolis-Hastings algorithm is as follows \citep{Gilks99}:

\begin{enumerate}
\item Pick an initial point in the parameter space
  ($\boldsymbol{\theta_{\text{old}}}$), and then propose a random
  ``jump'' to a new set of waveform parameters,
  $\boldsymbol{\theta_{\text{new}}}$.  The jump follows the
  (conditional) probability distribution $q\left(
  \boldsymbol{\theta_{\text{new}}} | \boldsymbol{\theta_{\text{old}}}
  \right)$.
\item Calculate the posterior probability,
  $p(\boldsymbol{\theta_{\text{new}}}|s)$, of the new parameters using
  \eqref{likelihood} and \eqref{posterior}.
\item Accept the new parameters with probability 
  \begin{equation}
    p_\mathrm{accept} = \min \left[ 1, \frac{p(\boldsymbol{\theta_{\text{new}}}|s) q\left(\boldsymbol{\theta_{\text{old}}} | \boldsymbol{\theta_{\text{new}}} \right)}{p(\boldsymbol{\theta_{\text{old}}}|s) q\left(\boldsymbol{\theta_{\text{new}}} | \boldsymbol{\theta_{\text{old}}} \right)} \right].
  \end{equation}
  If the new parameters are accepted, record
  $\boldsymbol{\theta_\text{new}}$ and repeat with
  $\boldsymbol{\theta_\text{old}} \gets
  \boldsymbol{\theta_\text{new}}$; otherwise, record
  $\boldsymbol{\theta_\text{old}}$, and repeat.
\end{enumerate}

The above procedure is designed to record a chain of samples whose
distribution is $p\left(\boldsymbol{\theta}|s\right)$.  Depending on
the proposal distribution, $q$, the convergence (mixing) of the chain
may be rapid or slow.  We employ multiple optimization techniques,
including both specially-crafted $q$ and parallel tempering, to ensure
adequate mixing of the Markov Chains throughout our parameter space.
The details of the algorithm can be found in
\citep{Sluys08,spinspiral2009, spinspiral2010}.

\subsection{Waveform Model}
\label{waveformSection}

We use a frequency domain waveform accurate up to $3.5$
post-Newtonian (pN) order in phase and amplitude.  We restrict ourselves to
quasi-circular waveforms as a simplifying assumption.  The standard
form of our waveform model, known as the \textit{TaylorF2}
approximant, is calculated via the stationary phase approximation \citep{BuonannoWaveform}.
  In this setup, the gravitational-wave
amplitude is given by
\begin{equation}
\tilde{h}(f) = A f^{-7/6}e^{i \psi(f)},
\label{amplitude}
\end{equation}
where $A \propto \mathcal{M}_c^{5/6}\Theta(\text{angle})/D$, $D$ is
the luminosity distance of the binary, and $\psi(f)$ is the pN phase.
$\Theta(\text{angle})$ is a function of the orbital orientation with
respect to the detector network in terms of the sky position, orbital
inclination, and the wave polarization.  In addition to the total
mass, $M\equiv m_1+m_2$, it is convenient to work with the
\textit{symmetric mass ratio} and \textit{chirp mass}, defined by
\begin{equation}
  \eta\equiv m_1m_2/M^2~~~~\text{and}~~~~\mathcal{M}_c = \eta^{3/5}M,
\end{equation}
respectively.  Then, in terms of the Newtonian orbital velocity
$v=(\pi M f)^{1/3}$, the 2pN phase is
\begin{equation}
\psi(f) = 2 \pi f t_c - \phi_0 + \frac{\pi}{4} + \frac{3}{128 \eta}v^{-5}\sum^{4}_{k=0}\alpha_{k}v^k
\label{phase}
\end{equation}
with coefficients
\begin{align}
\alpha_0 &= 1\\
\alpha_1 &= 0 \nonumber\\
\alpha_2 &= \frac{20}{9}\left(\frac{743}{336}+\frac{11}{4}\eta\right)\nonumber\\
\alpha_3 &= -16\pi \nonumber\\
\alpha_4 &= 10\left(\frac{3058673}{1016064}+\frac{5249}{1008}\eta+\frac{617}{144}\eta^2  \right) . \nonumber\\
\alpha_5 &= \pi\left(\frac{38645}{756}-\frac{65}{9}\eta\right)\left(1+3\log\left(\frac{v}{v_{\text{ISCO}}}\right)\right)\nonumber\\
\alpha_6 &= \frac{11583231236531}{4694215680} - \frac{640}{3}\pi^2 - \frac{6848}{21}\gamma_{\text{euler}} \nonumber\\
         &~~- \frac{6848}{21} \log\left(4 \frac{v}{v_{\text{ISCO}}}\right) -\left(\frac{15737765635}{3048192}-\frac{2255}{12}\pi^2\right)\eta\nonumber\\
           &~~+ \frac{76055}{1728}\eta^2 - \frac{127825}{1296}\eta^3\nonumber\\
\alpha_7 &= \pi\left(\frac{77096675}{254016}+\frac{1014115}{3024}\eta - \frac{36865}{368}\eta^2\right)\nonumber
\end{align}
The terms $t_c$ and $\phi_0$ in equation (\ref{phase}) are constants
of integration, referring to the chirp time and coalescence phase,
respectively.  Although uninteresting physically, they must be
accounted for in any parameter estimation study of the waveform phase.

To perform the integral defined in \eqref{innerProduct}, we used an
analytic noise curve for the Initial LIGO configuration, provided in
\citet{DarmourNoiseCurve}, which takes the form:
\begin{align}
 S_h(f)=&S_0\Big[ \left(\frac{4.49 f}{f_0} \right)^{-56} + \nonumber\\
 &\left(\frac{0.16f}{f_0}\right) ^{-4.52}+0.52+0.32\left( \frac{f}{f_0}\right) ^2\Big],
 \label{PSD}
\end{align}
where $f_0 = 150~\text{Hz}$, and $S_0 = 9\times
10^{-46}\text{Hz}^{-1}$.  We consider the complete initial detector
network consisting of the two LIGO sites (in Hanford, WA and
Livingston, LA) and the Virgo site (in Pisa), although for simplicity
we use the Initial LIGO sensitivity for all three detectors.  For a
multi-detector network, the noise-weighted inner products
\eqref{innerProduct} combine linearly, allowing us to use the above
formalism with minimal modification.  We integrate the inner product
from a lower frequency cutoff of $40\text{Hz}$ to the
innermost-stable-circular orbit of the system in question, which for a
non-spinning binary is given by
\begin{equation}
  \pi f_{\text{ISCO}} = \frac{1}{6^{3/2}M}.
  \label{ISCOFrequency}
\end{equation}

In addition to the intrinsic parameters listed above ($\mathcal{M}_c,
\eta, \phi_0,t_c$), we include an additional 5 extrinsic parameters in
our parameter estimation, in order to explore how a full parameter
estimation study on real data, including parameters such as sky
location, will compare to their FIM counterparts.  This leads to our
9-dimensional parameter space for non-spinning systems:
\begin{equation}
\boldsymbol{\theta} =  (\mathcal{M}_c, \eta, \phi_0,t_c,D,\iota,\psi,\alpha,\delta)
\label{parameterspace}
\end{equation}
where $D$ is the luminosity distance to the binary, $\iota$ is the
orbital inclination, $\psi$ the gravitational-wave polarization, and
$\alpha$ and $\delta$ the right ascension and declination of the
source on the sky.

Note that the signal-to-noise ratio (SNR) of a gravitational wave in a
single detector is
\begin{equation}
  \rho \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{| \tilde{s}(f)\tilde{h}^{*}(f)|}{S_{n}(f)}df
  \label{formalSNR}
\end{equation}
where $\rho$ is the SNR and $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
the frequency-domain signal and template, respectively.  The SNRs for
multiple detectors add in quadrature.  The normalization $\sigma$ is
given by
\begin{equation}
  \sigma^2 = 4\int^{\infty}_{0}\frac{| \tilde{h}(f)|^2}{S_n(f)}df.
  \label{SNRnorm}
\end{equation}
For our MCMC analysis, we compute the SNR directly using
\eqref{formalSNR}.  In the case of the FIM, we approximate the SNR
using $\sigma$ from equation (\ref{SNRnorm}) for a network of
detectors as
\begin{equation}
\rho = \sqrt{\sum_i \sigma_i^2}
\label{snr}
\end{equation}
where the index $i$ refers to the signal and noise spectrum of the
$i^{\text{th}}$ detector.  It should be noted that equation
\eqref{snr} is only valid in case of stationary Gaussian noise.

\begin{figure*}[h]
\begin{center}
\includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.57]{9dpdf.pdf}
%\begin{array}{ccc} 
%\includegraphics[width=2.2in]{1dpdfs/mc.pdf} &\includegraphics[width=2.2in]{1dpdfs/eta.pdf}  & \includegraphics[width=2.2in]{1dpdfs/m1.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/time.pdf} &\includegraphics[width=2.2in]{1dpdfs/dist.pdf}  &\includegraphics[width=2.2in]{1dpdfs/iota.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/ra.pdf} & \includegraphics[width=2.2in]{1dpdfs/dec.pdf} & \includegraphics[width=2.2in]{1dpdfs/m2.pdf}
%\end{array}$
\end{center}
\caption{Marginalized 1D posterior probability density functions taken from a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS system.  We have plotted each of the 9 parameters for our non-spinning BNS problem as stated in section \ref{waveformSection}.  Note how, even for parameters with excellent recovery, the peak of the 1D Gaussian is displaced from the injected value (in dashed red).  This is not due to a systematic bias, but is caused by the marginalization of a single dimmension from the full 9D posterior space.}
\end{figure*}

\begin{figure*}[h!]
  \centering
 \includegraphics[trim=2cm 0cm 2cm 0cm, clip=true,scale=0.63]{1414masses2D.pdf}
 \label{1414masses}
 \caption{2D marginalized posterior probability density functions for the mass parameters recovered in typical a $1.4M_{\odot}/1.4M_{\odot}$ system.  The posteriors are plotted in terms of parameters used in the waveform, chirp mass ($\mathcal{M}_C$) and the reduced mass ratio ($\eta$), and in the individual component masses of the binary ($M_1$ and $M_2$).  In the $\mathcal{M}_c$-$\eta$ space, the posterior would resemble a Gaussian if not for the limitation of $\eta \leq 0.25$.  The presence of the $\eta$ cutoff and the convention that $M_1 \geq M_2$ inform the non-Gaussian features present.  When projected as 1D marginalized posteriors, the component masses resemble the posterior PDFs shown in figure \ref{masses}.}
\end{figure*}

\begin{figure*}[h!]
  \centering
 \includegraphics[trim=2cm 0cm 2cm 0cm, clip=true,scale=0.63]{125masses2D.pdf}
 \label{125masses}
 \caption{Similar to figure \ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.  The unequal mass ratio displaces the posterior PDFs from the $\eta \leq 0.25$ present in the equal mass case, yielding a Gaussian PDF in both the $\mathcal{M}_c$-$\eta$ and $M_1$-$M_2$ spaces.}
\end{figure*}

\begin{figure*}[h!]
  \centering
 \includegraphics[trim=2cm 0cm 2cm 0cm, clip=true,scale=0.67]{newMasses.pdf}
 \label{masses}
 \caption{Typical 2D mass PDFs for the }
\end{figure*}

%\begin{figure*}[h]
%\begin{center}$
%\begin{array}{cc} 
%\includegraphics[width=3.2in]{skyPos/2.png} &\includegraphics[width=3.2in]{skyPos/4.png}  \\
%\includegraphics[width=3.2in]{skyPos/5.png} & \includegraphics[width=3.2in]{skyPos/7.png} 
%\end{array}$
%\end{center}
%\caption{Example SkyPlots}
%\end{figure*}

\begin{figure*}[tp!]
  \centering
 \includegraphics[angle=0,scale=0.49, trim=5cm 0cm 3cm 0cm]{skyLoc.pdf}
 \caption{The uncertainty on the sky of the 160 BNS systems.  Each region represents a single injection, with the colored central region representing the 65\% \carl{[CHECK THAT]} uncertainty region on the sphere, and the gray region representing the 90\% uncertainty region.  The color scheme indicates the total solid angle size of the 65\% region.  Note the similar shape of the uncertainty regions at particular points; this is due to the specific realization of our network pattern sensitivity.}
 \label{2525SkyLoc}
\end{figure*}

\begin{figure*}[h!]
  \centering
 \includegraphics[trim=2cm 0cm 2cm 0cm, clip=true,scale=0.575]{distIota2D.pdf}
 \label{masses}
 \caption{Typical 2D mass PDFs for the }
\end{figure*}

\begin{table*}[t!]
\caption{}
\begin{tabular}{lcccccccccccc}

\hline\hline
System & \vline &  $\Delta \mathcal{M}_c / \mathcal{M}_c$ & \vline & $\Delta \eta$ & \vline & $\Delta M_1/ M_1$ & \vline & $\Delta M_2 / M_2$ & \vline & $\Delta \phi_c$ & \vline &  $\Delta t_c$ (ms)\\
\hline\hline
$1M_{\odot}-1M_{\odot}$ & \vline & & \vline & & \vline & & \vline & & \vline & & \vline &\\
\hline
$1.4M_{\odot}-1.4M_{\odot}$ & \vline & & \vline & & \vline & & \vline & & \vline & & \vline &\\
\hline
$1M_{\odot}-2.5M_{\odot}$ & \vline & & \vline & & \vline & & \vline & & \vline & & \vline &\\
\hline
$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.29 \times 10^{-4}$ & \vline & $1.34 \times 10^{-3}$ & \vline & $ 4.01 \times 10^{-2}$ & \vline & $3.65\times 10^{-2}$ & \vline & 1.807 & \vline & 0.418 \\
\hline\hline

\end{tabular}
\label{biasedUnbiasedChirpMassErrors}
\end{table*}

\section{Results}
\label{resultsSection}

Of the 9 parameters in the domain of the waveform, only 6 are particularly physically interesting: the masses of the two binaries, $M_1$ and $M_2$, the inclination of the binary with respect to the observer, $\iota$, the angular position on the sky, $\alpha$ and $\delta$, and the distance of the source, $D$.

\subsection{Mass Parameters}

Of the 9 variables in our parameter space \eqref{parameterspace}, the two of immediate physical interest are the two parameters, $\mathcal{M}_c$ and $\eta$, or correspondingly the direct masses of the two companions, $M_1$ and $M_2$.    As stated in section \ref{BNSsection}, the ability of Advanced LIGO/VIRGO to construct a population of BNS masses will be critical to the science potential of gravitational-wave astronomy.

We find that there is virtually no difference between the mass PDFs of our different injected signals within each mass bin.  At first, this may seem disconcerting; however, it is to be expected.  Recall that of the BNS signals were injected with a network SNR of $\rho = 20$ into a zero-noise detector realization.  Furthermore, note that the mass parameters are the only two which directly effect the phase of the TaylorF2 waveform \eqref{phase}.  Therefore, as long as the injected mass parameters are identical within each mass system (they are), and as long as the injected SNR is identical (it is), the amount of recoverable information in each mass parameter should be \emph{almost} identical, and for a sufficiently converged MCMC chain, the recovered posterior PDF should be \emph{almost} identical.

The ``almost'' in the previous sentence is to draw attention to one critical, neglected fact: while the mass parameters are independent of the injected signals position with respect to the detector network, the other parameters are certainly not.  Obviously many of the other parameters (i.e. sky location, polarization, distance, inclination, and time-of-arrival) all depend on the orientation of the binary inspiral with respect to each of the individual detector locations.  Since our 9-dimensional parameter space can be highly correlated, it is entirely reasonable to assume that cross-correlations between the extrinsic parameters and the mass parameters will cause variation in the recovery of the individual injection PDFs.

In practice, it was found that the cross-correlations between the extrinsic parameters and signal time-of-arrival were several orders of magnitude \carl{[QUANTIFY THIS]} below the uncertainties in $\mathcal{M}_c$ and $\eta$.  It should be noted that, in practice, this will \emph{not} be the case: in reality, the noise power-spectral density of each detector varies as a function of time, including both natural variations in sensitivity and detector glitches \carl{[CITE SOMETHING]}.  In such a case, the base sensitivity of a gravitational-wave detector to even the easiest to recover parameters will vary as a function of position and time.  What we report here can thus be considered an idealized, ``glitch-free'' world in which each detector has an identical noise realization at all times.  In Section \ref{NoisySubSection}, we provide each detector with a random, but not identical, noise model based on the Advanced LIGO PSD, thus giving an insight into this time-dependent variation \carl{[PLEASE TELL ME THAT'S WHAT LALINFERENCE DOES...]} (while still ignoring instrumentation glitches).

In Figures \ref{1414masses} and \ref{125masses}, we show the marginalized 2D posterior PDFs of our mass parameters a prototypical equal mass and unequal mass binaries.  We include the PDF in both the $\mathcal{M}_c$-$\eta$ space (relevant for the waveform), and the more physically interesting component mass space ($M_1$-$M_2$).  Although only the $1.4M_{\odot}/1.4M_{\odot}$ system is included in Figure \ref{1414masses}, the PDF is virtually identical to the other equal mass cases, modulo a scaling factor.  Again, this is unsurprising due to the identical SNR of each of the injected signals.

\subsection{Sky Localization}

\subsection{Inclination and Distance}

\begin{enumerate}
\item Inclination for GRB folks
\item Distance for population studies
\item degeneracy between the two
\end{enumerate}

\subsection{Varied Noise Realizations}
\label{NoisySubSection}
\subsection{Testing MCMC Convergence}

\carl{include a paragraph on our standard convergence checks}.  However, there is an additional check we can consider: the standard matched filtering searches employed by the LIGO/VIRGO collaboration assume that a detection will occur when one of the template waveforms matches the detector data with a signal overlap of 97\% or better \carl{cite something}.  That is, for a template waveform $h^{t}(f)$ and detector output $s(f)$, an overlap of

\begin{equation}
\left< s | h^{t}\right> \geq 97\%
\nonumber
\end{equation}

\noindent  yields a detection.  This requirement provides us with a convenient test for the effectiveness of our parameter estimation.  First, we note that maximizing our likelihood function, \eqref{likelihood}, is identical to maximizing the SNR \eqref{formalSNR} of our template waveform in a given stretch of data.  Therefore, the better the match between the template waveform and the data, the higher the SNR.  Since we assume, quite tautologically, that our parameter estimation code should estimate parameters at least as well as a matched filtering approach, we would be immediately suspicious of any MCMC run whose maximum-likelihood waveform had an SNR below that of our pipeline trigger.   In that case, we would perform the MCMC with a much longer runtime, until the maximum likelihood of our posterior distribution had an SNR at least as high as the detection.

For the purposes of our present study, we reproduce this information as follows: since we know the true SNR of the signal we are simulating, we assume that the ``trigger'' SNR returned by our detection pipeline is 97\% of the true SNR.  We then assume any posterior distribution whose maximum likelihood satisfies

\begin{equation}
\text{Maximum Likelihood} \leq 0.97 \times \left(\frac{\rho_{inj}^2}{2}\right) 
\nonumber
\end{equation}

\noindent has not converged.  As one would expect, the lower-mass, longer waveform systems require longer to converge.  With our original runtime of one week over 8 processors, we found that seven of our $1M_{\odot}/1M_{\odot}$ systems had not converged, while all but one system for our $1.4M_{\odot}/1.4M_{\odot}$ and $1M_{\odot}/2.5M_{\odot}$ systems had converged.  All of the $2.5M_{\odot}/2.5M_{\odot}$ systems converged within the week.

We performed a second run for each of the non-converged systems

\bibliographystyle{apj}
\bibliography{paper}{}

\end{document}

### 2013-04-13 9oneDpdfs.py

@@ -1,0 +1,70 @@
+import scipy.stats
+from matplotlib import pyplot as plt,cm as mpl_cm,lines as mpl_lines,colorbar
+
+def m1m2fromMcq(Mc,q):
+
+	m1 = Mc*((1+q)/q**3)**0.2
+	m2 = Mc*(q**2 * (1+q))**0.2
+	if m1<m2:
+		m1,m2 = m2,m1
+
+	return m1, m2
+
+file = open('posterior_samples.dat')
+filedata = file.readlines()
+file.close()
+
+postSamp = [[] for i in range(9)]
+num = [11, 10, 8, 6,5,7,3,4,9]
+names = ["$\mathcal{M}_c$","$\eta$","$\phi_c$","$\\alpha$","$\delta$","$D$","$\iota$","$\psi$","$Time$"]
+xaxis = ["Chirp Mass $(M_{\odot})$","Mass Ratio","Chirp Phase $(rad.)$","Right Ascension $(rad.)$","Declination $(rad.)$","Distance $(MPC)$","Inclination $(rad.)$","Polarization $(rad.)$","Time $(msec.)$"]
+inject = [1.21877,0.24995,2.68833,4.662361,-0.4254096,99.15952,2.353028,2.153679,0.]
+ticks = [[1.2183,1.2185,1.2187,1.2189],
+         [0.24,0.2425,0.245,0.2475,0.25],
+		 [0,1,2,3,4,5,6],
+		 [4.65,4.66,4.67,4.68,4.69],
+		 [-0.6,-0.55,-0.5,-0.45,-0.4,-0.35],
+		 [40,60,80,100,120,140,160,180],
+		 [1.8,2,2.2,2.4,2.6,2.8,3.0],
+		 [0,0.5,1,1.5,2,2.5,3,3.5],
+		 [-2,-1,0,1]]
+		 
+
+for i in range(1,len(filedata)):
+	for j in range(9):
+			postSamp[j].append(float(filedata[i].split()[num[j]]))
+			if j==1:
+				m1, m2 = m1m2fromMcq(postSamp[0][i-1],postSamp[1][i-1])
+				postSamp[1][i-1] = m1*m2 / (m1+m2)**2 
+			if j == 8:
+				postSamp[j][i-1] = (postSamp[j][i-1] - 894429279.)*1000
+
+
+KDEdataX = []
+KDEdataY = []
+
[…]

### 2013-04-13 DistIotaComp.py

@@ -1,0 +1,35 @@
+from math import *
+from numpy import *
+from pylal import bayespputils as bppu
+
+Dist= [[] for i in range(4)]
+Iota= [[] for i in range(4)]
+filenumbers = ['5','27','40','36']
+injected = [(100.8422,1.5548),(124.73,1.782),(170.41,2.135),(145.78,1.671)]
+
+for j in range(4):
+		file = open('1.4_1.4/' + filenumbers[j] + '/post/posterior_samples.dat')
+		filedata = file.readlines()
+		file.close()
+
+		for i in range(1,len(filedata)):
+			[dist,chain,v1_end_time,f_lower,logll1,logl,loglh1,loglh2,v1h1_delay,l1v1_delay,l1h1_delay,loglv1,m1,ra,l1_end_time,m2,iota,v1l1_delay,psi,post,cycle,mc,h1v1_delay,logprior,phi_orb,h1l1_delay,q,prior,h1_end_time,eta,time,cosiota,dec] = filedata[i].split()
+			Dist[j].append(float(dist))
+			Iota[j].append(float(iota))
+
+
+subplots_adjust(left=None, bottom=None, right=None, top=0.83, wspace=None, hspace=0.4)
+for j in range(1,5):
+		suptitle("2D Marginalized Distance/Inclination Posteriors", fontsize=26)
+		subplot(2,2,j)
+		#ax.set_xticks([1.3484,1.3486,1.3488, 1.3490,1.3492])
+		gridsize = 60
+		hexbin(Dist[j-1],Iota[j-1], gridsize=gridsize, cmap=cm.gist_stern, bins=None)
+		plot(injected[j-1][0],injected[j-1][1],marker='o', color='w',markersize=18)
+		pyplot.colorbar()
+		title('$D$ vs. $\iota$',fontsize=24)
+		xlabel('$D (mpc)$',fontsize=18)
+		ylabel('$\iota (rad)$',fontsize=18)
+
+draw()
+show()

### 2013-04-13 McEtaComp.py

@@ -1,0 +1,40 @@
+from math import *
+from numpy import *
+from pylal import bayespputils as bppu
+
+Mc = []
+Eta = []
+M1 = []
+M2 = []
+
+file = open('postSamp1414.dat')
+filedata = file.readlines()
+file.close()
+
+for i in range(1,len(filedata)):
+	[dist,chain,v1_end_time,f_lower,logll1,logl,loglh1,loglh2,v1h1_delay,l1v1_delay,l1h1_delay,loglv1,m1,ra,l1_end_time,m2,iota,v1l1_delay,psi,post,cycle,mc,h1v1_delay,logprior,phi_orb,h1l1_delay,q,prior,h1_end_time,eta,time,cosiota,dec] = filedata[i].split()
+	Eta.append(float(eta))
+	Mc.append(float(mc))
+	M1.append(float(m1))
+	M2.append(float(m2))
+
+
+suptitle("2D Marginalized Mass Posteriors for $1.4M_{\odot}/1.4M_{\odot}$ System", fontsize=30)
+ax = subplot(1,2,1)
+#ax.set_xticks([1.3484,1.3486,1.3488, 1.3490,1.3492])
+subplots_adjust(left=None, bottom=None, right=None, top=0.83, wspace=None, hspace=0.15)
+gridsize = 60
+hexbin(Mc,Eta, gridsize=gridsize, cmap=cm.gist_stern, bins=None)
+title('$\mathcal{M}_c$ vs. $\eta$',fontsize=24)
+xlabel('$\mathcal{M}_c$',fontsize=18)
+ylabel('$\eta$',fontsize=18)
+cb = pyplot.colorbar()
+ax = subplot(1,2,2)
+hexbin(M1,M2, gridsize=gridsize, cmap=cm.gist_stern, bins=None)
+title('$M_1$ vs. $M_2$',fontsize=24)
+xlabel('$M_1$',fontsize=18)
+ylabel('$M_2$',fontsize=18)
+cb = pyplot.colorbar()
+
+draw()
+show()

### 2013-04-13 SAcounter.py

@@ -1,0 +1,37 @@
+#!/opt/local/bin/python
+from math import *
+
+file = open('ranked_sky_pixels.dat')
+filedata = file.readlines()
+file.close()
+
+i = 0
+cum = float(filedata[1].split()[3]) 
+maxLra= float(filedata[1].split()[1])*0.26179938779
+maxLdec = float(filedata[1].split()[0])*0.01745329251
+
+while cum <= 0.6827: #one sigma
+	cum = float(filedata[i+2].split()[3]) 
+	i += 1
+
+
+radOut = i*(12.56637) / (len(filedata) - 1)
+degOut = i*(41252.96129655765) / (len(filedata) - 1)
+
+dPhi = sqrt(radOut/6.28318530718)
+
+dSigmaCircle = acos(sin(maxLdec)**2 + (cos(maxLdec)**2)*cos(dPhi))
+
+j = 1
+numInCircle = 1.
+cum = 0
+while cum <= 0.6827: #one sigma
+	cum = float(filedata[j+1].split()[3]) 
+	ra= float(filedata[j+1].split()[1])*0.26179938779
+	dec = float(filedata[j+1].split()[0])*0.01745329251
+	dSigma= acos(sin(maxLdec)*sin(dec) + cos(maxLdec)*cos(dec)*cos(maxLra - ra))
+	if dSigma < dSigmaCircle:
+		numInCircle += 1.
+	j += 1
+
+print maxLra, maxLdec, degOut, (numInCircle/i)*100 

### 2013-04-13 fullSkyPlot.py

@@ -1,0 +1,151 @@
+from mpl_toolkits.basemap import Basemap
+import scipy.ndimage as ndimage
+from matplotlib import pyplot as plt,cm as mpl_cm,lines as mpl_lines,colorbar
+
+np.seterr(under='ignore')
+
+myfig=plt.figure()
+plt.clf()
+m=Basemap(projection='moll',lon_0=0.0,lat_0=0.0)
+
+
+m.drawmapboundary()
+m.drawcoastlines(linewidth=0.5)
+m.drawparallels(np.arange(-90.,90.,45.),labels=[1,0,0,0],labelstyle='+/-')
+#m.fillcontinents(color='#cc9966',lake_color='#99ffff',alpha=0.7)
+# draw parallels
+m.drawmeridians(np.arange(0.,360.,90.),labels=[0,0,0,1],labelstyle='+/-')
+# draw meridians
+plt.title("Sky Location Uncertainty", fontsize=22) # add a title
+m.drawmapboundary()
+#colorbar.ColorbarBase.set_label(test,'$\log_{10}$($\Omega$)  $(deg)^2$', fontsize=15)
+
+ra = []
+dec= []
+sa = []
+deg= []
+for prefix in ['2.5_2.5']:
+#for prefix in ['1_1','1.4_1.4','1_2.5','2.5_2.5']:
+	for run in range(1,41):
+		filename = prefix + '/' + str(run) + '/post/ranked_sky_pixels.dat'
+		try: 
+			file = open(filename)
+		except IOError:
+			print "Warning, " + filename + " isn\' there"
+			continue
+		filedata = file.readlines()
+		file.close()
+
+		fileSummaryName = prefix + '/' + str(run) + '/post/summary_statistics.dat'
+		try: 
+			fileSummary = open(fileSummaryName)
+		except IOError:
+			print "Warning, " + filenameSummaryName + " isn\' there"
+			continue
+		fileSummaryData = fileSummary.readlines()
+		fileSummary.close()
+		gmst = float(fileSummaryData[31].split()[6])
+		gmst = np.mod(gmst/3600.,24.)
+		print gmst
+
+		i = 0
+		cum = float(filedata[1].split()[3]) 
+
+		while cum <= 0.95: #two sigma
+			cum = float(filedata[i+2].split()[3]) 
[…]

### 2013-04-13 massPDFs.py

@@ -1,0 +1,154 @@
+import scipy.stats
+from matplotlib import pyplot as plt,cm as mpl_cm,lines as mpl_lines,colorbar
+
+def m1m2fromMcq(Mc,q):
+
+	m1 = Mc*((1+q)/q**3)**0.2
+	m2 = Mc*(q**2 * (1+q))**0.2
+	if m1<m2:
+		m1,m2 = m2,m1
+
+	return m1, m2
+
+massBins = ['11','114','125','2525']
+chirpMasses = [0.870661, 1.218771, 1.348809, 2.176374]
+massRatios = [1,1,0.4,1]
+indivMasses = [(1.,1.),(1.4,1.4),(1.,2.5),(2.5,2.5)]
+Bin = 0
+colors=['black','blue','red','green']
+
+for number in massBins:
+		file = open('mc' + number + 'Meta.dat')
+		mcdata = file.readlines()
+		file.close()
+		file = open('q' + number +'Meta.dat')
+		qdata = file.readlines()
+		file.close()
+
+		q  = []
+		mc = []
+		m1 = []
+		m2 = []
+		M  = []
+		k = 0
+
+		for i in range(0,len(mcdata),50):
+			q.append(float(qdata[i].rstrip())*massRatios[Bin])
+			mc.append(float(mcdata[i].rstrip()))
+			m1Temp, m2Temp = m1m2fromMcq(mc[k]*chirpMasses[Bin],q[k])
+			m1.append(m1Temp / indivMasses[Bin][1])
+			m2.append(m2Temp / indivMasses[Bin][0])
+			M.append((m1Temp + m2Temp)/sum(indivMasses[Bin]))
+			k += 1
+
+		m1KDE = scipy.stats.gaussian_kde(m1)
+		m2KDE = scipy.stats.gaussian_kde(m2)
+		mcKDE = scipy.stats.gaussian_kde(mc)
+		mKDE  = scipy.stats.gaussian_kde(mc)
+		qKDE  = scipy.stats.gaussian_kde(q)
+
+		Xm1 = []
+		Ym1 = []
+		Xm2 = []
+		Ym2 = []
+		Xmc = []
+		Ymc = []
+		Xm  = []
+		Ym  = []
+		Xq  = []
+		Yq  = []
+
+		m1Min = min(m1)
+		m1Max = max(m1)
+		dx = (m1Max- m1Min) / 1000.
+		n = m1Min
[…]

### 2013-04-13 skyPlot.py

@@ -1,0 +1,59 @@
+from mpl_toolkits.basemap import Basemap
+from matplotlib import pyplot as plt,cm as mpl_cm,lines as mpl_lines,colorbar
+
+np.seterr(under='ignore')
+
+myfig=plt.figure()
+plt.clf()
+m=Basemap(projection='moll',lon_0=0.0,lat_0=0.0)
+
+file = open('SolidAngles_2.5_2.5.dat')
+filedata = file.readlines()
+file.close()
+
+ra = []
+dec= []
+sa = []
+per= []
+for i in range(1,len(filedata)):
+	ra.append(float(filedata[i].split()[0]))
+	dec.append(float(filedata[i].split()[1]))
+	sa.append(float(filedata[i].split()[2]))
+	per.append(float(filedata[i].split()[3])/100.)
+
+ra = np.array(ra)
+dec= np.array(dec)
+
+ra_reverse = 2*pi - ra*57.296
+
+plx,ply=m(
+          ra_reverse,
+          dec*57.296
+          )
+
+#m.contourf(plx,ply,data,cmap=mpl_cm.jet,alpha=0.8,tri=True)
+#ax = subplot(2,1,1)
+m.drawmapboundary()
+m.drawcoastlines(linewidth=0.5)
+m.drawparallels(np.arange(-90.,90.,45.),labels=[1,0,0,0],labelstyle='+/-')
+# draw parallels
+m.drawmeridians(np.arange(0.,360.,90.),labels=[0,0,0,1],labelstyle='+/-')
+m.scatter(plx,ply,s=60,c=log10(sa),alpha=0.8)
+# draw meridians
+plt.title("Sky Location Uncertainty", fontsize=22) # add a title
+test = m.colorbar(location='bottom')
+colorbar.ColorbarBase.set_label(test,'$\log_{10}$($\Omega$)  $(deg)^2$', fontsize=15)
+#ax = subplot(2,1,2)
+#m.drawmapboundary()
+#m.drawcoastlines(linewidth=0.5)
+#m.drawparallels(np.arange(-90.,90.,45.),labels=[1,0,0,0],labelstyle='+/-')
+# draw parallels
+#m.drawmeridians(np.arange(0.,360.,90.),labels=[0,0,0,1],labelstyle='+/-')
+#m.scatter(plx,ply,s=60,c=per,alpha=0.8)
+# draw meridians
+#plt.title("Circularity", fontsize=22) # add a title
[…]

### 2013-04-13 times.py

@@ -1,0 +1,25 @@
+from matplotlib import pyplot as plt,cm as mpl_cm,lines as mpl_lines,colorbar
+
+massBins = ["1_1","1.4_1.4","1_2.5","2.5_2.5"]
+names=["$1M_{\odot} - 1M_{\odot}$","$1.4M_{\odot} - 1.4M_{\odot}$","$1M_{\odot} - 2.5M_{\odot}$","$2.5M_{\odot} - 2.5M_{\odot}$"]
+times = [[] for i in range(4)]
+i = 0
+
+for mass in massBins:
+	file = open(mass + '-times.dat')
+	filedata = file.readlines()
+	for j in range(len(filedata)):
+		hrs,mins,secs = filedata[j].split(":")
+		times[i].append(float(hrs) + float(mins)/60. + float(secs)/3600.)
+	file.close()
+	i += 1
+
+ax = subplot(111)
+ax.set_xlabel('Hours')
+ax.set_ylabel('Number')
+for i in range(4):
+		ax1 = subplot(2,2,i+1)
+		ax1.hist(times[i])
+		title(names[i], fontsize = 18)
+
+show()

### 2013-05-14 doc/paper.tex
rough draft

@@
 %\IfFileExists{revtex4.cls}{\documentclass[prd, twocolumn, lengthcheck, superscriptaddress, showpacs, letterpaper]{revtex4}}{}}
-\documentclass{emulateapj}
+\documentclass[11pt,a4paper]{emulateapj}
+\bibliographystyle{apj}
+
+\usepackage{epsfig}
+%\usepackage{amsmath}
+\usepackage{natbib}
 
@@
 \usepackage{acronym}
+\usepackage{comment}
 \usepackage{multirow}
@@
 \title{Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/VIRGO Network}
-\author{Carl L. Rodriguez}
-\email{carlrodriguez2015@u.northwestern.edu}
-\affiliation{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) \& Dept.~of Physics and Astronomy, Northwestern University, 2145 Sheridan Rd, Evanston, IL 60208, USA}
+\author{Carl L. Rodriguez \altaffilmark{1}
+%\email{rodriguez@u.northwestern.edu}
+,Benjamin Farr \altaffilmark{1}
+%\email{bfarr@u.northwestern.edu} 
+Vivien Raymond \altaffilmark{1,2}
+Will M. Farr \altaffilmark{1}
+%\email{w-farr@northwestern.edu} 
+Tyson Littenberg\altaffilmark{1}
+%\email{tyson.littenberg@northwestern.edu}
+Diego Fazi\altaffilmark{1}
+%\email{d-fazi@northwestern.edu}
+Vicky Kalogera\altaffilmark{1}}
+%\email{vicky@northwestern.edu}
+
+\altaffiltext{1}{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) \& Dept.~of Physics and Astronomy, Northwestern University, 2145 Sheridan Rd, Evanston, IL 60208, USA; [e-mail: {\tt cr@u.northwestern.edu}]}
+\altaffiltext{2}{California Institute of Technology, Pasadena, CA 92215, USA}
 
 \begin{abstract}
+
+Within the next 5 years, the Advanced LIGO/VIRGO network will have reached a sensitivity sufficient to enable the routine detection of gravitational waves.
+Beyond the initial detection, the scientific promise of these instruments relies on the efficiency of the parameter estimation techniques being currently developed.
+The majority of this effort has been towards the detection and characterization of gravitational waves from compact binary coalescence, i.e.
+the coalescence of black holes and/or neutron stars.
+While several previous studies have focused on the parameter estimation abilities of advanced detectors, the vast majority have relied on approximation techniques (such as the Fisher Matrix) when characterizing the uncertainties.
+Here, we report the statistical uncertainties that will be achievable, in practice, using the parameter estimation code \texttt{LALInference} to recover the parameters of binary neutron star systems detected in various configurations of the Advanced LIGO/VIRGO network.
+We find that the recovery of the individual masses will be, on average, sufficient to differentiate neutron stars from black holes by the masses alone.
+We also report the average uncertainties on the sky-locations, luminosity distance, and orbital inclinations of randomly generated sources that can be recovered by the expected three and four-detector networks.
 \end{abstract}
@@
 
- By 2016 (\carl{?}), the field of gravitational-wave astrophysics will mature from a speculative scientific genre into an ideal tool for exploring the gravitational side of the universe.
- Within the next few years, the first generation of gravitational-wave detectors capable of regularly resolving astrophysical sources will come online \carl{cite}.
-The Advanced LIGO and VIRGO detectors will provide  the first insights into the final moment of binary compact object mergers, including the merger of binary neutron star systems.
-Intense preparations are currently underway to prepare to characterize and extract as much physical information as possible from these signals.
+ By 2016, the field of gravitational-wave astrophysics will
+ mature from a speculative scientific genre into an ideal tool for 
+ exploring the gravitational side of the universe. Within the next few
+ years, the first generation of gravitational-wave detectors capable 
+ of regularly resolving astrophysical sources will come online \carl{[CITE]}.
+ The Advanced LIGO and VIRGO detectors will provide the first insights
+ into the final moment of binary compact object mergers, including the 
+ merger of binary neutron star systems.  Intense preparations are currently
+ underway to prepare to characterize and extract as much physical 
+ information as possible from these signals.
 
-The mergers of binary neutron stars are expected to be the most ubiquitous source in the advanced detector era \carl{cite}.
-Models from stellar evolution suggest that the number of binary neutron star mergers within Advanced LIGO/VIRGO's detection horizon could reach into the hundreds per year \carl{cite}.
-Although the peak sensitivity of ground-based detectors is not focused on the frequency at which BNS systems merge, it should still be possible to extract information about both strong field gravitational physics \carl{cite} and the hydrodynamics of dense matter (e.g.
-the equation of state of nuclear matter) \carl{cite}.
-As such, BNS systems will likely form the ``bread and butter'' of the compact object efforts in the coming years \carl{the high-mass folks might not like this, but fuck 'em}.
+The mergers of binary neutron stars are expected to be the most ubiquitous
+source in the advanced detector era \carl{[CITE]}.   Models from stellar 
+evolution suggest that the number of binary neutron star mergers within 
+Advanced LIGO/VIRGO's detection horizon could reach into the hundreds per 
+year \carl{[CITE]}.  Although the peak sensitivity of ground-based detectors
+is not focused on the frequency at which BNS systems merge, it should still
+be possible to extract information about both strong field gravitational 
+physics \carl{[CITE]} and the hydrodynamics of dense matter (e.g. the equation 
+of state of nuclear matter) \carl{[CITE]}.  Furthermore, the observations of multiple BNS
+systems will provide key insight into the evolution of binary systems in the field \carl{[CITE]},
+and in globular clusters \carl{[CITE]}. As such, BNS systems will likely 
+form the ``bread and butter'' of the compact object efforts in the coming 
+years.
 
-Of course, in this context, one must distinguish between the detection of such events, and the precision measurement of the relevant physical parameters.
-There are two separate issues to consider in this context: the detection of BNS systems will be performed with a matched filtering approach, which allows one to search the time domain data at a sufficiently fast rate \carl{[yeah that phrasing sucks]} by comparing the data stream to a bank of theoretical templates.
-When the overlap between one of the template waveforms and the detector output is sufficiently large (97\%), a detection is claimed.
-However, the parameter space of our signals can be highly degenerate, with several locations in parameter space corresponding to near identical waveforms.
-In order to fully realize the science potential of these instruments, we must perform a full exploration of the parameter space for each detection.
-By analyzing each candidate's parameter space with fully Bayesian techniques and proper sampling, we will be able to make precise, scientifically meaningful statements about the composition and formation of these objections.
-To this end, we employ a Markov-Chain Monte Carlo sampling algorithm, included in the LIGO Application Library parameter estimation code, \texttt{LALInferenceMCMC}.
+Of course one must distinguish between the detection of 
+such events, and the precision measurement of the relevant physical parameters.
+The detection of BNS systems will be performed with a matched filtering approach.  
+By comparing the data stream to a bank of theoretical templates, the roughly 16KHz
+ time-series data can be searched for candidate signals at a sufficiently
+  rapid rate to analyze months of data.  When the overlap between one of the template waveforms and the 
+detector output is sufficiently large (97\%), a detection is claimed.  However,
+the parameter space of these signals can be highly degenerate, with several 
+locations in parameter space corresponding to near identical waveforms.  In 
+order to fully realize the science potential of these instruments, we must 
+perform a full exploration of the parameter space for each detection.  By 
+analyzing the parameter space of each candidate with a Bayesian inference technique 
+and proper sampling, we will be able to make precise, scientifically meaningful
+statements about the physics of these detectible systemss.  To 
+that end, we employ a Markov-Chain Monte Carlo sampling algorithm, 
+\texttt{lalinference\_mcmc}, included in the LIGO Application Library parameter
+estimation code, \texttt{LALInference}.
 
-By employing the full parameter estimation machinery that will eventually be used in the Advanced Detector era, our results give the first estimate at the realistic capabilities of Advanced ground-based detectors.
-Until recently, the majority of studies have employed the Fisher matrix formalism as it was first adapted for gravitational-wave parameter estimation by \cite{FinnDetection}.
-While each of these studies (\cite{PoissonWill,CutlerFlanagan,ArunPE}, among many others) have done their due diligence in pointing out the limitations and flaws of the Fisher Information Matrix, there has been no study which states the BNS parameter estimation capabilities of Advanced LIGO/VIRGO via the techniques that will eventually be employed.
-The recent work of \cite{Vallisneri} and our own work \citep{Inadequacies} has demonstrated that the Fisher matrix cannot even be treated as a lower bound on the standard deviations about certain parameters (particularly the masses) measurable in advanced detectors.
+By employing the full parameter-estimation machinery that will eventually be
+used in the Advanced LIGO/VIRGO era, our results give the first estimate at the 
+realistic capabilities of advanced ground-based detectors to characterize BNS systems.
+  Until recently, the majority of studies have employed the Fisher matrix formalism which was 
+first adapted for gravitational-wave parameter estimation by \citep{FinnDetection}.
+While each of these studies (\cite{PoissonWill,CutlerFlanagan,ArunPE}, among 
+many others) have done their due diligence in pointing out the limitations 
+and flaws of the Fisher Information Matrix, there has been no study which states
+the BNS parameter estimation capabilities of Advanced LIGO/VIRGO via the techniques
+that will eventually be employed.  The recent work of \cite{Vallisneri} and our 
+own work \citep{Inadequacies} has demonstrated that the Fisher matrix cannot even
+be treated as a lower bound on the standard deviations about certain parameters
+(particularly the masses) measurable in gravitational-wave detectors.
 
-In this paper, we perform a systematic study of the statistical uncertainty with which the Advanced LIGO network will be able to measure the basic parameters of binary neutron stars.
-In section \ref{BNSsection}, we review some of the basic physics of gravitational waves from binary neutron stars, including the potential science case to be made with Advanced LIGO.
-In section \ref{PEsection}, we describe the machinery of our parameter estimation code, \texttt{LALInferenceMCMC}, as well as the gravitational-wave template used for signal extraction.
-In section \ref{ResultsSection}, we
-
-\begin{itemize}
- \item BNS source
-\item PE vs detection
-\item Why not FIM
-\item Overview
-\end{itemize}
-
-\section{BNS systems}
-\label{BNSsection}
-\begin{itemize}
-\item expected rates
-\item interesting physics
-\item Expected parameters (non spinning, SNR distribution, etc)
-\item waveform issues
-\end{itemize}
+In this paper, we perform a systematic study of the statistical uncertainties with
+which the Advanced LIGO/VIRGO network will be able to measure the basic parameters of 
+binary neutron stars.  In Section \ref{PEsection}, we describe
+the machinery of our parameter estimation code, \texttt{LALInference}, and the associated
+MCMC sampler, \texttt{lalinference\_mcmc}, as well as the frequency-domain gravitational-wave template we employ.   
+In Section \ref{resultsSection}, we qualitatively analyze the posterior probability density functions for BNS systems with different masses and extrinsic parameters.
+The results are divided into three parameter sets of interest: the recovery of the mass parameters (Section \ref{massSection}), the recovery of the orbital inclination and luminosity distance (Section \ref{idSection}), and the isolation of sources in the sky (Section \ref{skySection}).
+Finally we provide quantitative 1-dimensional confidence intervals on the parameter recovery in Section \ref{ciSection}.
+We assume that $G=c=1$ throughout.
 
@@
 \label{PEsection}
-
-\begin{itemize}
-\item parameter estimation setup
-\item MCMC
-\item Waveform model
-\end{itemize}
-\label{peSection}
 
@@
 \end{equation}
-Since our noise is assumed to be Gaussian, we can write the
+Since our noise model is Gaussian, we can write the
 probability of a specific signal realization $s$ as the probability
@@
 where $\boldsymbol{\theta}$ is the set of parameters for our template
-waveforms.The inner product, $\left< ~|~ \right> $, is defined using the noise
+waveforms.  The inner product, $\left< ~|~ \right> $, is defined using the noise
 spectrum of the detectors as
@@
 pick a set of parameters $\boldsymbol{\theta}$ such that
-$h(\boldsymbol{\theta}) = h_0$, then our posterior \eqref{posterior}
+$h(\boldsymbol{\theta}) = h_0$, then the posterior \eqref{posterior}
 will be near a global maximum; however, the presence of noise will in
@@
 no guarantee that the maximum-likelihood of our signal corresponds to
-the true parameters of the system.  Hence our use of the term
-``best-fit parameters'' (\citep{CutlerFlanagan}), particularly when
-discussing the point in parameter space where the FIM is evaluated.
-The goal of parameter estimation is to sample the available parameter
-space, considering all areas of posterior support, to determine best
-estimates on the parameters of the signal and their uncertainties.  We
-will discuss one such sampling technique, Markov-Chain Monte Carlo, in
-\ref{MCMCSection}.
+the true parameters of the system.
 
-\subsection{Parameter estimation via Markov-Chain Monte Carlo}
+\subsection{Markov-Chain Monte Carlo}
 \label{MCMCSection}
 
-Our parameter estimation code, \texttt{LALInferenceMCMC}, is an
-enhancement of the previously described MCMC parameter estimation code
-\texttt{SpinSpiral} \citep{spinspiral2009, spinspiral2010}.  The basic
-description of the Markov-Chain Monte Carlo via the
-Metropolis-Hastings algorithm is as follows \citep{Gilks99}:
+The LIGO Algorithm Library parameter estimation code, \texttt{LALInference}, is designed as 
+a unified framework for gravitational-wave parameter estimation.  By using a common setup for 
+waveform generation, PSD estimation, data handling, and other associated techniques from gravitational-wave parameter estimation, \texttt{LALInference} allows the implementation of multiple parameter samplers in using identical parameter setups, including nested sampling (\texttt{lalinference\_nest}) and Markov-Chain Monte Carlo (\texttt{lalinference\_mcmc}).
+We elect to use the MCMC sampler for this study.
+\texttt{lalinference\_mcmc} is based upon the previously described code,
+\texttt{SpinSpiral} \citep{spinspiral2009, spinspiral2010}.  The MCMC employs a Metropolis-Hastings sampling algorithm, which can be described as follows \citep{Gilks99}:
 
@@
 The details of the algorithm can be found in
-\citep{Sluys08,spinspiral2009, spinspiral2010}.
+\citep{Sluys08,spinspiral2009, spinspiral2010}.  Both samplers were tuned and 
+developed during the last science run of the Initial LIGO/VIRGO network.  
+A description of the parameter estimation capabilities, c.f. 2010, can be found
+in \cite{S6PE}.
 
@@
 form of our waveform model, known as the \textit{TaylorF2}
-approximant, is calculated via the stationary phase approximation \citep{BuonannoWaveform}.
+approximant, is calculated via the stationary-phase approximation.
   In this setup, the gravitational-wave
@@
 inclination, and the wave polarization.  In addition to the total
-mass, $M\equiv m_1+m_2$, it is convenient to work with the
-\textit{symmetric mass ratio} and \textit{chirp mass}, defined by
+mass, $M\equiv M_1+M_2$, it is convenient to work with the
+\textit{mass ratio} and \textit{chirp mass}, defined by
 \begin{equation}
-  \eta\equiv m_1m_2/M^2~~~~\text{and}~~~~\mathcal{M}_c = \eta^{3/5}M,
+  q\equiv M_1/M_2~~~~\text{and}~~~~\mathcal{M}_c = (M_1 M_2)^{3/5} M^{-1/5},
 \end{equation}
-respectively.  Then, in terms of the Newtonian orbital velocity
-$v=(\pi M f)^{1/3}$, the 2pN phase is
+respectively.\footnote{Most gravitational-wave literature instead use the \textit{symmetric mass ratio}, defined as $\eta \equiv M_1 M_2 / M^2$.
+We elect to use $q$ as it is empirically superior when proposing MCMC parameter jumps, and is more physically intuitive.}  The stationary phase then becomes an expansion in the
+Newtonian orbital velocity, $v=(\pi M f)^{1/3}$, 
 \begin{equation}
-\psi(f) = 2 \pi f t_c - \phi_0 + \frac{\pi}{4} + \frac{3}{128 \eta}v^{-5}\sum^{4}_{k=0}\alpha_{k}v^k
+\psi(f) = 2 \pi f t_c - \phi_0 + \frac{\pi}{4} + \frac{3}{128}\left(\frac{M}{\mathcal{M}_c}\right)^{5/3}\sum^{n}_{k=0}\alpha_{k}v^{k-5}
 \label{phase}
 \end{equation}
-with coefficients
-\begin{align}
-\alpha_0 &= 1\\
-\alpha_1 &= 0 \nonumber\\
-\alpha_2 &= \frac{20}{9}\left(\frac{743}{336}+\frac{11}{4}\eta\right)\nonumber\\
-\alpha_3 &= -16\pi \nonumber\\
-\alpha_4 &= 10\left(\frac{3058673}{1016064}+\frac{5249}{1008}\eta+\frac{617}{144}\eta^2  \right) . \nonumber\\
-\alpha_5 &= \pi\left(\frac{38645}{756}-\frac{65}{9}\eta\right)\left(1+3\log\left(\frac{v}{v_{\text{ISCO}}}\right)\right)\nonumber\\
-\alpha_6 &= \frac{11583231236531}{4694215680} - \frac{640}{3}\pi^2 - \frac{6848}{21}\gamma_{\text{euler}} \nonumber\\
-         &~~- \frac{6848}{21} \log\left(4 \frac{v}{v_{\text{ISCO}}}\right) -\left(\frac{15737765635}{3048192}-\frac{2255}{12}\pi^2\right)\eta\nonumber\\
-           &~~+ \frac{76055}{1728}\eta^2 - \frac{127825}{1296}\eta^3\nonumber\\
-\alpha_7 &= \pi\left(\frac{77096675}{254016}+\frac{1014115}{3024}\eta - \frac{36865}{368}\eta^2\right)\nonumber
-\end{align}
+
+\noindent where the $\alpha_{k}$ coefficients are taken from the pN expansion to order $n/2$.  See \cite{BuonannoWaveform} for a description and comparison of different waveform families.
+
 The terms $t_c$ and $\phi_0$ in equation (\ref{phase}) are constants
@@
 
-To perform the integral defined in \eqref{innerProduct}, we used an
-analytic noise curve for the Initial LIGO configuration, provided in
-\citet{DarmourNoiseCurve}, which takes the form:
-\begin{align}
- S_h(f)=&S_0\Big[ \left(\frac{4.49 f}{f_0} \right)^{-56} + \nonumber\\
- &\left(\frac{0.16f}{f_0}\right) ^{-4.52}+0.52+0.32\left( \frac{f}{f_0}\right) ^2\Big],
- \label{PSD}
-\end{align}
-where $f_0 = 150~\text{Hz}$, and $S_0 = 9\times
-10^{-46}\text{Hz}^{-1}$.  We consider the complete initial detector
-network consisting of the two LIGO sites (in Hanford, WA and
-Livingston, LA) and the Virgo site (in Pisa), although for simplicity
-we use the Initial LIGO sensitivity for all three detectors.  For a
-multi-detector network, the noise-weighted inner products
+To perform the integral defined in \eqref{innerProduct}, we used the best estimate
+for a high-power, zero-detuning configuration of Advanced LIGO, provided by the LIGO Scientific Collaboration.
+Both the noise curve and technical reports describing it can be found in \cite{ADVLIGONoise}.
+We consider two configurations of the advanced detector
+network: a three-detector configuation consistanting of the two LIGO sites 
+(in Hanford, WA and Livingston, LA) and the Virgo site (in Pisa), and a four-detector
+configuration with adds the proposed LIGO-India detector (in Chitradurga, KA).
+For simplicity, we assume each detector to be operating at the Advanced LIGO sensitivity. 
+For a multi-detector network, the noise-weighted inner products
 \eqref{innerProduct} combine linearly, allowing us to use the above
 formalism with minimal modification.  We integrate the inner product
-from a lower frequency cutoff of $40\text{Hz}$ to the
-innermost-stable-circular orbit of the system in question, which for a
-non-spinning binary is given by
+from a lower-frequency cutoff of $20\text{Hz}$ to the
+innermost-stable-circular orbit of the systems in question, which for a
+non-spinning binary is a function only of the total mass:
+
 \begin{equation}
@@
 
-In addition to the intrinsic parameters listed above ($\mathcal{M}_c,
-\eta, \phi_0,t_c$), we include an additional 5 extrinsic parameters in
-our parameter estimation, in order to explore how a full parameter
-estimation study on real data, including parameters such as sky
-location, will compare to their FIM counterparts.  This leads to our
-9-dimensional parameter space for non-spinning systems:
+We consier the mass parameters ($\mathcal{M}_c,q$) and the phasing parameters,
+($\phi_0,t_c$), to be the intrinsic parameters of a gravitational-wave signal.  There 
+are an additional 5 extrinsic parameters, independent of the pN orbital phase, which can
+modulate the amplitude of the signal in an independent fashion for each detector.  
+Combining these leads to our 9-dimensional parameter space for non-spinning systems:
 \begin{equation}
-\boldsymbol{\theta} =  (\mathcal{M}_c, \eta, \phi_0,t_c,D,\iota,\psi,\alpha,\delta)
+\boldsymbol{\theta} =  (\mathcal{M}_c, q, \phi_0,t_c,D,\iota,\psi,\alpha,\delta)
 \label{parameterspace}
 \end{equation}
-where $D$ is the luminosity distance to the binary, $\iota$ is the
-orbital inclination, $\psi$ the gravitational-wave polarization, and
-$\alpha$ and $\delta$ the right ascension and declination of the
+where to summarize
+
+\begin{itemize}
+\item $\mathcal{M}_c$ is the chirp mass,
+\item $q$ is the mass ratio,
+\item $\phi_0$ and $t_c$ are the chirp phase and chirp time, arbitrary phasing parameters,
+\item $D$ is the luminosity distance to the binary,
+\item $\iota$ is the orbital inclination, 
+\item $\psi$ the gravitational-wave polarization, and
+\item $\alpha$ and $\delta$ the right ascension and declination of the
 source on the sky.
+\end{itemize}
+  Since the wave amplitude depends on the orientation of the
+binary with respect to each detector, most of the information about these extrinsic
+parameters comes from two sources: the time-of-arrival triangulation of 
+the source locations, and the relative amplitudes within the detector network.
 
-Note that the signal-to-noise ratio (SNR) of a gravitational wave in a
+We define the signal-to-noise ratio (SNR) of a gravitational wave in a
 single detector is
@@
 where $\rho$ is the SNR and $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
-the frequency-domain signal and template, respectively.  The SNRs for
-multiple detectors add in quadrature.  The normalization $\sigma$ is
+the frequency-domain signal and template, respectively, and the normalization $\sigma$ is
 given by
@@
 \end{equation}
-For our MCMC analysis, we compute the SNR directly using
-\eqref{formalSNR}.  In the case of the FIM, we approximate the SNR
-using $\sigma$ from equation (\ref{SNRnorm}) for a network of
-detectors as
+
+When dealing with network of gravitational-wave detectors, the SNRs of the individual detectors add in quadrature.  That is, the network SNR for a detection is
+
 \begin{equation}
-\rho = \sqrt{\sum_i \sigma_i^2}
-\label{snr}
+\rho_{\text{network}} = \sqrt{\sum_i \rho_{i}}
+\label{SNRnetwork}
 \end{equation}
-where the index $i$ refers to the signal and noise spectrum of the
-$i^{\text{th}}$ detector.  It should be noted that equation
-\eqref{snr} is only valid in case of stationary Gaussian noise.
 
-\begin{figure*}[h]
-\begin{center}
-\includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.57]{9dpdf.pdf}
+\noindent where $\rho_i$ is the SNR, given by \eqref{formalSNR}, of the $i^{\text{th}}$ detector.
+
+For this study, we consider four seperate populations of BNS systems, with component mass 
+combinations of $1M_{\odot}/1M_{\odot}$, $1.4M_{\odot}/1.4M_{\odot}$, $1M_{\odot}/2.5M_{\odot}$, 
+and $2.5M_{\odot}/2.5M_{\odot}$.  Each population consisted of 40 signals distributed randomly
+in sky location, polarization, inclination, time-of-arrival, and coalescence phase.  The luminosity 
+distance, $D$, was selected to provide a network SNR of $\rho_{\text{network}}=20$ for each source.
+While unphysical from an astrophysical perspective (binary sources should be 
+distributed evenly in comoving volume), this choice allows us to explore the parameter estimation
+in the context of viable detection candidates.
+
+Finally, note that the power-spectral density that defines the inner product \eqref{innerProduct} is simply 
+the time-averaged sensitivity of a given detector to a specific frequency.  Ignoring non-Gaussian glitches,
+ any stretch of data should contain a specific noise realization drawn from a Gaussian colored by the PSD.
+   However, what we are interested in is not the parameter estimation that can occur in a specific draw
+    from this probability of noises, but the uncertainties averaged over all possible noise realizations.
+    \footnote{Similarly to how the Fisher matrix formalism can provide the Cramer-Rao bound averaged over
+     all noise realizations} Since our noise model is assumed to be Gaussian, it is unnecessary to recover the
+      parameters from a large sample of identical waveforms in different noise; we can simply assume the 
+      noise \emph{is} the mean defined by the power-spectral density.  This ``zero-noise'' parameter estimation
+       provides a statical statement on the measurable uncertainties, and is what is reported here.  In Section
+        \ref{noiseSection} we provide an example of parameter estimation in several non-zero noise realizations
+compared to the zero-noise equivelant.
+
+\section{Results}
+\label{resultsSection}
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[trim=7cm 0cm 0cm 0cm, clip=true,scale=0.55]{9dpdf.pdf}
 %\begin{array}{ccc} 
@@
 %\end{array}$
-\end{center}
-\caption{Marginalized 1D posterior probability density functions taken from a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS system.
-We have plotted each of the 9 parameters for our non-spinning BNS problem as stated in section \ref{waveformSection}.
-Note how, even for parameters with excellent recovery, the peak of the 1D Gaussian is displaced from the injected value (in dashed red).
-This is not due to a systematic bias, but is caused by the marginalization of a single dimmension from the full 9D posterior space.}
+\caption{Marginalized 1D posterior probability density functions taken from a typical 
+$1.4M_{\odot}/1.4M_{\odot}$ BNS system.  We have plotted each of the 9 parameters for 
+our non-spinning BNS problem as stated in section \ref{waveformSection}.  Note how, 
+even for parameters with excellent recovery, the peak of the 1D Gaussian is displaced from 
+the injected value (in dashed red).  This is not due to a systematic bias, but is caused by the 
+marginalization of a single dimension from the full 9D posterior space.  To better see this effect, 
+compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in Figure~\label{9dPDF}}
 \end{figure*}
 
-\begin{figure*}[h!]
+Of the 9 parameters in the domain of the waveform, only 6 are particularly physically
+interesting: the masses of the two binaries, $M_1$ and $M_2$, the orbital inclination,
+$\iota$, the angular position on the sky, $\alpha$ and $\delta$, and the luminosity 
+distance of the source, $D$.  While the coalescence phase $\phi_c$, the coalescence time
+$t_c$, and the wave polarization $\psi$ must be included in any parameter estimation of the 
+waveform, they do not encode any information of particular astrophysical interest.
+\footnote{For systems whose components are non-spinning.  The presence of intrinsic angular 
+momentum will, in general, couple to the coalescence phase and wave polarization.}
+
+In Figure~\ref{9dPDF}, we provide an example of the 9, 1-dimensional marginalized posterior 
+probability density functions recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system. 
+ These PDFs are typical of what will be produced by parameter estimation studies in the advanced 
+ detector era.  Notice that the peak of several parameters, including the chirp mass, $\mathcal{M}_c$, 
+ appears to be displaced from the true values in red.  This effect is due to the reduction of the
+  9-dimensional PDF to a series of marginalized 1-dimensional PDFs.  For instance, the 1-dimensional 
+  PDF for chirp mass is marginalized via
+
+\begin{equation}
+p(\mathcal{M}_c | s) = \int _{\boldsymbol{\theta} \setminus \mathcal{M}_c} p(\boldsymbol{\theta} | s)~d(\boldsymbol{\theta} \setminus \mathcal{M}_c)
+\label{mcMarginalization}
+\end{equation}
+
+\noindent Other parameter and higher-dimensional marginalizations follow a similar convention.
+
+\subsection{Mass Parameters}
+\label{massSection}
+
+\begin{figure}[h!]
   \centering
- \includegraphics[trim=2cm 0cm 2cm 0cm, clip=true,scale=0.63]{1414masses2D.pdf}
+ \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{1414masses2D.pdf}
+ \caption{2D marginalized posterior probability density functions for the mass parameters recovered in typical a $1.4M_{\odot}/1.4M_{\odot}$ system.
+The posteriors are plotted in terms of parameters used in the waveform, chirp mass ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual component masses of the binary ($M_1$ and $M_2$).
+In the $\mathcal{M}_c$-$q$ space, the posterior would resemble a Gaussian if not for the limitation of $q \leq 1$.
+The presence of the $q$ cutoff and the convention that $M_1 \geq M_2$ inform the non-Gaussian features present.
+When projected as 1D marginalized posteriors, the component masses resemble the posterior PDFs shown in figure \ref{metaMassPDFs}.}
   \label{1414masses}
- \caption{2D marginalized posterior probability density functions for the mass parameters recovered in typical a $1.4M_{\odot}/1.4M_{\odot}$ system.
-The posteriors are plotted in terms of parameters used in the waveform, chirp mass ($\mathcal{M}_C$) and the reduced mass ratio ($\eta$), and in the individual component masses of the binary ($M_1$ and $M_2$).
-In the $\mathcal{M}_c$-$\eta$ space, the posterior would resemble a Gaussian if not for the limitation of $\eta \leq 0.25$.
-The presence of the $\eta$ cutoff and the convention that $M_1 \geq M_2$ inform the non-Gaussian features present.
-When projected as 1D marginalized posteriors, the component masses resemble the posterior PDFs shown in figure \ref{masses}.}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+ \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{125masses2D.pdf}
+ \caption{Similar to Figure~\ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.
+The unequal mass ratio displaces the posterior PDFs from the $q \leq 1$ present in the equal mass case, yielding a Gaussian PDF in both the $\mathcal{M}_c$-$q$ and $M_1$-$M_2$ spaces.}
+  \label{125masses}
+\end{figure}
+
+\begin{figure*}[ht!]
+  \centering
+ \includegraphics[trim=2cm 0cm 2cm 0cm, clip=false,scale=0.7]{newMasses.pdf}
+ \caption{Mass PDFs for the four BNS systems, averaged over each of the 40 injections.
+The average is reported since, in practice, there was virtually no difference between the recovered PDFs for different systems with identical masses and SNRs \carl{[QUANTIFY]}.
+Notice how the PDFs for systems with identical mass ratios but different total masses are identical when normalized to the true total mass.}
+  \label{metaMassPDFs}
 \end{figure*}
 
-\begin{figure*}[h!]
-  \centering
- \includegraphics[trim=2cm 0cm 2cm 0cm, clip=true,scale=0.63]{125masses2D.pdf}
- \label{125masses}
- \caption{Similar to figure \ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.
-The unequal mass ratio displaces the posterior PDFs from the $\eta \leq 0.25$ present in the equal mass case, yielding a Gaussian PDF in both the $\mathcal{M}_c$-$\eta$ and $M_1$-$M_2$ spaces.}
-\end{figure*}
+Of the 9 variables in our parameter space \eqref{parameterspace}, the two of immediate physical
+interest are the two parameters, $\mathcal{M}_c$ and $q$, or correspondingly the direct masses 
+of the two companions, $M_1$ and $M_2$.    As stated above, the ability of
+Advanced LIGO/VIRGO to construct a population of BNS masses will be critical to the science
+potential of gravitational-wave astronomy.
 
-\begin{figure*}[h!]
-  \centering
- \includegraphics[trim=2cm 0cm 2cm 0cm, clip=true,scale=0.67]{newMasses.pdf}
- \label{masses}
- \caption{Typical 2D mass PDFs for the }
-\end{figure*}
-
-%\begin{figure*}[h]
-%\begin{center}$
-%\begin{array}{cc} 
-%\includegraphics[width=3.2in]{skyPos/2.png} &\includegraphics[width=3.2in]{skyPos/4.png}  \\
-%\includegraphics[width=3.2in]{skyPos/5.png} & \includegraphics[width=3.2in]{skyPos/7.png} 
-%\end{array}$
-%\end{center}
-%\caption{Example SkyPlots}
-%\end{figure*}
-
-\begin{figure*}[tp!]
-  \centering
- \includegraphics[angle=0,scale=0.49, trim=5cm 0cm 3cm 0cm]{skyLoc.pdf}
- \caption{The uncertainty on the sky of the 160 BNS systems.
-Each region represents a single injection, with the colored central region representing the 65\% \carl{[CHECK THAT]} uncertainty region on the sphere, and the gray region representing the 90\% uncertainty region.
-The color scheme indicates the total solid angle size of the 65\% region.
-Note the similar shape of the uncertainty regions at particular points; this is due to the specific realization of our network pattern sensitivity.}
- \label{2525SkyLoc}
-\end{figure*}
-
-\begin{figure*}[h!]
-  \centering
- \includegraphics[trim=2cm 0cm 2cm 0cm, clip=true,scale=0.575]{distIota2D.pdf}
- \label{masses}
- \caption{Typical 2D mass PDFs for the }
-\end{figure*}
-
-\begin{table*}[t!]
-\caption{}
-\begin{tabular}{lcccccccccccc}
-
-\hline\hline
-System & \vline &  $\Delta \mathcal{M}_c / \mathcal{M}_c$ & \vline & $\Delta \eta$ & \vline & $\Delta M_1/ M_1$ & \vline & $\Delta M_2 / M_2$ & \vline & $\Delta \phi_c$ & \vline &  $\Delta t_c$ (ms)\\
-\hline\hline
-$1M_{\odot}-1M_{\odot}$ & \vline & & \vline & & \vline & & \vline & & \vline & & \vline &\\
-\hline
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline & & \vline & & \vline & & \vline & & \vline & & \vline &\\
-\hline
-$1M_{\odot}-2.5M_{\odot}$ & \vline & & \vline & & \vline & & \vline & & \vline & & \vline &\\
-\hline
-$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.29 \times 10^{-4}$ & \vline & $1.34 \times 10^{-3}$ & \vline & $ 4.01 \times 10^{-2}$ & \vline & $3.65\times 10^{-2}$ & \vline & 1.807 & \vline & 0.418 \\
-\hline\hline
-
-\end{tabular}
-\label{biasedUnbiasedChirpMassErrors}
-\end{table*}
-
-\section{Results}
-\label{resultsSection}
-
-Of the 9 parameters in the domain of the waveform, only 6 are particularly physically interesting: the masses of the two binaries, $M_1$ and $M_2$, the inclination of the binary with respect to the observer, $\iota$, the angular position on the sky, $\alpha$ and $\delta$, and the distance of the source, $D$.
-
-\subsection{Mass Parameters}
-
-Of the 9 variables in our parameter space \eqref{parameterspace}, the two of immediate physical interest are the two parameters, $\mathcal{M}_c$ and $\eta$, or correspondingly the direct masses of the two companions, $M_1$ and $M_2$.
-As stated in section \ref{BNSsection}, the ability of Advanced LIGO/VIRGO to construct a population of BNS masses will be critical to the science potential of gravitational-wave astronomy.
-
-We find that there is virtually no difference between the mass PDFs of our different injected signals within each mass bin.
-At first, this may seem disconcerting; however, it is to be expected.
-Recall that of the BNS signals were injected with a network SNR of $\rho = 20$ into a zero-noise detector realization.
+We find that there is virtually no difference between the mass PDFs of our different injected signals
+within each mass bin.
+While this may initially seem disconcerting, it is to be expected.
+Recall that of the BNS signals were injected with a network SNR of 20 into a zero-noise detector realization.
 Furthermore, note that the mass parameters are the only two which directly effect the phase of the TaylorF2 waveform \eqref{phase}.
-Therefore, as long as the injected mass parameters are identical within each mass system (they are), and as long as the injected SNR is identical (it is), the amount of recoverable information in each mass parameter should be \emph{almost} identical, and for a sufficiently converged MCMC chain, the recovered posterior PDF should be \emph{almost} identical.
+Therefore, as long as the injected mass parameters are identical within each mass system, and as long as the injected SNR is identical, the amount of recoverable information in each mass parameter should be \emph{almost} identical, and for a sufficiently converged MCMC chain, the recovered posterior PDF should be \emph{almost} identical.
 
@@
 Obviously many of the other parameters (i.e.
-sky location, polarization, distance, inclination, and time-of-arrival) all depend on the orientation of the binary inspiral with respect to each of the individual detector locations.
+sky location, polarization, distance, inclination, and time-of-arrival) all depend on the orientation of the binary with respect to each of the individual detectors.
 Since our 9-dimensional parameter space can be highly correlated, it is entirely reasonable to assume that cross-correlations between the extrinsic parameters and the mass parameters will cause variation in the recovery of the individual injection PDFs.
 
-In practice, it was found that the cross-correlations between the extrinsic parameters and signal time-of-arrival were several orders of magnitude \carl{[QUANTIFY THIS]} below the uncertainties in $\mathcal{M}_c$ and $\eta$.
-It should be noted that, in practice, this will \emph{not} be the case: in reality, the noise power-spectral density of each detector varies as a function of time, including both natural variations in sensitivity and detector glitches \carl{[CITE SOMETHING]}.
+In practice, it was found that the cross-correlations between the extrinsic parameters and signal time-of-arrival were several orders of magnitude \carl{[QUANTIFY]} below the uncertainties in $\mathcal{M}_c$ and $q$.
+It should be noted that, in practice, this will \emph{not} be the case: in reality, the noise power-spectral density of each detector varies as a function of time, including both natural variations in sensitivity and detector glitches \carl{[CITE]}.
 In such a case, the base sensitivity of a gravitational-wave detector to even the easiest to recover parameters will vary as a function of position and time.
-What we report here can thus be considered an idealized, ``glitch-free'' world in which each detector has an identical noise realization at all times.
-In Section \ref{NoisySubSection}, we provide each detector with a random, but not identical, noise model based on the Advanced LIGO PSD, thus giving an insight into this time-dependent variation \carl{[PLEASE TELL ME THAT'S WHAT LALINFERENCE DOES...]} (while still ignoring instrumentation glitches).
 
-In Figures \ref{1414masses} and \ref{125masses}, we show the marginalized 2D posterior PDFs of our mass parameters a prototypical equal mass and unequal mass binaries.
-We include the PDF in both the $\mathcal{M}_c$-$\eta$ space (relevant for the waveform), and the more physically interesting component mass space ($M_1$-$M_2$).
+In Figures~\ref{1414masses} and~\ref{125masses}, we show the marginalized 2D posterior PDFs of our mass parameters a prototypical equal mass and unequal mass binaries.
+We include the PDF in both the $\mathcal{M}_c$-$q$ space (relevant for the waveform and the MCMC algorithm), and the more physically interesting component mass space ($M_1$-$M_2$).
 Although only the $1.4M_{\odot}/1.4M_{\odot}$ system is included in Figure \ref{1414masses}, the PDF is virtually identical to the other equal mass cases, modulo a scaling factor.
@@
 
-\subsection{Sky Localization}
+As the PDFs of the masses are virtually identical, we average the 1-dimensional mass PDFs into a single posterior probability for
+system.
+See Figure~\ref{metaMassPDFs}.
+Notice how when averaged and normalized to the injected values, the recovery of the component masses depends only on the mass ratio.
+Furthermore, for systems of equal masses, the posterior barely extends beyond 15\% of the injected values (see also Table~\ref{ciTable} in Section~\ref{ciSection}).
+If one assumes that the threshold between black holes and neutron stars lies at approximately $3M_{\odot}$ \carl{[CITE WILL]}, then it will be possible to reliably distinguish the components of each inspiral as a neutron star.
 
 \subsection{Inclination and Distance}
+\label{idSection}
 
-\begin{enumerate}
-\item Inclination for GRB folks
-\item Distance for population studies
-\item degeneracy between the two
-\end{enumerate}
+\begin{figure}[h!]
+  \centering
+ \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.8]{distIota2D.pdf}
+ \caption{Typical marginalized 2D mass PDFs for luminosity distance $D$ and orbital inclination $\iota$. }
+ \label{distIotaPDF}
+\end{figure}
 
-\subsection{Varied Noise Realizations}
-\label{NoisySubSection}
+Since it is assumed that binary neutron star systems (along with neutron star/black systems) are the progenitors for short gamma-ray bursts, emitting the burst along the axis of orbital angular momentum, the inclination of the binary system will be of particular interest to gamma-ray astronomy \carl{[CITE]}.
+The inclination is detected as a relative amplitude difference between the two gravitational-wave polarization, such that to lowest order
+
+\begin{align}
+h_+(f) &= \frac{1+\cos^2(\iota)}{2 D} \tilde{h}(f) \nonumber \\
+h_\times(f) &= i \frac{\cos(\iota)}{D}\tilde{h}(f)
+\end{align}
+
+\noindent It should be apparent that the luminosity distance $D$ and the inclination $\iota$ can be highly correlated in any parameter estimation study, given that both terms modulate the amplitude of a gravitational wave \carl{[QUANTIFY THIS]},
+
+Given this degeneracy, it should come as no surprise that the 2D marginalized posteriors of distance and inclination are the worst of the 6 
+parameters of physical interest.  Four typical 2D PDFs are presented in Figure~\ref{distIotaPDF}.  Notice the large, bimodal uncertainties 
+present in some of the 2D PDFs along the $\iota$ axis, due to the similarity between the evaluated likelihoods at $\iota$ and $\iota + \pi/2$. 
+ As the majority of the information extracted via parameter estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$
+ space will be limited, even during the Advanced LIGO/VIRGO era; however, there will be cases (such as the first PDF in Figure~\ref{distIotaPDF}) 
+ that will prove copacetic to simultaneous measurements accurate enough for coincidence measurements with GRB observers.
+
+\subsection{Sky Localization}
+\label{skySection}
+
+Unlike the mass parameters, the recovery of the position on the sky is highly dependent 
+on the location of the source with respect to the detector network in question. 
+For the HLV configuration, the three-detector network can only localize signals to one of
+two points in the sky.  That is, when using only time-of-arrival information, there is 
+equal support in the probability density functions at the true location and at the 
+point reflected through the plane formed by the three detectors.  In practice, 
+correlated information from the wave polarization can break this degeneracy, so for runs in 
+zero noise, the MCMC properly explores the correct peak on the sky.
+
+The sky location uncertainties for HLV and HLVI are shown in Figures \ref{2525SkyLocHLV}
+ and \ref{2525SkyLocHLVI} respectively.  We show all four mass bins together, since in practice
+  the mass of the signals had no effect on the recovery of the sky location.  Only the location on 
+  the sky, the network configuration, and the other extrinsic parameters were found to be relevant.  
+  In particular, notice the increase in efficiency between the HLV configuration and the HLVI 
+  configuration.  This is hardly surprising, since four detectors allows one to accurately isolate
+   any signal using time-of-arrival.  In the case of the three-detector configuration, there exist locations 
+   in the sky in which a signal is close to its degeneracy point (the point reflected through the plane
+    of the three detectors).  The posteriors recovered for signals from these locations tend to appear
+     stretched, achieving posterior support at both points.  See  \carl{[CITE FAIRHURST]} for a global 
+     analysis of time-of-arrival accuracy for various network configurations, and \carl{[LIGO INDIA PAPER]}
+
+\begin{figure*}[ht!]
+  \centering
+ \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm 0cm]{2p5_2p5_HLV.pdf}
+ \caption{The uncertainty on the sky of 160 BNS systems in the HLV detector configuration.
+Each region represents a single injection, with the colored central region representing the 65\% uncertainty region on the sphere, and the gray region representing the 90\% uncertainty region.
+The color scheme indicates the total solid angle size of the 65\% region.
+Note the similar shape of the uncertainty regions at particular points; this is due to the specific realization of our network pattern sensitivity.}
+ \label{2525SkyLocHLV}
+\end{figure*}
+
+\begin{figure*}[ht!]
+  \centering
+ \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm 0cm]{2p5_2p5_HLVI.pdf}
+ \caption{The same as Fig \ref{2525SkyLocHLV}, except for the HLVI detector configuration.
+Note the substaintally lower average uncertainties on the skies for the majority of the injections.
+Also note the lack of large, ``banana-shaped'' uncertainties that were recovered by the HLV configuration.
+The two improvements are due to the breaking of the degeneracy in sky location recovery that is facilitated by the transition to a four-detector network.}
+ \label{2525SkyLocHLVI}
+\end{figure*}
+
 \subsection{Testing MCMC Convergence}
 
-\carl{include a paragraph on our standard convergence checks}.
-However, there is an additional check we can consider: the standard matched filtering searches employed by the LIGO/VIRGO collaboration assume that a detection will occur when one of the template waveforms matches the detector data with a signal overlap of 97\% or better \carl{cite something}.
+Each set of MCMC samples is tested for convergence by examining both the Gelman-Rubin diagnostic and the auto-correlation length of the MCMC chains, the details of which can be found in \carl{[CITE]} and \carl{[CITE]}, respectively.
+However, there is an additional check we can consider: the standard matched filtering searches employed by the LIGO/VIRGO collaboration assume that a detection will occur when one of the template waveforms matches the detector data with a signal overlap of 97\% or better \carl{[CITE]}.
 That is, for a template waveform $h^{t}(f)$ and detector output $s(f)$, an overlap of
@@
 
-\noindent  yields a detection.
-This requirement provides us with a convenient test for the effectiveness of our parameter estimation.
-First, we note that maximizing our likelihood function, \eqref{likelihood}, is identical to maximizing the SNR \eqref{formalSNR} of our template waveform in a given stretch of data.
-Therefore, the better the match between the template waveform and the data, the higher the SNR.
-Since we assume, quite tautologically, that our parameter estimation code should estimate parameters at least as well as a matched filtering approach, we would be immediately suspicious of any MCMC run whose maximum-likelihood waveform had an SNR below that of our pipeline trigger.
-In that case, we would perform the MCMC with a much longer runtime, until the maximum likelihood of our posterior distribution had an SNR at least as high as the detection.
+\noindent  yields a detection.  This requirement provides us with a convenient test for the effectiveness 
+of our parameter estimation.  First, we note that maximizing our likelihood function, \eqref{likelihood},
+is identical to maximizing the SNR \eqref{formalSNR} of our template waveform in a given stretch of data.
+Therefore, the better the match between the template waveform and the data, the higher the SNR.  Since we
+assume, quite tautologically, that our parameter estimation code should estimate parameters at least as 
+well as a matched filtering approach, we would be immediately suspicious of any MCMC run whose 
+maximum-likelihood waveform had an SNR below that of our pipeline trigger.   In that case, we would perform
+the MCMC with a much longer runtime, until the maximum likelihood of our posterior distribution had an SNR
+at least as high as the detection.
 
-For the purposes of our present study, we reproduce this information as follows: since we know the true SNR of the signal we are simulating, we assume that the ``trigger'' SNR returned by our detection pipeline is 97\% of the true SNR.
-We then assume any posterior distribution whose maximum likelihood satisfies
+For the purposes of our present study, we reproduce this information as follows: since we know the true SNR
+of the signal we are simulating, we assume that the ``trigger'' SNR returned by our detection pipeline is 
+97\% of the true SNR.  We then assume any posterior distribution whose maximum likelihood satisfies
 
@@
 
-\noindent has not converged.
-As one would expect, the lower-mass, longer waveform systems require longer to converge.
-With our original runtime of one week over 8 processors, we found that seven of our $1M_{\odot}/1M_{\odot}$ systems had not converged, while all but one system for our $1.4M_{\odot}/1.4M_{\odot}$ and $1M_{\odot}/2.5M_{\odot}$ systems had converged.
-All of the $2.5M_{\odot}/2.5M_{\odot}$ systems converged within the week.
+\noindent has not converged.  As one would expect, the lower-mass, longer waveform systems require longer 
+to converge.  With our original runtime of one week over 8 processors, we found that seven of our 
+$1M_{\odot}/1M_{\odot}$ systems had not converged, while all but one system for our $1.4M_{\odot}/1.4M_{\odot}$
+and $1M_{\odot}/2.5M_{\odot}$ systems had converged.  All of the $2.5M_{\odot}/2.5M_{\odot}$ systems 
+converged within one week.
 
-We performed a second run for each of the non-converged systems
+\carl{[THIS SECTION INCOMPLETE  WILL REQUIRE THE FINISHED HLV/HLVI RUNS BEFORE I CAN COMPLETE IT]}
+
+\subsection{Varied Noise Realizations}
+\label{noiseSection}
+
+\begin{figure}[ht!]
+  \centering
+ \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.59]{noisePDF.pdf}
+ \label{noisePDFs}
+ \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the Advanced LIGO noise curve.
+Each PDF represents the recovery of the same $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked at random from the Gaussian colored noise defined by the Advanced LIGO power spectral density.
+Notice how the curve is relatively unchanged, but usually assumes a Gaussian PDF displaced from the true value.
+This only holds true for glitch-free data, which is an unrealistic idealization when compared to real data.}
+\end{figure}
+
+While we have, for a variety of reasons, performed the current analysis on zero-noise injections,
+parameter estimation in the advanced detector error will not be so copacetic. 
+Each detection will occur in noisy data, with a specific realization of the PSD provided and with 
+possible instrumentation and environmental glitches.  In the case of a unique Gaussian realization
+of the Advanced-LIGO noise curve, each realization causes the maximum likelihood of the posterior probability 
+distribution to be translated away from the true value; however, these displacements are drawn
+according to the zero-noise distribution \citep{Inadequacies}.  Once averaged, the mean
+uncertainties should be equal to the uncertainty drawn from the zero-noise runs.
+
+As a demonstration of this, we injected a single $1.4M_{\odot}/1.4M_{\odot}$ system, 
+detected in HLVI,  into 5 separate realizations of Gaussian noise colored by the Advanced LIGO PSD, 
+and compared the results to the same MCMC recovery in the zero-noise case.  This example
+can be seen for one-dimensional marginalization of $\mathcal{M}_c$ and $q$ in Fig. \ref{noisePDFs}.  In effect, the ``real answer'' that will be recovered is a single PDF with similar 
+width to the zero-noise PDF, but with the peak likelihood displaced from the true value.
+
+Of course, the largest concern for gravitational-wave parameter estimation will not the specific
+realization of Gaussian noise, but the effects of glitches in the data.  These time-series 
+glitches have a variety of well-known and not-so-well-known physical causes in the instrument,
+and can cause substantially greater errors in parameter recovery than any specific realization noise realizations.  This has already been addressed for the case of space-based gravitational-wave
+detectors (LISA), and is currently being implemented in \texttt{lalinference\_mcmc} 
+\carl{[CITE TYSON, PROTO-TYSON]}.
+
+\begin{comment}
+\subsection{Timescale for Parameter Estimation}
+\label{PEtimesSection}
+
+\begin{figure*}[h!]
+  \centering
+ \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.65]{HLVRuntimes.pdf}
+ \label{HLVRuntimes}
+ \caption{Typical Runtimes for the HLV Network Configuration.  Each run was done on the local Northwestern supercomputer}
+\end{figure*}
+
+\begin{figure*}[h!]
+  \centering
+ \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.65]{HLVIRuntimes.pdf}
+ \label{HLVIRuntimes}
+ \caption{\carl{this is superfluous; combine this into one figure with two colors.} }
+\end{figure*}
+
+The parameter estimation techniques described here will be performed as a follow-up analysis
+to the detections returned by various on-line analyses in the Advanced LIGO/VIRGO era.  While
+there exist specific PE analyses that will be performed in real-time for time sensitive signals 
+(i.e. extrinsic parameters for signals with a potential optimal counterpart \carl{[CITE PROTO-BEN
+OR LEO SINGER]}), most PE will require several days to weeks to complete the analysis upon a 
+single event.  We display the distribution of runtimes for the two network configuration in Figures~\ref{HLVRuntimes} and ~\ref{HLVIRuntimes} 
+\end{comment}
+
+\section{Confidence Intervals}
+\label{ciSection}
+
+The correct answer to the question ``how well can Advanced LIGO/VIRGO measure the parameters of binary neutron star systems'' is the full 9-dimensional PDFs; however, for both convenience and comparison, it is useful and elucidating to speak in terms of the confidence intervals of a single parameter.
+To that end, we state the averaged 65\% and 90\% confidence intervals about the single parameters for each of the three parameter pairs of interest.
+These were already plotted for the sky locations in Figures~\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI}.
+
+There are several different ways of computing the width of a confidence interval in this setup.
+If one considers the points in the MCMC as random draws from the true posterior, then the $\alpha$-level confidence interval can be computed by simply ordering the points, removing $N(\alpha / 2)$ points from both sides of the posterior samples symmetrically, and measuring the width of the remaining points.
+While this procedure can proven hazardous for multi-modal distributions, it is strait-forward and reliable for single-peaked distributions as reported here.
+
+In Table~\ref{ciTable}, we list the mean 65\% confidence intervals recovered for the four mass configurations in both network configurations. 
+This essentially quantifies the widths of the posteriors plotted throughout Section~\ref{resultsSection}.  Again notice how the small confidence
+intervals on the individual component masses suggest it will be possible, on average, to discern neutron stars from black holes in binary inspirals.  
+The purpose of Table~\ref{ciTable} is to provide a quantitative and quotable source for studies seeking to determine how well a physical question
+about BNS systems can be answered with the Advanced LIGO/VIRGO network.
+
+\begin{table*}[t!]
+\centering
+\caption{\carl{65\% confidence intervals, but since they're incomplete these are just place holders for now (the real ones will have upper and lower bounds, as well as units, normalization to the injected values, 2d sky areas, and component masses) also, double check the ra on 2.5 2.5 HLVI}}
+\begin{tabular}{lcccccccccccc}
+
+\\HLVI\\
+\hline\hline
+System & \vline &  $\Delta \mathcal{M}_c$ & \vline & $\Delta q$ & \vline & $\Delta D$ & \vline & $\Delta \iota$ & \vline & $\Delta \alpha$ & \vline &  $\Delta \delta$\\
+\hline\hline
+$1M_{\odot}-1M_{\odot}$ & \vline & $4.33\times10^{-5}$ & \vline & $0.123$& \vline & $39.1$ & \vline & $0.45$ & \vline & $0.028$ & \vline & 0.028\\
+\hline
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $1.07\times10^{-4}$ & \vline & 0.13 & \vline & 60.3 & \vline & 0.45 & \vline & 0.028 & \vline & 0.028\\
+\hline
+$1M_{\odot}-2.5M_{\odot}$ & \vline & $2.37\times10^{-4}$ & \vline & 0.014 & \vline & 70.13 & \vline & 0.52 & \vline & 0.029 & \vline &0.030\\
+\hline
+$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $0.53\times10^{-4}$ & \vline & 0.15 & \vline & 111.67 & \vline & 0.56 & \vline & 0.18 & \vline & 0.030 \\
+\hline\hline
+
+\\
+HLV\\
+
+\hline\hline
+System & \vline &  $\Delta \mathcal{M}_c$ & \vline & $\Delta q$ & \vline & $\Delta D$ & \vline & $\Delta \iota$ & \vline & $\Delta \alpha$ & \vline &  $\Delta \delta$\\
+\hline\hline
+$1M_{\odot}-1M_{\odot}$ & \vline & $4.33\times10^{-5}$ & \vline & $0.123$& \vline & $46.14$ & \vline & $0.55$ & \vline & $0.26$ & \vline & 0.11\\
+\hline
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $1.08\times10^{-4}$ & \vline & 0.13 & \vline & 56.3 & \vline & 0.57 & \vline & 0.125 & \vline & 0.130\\
+\hline
+$1M_{\odot}-2.5M_{\odot}$ & \vline & $2.37\times10^{-4}$ & \vline & 0.014 & \vline & 66.05 & \vline & 0.66 & \vline & 0.05 & \vline &0.070\\
+\hline
+$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $0.53\times10^{-4}$ & \vline & 0.15 & \vline & 109.5 & \vline & 0.70 & \vline & 0.20 & \vline & 0.06 \\
+\hline\hline
+
+\end{tabular}
+\label{ciTable}
+\end{table*}
+
+\section{Conclusion}
+\label{conclusionSection}
+
+In this paper, we performed an MCMC parameter estimation analysis on the recoverability of basic information about binary neutron stars, using two projected version of the Advanced LIGO/VIRGO network.
+We focused on the recovery of the two masses, the luminosity distance, orbital inclination, and the sky location, as these are the six basic parameters of physical interest to the problem.
+We found that \carl{[WAIT UNTIL RUNS ARE DONE AND TABLE IS FINISHED TO SUMMARIZE RESULTS]}
+
+It should be noted that there are two distinct types of systematic error, highly relevant to the gravitational-wave parameter estimation problem, that we have not addressed in this study.
+First, we have studied the parameter estimation uncertainties under the assumption that the waveform template we use to recover the signal template exactly matches the fully relativistic waveforms nature provides.
+In practice, these waveforms are only approximations to the fully general-relativistic physics required to solve the problem.
+See \carl{[CITE]} for a better description of the systematic uncertainties present in the most common waveform families.
+
+Secondly, as stated above, the noise realization that we have employed here is an extreme idealization.
+In practice the noise levels of Advanced LIGO and Advanced VIRGO will be highly variable over time, and will \emph{not} be stationary or Gaussian, as is commonly assumed.
+Unfortunately, there is no reliable or simple way to simulate the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.
+Since the realization of noise be the primary factor in the deflection of true signal PDFs from the averages quoted here, this effect will be critical to properly characterizing gravitational-wave detections \carl{[CITE TYSON AGAIN]}
+
+In this study, we have ignored several of the more interesting parameters that can be included in parameter estimation, such as modifications to general relativity \carl{[CITE]} and the neutron star equation-of-state \carl{[CITE]}.
+We elected to focus on the basic parameters that will be measured routinely in the Advanced Detector era.
+Future work will explore how well these specific questions can be answered using \texttt{LALInferece}, and what prospects such parameter estimation will have for answering longstanding questions in relativistic astrophysics.
 

### 2013-05-21 9oneDpdfs.py
added modified plotting scripts

@@ -16,11 +16,11 @@ file.close()
 
 postSamp = [[] for i in range(9)]
 num = [11, 10, 8, 6,5,7,3,4,9]
-names = ["$\mathcal{M}_c$","$\eta$","$\phi_c$","$\\alpha$","$\delta$","$D$","$\iota$","$\psi$","$Time$"]
+names = ["$\mathcal{M}_c$","$q$","$\phi_c$","$\\alpha$","$\delta$","$D$","$\iota$","$\psi$","$Time$"]
 xaxis = ["Chirp Mass $(M_{\odot})$","Mass Ratio","Chirp Phase $(rad.)$","Right Ascension $(rad.)$","Declination $(rad.)$","Distance $(MPC)$","Inclination $(rad.)$","Polarization $(rad.)$","Time $(msec.)$"]
-inject = [1.21877,0.24995,2.68833,4.662361,-0.4254096,99.15952,2.353028,2.153679,0.]
+inject = [1.21877,1.,2.68833,4.662361,-0.4254096,99.15952,2.353028,2.153679,0.]
 ticks = [[1.2183,1.2185,1.2187,1.2189],
-         [0.24,0.2425,0.245,0.2475,0.25],
+         [0.7,0.75,0.8,0.85,0.9,0.95,1],
 		 [0,1,2,3,4,5,6],
 		 [4.65,4.66,4.67,4.68,4.69],
 		 [-0.6,-0.55,-0.5,-0.45,-0.4,-0.35],
@@ -33,9 +33,9 @@ ticks = [[1.2183,1.2185,1.2187,1.2189],
 for i in range(1,len(filedata)):
 	for j in range(9):
 			postSamp[j].append(float(filedata[i].split()[num[j]]))
-			if j==1:
-				m1, m2 = m1m2fromMcq(postSamp[0][i-1],postSamp[1][i-1])
-				postSamp[1][i-1] = m1*m2 / (m1+m2)**2 
+	#		if j==1:
+	#			m1, m2 = m1m2fromMcq(postSamp[0][i-1],postSamp[1][i-1])
+	#			postSamp[1][i-1] = m1*m2 / (m1+m2)**2 
 			if j == 8:
 				postSamp[j][i-1] = (postSamp[j][i-1] - 894429279.)*1000
 

### 2013-05-21 DistIotaComp.py

@@ -1,11 +1,12 @@
 from math import *
 from numpy import *
-from pylal import bayespputils as bppu
 
-Dist= [[] for i in range(4)]
-Iota= [[] for i in range(4)]
+Dist= [[] for i in range(5)]
+Iota= [[] for i in range(5)]
 filenumbers = ['5','27','40','36']
+#filenumbers = ['5','27','36']
 injected = [(100.8422,1.5548),(124.73,1.782),(170.41,2.135),(145.78,1.671)]
+#injected = [(100.8422,1.5548),(124.73,1.782),(145.78,1.671)]
 
 for j in range(4):
 		file = open('1.4_1.4/' + filenumbers[j] + '/post/posterior_samples.dat')
@@ -18,18 +19,18 @@ for j in range(4):
 			Iota[j].append(float(iota))
 
 
-subplots_adjust(left=None, bottom=None, right=None, top=0.83, wspace=None, hspace=0.4)
+subplots_adjust(left=0.15, bottom=None, right=None, top=0.92, wspace=None, hspace=0.5)
 for j in range(1,5):
-		suptitle("2D Marginalized Distance/Inclination Posteriors", fontsize=26)
-		subplot(2,2,j)
+		suptitle("Distance/Inclination PDFs", fontsize=20)
+		subplot(4,1,j)
 		#ax.set_xticks([1.3484,1.3486,1.3488, 1.3490,1.3492])
 		gridsize = 60
 		hexbin(Dist[j-1],Iota[j-1], gridsize=gridsize, cmap=cm.gist_stern, bins=None)
 		plot(injected[j-1][0],injected[j-1][1],marker='o', color='w',markersize=18)
 		pyplot.colorbar()
-		title('$D$ vs. $\iota$',fontsize=24)
-		xlabel('$D (mpc)$',fontsize=18)
-		ylabel('$\iota (rad)$',fontsize=18)
+		title('$D$ vs. $\iota$',fontsize=16)
+		xlabel('$D (mpc)$',fontsize=14)
+		ylabel('$\iota (rad)$',fontsize=14)
 
 draw()
 show()

### 2013-05-21 McEtaComp.py

@@ -1,39 +1,42 @@
 from math import *
 from numpy import *
-from pylal import bayespputils as bppu
 
 Mc = []
-Eta = []
+Q = []
 M1 = []
 M2 = []
 
-file = open('postSamp1414.dat')
+file = open('postSamp125.dat')
 filedata = file.readlines()
 file.close()
 
 for i in range(1,len(filedata)):
 	[dist,chain,v1_end_time,f_lower,logll1,logl,loglh1,loglh2,v1h1_delay,l1v1_delay,l1h1_delay,loglv1,m1,ra,l1_end_time,m2,iota,v1l1_delay,psi,post,cycle,mc,h1v1_delay,logprior,phi_orb,h1l1_delay,q,prior,h1_end_time,eta,time,cosiota,dec] = filedata[i].split()
-	Eta.append(float(eta))
+	Q.append(float(q))
 	Mc.append(float(mc))
 	M1.append(float(m1))
 	M2.append(float(m2))
 
 
-suptitle("2D Marginalized Mass Posteriors for $1.4M_{\odot}/1.4M_{\odot}$ System", fontsize=30)
-ax = subplot(1,2,1)
-#ax.set_xticks([1.3484,1.3486,1.3488, 1.3490,1.3492])
-subplots_adjust(left=None, bottom=None, right=None, top=0.83, wspace=None, hspace=0.15)
+suptitle("Mass PDFs for $1M_{\odot}/2.5M_{\odot}$ System", fontsize=20)
+subplots_adjust(left=None, bottom=None, right=None, top=None,
+                  wspace=None, hspace=1)
+ax = subplot(2,1,1)
+ax.set_xticks([1.3484,1.3486,1.3488, 1.3490,1.3492])
+subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=None, hspace=0.3)
 gridsize = 60
-hexbin(Mc,Eta, gridsize=gridsize, cmap=cm.gist_stern, bins=None)
-title('$\mathcal{M}_c$ vs. $\eta$',fontsize=24)
-xlabel('$\mathcal{M}_c$',fontsize=18)
-ylabel('$\eta$',fontsize=18)
+hexbin(Mc,Q, gridsize=gridsize, cmap=cm.gist_stern, bins=None)
+plot(1.348809,0.4,marker='o', color='w',markersize=18)
[…]

### 2013-05-21 doc/paper.tex
added diegos comments

@@
 \newcommand{\carl}[1]{{\color{red}  #1}}
-\newcommand{\ilya}[1]{{\color{blue} #1}}
+\newcommand{\tyson}[1]{{\color{blue} #1}}
 \newcommand{\ben}[1]{{\color{green} #1}}
 \newcommand{\will}[1]{{\color{cyan} #1}}
+\newcommand{\vivien}[1]{{\color{purple} #1}}
+\newcommand{\diego}[1]{{\color{pink} #1}}
+
+\newcommand{\thpara}{\boldsymbol{\theta}}
+\newcommand{\chmass}{\mathcal{M}_c}
 
@@
  By 2016, the field of gravitational-wave astrophysics will
- mature from a speculative scientific genre into an ideal tool for 
+ mature into an ideal tool for 
  exploring the gravitational side of the universe. Within the next few
@@
  into the final moment of binary compact object mergers, including the 
- merger of binary neutron star systems.  Intense preparations are currently
- underway to prepare to characterize and extract as much physical 
+ merger of binary neutron star systems.  Intense work is being undertaken
+ to prepare to characterize and extract as much physical 
  information as possible from these signals.
@@
 The detection of BNS systems will be performed with a matched filtering approach.  
-By comparing the data stream to a bank of theoretical templates, the roughly 16KHz
+By comparing the data stream with a bank of theoretical templates, the roughly 16KHz
  time-series data can be searched for candidate signals at a sufficiently
   rapid rate to analyze months of data.  When the overlap between one of the template waveforms and the 
-detector output is sufficiently large (97\%), a detection is claimed.  However,
+detector output is sufficiently large (97\%), a detection candidate is found.  However,
 the parameter space of these signals can be highly degenerate, with several 
-locations in parameter space corresponding to near identical waveforms.  In 
+locations in parameter space corresponding to nearly identical waveforms.  In 
 order to fully realize the science potential of these instruments, we must 
@@
 and proper sampling, we will be able to make precise, scientifically meaningful
-statements about the physics of these detectible systemss.  To 
+statements about the physics of these detectible systems.  To 
 that end, we employ a Markov-Chain Monte Carlo sampling algorithm, 
@@
 While each of these studies (\cite{PoissonWill,CutlerFlanagan,ArunPE}, among 
-many others) have done their due diligence in pointing out the limitations 
-and flaws of the Fisher Information Matrix, there has been no study which states
+many others) have pointed out the limitations 
+and flaws of the Fisher Information Matrix, there has been no study which investigates
 the BNS parameter estimation capabilities of Advanced LIGO/VIRGO via the techniques
@@
 own work \citep{Inadequacies} has demonstrated that the Fisher matrix cannot even
-be treated as a lower bound on the standard deviations about certain parameters
+be treated as a lower bound on the standard deviations of certain parameters
 (particularly the masses) measurable in gravitational-wave detectors.
@@
 %techniques must be introduced.  First,
-We assume that the time-domain signal in our gravitational wave
+We assume that the time-domain signal in a gravitational-wave
 network can be written as a combination of a gravitational
@@
 Since our noise model is Gaussian, we can write the
-probability of a specific signal realization $s$ as the probability
+probability of a specific signal realization $s$ as proportional to the probability
 that our signal is Gaussian once the waveform has been subtracted
 \begin{align}
-  p(s | \boldsymbol{\theta}) &\propto \exp\left[-\frac{1}{2}\left<n|n
+  p(s | \thpara) &\propto \exp\left[-\frac{1}{2}\left<n|n
     \right>\right] \nonumber \\ &= \exp\left[-\frac{1}{2}\left < s -
-    h(\boldsymbol{\theta}) | s-h(\boldsymbol{\theta})\right >\right] ,
+    h(\thpara) | s-h(\thpara)\right >\right] ,
   \label{likelihood}
 \end{align}
-where $\boldsymbol{\theta}$ is the set of parameters for our template
+where $\thpara$ is the set of parameters for our template
 waveforms.  The inner product, $\left< ~|~ \right> $, is defined using the noise
@@
 employ Bayes Rule to obtain the posterior probability of the system
-parameters $\boldsymbol{\theta}$ given the signal $s$ as
+parameters $\thpara$ given the signal $s$ as
 \begin{align}
-  p(\boldsymbol{\theta} | s) &= \frac{p(\boldsymbol{\theta})p(s | \boldsymbol{\theta})}{p(s)} \nonumber\\
-  & \propto p(\boldsymbol{\theta}) \exp\left[-\frac{1}{2}\big < s - h(\boldsymbol{\theta}) | s-h(\boldsymbol{\theta}) \big > \right] ,
+  p(\thpara | s) &= \frac{p(\thpara)p(s | \thpara)}{p(s)} \nonumber\\
+  & \propto p(\thpara) \exp\left[-\frac{1}{2}\big < s - h(\thpara) | s-h(\thpara) \big > \right] ,
   \label{posterior}
 \end{align}
-where $p(\boldsymbol{\theta})$ are the prior probabilities on our
+where $p(\thpara)$ are the prior probabilities on our
 source parameters and $p(s)$ is a normalization constant.  Our prior
@@
 from our \textit{a priori} knowledge of astrophysical systems. If we
-pick a set of parameters $\boldsymbol{\theta}$ such that
-$h(\boldsymbol{\theta}) = h_0$, then the posterior \eqref{posterior}
+pick a set of parameters $\thpara$ such that
+$h(\thpara) = h_0$, then the posterior \eqref{posterior}
 will be near a global maximum; however, the presence of noise will in
 general deflect the maximum of our posterior away from the value at
-$\boldsymbol{\theta}_0$. That is, in the presence of noise, there is
+$\thpara_0$. That is, in the presence of noise, there is
 no guarantee that the maximum-likelihood of our signal corresponds to
@@
 The above procedure is designed to record a chain of samples whose
-distribution is $p\left(\boldsymbol{\theta}|s\right)$.  Depending on
+distribution is $p\left(\thpara|s\right)$.  Depending on
 the proposal distribution, $q$, the convergence (mixing) of the chain
@@
 \end{equation}
-where $A \propto \mathcal{M}_c^{5/6}\Theta(\text{angle})/D$, $D$ is
+where $A \propto \chmass^{5/6}\Theta(\text{angle})/D$, $D$ is
 the luminosity distance of the binary, and $\psi(f)$ is the pN phase.
@@
 \begin{equation}
-  q\equiv M_1/M_2~~~~\text{and}~~~~\mathcal{M}_c = (M_1 M_2)^{3/5} M^{-1/5},
+  q\equiv M_1/M_2~~~~\text{and}~~~~\chmass = (M_1 M_2)^{3/5} M^{-1/5},
 \end{equation}
-respectively.\footnote{Most gravitational-wave literature instead use the \textit{symmetric mass ratio}, defined as $\eta \equiv M_1 M_2 / M^2$.
+respectively.\footnote{Most gravitational-wave literature instead uses the \textit{symmetric mass ratio}, defined as $\eta \equiv M_1 M_2 / M^2$.
 We elect to use $q$ as it is empirically superior when proposing MCMC parameter jumps, and is more physically intuitive.}  The stationary phase then becomes an expansion in the
@@
 \begin{equation}
-\psi(f) = 2 \pi f t_c - \phi_0 + \frac{\pi}{4} + \frac{3}{128}\left(\frac{M}{\mathcal{M}_c}\right)^{5/3}\sum^{n}_{k=0}\alpha_{k}v^{k-5}
+\psi(f) = 2 \pi f t_c - \phi_0 + \frac{\pi}{4} + \frac{3}{128}\left(\frac{M}{\chmass}\right)^{5/3}\sum^{n}_{k=0}\alpha_{k}v^{k-5}
 \label{phase}
@@
 The terms $t_c$ and $\phi_0$ in equation (\ref{phase}) are constants
-of integration, referring to the chirp time and coalescence phase,
+of integration, referred to as the chirp time and coalescence phase,
 respectively.  Although uninteresting physically, they must be
@@
 
-To perform the integral defined in \eqref{innerProduct}, we used the best estimate
-for a high-power, zero-detuning configuration of Advanced LIGO, provided by the LIGO Scientific Collaboration.
-Both the noise curve and technical reports describing it can be found in \cite{ADVLIGONoise}.
+To perform the integral defined in \eqref{innerProduct}, we used as our power-spectral
+density the best estimate for a high-power, zero-detuning configuration of Advanced 
+LIGO, provided by the LIGO Scientific Collaboration.  Both the noise curve and technical 
+reports describing it can be found in \cite{ADVLIGONoise}.
 We consider two configurations of the advanced detector
 network: a three-detector configuation consistanting of the two LIGO sites 
-(in Hanford, WA and Livingston, LA) and the Virgo site (in Pisa), and a four-detector
-configuration with adds the proposed LIGO-India detector (in Chitradurga, KA).
-For simplicity, we assume each detector to be operating at the Advanced LIGO sensitivity. 
+(in Hanford, WA and Livingston, LA) and the Virgo site (in Pisa, Italy), and a 
+four-detector configuration with adds the proposed LIGO-India detector
+(in Chitradurga, KA).  For simplicity, we assume each detector to be 
+operating at the Advanced LIGO sensitivity.
+
 For a multi-detector network, the noise-weighted inner products
@@
 
-We consier the mass parameters ($\mathcal{M}_c,q$) and the phasing parameters,
+We consier the mass parameters ($\chmass,q$) and the phasing parameters,
 ($\phi_0,t_c$), to be the intrinsic parameters of a gravitational-wave signal.  There 
@@
 \begin{equation}
-\boldsymbol{\theta} =  (\mathcal{M}_c, q, \phi_0,t_c,D,\iota,\psi,\alpha,\delta)
+\thpara =  (\chmass, q, \phi_0,t_c,D,\iota,\psi,\alpha,\delta)
 \label{parameterspace}
@@
 \begin{itemize}
-\item $\mathcal{M}_c$ is the chirp mass,
+\item $\chmass$ is the chirp mass,
 \item $q$ is the mass ratio,
@@
 We define the signal-to-noise ratio (SNR) of a gravitational wave in a
-single detector is
+single detector as 
 \begin{equation}
@@
  These PDFs are typical of what will be produced by parameter estimation studies in the advanced 
- detector era.  Notice that the peak of several parameters, including the chirp mass, $\mathcal{M}_c$, 
+ detector era.  Notice that the peak of several parameters, including the chirp mass, $\chmass$, 
  appears to be displaced from the true values in red.  This effect is due to the reduction of the
@@
 \begin{equation}
-p(\mathcal{M}_c | s) = \int _{\boldsymbol{\theta} \setminus \mathcal{M}_c} p(\boldsymbol{\theta} | s)~d(\boldsymbol{\theta} \setminus \mathcal{M}_c)
+p(\chmass | s) = \int _{\thpara \setminus \chmass} p(\thpara | s)~d(\thpara \setminus \chmass)
 \label{mcMarginalization}
@@
 
-\noindent Other parameter and higher-dimensional marginalizations follow a similar convention.
+\noindent where the notation $\thpara \setminus \chmass$ implies all
+parameter of \eqref{parameterspace} except $\chmass$.  Other parameter and higher-dimensional marginalizations follow a similar convention.
 
@@
 The posteriors are plotted in terms of parameters used in the waveform, chirp mass ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual component masses of the binary ($M_1$ and $M_2$).
-In the $\mathcal{M}_c$-$q$ space, the posterior would resemble a Gaussian if not for the limitation of $q \leq 1$.
+In the $\chmass$-$q$ space, the posterior would resemble a Gaussian if not for the limitation of $q \leq 1$.
 The presence of the $q$ cutoff and the convention that $M_1 \geq M_2$ inform the non-Gaussian features present.
@@
  \caption{Similar to Figure~\ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.
-The unequal mass ratio displaces the posterior PDFs from the $q \leq 1$ present in the equal mass case, yielding a Gaussian PDF in both the $\mathcal{M}_c$-$q$ and $M_1$-$M_2$ spaces.}
+The unequal mass ratio displaces the posterior PDFs from the $q \leq 1$ present in the equal mass case, yielding a Gaussian PDF in both the $\chmass$-$q$ and $M_1$-$M_2$ spaces.}
   \label{125masses}
@@
 Of the 9 variables in our parameter space \eqref{parameterspace}, the two of immediate physical
-interest are the two parameters, $\mathcal{M}_c$ and $q$, or correspondingly the direct masses 
+interest are the two parameters, $\chmass$ and $q$, or correspondingly the direct masses 
 of the two companions, $M_1$ and $M_2$.    As stated above, the ability of
@@
 
-In practice, it was found that the cross-correlations between the extrinsic parameters and signal time-of-arrival were several orders of magnitude \carl{[QUANTIFY]} below the uncertainties in $\mathcal{M}_c$ and $q$.
+In practice, it was found that the cross-correlations between the extrinsic parameters and signal time-of-arrival were several orders of magnitude \carl{[QUANTIFY]} below the uncertainties in $\chmass$ and $q$.
 It should be noted that, in practice, this will \emph{not} be the case: in reality, the noise power-spectral density of each detector varies as a function of time, including both natural variations in sensitivity and detector glitches \carl{[CITE]}.
@@
 In Figures~\ref{1414masses} and~\ref{125masses}, we show the marginalized 2D posterior PDFs of our mass parameters a prototypical equal mass and unequal mass binaries.
-We include the PDF in both the $\mathcal{M}_c$-$q$ space (relevant for the waveform and the MCMC algorithm), and the more physically interesting component mass space ($M_1$-$M_2$).
+We include the PDF in both the $\chmass$-$q$ space (relevant for the waveform and the MCMC algorithm), and the more physically interesting component mass space ($M_1$-$M_2$).
 Although only the $1.4M_{\odot}/1.4M_{\odot}$ system is included in Figure \ref{1414masses}, the PDF is virtually identical to the other equal mass cases, modulo a scaling factor.
@@
 
-Since it is assumed that binary neutron star systems (along with neutron star/black systems) are the progenitors for short gamma-ray bursts, emitting the burst along the axis of orbital angular momentum, the inclination of the binary system will be of particular interest to gamma-ray astronomy \carl{[CITE]}.
+Since it is assumed that binary neutron star systems (along with neutron star/black hole systems) are the progenitors for short gamma-ray bursts, emitting the burst along the axis of orbital angular momentum, the inclination of the binary system will be of particular interest to gamma-ray astronomy \carl{[CITE]}.
 The inclination is detected as a relative amplitude difference between the two gravitational-wave polarization, such that to lowest order
@@
 
-\noindent  yields a detection.  This requirement provides us with a convenient test for the effectiveness 
+\noindent  yields a detection candidate.  This requirement provides us with a convenient test for the effectiveness 
 of our parameter estimation.  First, we note that maximizing our likelihood function, \eqref{likelihood},
@@
  \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.59]{noisePDF.pdf}
- \label{noisePDFs}
  \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the Advanced LIGO noise curve.
@@
 This only holds true for glitch-free data, which is an unrealistic idealization when compared to real data.}
+ \label{noisePDFs}
 \end{figure}
@@
 and compared the results to the same MCMC recovery in the zero-noise case.  This example
-can be seen for one-dimensional marginalization of $\mathcal{M}_c$ and $q$ in Fig. \ref{noisePDFs}.  In effect, the ``real answer'' that will be recovered is a single PDF with similar 
+can be seen for one-dimensional marginalization of $\chmass$ and $q$ in Fig. \ref{noisePDFs}.  In effect, the ``real answer'' that will be recovered is a single PDF with similar 
 width to the zero-noise PDF, but with the peak likelihood displaced from the true value.
 
-Of course, the largest concern for gravitational-wave parameter estimation will not the specific
+Of course, the largest concern for gravitational-wave parameter estimation will not be the specific
 realization of Gaussian noise, but the effects of glitches in the data.  These time-series 
@@
 There are several different ways of computing the width of a confidence interval in this setup.
-If one considers the points in the MCMC as random draws from the true posterior, then the $\alpha$-level confidence interval can be computed by simply ordering the points, removing $N(\alpha / 2)$ points from both sides of the posterior samples symmetrically, and measuring the width of the remaining points.
-While this procedure can proven hazardous for multi-modal distributions, it is strait-forward and reliable for single-peaked distributions as reported here.
+If one considers the points in the MCMC as random draws from the true posterior, then the $\alpha$-level confidence interval can be computed by simply ordering the points, removing $N(1-\alpha )/2$ points from both sides of the posterior samples symmetrically, and measuring the width of the remaining points.
+While this procedure can prove hazardous for multi-modal distributions, it is straightforward and reliable for single-peaked distributions as reported here.
 
 In Table~\ref{ciTable}, we list the mean 65\% confidence intervals recovered for the four mass configurations in both network configurations. 
-This essentially quantifies the widths of the posteriors plotted throughout Section~\ref{resultsSection}.  Again notice how the small confidence
+This essentially quantifies the widths of the posteriors plotted throughout Section~\ref{resultsSection}.  Again, it is worth noting how the small confidence
 intervals on the individual component masses suggest it will be possible, on average, to discern neutron stars from black holes in binary inspirals.  
@@
 \hline\hline
-System & \vline &  $\Delta \mathcal{M}_c$ & \vline & $\Delta q$ & \vline & $\Delta D$ & \vline & $\Delta \iota$ & \vline & $\Delta \alpha$ & \vline &  $\Delta \delta$\\
+System & \vline &  $\Delta \chmass$ & \vline & $\Delta q$ & \vline & $\Delta D$ & \vline & $\Delta \iota$ & \vline & $\Delta \alpha$ & \vline &  $\Delta \delta$\\
 \hline\hline
@@
 
-Secondly, as stated above, the noise realization that we have employed here is an extreme idealization.
+Secondly, as stated above, the noise realization that we have employed here is an substaintial idealization.
 In practice the noise levels of Advanced LIGO and Advanced VIRGO will be highly variable over time, and will \emph{not} be stationary or Gaussian, as is commonly assumed.
 Unfortunately, there is no reliable or simple way to simulate the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.
-Since the realization of noise be the primary factor in the deflection of true signal PDFs from the averages quoted here, this effect will be critical to properly characterizing gravitational-wave detections \carl{[CITE TYSON AGAIN]}
+Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here, this effect will be critical to properly characterizing gravitational-wave detections \carl{[CITE TYSON AGAIN]}
 

### 2013-05-24 doc/paper.tex
finished addressing most of tysons comments and added (almost) finalized sky plots and CI tables

@@
 \begin{document}
-\title{Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/VIRGO Network}
+\title{Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network}
 \author{Carl L. Rodriguez \altaffilmark{1}
@@
 
-Within the next 5 years, the Advanced LIGO/VIRGO network will have reached a sensitivity sufficient to enable the routine detection of gravitational waves.
-Beyond the initial detection, the scientific promise of these instruments relies on the efficiency of the parameter estimation techniques being currently developed.
-The majority of this effort has been towards the detection and characterization of gravitational waves from compact binary coalescence, i.e.
-the coalescence of black holes and/or neutron stars.
-While several previous studies have focused on the parameter estimation abilities of advanced detectors, the vast majority have relied on approximation techniques (such as the Fisher Matrix) when characterizing the uncertainties.
-Here, we report the statistical uncertainties that will be achievable, in practice, using the parameter estimation code \texttt{LALInference} to recover the parameters of binary neutron star systems detected in various configurations of the Advanced LIGO/VIRGO network.
-We find that the recovery of the individual masses will be, on average, sufficient to differentiate neutron stars from black holes by the masses alone.
-We also report the average uncertainties on the sky-locations, luminosity distance, and orbital inclinations of randomly generated sources that can be recovered by the expected three and four-detector networks.
+Within the next five years, the Advanced LIGO/Virgo network will have reached a sensitivity sufficient to enable the routine
+ detection of gravitational waves.  Beyond the initial detection, the scientific promise of these instruments relies the 
+ parameter estimation techniques being currently developed.  The majority of this effort has been towards the detection
+   and characterization of gravitational waves from compact binary coalescence, i.e. the coalescence of black holes and/or 
+   neutron stars.  While several previous studies have focused on the parameter estimation abilities of advanced detectors, 
+   the majority have relied on approximation techniques such as the Fisher Matrix.  Here, we report the statistical 
+   uncertainties that will be achievable, in practice, using the parameter estimation techniques which will be applied to 
+   detections of binary neutron star systems.  We find the recovery of the individual masses to be within fractionally within 
+   10\% at the 65\% confidence level for equal-mass systems, and within 2\% for unequal-mass systems.
+     We also report the average uncertainties on the sky-locations, luminosity distance, and orbital inclinations of randomly 
+     distributed sources that can be achieved by different network configurations. \carl{[PUT IN SA VALUES FOR SKY LOCATION]}
 \end{abstract}
@@
 
- By 2016, the field of gravitational-wave astrophysics will
+ By the end of the decade, the field of gravitational-wave astrophysics will
  mature into an ideal tool for 
@@
  of regularly resolving astrophysical sources will come online \carl{[CITE]}.
- The Advanced LIGO and VIRGO detectors will provide the first insights
+ The Advanced LIGO and Virgo detectors will provide the first insights
  into the final moment of binary compact object mergers, including the 
- merger of binary neutron star systems.  Intense work is being undertaken
- to prepare to characterize and extract as much physical 
+ merger of binary neutron star systems.  Intense preparations are underway
+ to characterize and extract as much physical 
  information as possible from these signals.
 
-The mergers of binary neutron stars are expected to be the most ubiquitous
+The mergers of binary neutron stars are expected to be the most common
 source in the advanced detector era \carl{[CITE]}.   Models from stellar 
 evolution suggest that the number of binary neutron star mergers within 
-Advanced LIGO/VIRGO's detection horizon could reach into the hundreds per 
+Advanced LIGO/Virgo's detection horizon could reach into the hundreds per 
 year \carl{[CITE]}.  Although the peak sensitivity of ground-based detectors
-is not focused on the frequency at which BNS systems merge, it should still
+is not focused on the frequency at which BNS systems merge, it could still
 be possible to extract information about both strong field gravitational 
@@
 and in globular clusters \carl{[CITE]}. As such, BNS systems will likely 
-form the ``bread and butter'' of the compact object efforts in the coming 
+form the ``bread and butter'' of the compact binary coalescence detection effort in the coming 
 years.
@@
 The detection of BNS systems will be performed with a matched filtering approach.  
-By comparing the data stream with a bank of theoretical templates, the roughly 16KHz
+By comparing the data stream with a bank of theoretical templates, the 
  time-series data can be searched for candidate signals at a sufficiently
@@
 analyzing the parameter space of each candidate with a Bayesian inference technique 
-and proper sampling, we will be able to make precise, scientifically meaningful
+ we will be able to make precise, scientifically meaningful
 statements about the physics of these detectible systems.  To 
@@
 \texttt{lalinference\_mcmc}, included in the LIGO Application Library parameter
-estimation code, \texttt{LALInference}.
+estimation code, \texttt{LALInference}, to analyze the parameter space of binary neutron star systems.
 
 By employing the full parameter-estimation machinery that will eventually be
-used in the Advanced LIGO/VIRGO era, our results give the first estimate at the 
+used in the Advanced LIGO/Virgo era, our results give the first estimate at the 
 realistic capabilities of advanced ground-based detectors to characterize BNS systems.
@@
 and flaws of the Fisher Information Matrix, there has been no study which investigates
-the BNS parameter estimation capabilities of Advanced LIGO/VIRGO via the techniques
+the BNS parameter estimation capabilities of Advanced LIGO/Virgo via the techniques
 that will eventually be employed.  The recent work of \cite{Vallisneri} and our 
@@
 In this paper, we perform a systematic study of the statistical uncertainties with
-which the Advanced LIGO/VIRGO network will be able to measure the basic parameters of 
+which the Advanced LIGO/Virgo network will be able to measure the basic parameters of 
 binary neutron stars.  In Section \ref{PEsection}, we describe
 the machinery of our parameter estimation code, \texttt{LALInference}, and the associated
-MCMC sampler, \texttt{lalinference\_mcmc}, as well as the frequency-domain gravitational-wave template we employ.   
-In Section \ref{resultsSection}, we qualitatively analyze the posterior probability density functions for BNS systems with different masses and extrinsic parameters.
-The results are divided into three parameter sets of interest: the recovery of the mass parameters (Section \ref{massSection}), the recovery of the orbital inclination and luminosity distance (Section \ref{idSection}), and the isolation of sources in the sky (Section \ref{skySection}).
-Finally we provide quantitative 1-dimensional confidence intervals on the parameter recovery in Section \ref{ciSection}.
+MCMC sampler, \texttt{lalinference\_mcmc}, as well as the frequency-domain 
+gravitational-wave template we employ.   In Section \ref{resultsSection}, we qualitatively 
+analyze the posterior probability density functions for BNS systems with different masses 
+and extrinsic parameters.  The results are divided into three parameter sets of interest: the
+recovery of the mass parameters (Section \ref{massSection}), the recovery of the orbital
+inclination and luminosity distance (Section \ref{idSection}), and the localization of sources 
+in the sky (Section \ref{skySection}).   Finally we provide quantitative 1-dimensional confidence
+ intervals on the parameter recovery in Section \ref{ciSection}.  These results, contained
+ in Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}, are intended as a reference for the 
+ optimal BNS parameter estimation capabilities of Advanced LIGO/Virgo.
    We assume that $G=c=1$ throughout.
@@
 waveform $h_0$ and the noise of the detector $n$.  We further assume
-that this noise is stationary and Gaussian with mean zero.  Therefore,
+that this noise is stationary and Gaussian with zero mean.  Therefore,
 the detector output is simply
@@
 probability of a specific signal realization $s$ as proportional to the probability
-that our signal is Gaussian once the waveform has been subtracted
+that our residual is Gaussian distributed once the waveform has been subtracted
 \begin{align}
@@
 where $\thpara$ is the set of parameters for our template
-waveforms.  The inner product, $\left< ~|~ \right> $, is defined using the noise
+waveforms, and $p(s | \thpara)$ is the likelihood of the signal $s$ given the parameters $\thpara$.
+  The inner product, $\left< ~|~ \right> $, is defined using the noise
 spectrum of the detectors as
@@
 Once we have the likelihood of the signal \eqref{likelihood}, we
-employ Bayes Rule to obtain the posterior probability of the system
+employ Bayes Theorem to obtain the posterior probability of the system
 parameters $\thpara$ given the signal $s$ as
@@
 where $p(\thpara)$ are the prior probabilities on our
-source parameters and $p(s)$ is a normalization constant.  Our prior
-information can come from physics limits in the parameter space, or
-from our \textit{a priori} knowledge of astrophysical systems. If we
-pick a set of parameters $\thpara$ such that
+source parameters and $p(s)$ is a normalization constant.
+
+We are interested in the posterior $p(\thpara | s)$ as it encodes information about
+prior state of knowledge about the problem.  For instance, since it is assumed that compact binaries
+form homogeneously in the local universe, we can safely assume that the population of
+sources will be distributed homogeneously in volume, or evenly in $D^2$. 
+ Our prior information can come from mathematical limits in the parameter space or
+from our \textit{a priori} knowledge of astrophysical systems.  We employ priors which are
+
+\begin{itemize}
+\item uniform in component masses from $0.8M_{\odot} \leq M_{1,2} \leq 30M_{\odot}$, with a minimum chirp mass  \eqref{eqRatioCM} of 0.6 $M_{\odot}$,
+\item uniform in volume, which implies a luminosity distance prior of $p(D) = D^2 dD$, and
+\item uniform in all other parameters.
+\end{itemize}
+
+If we pick a set of parameters $\thpara$ such that
 $h(\thpara) = h_0$, then the posterior \eqref{posterior}
@@
 a unified framework for gravitational-wave parameter estimation.  By using a common setup for 
-waveform generation, PSD estimation, data handling, and other associated techniques from gravitational-wave parameter estimation, \texttt{LALInference} allows the implementation of multiple parameter samplers in using identical parameter setups, including nested sampling (\texttt{lalinference\_nest}) and Markov-Chain Monte Carlo (\texttt{lalinference\_mcmc}).
+waveform generation, PSD estimation, data handling, and other associated techniques from gravitational-wave parameter estimation, \texttt{LALInference} allows the implementation of multiple parameter samplers in using identical parameter setups, including Nested Sampling (\texttt{lalinference\_nest})\carl{[CITE]} and Markov-Chain Monte Carlo (\texttt{lalinference\_mcmc}).
 We elect to use the MCMC sampler for this study.
@@
 The above procedure is designed to record a chain of samples whose
-distribution is $p\left(\thpara|s\right)$.  Depending on
+distribution is $p\left(\thpara|s\right)$.  By drawing a sufficient ($\sim 1000$) number
+ of effective samples from the posterior, the chains traces out the functional form of the posterior,
+ gathering more samples from regions with high posterior probability.  Depending on
 the proposal distribution, $q$, the convergence (mixing) of the chain
@@
 \citep{Sluys08,spinspiral2009, spinspiral2010}.  Both samplers were tuned and 
-developed during the last science run of the Initial LIGO/VIRGO network.  
-A description of the parameter estimation capabilities, c.f. 2010, can be found
-in \cite{S6PE}.
+developed during the last science run of the Initial LIGO/Virgo network.  
+A description of the parameter estimation capabilities of these two samplers with respect to
+real gravitational-wave data, as well as a more detailed description of the algorithms and
+checks for convergence, can be found in \cite{S6PE}.
 
@@
 post-Newtonian (pN) order in phase and amplitude.  We restrict ourselves to
-quasi-circular waveforms as a simplifying assumption.  The standard
+quasi-circular, non-spinning waveforms as a simplifying assumption.  The standard
 form of our waveform model, known as the \textit{TaylorF2}
@@
 \begin{equation}
-\tilde{h}(f) = A f^{-7/6}e^{i \psi(f)},
+\tilde{h}(f) = a(t_f) e^{i \psi(f)},
 \label{amplitude}
 \end{equation}
-where $A \propto \chmass^{5/6}\Theta(\text{angle})/D$, $D$ is
+where $a(t_f)$ is the amplitude evaluated at a stationary-phase reference point, which to lowest order
+takes the form $A \propto f^{-7/6} \chmass^{5/6}\Theta(\text{angle})/D$, $D$ is
 the luminosity distance of the binary, and $\psi(f)$ is the pN phase.
@@
 inclination, and the wave polarization.  In addition to the total
-mass, $M\equiv M_1+M_2$, it is convenient to work with the
+mass, $M_{tot}\equiv M_1+M_2$, it is convenient to work with the
 \textit{mass ratio} and \textit{chirp mass}, defined by
@@
   q\equiv M_1/M_2~~~~\text{and}~~~~\chmass = (M_1 M_2)^{3/5} M^{-1/5},
+  \label{eqRatioCM}
 \end{equation}
 respectively.\footnote{Most gravitational-wave literature instead uses the \textit{symmetric mass ratio}, defined as $\eta \equiv M_1 M_2 / M^2$.
-We elect to use $q$ as it is empirically superior when proposing MCMC parameter jumps, and is more physically intuitive.}  The stationary phase then becomes an expansion in the
+We elect to use $q$ as it is more physically intuitive, and the prior $p(q)$ is uniform when the component
+mass priors are uniform.}  The stationary phase then becomes an expansion in the 
 Newtonian orbital velocity, $v=(\pi M f)^{1/3}$, 
@@
 
-\noindent where the $\alpha_{k}$ coefficients are taken from the pN expansion to order $n/2$.  See \cite{BuonannoWaveform} for a description and comparison of different waveform families.
-
-The terms $t_c$ and $\phi_0$ in equation (\ref{phase}) are constants
-of integration, referred to as the chirp time and coalescence phase,
-respectively.  Although uninteresting physically, they must be
-accounted for in any parameter estimation study of the waveform phase.
+\noindent where the $\alpha_{k}$ coefficients are taken from the pN expansion to order $n/2$.
+See \cite{BuonannoWaveform} for a description and comparison of different waveform families.
+The terms $t_c$ and $\phi_0$ in equation (\ref{phase}) are constants of integration, referred to as the chirp time and coalescence phase, respectively.
 
@@
 \begin{equation}
-  \rho \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{| \tilde{s}(f)\tilde{h}^{*}(f)|}{S_{n}(f)}df
+  \rho \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{| \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df
   \label{formalSNR}
@@
 \begin{equation}
-\rho_{\text{network}} = \sqrt{\sum_i \rho_{i}}
+\rho_{\text{network}} = \sqrt{\sum_i \rho_{i}^2}
 \label{SNRnetwork}
@@
 distributed evenly in comoving volume), this choice allows us to explore the parameter estimation
-in the context of viable detection candidates.
+in the context of optimal detection candidates.
 
@@
    However, what we are interested in is not the parameter estimation that can occur in a specific draw
-    from this probability of noises, but the uncertainties averaged over all possible noise realizations.
-    \footnote{Similarly to how the Fisher matrix formalism can provide the Cramer-Rao bound averaged over
+    from this probability of noises, but the uncertainties averaged over all possible noise
+     realizations.\footnote{Similarly to how the Fisher matrix formalism can provide the Cramer-Rao bound averaged over
      all noise realizations} Since our noise model is assumed to be Gaussian, it is unnecessary to recover the
@@
       noise \emph{is} the mean defined by the power-spectral density.  This ``zero-noise'' parameter estimation
-       provides a statical statement on the measurable uncertainties, and is what is reported here.  In Section
+       provides a statistical statement on the measurable uncertainties, and is what is reported here.  In Section
         \ref{noiseSection} we provide an example of parameter estimation in several non-zero noise realizations
@@
 
-\section{Results}
-\label{resultsSection}
-
-\begin{figure*}[t!]
-\centering
-\includegraphics[trim=7cm 0cm 0cm 0cm, clip=true,scale=0.55]{9dpdf.pdf}
-%\begin{array}{ccc} 
-%\includegraphics[width=2.2in]{1dpdfs/mc.pdf} &\includegraphics[width=2.2in]{1dpdfs/eta.pdf}  & \includegraphics[width=2.2in]{1dpdfs/m1.pdf}\\
-%\includegraphics[width=2.2in]{1dpdfs/time.pdf} &\includegraphics[width=2.2in]{1dpdfs/dist.pdf}  &\includegraphics[width=2.2in]{1dpdfs/iota.pdf}\\
-%\includegraphics[width=2.2in]{1dpdfs/ra.pdf} & \includegraphics[width=2.2in]{1dpdfs/dec.pdf} & \includegraphics[width=2.2in]{1dpdfs/m2.pdf}
-%\end{array}$
-\caption{Marginalized 1D posterior probability density functions taken from a typical 
-$1.4M_{\odot}/1.4M_{\odot}$ BNS system.  We have plotted each of the 9 parameters for 
-our non-spinning BNS problem as stated in section \ref{waveformSection}.  Note how, 
-even for parameters with excellent recovery, the peak of the 1D Gaussian is displaced from 
-the injected value (in dashed red).  This is not due to a systematic bias, but is caused by the 
-marginalization of a single dimension from the full 9D posterior space.  To better see this effect, 
-compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in Figure~\label{9dPDF}}
-\end{figure*}
-
-Of the 9 parameters in the domain of the waveform, only 6 are particularly physically
-interesting: the masses of the two binaries, $M_1$ and $M_2$, the orbital inclination,
-$\iota$, the angular position on the sky, $\alpha$ and $\delta$, and the luminosity 
-distance of the source, $D$.  While the coalescence phase $\phi_c$, the coalescence time
-$t_c$, and the wave polarization $\psi$ must be included in any parameter estimation of the 
-waveform, they do not encode any information of particular astrophysical interest.
-\footnote{For systems whose components are non-spinning.  The presence of intrinsic angular 
-momentum will, in general, couple to the coalescence phase and wave polarization.}
-
-In Figure~\ref{9dPDF}, we provide an example of the 9, 1-dimensional marginalized posterior 
-probability density functions recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system. 
- These PDFs are typical of what will be produced by parameter estimation studies in the advanced 
- detector era.  Notice that the peak of several parameters, including the chirp mass, $\chmass$, 
- appears to be displaced from the true values in red.  This effect is due to the reduction of the
-  9-dimensional PDF to a series of marginalized 1-dimensional PDFs.  For instance, the 1-dimensional 
-  PDF for chirp mass is marginalized via
-
-\begin{equation}
-p(\chmass | s) = \int _{\thpara \setminus \chmass} p(\thpara | s)~d(\thpara \setminus \chmass)
-\label{mcMarginalization}
-\end{equation}
-
-\noindent where the notation $\thpara \setminus \chmass$ implies all
-parameter of \eqref{parameterspace} except $\chmass$.  Other parameter and higher-dimensional marginalizations follow a similar convention.
-
-\subsection{Mass Parameters}
-\label{massSection}
-
-\begin{figure}[h!]
-  \centering
- \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{1414masses2D.pdf}
- \caption{2D marginalized posterior probability density functions for the mass parameters recovered in typical a $1.4M_{\odot}/1.4M_{\odot}$ system.
-The posteriors are plotted in terms of parameters used in the waveform, chirp mass ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual component masses of the binary ($M_1$ and $M_2$).
-In the $\chmass$-$q$ space, the posterior would resemble a Gaussian if not for the limitation of $q \leq 1$.
-The presence of the $q$ cutoff and the convention that $M_1 \geq M_2$ inform the non-Gaussian features present.
-When projected as 1D marginalized posteriors, the component masses resemble the posterior PDFs shown in figure \ref{metaMassPDFs}.}
-  \label{1414masses}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
- \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{125masses2D.pdf}
- \caption{Similar to Figure~\ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.
-The unequal mass ratio displaces the posterior PDFs from the $q \leq 1$ present in the equal mass case, yielding a Gaussian PDF in both the $\chmass$-$q$ and $M_1$-$M_2$ spaces.}
-  \label{125masses}
-\end{figure}
-
-\begin{figure*}[ht!]
-  \centering
- \includegraphics[trim=2cm 0cm 2cm 0cm, clip=false,scale=0.7]{newMasses.pdf}
- \caption{Mass PDFs for the four BNS systems, averaged over each of the 40 injections.
-The average is reported since, in practice, there was virtually no difference between the recovered PDFs for different systems with identical masses and SNRs \carl{[QUANTIFY]}.
-Notice how the PDFs for systems with identical mass ratios but different total masses are identical when normalized to the true total mass.}
-  \label{metaMassPDFs}
-\end{figure*}
-
-Of the 9 variables in our parameter space \eqref{parameterspace}, the two of immediate physical
-interest are the two parameters, $\chmass$ and $q$, or correspondingly the direct masses 
-of the two companions, $M_1$ and $M_2$.    As stated above, the ability of
-Advanced LIGO/VIRGO to construct a population of BNS masses will be critical to the science
-potential of gravitational-wave astronomy.
-
-We find that there is virtually no difference between the mass PDFs of our different injected signals
-within each mass bin.
-While this may initially seem disconcerting, it is to be expected.
-Recall that of the BNS signals were injected with a network SNR of 20 into a zero-noise detector realization.
-Furthermore, note that the mass parameters are the only two which directly effect the phase of the TaylorF2 waveform \eqref{phase}.
-Therefore, as long as the injected mass parameters are identical within each mass system, and as long as the injected SNR is identical, the amount of recoverable information in each mass parameter should be \emph{almost} identical, and for a sufficiently converged MCMC chain, the recovered posterior PDF should be \emph{almost} identical.
-
-The ``almost'' in the previous sentence is to draw attention to one critical, neglected fact: while the mass parameters are independent of the injected signals position with respect to the detector network, the other parameters are certainly not.
-Obviously many of the other parameters (i.e.
-sky location, polarization, distance, inclination, and time-of-arrival) all depend on the orientation of the binary with respect to each of the individual detectors.
-Since our 9-dimensional parameter space can be highly correlated, it is entirely reasonable to assume that cross-correlations between the extrinsic parameters and the mass parameters will cause variation in the recovery of the individual injection PDFs.
-
-In practice, it was found that the cross-correlations between the extrinsic parameters and signal time-of-arrival were several orders of magnitude \carl{[QUANTIFY]} below the uncertainties in $\chmass$ and $q$.
-It should be noted that, in practice, this will \emph{not} be the case: in reality, the noise power-spectral density of each detector varies as a function of time, including both natural variations in sensitivity and detector glitches \carl{[CITE]}.
-In such a case, the base sensitivity of a gravitational-wave detector to even the easiest to recover parameters will vary as a function of position and time.
-
-In Figures~\ref{1414masses} and~\ref{125masses}, we show the marginalized 2D posterior PDFs of our mass parameters a prototypical equal mass and unequal mass binaries.
-We include the PDF in both the $\chmass$-$q$ space (relevant for the waveform and the MCMC algorithm), and the more physically interesting component mass space ($M_1$-$M_2$).
-Although only the $1.4M_{\odot}/1.4M_{\odot}$ system is included in Figure \ref{1414masses}, the PDF is virtually identical to the other equal mass cases, modulo a scaling factor.
-Again, this is unsurprising due to the identical SNR of each of the injected signals.
-
-As the PDFs of the masses are virtually identical, we average the 1-dimensional mass PDFs into a single posterior probability for
-system.
-See Figure~\ref{metaMassPDFs}.
-Notice how when averaged and normalized to the injected values, the recovery of the component masses depends only on the mass ratio.
-Furthermore, for systems of equal masses, the posterior barely extends beyond 15\% of the injected values (see also Table~\ref{ciTable} in Section~\ref{ciSection}).
-If one assumes that the threshold between black holes and neutron stars lies at approximately $3M_{\odot}$ \carl{[CITE WILL]}, then it will be possible to reliably distinguish the components of each inspiral as a neutron star.
-
-\subsection{Inclination and Distance}
-\label{idSection}
-
-\begin{figure}[h!]
-  \centering
- \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.8]{distIota2D.pdf}
- \caption{Typical marginalized 2D mass PDFs for luminosity distance $D$ and orbital inclination $\iota$. }
- \label{distIotaPDF}
-\end{figure}
-
-Since it is assumed that binary neutron star systems (along with neutron star/black hole systems) are the progenitors for short gamma-ray bursts, emitting the burst along the axis of orbital angular momentum, the inclination of the binary system will be of particular interest to gamma-ray astronomy \carl{[CITE]}.
-The inclination is detected as a relative amplitude difference between the two gravitational-wave polarization, such that to lowest order
-
-\begin{align}
-h_+(f) &= \frac{1+\cos^2(\iota)}{2 D} \tilde{h}(f) \nonumber \\
-h_\times(f) &= i \frac{\cos(\iota)}{D}\tilde{h}(f)
-\end{align}
-
-\noindent It should be apparent that the luminosity distance $D$ and the inclination $\iota$ can be highly correlated in any parameter estimation study, given that both terms modulate the amplitude of a gravitational wave \carl{[QUANTIFY THIS]},
-
-Given this degeneracy, it should come as no surprise that the 2D marginalized posteriors of distance and inclination are the worst of the 6 
-parameters of physical interest.  Four typical 2D PDFs are presented in Figure~\ref{distIotaPDF}.  Notice the large, bimodal uncertainties 
-present in some of the 2D PDFs along the $\iota$ axis, due to the similarity between the evaluated likelihoods at $\iota$ and $\iota + \pi/2$. 
- As the majority of the information extracted via parameter estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$
- space will be limited, even during the Advanced LIGO/VIRGO era; however, there will be cases (such as the first PDF in Figure~\ref{distIotaPDF}) 
- that will prove copacetic to simultaneous measurements accurate enough for coincidence measurements with GRB observers.
-
-\subsection{Sky Localization}
-\label{skySection}
-
-Unlike the mass parameters, the recovery of the position on the sky is highly dependent 
-on the location of the source with respect to the detector network in question. 
-For the HLV configuration, the three-detector network can only localize signals to one of
-two points in the sky.  That is, when using only time-of-arrival information, there is 
-equal support in the probability density functions at the true location and at the 
-point reflected through the plane formed by the three detectors.  In practice, 
-correlated information from the wave polarization can break this degeneracy, so for runs in 
-zero noise, the MCMC properly explores the correct peak on the sky.
-
-The sky location uncertainties for HLV and HLVI are shown in Figures \ref{2525SkyLocHLV}
- and \ref{2525SkyLocHLVI} respectively.  We show all four mass bins together, since in practice
-  the mass of the signals had no effect on the recovery of the sky location.  Only the location on 
-  the sky, the network configuration, and the other extrinsic parameters were found to be relevant.  
-  In particular, notice the increase in efficiency between the HLV configuration and the HLVI 
-  configuration.  This is hardly surprising, since four detectors allows one to accurately isolate
-   any signal using time-of-arrival.  In the case of the three-detector configuration, there exist locations 
-   in the sky in which a signal is close to its degeneracy point (the point reflected through the plane
-    of the three detectors).  The posteriors recovered for signals from these locations tend to appear
-     stretched, achieving posterior support at both points.  See  \carl{[CITE FAIRHURST]} for a global 
-     analysis of time-of-arrival accuracy for various network configurations, and \carl{[LIGO INDIA PAPER]}
-
-\begin{figure*}[ht!]
-  \centering
- \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm 0cm]{2p5_2p5_HLV.pdf}
- \caption{The uncertainty on the sky of 160 BNS systems in the HLV detector configuration.
-Each region represents a single injection, with the colored central region representing the 65\% uncertainty region on the sphere, and the gray region representing the 90\% uncertainty region.
-The color scheme indicates the total solid angle size of the 65\% region.
-Note the similar shape of the uncertainty regions at particular points; this is due to the specific realization of our network pattern sensitivity.}
- \label{2525SkyLocHLV}
-\end{figure*}
-
-\begin{figure*}[ht!]
-  \centering
- \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm 0cm]{2p5_2p5_HLVI.pdf}
- \caption{The same as Fig \ref{2525SkyLocHLV}, except for the HLVI detector configuration.
-Note the substaintally lower average uncertainties on the skies for the majority of the injections.
-Also note the lack of large, ``banana-shaped'' uncertainties that were recovered by the HLV configuration.
-The two improvements are due to the breaking of the degeneracy in sky location recovery that is facilitated by the transition to a four-detector network.}
- \label{2525SkyLocHLVI}
-\end{figure*}
-
+\begin{comment}
 \subsection{Testing MCMC Convergence}
@@
 Each set of MCMC samples is tested for convergence by examining both the Gelman-Rubin diagnostic and the auto-correlation length of the MCMC chains, the details of which can be found in \carl{[CITE]} and \carl{[CITE]}, respectively.
-However, there is an additional check we can consider: the standard matched filtering searches employed by the LIGO/VIRGO collaboration assume that a detection will occur when one of the template waveforms matches the detector data with a signal overlap of 97\% or better \carl{[CITE]}.
+However, there is an additional check we can consider: the standard matched filtering searches employed by the LIGO/Virgo collaboration assume that a detection will occur when one of the template waveforms matches the detector data with a signal overlap of 97\% or better \carl{[CITE]}.
 That is, for a template waveform $h^{t}(f)$ and detector output $s(f)$, an overlap of
@@
 \carl{[THIS SECTION INCOMPLETE  WILL REQUIRE THE FINISHED HLV/HLVI RUNS BEFORE I CAN COMPLETE IT]}
+\end{comment}
+
+\section{Results}
+\label{resultsSection}
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[trim=7cm 0cm 0cm 0cm, clip=true,scale=0.55]{9dpdf.pdf}
+%\begin{array}{ccc} 
+%\includegraphics[width=2.2in]{1dpdfs/mc.pdf} &\includegraphics[width=2.2in]{1dpdfs/eta.pdf}  & \includegraphics[width=2.2in]{1dpdfs/m1.pdf}\\
+%\includegraphics[width=2.2in]{1dpdfs/time.pdf} &\includegraphics[width=2.2in]{1dpdfs/dist.pdf}  &\includegraphics[width=2.2in]{1dpdfs/iota.pdf}\\
+%\includegraphics[width=2.2in]{1dpdfs/ra.pdf} & \includegraphics[width=2.2in]{1dpdfs/dec.pdf} & \includegraphics[width=2.2in]{1dpdfs/m2.pdf}
+%\end{array}$
+\caption{Marginalized 1D posterior probability density functions taken from a typical 
+$1.4M_{\odot}/1.4M_{\odot}$ BNS system.  We have plotted each of the 9 parameters for 
+our non-spinning BNS problem as stated in section \ref{waveformSection}.  Note how, 
+even for parameters with excellent recovery, the peak of the 1D Gaussian is displaced from 
+the injected value (in dashed red).  This is not due to a systematic bias, but is caused by the 
+marginalization of a single dimension from the full 9D posterior space.  To better see this effect, 
+compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in Figure~\label{9dPDF}}
+\end{figure*}
+
+Of the nine parameters in the domain of the waveform, only six are particularly physically
+interesting: the masses of the two binaries, $M_1$ and $M_2$, the orbital inclination,
+$\iota$, the angular position on the sky, $\alpha$ and $\delta$, and the luminosity 
+distance of the source, $D$.  While the coalescence phase $\phi_c$, the coalescence time
+$t_c$, and the wave polarization $\psi$ must be included in any parameter estimation of the 
+waveform, they do not encode any information of particular astrophysical interest.
+\footnote{For systems whose components are non-spinning.  The presence of intrinsic angular 
+momentum will, in general, couple to the coalescence phase and wave polarization.}
+
+In Figure~\ref{9dPDF}, we provide an example of the nine, 1-dimensional marginalized posterior 
+probability density functions recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system. 
+ These PDFs are the typical of the type of results that will be produced by parameter estimation
+  studies in the advanced  detector era.  Notice that the peak of several parameters, including the 
+  chirp mass, $\chmass$,  appears to be displaced from the true values in red.  This effect is due to 
+  the reduction of the  9-dimensional PDF to a series of marginalized 1-dimensional PDFs. 
+   For instance, the 1-dimensional PDF for chirp mass is marginalized via
+
+\begin{equation}
+p(\chmass | s) = \int _{\thpara \setminus \chmass} p(\thpara | s)~d(\thpara \setminus \chmass)
+\label{mcMarginalization}
+\end{equation}
+
+\noindent where the notation $\thpara \setminus \chmass$ implies all
+parameter of \eqref{parameterspace} except $\chmass$.  Other parameter and higher-dimensional marginalizations follow
+ a similar convention.  In practice, the MCMC samples make this integral trivial: since the samples are distributed according 
+to the posterior, \eqref{mcMarginalization} can be calculated by simply reading off the relevant samples in a single parameter, 
+implicitly calculating a Monte-Carlo integral over all other parameters.
+
+\subsection{Mass Parameters}
+\label{massSection}
+
+\begin{figure}[h!]
+  \centering
+ \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{1414masses2D.pdf}
+ \caption{2D marginalized posterior probability density functions for the mass parameters recovered in typical a $1.4M_{\odot}/1.4M_{\odot}$ system.
+The posteriors are plotted in terms of parameters used in the waveform, chirp mass ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual component masses of the binary ($M_1$ and $M_2$).
+In the $\chmass$-$q$ space, the posterior would resemble a Gaussian if not for the limitation of $q \leq 1$.
+The presence of the $q$ cutoff and the convention that $M_1 \geq M_2$ inform the non-Gaussian features present.
+When projected as 1D marginalized posteriors, the component masses resemble the posterior PDFs shown in figure \ref{metaMassPDFs}.}
+  \label{1414masses}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+ \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{125masses2D.pdf}
+ \caption{Similar to Figure~\ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.
+The unequal mass ratio displaces the posterior PDFs from the $q \leq 1$ present in the equal mass case, yielding a Gaussian PDF in both the $\chmass$-$q$ and $M_1$-$M_2$ spaces.}
+  \label{125masses}
+\end{figure}
+
+\begin{figure*}[ht!]
+  \centering
+ \includegraphics[trim=2cm 0cm 2cm 0cm, clip=false,scale=0.7]{newMasses.pdf}
+ \caption{Mass PDFs for the four BNS systems, averaged over each of the 40 injections.
+The average is reported since, in practice, there was quantitatively no difference between the recovered PDFs for different systems with identical masses and SNRs.
+Notice how the PDFs for systems with identical mass ratios but different total masses are identical when normalized to the true total mass.}
+  \label{metaMassPDFs}
+\end{figure*}
+
+Of the nine variables in our parameter space \eqref{parameterspace}, the two of immediate physical
+interest are the two parameters, $\chmass$ and $q$, or correspondingly the direct masses 
+of the two companions, $M_1$ and $M_2$.    As stated above, the ability of
+Advanced LIGO/Virgo to construct a population of BNS masses will be one of the more useful applications
+of gravitational-wave astronomy.
+
+We find that there is virtually no difference between the mass PDFs of our different injected signals
+within each mass bin.
+While this may initially seem disconcerting, it is to be expected.
+Recall that of the BNS signals were injected with a network SNR of 20 into a zero-noise detector realization.
+Furthermore, note that the mass parameters are the only two which directly effect the phase of the TaylorF2 waveform \eqref{phase}.
+Therefore, as long as the injected mass parameters are identical within each mass system, and as long as the injected SNR is identical, the amount of recoverable information in each mass parameter should be almost identical, and for a sufficiently converged MCMC chain, the recovered posterior PDF should be identical.
+
+This effect can be summarized as follows: for non-spinning systems, the posterior probability of the masses,
+$p(\chmass, q | s)$, does not depend strongly on the recovery of the extrinsic parameters, $\phi_0$ or $t_c$.  Therefore, 
+systems with identical masses will produce identical mass PDFs.  The only noticeable difference will come from
+ the specific realization of noise produced by the detector, which we address in Section \ref{noiseSection}.
+
+%The ``almost'' in the previous sentence is to draw attention to one critical, neglected fact: while the mass parameters are independent of the injected signals position with respect to the detector network, the other parameters are certainly not.
+Obviously many of the other parameters (i.e.
+sky location, polarization, distance, inclination, and time-of-arrival) all depend on the orientation of the binary with respect to each of the individual detectors.
+Since our 9-dimensional parameter space can be highly correlated, it is entirely reasonable to assume that cross-correlations between the extrinsic parameters and the mass parameters will cause variation in the recovery of the individual injection PDFs.
+
+%In practice, it was found that the cross-correlations between the extrinsic parameters and signal time-of-arrival were several orders of magnitude \carl{[QUANTIFY]} below the uncertainties in $\chmass$ and $q$.
+It should be noted that, in practice, this will \emph{not} be the case: in reality, the noise power-spectral density of each detector varies as a function of time, including both natural variations in sensitivity and detector glitches \carl{[CITE]}.
+In such a case, the base sensitivity of a gravitational-wave detector to even the easiest to recover parameters will vary as a function of position and time.
+
+In Figures~\ref{1414masses} and~\ref{125masses}, we show the marginalized 2D posterior PDFs of our
+ mass parameters for  prototypical equal mass and unequal mass binaries.  We include the PDF in both
+  the $\chmass$-$q$ space (relevant for the waveform and the MCMC algorithm), and the more physically 
+  interesting component mass space ($M_1$-$M_2$).  Although only the $1.4M_{\odot}/1.4M_{\odot}$ system
+   is included in Figure \ref{1414masses}, the PDF is quantitatively identical to the other equal mass cases, 
+   modulo a scaling factor.
+
+To condense the results into a single figure of merit, we average the 1-dimensional mass PDFs into a single 
+posterior probability for system.  See Figure~\ref{metaMassPDFs}.  Notice how when averaged and
+ normalized to the injected values, the recovery of the component masses depends only on the mass ratio.  
+ Furthermore, for systems of equal masses, the posterior barely extends beyond 15\% of the injected values.  
+ If one assumes that the threshold between black
+   holes and neutron stars lies at approximately $3M_{\odot}$ \carl{[CITE WILL]}, then it might be assumed that
+   the mass recovery would allow one to discriminate between black holes and neutron stars.
+
+Unfortunately, this will not be feasible in practice.  We have neglected the spin of the binaries, which will be highly
+correlated to the masses.  This coupling means that a higher-massed spinning black hole systems can produce
+ waveforms very similar to non-spinning, low-mass, making it impossible to discern between non-spinning neutron stars
+ and spinning, more massive black holes.  However, the situation is not hopeless: if the spins are misaligned, the spin 
+ vectors will couple to the orientation of the binary (encoded in the three angles $\phi_0$, $\iota$, and $\psi$) via
+ relativistic precession.  It remains to be seen if using fully spinning waveforms will make it possible for Advanced\
+  LIGO/Virgo to discern binary neutron stars from their spinning black hole counterparts.
+
+In Table \ref{ciTableIntrinsic}, we list the 65\% fractional confidence intervals for the mass parameters.  We find that the 
+component masses for equal mass systems can be isolated to between 6\% and 9\% fractional uncertainty at the 65\% confidence interval.
+This value drops to less than 2\$ for the components of the unequal mass systems.
+Again, this
+neglects the effects of spin which can substantially increase these values.
+
+\subsection{Inclination and Distance}
+\label{idSection}
+
+\begin{figure}[h!]
+  \centering
+ \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.8]{distIota2D.pdf}
+ \caption{Typical marginalized 2D mass PDFs for luminosity distance $D$ and orbital inclination $\iota$. }
+ \label{distIotaPDF}
+\end{figure}
+
+Binary neutron star systems (along with neutron star/black hole systems) are one of the best candidates for progenitors of short gamma-ray bursts \carl{CITE}.
+After merger, the remnant is believed to emit the burst along the axis of orbital angular momentum, making the inclination of the binary system of particular interest to gamma-ray astronomy \carl{[CITE]}.
+The inclination is detected as a relative amplitude difference between the two gravitational-wave polarization, such that to lowest order
+
+\begin{align}
+h_+(f) &= \frac{1+\cos^2(\iota)}{2 D} \tilde{h}(f) \nonumber \\
+h_\times(f) &= i \frac{\cos(\iota)}{D}\tilde{h}(f)
+\end{align}
+
+\noindent It should be apparent that the luminosity distance $D$ and the inclination $\iota$ can be highly correlated in any parameter estimation study, given that both terms modulate the amplitude of a gravitational wave \carl{[QUANTIFY THIS]},
+
+Given this degeneracy, it should come as no surprise that the 2D marginalized posteriors of distance
+ and inclination are the worst of the six physically interesting parameters.  Four typical 2D PDFs are
+  presented in Figure~\ref{distIotaPDF}.  Notice the large, bimodal uncertainties 
+present in some of the 2D PDFs along the $\iota$ axis, due to the similarity between the evaluated
+ likelihoods at $\iota$ and $\iota + \pi/2$.  As the majority of the information extracted via parameter 
+ estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$ space will be 
+ limited, even during the Advanced LIGO/Virgo era; however, there will be cases (such as the first 
+ PDF in Figure~\ref{distIotaPDF})  that will prove copacetic to simultaneous measurements accurate 
+ enough for coincidence measurements with GRB observers.  Conversely, if a gravitational-wave signal is 
+ matched to a detected GRB counterpart, the optical information about the orbital inclination
+ will provide an additional constraint on the D-$\iota$ space to vastly improve the results quoted here.
+
+In Table \ref{ciTableExtrinsic}, we list the averaged 65\% confidence intervals for distance and inclination.  
+Notice that, while the uncertainties on distance can be extreme, from tens to hundreds of $mpc$, the uncertainties
+on inclination are reasonably small\carl{[QUANTIFY THIS WITH CORRECT JACOBIAN]}.  If it is assumed that a
+ compact object generated GRB maintains bipolar symmetry, the the quantity of interest is $|\cos(\iota)|$, not 
+ $\iota$, since observing a compact merger at $\iota$ and $\iota + \pi/2$ should produce identical optical counterparts.  
+Since $|\cos(\iota)|$ maps the bi-modal structure in the inclination PDFs seen in Figure \ref{distIotaPDF} to a single
+mode, the uncertainties in $\iota$ will sufficiently small \carl{[QUANTIFY]} to provide coincident information on
+GRB beaming angles.
+
+\subsection{Sky Localization}
+\label{skySection}
+
+Unlike the mass parameters, the recovery of the position on the sky is highly dependent 
+on the location of the source with respect to the detector network in question. 
+For the HLV configuration, the three-detector network can only localize signals to one of
+two points in the sky.  That is, when using only time-of-arrival information, there is 
+equal support in the probability density functions near true location and near the 
+point reflected through the plane formed by the three detectors.  See  \carl{[CITE FAIRHURST]} for
+ a global analysis of time-of-arrival accuracy for various network configurations, including those considered
+ here.
+
+  In practice, however, additional information from the wave polarization, can break this plane-reflected degeneracy,
+   leading to a bi-modal distribution with significantly more support in one mode of the PDF.
+     By fitting for the sky location and the polarization simultaneously, the MCMC can identify
+   the correct mode on the sky.  For the four-detector configuration, this concern is irrelevant: even with time-of-arrival
+   data alone, the HLVI network can constrain any source to a single mode on the sky.  Even then, there are still locations 
+   on the sky in which two or more detectors are not sensitive to the gravitational-wave signal, distorted, non-Gaussian PDFs.
+
+The sky location uncertainties for HLV and HLVI are shown in Figures \ref{2525SkyLocHLV}
+ and \ref{2525SkyLocHLVI} respectively.  We show all four mass bins together, since in practice
+  the mass of the signals has no effect on the recovery of the sky location.  Only the location on 
+  the sky, the network configuration, and the other extrinsic parameters were found to be relevant.  
+  In particular, notice the increase in efficiency between the HLV configuration and the HLVI 
+  configuration.  In the HLV configuration, there exist points on the sky in which the signal was injected
+  near the plane of the detector network.  This causes the elongated, ``banana-shaped'' PDFs seen in
+  Figure \ref{2525SkyLocHLV}.  In the HLVI configuration, the plane is no longer relevant, and there are substantially
+  less regions in which only two detectors see a sufficiently strong signal.  
+  See \cite{Veitch2012} for a more detailed comparison of the sky-localization benefits of the HLVI 
+  configuration verses the three-detector network.  As previously, the quantitative results for the two network configurations
+  are reported in Table \ref{ciTableExtrinsic}.
+
+\begin{figure*}[ht!]
+  \centering
+ \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm 0cm]{HLVsky.pdf}
+ \caption{The uncertainty on the sky of 160 BNS systems in the HLV detector configuration.
+Each region represents a single injection, with the colored central region representing the 65\% uncertainty region on the sphere, and the gray region representing the 90\% uncertainty region.
+The color scheme indicates the total solid angle size of the 65\% region.
+Note the similar shape of the uncertainty regions at particular points; this is due to the specific realization of our network pattern sensitivity.}
+ \label{2525SkyLocHLV}
+\end{figure*}
+
+\begin{figure*}[ht!]
+  \centering
+ \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm 0cm]{HLVIsky.pdf}
+ \caption{The same as Fig \ref{2525SkyLocHLV}, except for the HLVI detector configuration.
+Note the substaintally lower average uncertainties on the skies for the majority of the injections.
+Also note the lack of large, ``banana-shaped'' uncertainties that were recovered by the HLV configuration.
+The two improvements are due to the breaking of the degeneracy in sky location recovery that is facilitated by the transition to a four-detector network.}
+ \label{2525SkyLocHLVI}
+\end{figure*}
 
@@
 
-While we have, for a variety of reasons, performed the current analysis on zero-noise injections,
-parameter estimation in the advanced detector error will not be so copacetic. 
+We have performed the current analysis on zero-noise injections for two reason.  First, the results of a zero-noise realization
+analysis are identical to those that would be achieved by averaging the results of multiple identical injections 
+in different Gaussian noise realizations, as was argued in Section \ref{waveformSection}.  The second reason is simply
+that no good model exists for the true (decidedly non-Gaussian) noise that will arrive with a single detection candidate,
 Each detection will occur in noisy data, with a specific realization of the PSD provided and with 
@@
 The parameter estimation techniques described here will be performed as a follow-up analysis
-to the detections returned by various on-line analyses in the Advanced LIGO/VIRGO era.  While
+to the detections returned by various on-line analyses in the Advanced LIGO/Virgo era.  While
 there exist specific PE analyses that will be performed in real-time for time sensitive signals 
@@
 
-The correct answer to the question ``how well can Advanced LIGO/VIRGO measure the parameters of binary neutron star systems'' is the full 9-dimensional PDFs; however, for both convenience and comparison, it is useful and elucidating to speak in terms of the confidence intervals of a single parameter.
-To that end, we state the averaged 65\% and 90\% confidence intervals about the single parameters for each of the three parameter pairs of interest.
-These were already plotted for the sky locations in Figures~\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI}.
+When quoting parameter estimation results, it is often convienant to reduce the full parameter space to
+confidence intervals about single, marginalized parameters..  To that end, we state the averaged 65\% 
+confidence intervals about the single parameters for each of the three parameter pairs of interest.  These were already
+ plotted for the sky locations in Figures~\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI}.
 
-There are several different ways of computing the width of a confidence interval in this setup.
-If one considers the points in the MCMC as random draws from the true posterior, then the $\alpha$-level confidence interval can be computed by simply ordering the points, removing $N(1-\alpha )/2$ points from both sides of the posterior samples symmetrically, and measuring the width of the remaining points.
-While this procedure can prove hazardous for multi-modal distributions, it is straightforward and reliable for single-peaked distributions as reported here.
+There are several different ways of computing the width of a confidence interval in this setup.  If one considers the points in
+ the MCMC as random draws from the true posterior, then the $\alpha$-level confidence interval can be computed by simply
+  ordering the points, removing $N(1-\alpha )/2$ points from both sides of the posterior samples symmetrically, and measuring
+   the width of the remaining points.  While this procedure can prove hazardous for multi-modal distributions, it is 
+   straightforward and reliable for single-peaked distributions as reported here.
 
-In Table~\ref{ciTable}, we list the mean 65\% confidence intervals recovered for the four mass configurations in both network configurations. 
-This essentially quantifies the widths of the posteriors plotted throughout Section~\ref{resultsSection}.  Again, it is worth noting how the small confidence
-intervals on the individual component masses suggest it will be possible, on average, to discern neutron stars from black holes in binary inspirals.  
-The purpose of Table~\ref{ciTable} is to provide a quantitative and quotable source for studies seeking to determine how well a physical question
-about BNS systems can be answered with the Advanced LIGO/VIRGO network.
+In Table~\ref{ciTableIntrinsic}, we list the mean 65\% confidence intervals recovered for the four mass configurations in both 
+network configurations. This essentially quantifies the widths of the posteriors plotted throughout Section~\ref{resultsSection}.
+  The purpose of Tables~\ref{ciTableIntrinsic} and \ref{ciTableExtrinsic} is to provide a quantitative and quotable source for studies seeking to determine how 
+  well a physical question about BNS systems can be answered with the Advanced LIGO/Virgo network.
 
@@
 \centering
-\caption{\carl{65\% confidence intervals, but since they're incomplete these are just place holders for now (the real ones will have upper and lower bounds, as well as units, normalization to the injected values, 2d sky areas, and component masses) also, double check the ra on 2.5 2.5 HLVI}}
-\begin{tabular}{lcccccccccccc}
+\caption{\carl{65\% confidence intervals}}
+\begin{tabular}{lcccccccccc}
 
@@
 \hline\hline
-System & \vline &  $\Delta \chmass$ & \vline & $\Delta q$ & \vline & $\Delta D$ & \vline & $\Delta \iota$ & \vline & $\Delta \alpha$ & \vline &  $\Delta \delta$\\
+System & \vline &  $\Delta \chmass / \chmass$ & \vline & $\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline & $\Delta M_{tot}/M_{tot}$ & \vline & $\Delta q$\\
 \hline\hline
-$1M_{\odot}-1M_{\odot}$ & \vline & $4.33\times10^{-5}$ & \vline & $0.123$& \vline & $39.1$ & \vline & $0.45$ & \vline & $0.028$ & \vline & 0.028\\
+$1M_{\odot}-1M_{\odot}$ & \vline & $4.70\times 10^{-5}$ & \vline & $6.83\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline & $3.67\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$\\
 \hline
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $1.07\times10^{-4}$ & \vline & 0.13 & \vline & 60.3 & \vline & 0.45 & \vline & 0.028 & \vline & 0.028\\
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.27\times 10^{-5}$ & \vline & $7.27\times 10^{-2}$ & \vline & $6.45\times 10^{-2}$ & \vline & $4.10\times 10^{-3}$ & \vline & $1.24\times 10^{-1}$ \\
 \hline
-$1M_{\odot}-2.5M_{\odot}$ & \vline & $2.37\times10^{-4}$ & \vline & 0.014 & \vline & 70.13 & \vline & 0.52 & \vline & 0.029 & \vline &0.030\\
-\hline
-$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $0.53\times10^{-4}$ & \vline & 0.15 & \vline & 111.67 & \vline & 0.56 & \vline & 0.18 & \vline & 0.030 \\
+$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline & $1.74\times 10^{-2}$ & \vline & $1.49\times 10^{-2}$ & \vline & $8.15\times 10^{-3}$ & \vline & $1.29\times 10^{-2}$\\\hline
+$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.29\times 10^{-4}$ & \vline & $8.52\times 10^{-2}$ & \vline & $7.41\times 10^{-2}$ & \vline & $5.51\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$\\
 \hline\hline
@@
 \hline\hline
-System & \vline &  $\Delta \chmass$ & \vline & $\Delta q$ & \vline & $\Delta D$ & \vline & $\Delta \iota$ & \vline & $\Delta \alpha$ & \vline &  $\Delta \delta$\\
+System & \vline &  $\Delta \chmass / \chmass$ & \vline & $\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline & $\Delta M_{tot}/M_{tot}$ & \vline & $\Delta q$\\
 \hline\hline
-$1M_{\odot}-1M_{\odot}$ & \vline & $4.33\times10^{-5}$ & \vline & $0.123$& \vline & $46.14$ & \vline & $0.55$ & \vline & $0.26$ & \vline & 0.11\\
+$1M_{\odot}-1M_{\odot}$ & \vline & $4.66\times 10^{-5}$ & \vline & $6.82\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline & $3.64\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$ \\
 \hline
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $1.08\times10^{-4}$ & \vline & 0.13 & \vline & 56.3 & \vline & 0.57 & \vline & 0.125 & \vline & 0.130\\
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.31\times 10^{-5}$ & \vline & $7.35\times 10^{-2}$ & \vline & $6.51\times 10^{-2}$ & \vline & $4.18\times 10^{-3}$ & \vline & $1.25\times 10^{-1}$\\
 \hline
-$1M_{\odot}-2.5M_{\odot}$ & \vline & $2.37\times10^{-4}$ & \vline & 0.014 & \vline & 66.05 & \vline & 0.66 & \vline & 0.05 & \vline &0.070\\
+$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline & $1.75\times 10^{-2}$ & \vline & $1.50\times 10^{-2}$ & \vline & $8.19\times 10^{-3}$ & \vline & $1.30\times 10^{-2}$ \\
 \hline
-$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $0.53\times10^{-4}$ & \vline & 0.15 & \vline & 109.5 & \vline & 0.70 & \vline & 0.20 & \vline & 0.06 \\
+$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.30\times 10^{-4}$ & \vline & $8.53\times 10^{-2}$ & \vline & $7.42\times 10^{-2}$ & \vline & $5.52\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$ \\
 \hline\hline
@@
 \end{tabular}
-\label{ciTable}
+\label{ciTableIntrinsic}
+\end{table*}
+
+\begin{table*}[t!]
+\centering
+\caption{\carl{65\% confidence intervals ADD SKY LOCATION SOLID ANGLE UNCERTAINTIES}}
+\begin{tabular}{lcccccccc}
+
+\\HLVI\\
+\hline\hline
+ System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(rad)$& \vline &  $\Delta \delta$   $(rad)$\\
+\hline\hline
+ $1M_{\odot}-1M_{\odot}$ & \vline & $3.56\times 10^{1}$ & \vline & $2.20\times 10^{-1}$ & \vline & $1.02\times 10^{-1}$ & \vline & $6.22\times 10^{-2}$ \\
+\hline
+ $1.4M_{\odot}-1.4M_{\odot}$ & \vline & $5.52\times 10^{1}$ & \vline & $2.56\times 10^{-1}$ & \vline & $2.60\times 10^{-2}$ & \vline & $2.62\times 10^{-2}$ \\
+\hline
+ $1M_{\odot}-2.5M_{\odot}$  & \vline & $6.48\times 10^{1}$ & \vline & $2.93\times 10^{-1}$ & \vline & $2.68\times 10^{-2}$ & \vline & $2.87\times 10^{-2}$ \\\hline
+ $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.06\times 10^{2}$ & \vline & $2.99\times 10^{-1}$ & \vline & $1.80\times 10^{-1}$ & \vline & $2.80\times 10^{-2}$ \\
+\hline\hline
+
+\\
+HLV\\
+
+\hline\hline
+ System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(rad)$& \vline &  $\Delta \delta$   $(rad)$\\
+\hline\hline
+ $1M_{\odot}-1M_{\odot}$ & \vline & $4.34\times 10^{1}$ & \vline & $3.04\times 10^{-1}$ & \vline & $2.53\times 10^{-1}$ & \vline & $1.09\times 10^{-1}$ \\
+\hline
+ $1.4M_{\odot}-1.4M_{\odot}$  & \vline & $5.32\times 10^{1}$ & \vline & $2.87\times 10^{-1}$ & \vline & $1.21\times 10^{-1}$ & \vline & $1.24\times 10^{-1}$ \\
+\hline
+  $1M_{\odot}-2.5M_{\odot}$& \vline & $6.13\times 10^{1}$ & \vline & $3.12\times 10^{-1}$ & \vline & $4.68\times 10^{-2}$ & \vline & $7.44\times 10^{-2}$ \\
+\hline
+ $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.04\times 10^{2}$ & \vline & $3.42\times 10^{-1}$ & \vline & $1.97\times 10^{-1}$ & \vline & $5.77\times 10^{-2}$ \\
+\hline\hline
+
+\end{tabular}
+\label{ciTableExtrinsic}
 \end{table*}
@@
 
-In this paper, we performed an MCMC parameter estimation analysis on the recoverability of basic information about binary neutron stars, using two projected version of the Advanced LIGO/VIRGO network.
-We focused on the recovery of the two masses, the luminosity distance, orbital inclination, and the sky location, as these are the six basic parameters of physical interest to the problem.
-We found that \carl{[WAIT UNTIL RUNS ARE DONE AND TABLE IS FINISHED TO SUMMARIZE RESULTS]}
+In this paper, we performed an MCMC parameter estimation analysis on the recoverability of basic information about binary 
+neutron stars, using two projected version of the Advanced LIGO/Virgo network.  We focused on the recovery of the two 
+masses, the luminosity distance, orbital inclination, and the sky location, as these are the six basic parameters of physical 
+interest to the problem.  We found that, neglecting the effects of spin, the component masses can be constrained to less
+ than 10\% of their true value to a confidence of 65\%.  This value drops below 2\% for systems with an asymmetric mass ratio.
+ These results were summarized in Table \ref{ciTableIntrinsic}
+
+We also reported on the ability of the two network configurations to constrain the
+luminosity distance and orbital inclination.  For distance, it was found that the uncertainties
+will fall anywhere from 40 to 100 MPC at 65\% confidence, making the uncertainties frequently larger than the luminosity
+distances themselves.  However, it was found that the cosine of the orbital inclination can be constrained to within 
+0.3 at the 65\% level, suggesting that Advanced LIGO/Virgo will be able to offer some information on GRB beaming
+angles in coincidence with electromagnetic observations.
+
+Finally, we reported the ability of advanced networks to constrain the sky location of BNS signals.  It was found that 
+the three detector configuration, consisting of the Washington and Louisiana LIGO sites plus the Italian Virgo site,
+ was able to constrain all signals with within 50 $deg^2$ on the sky, while the four-detector
+configuration, consisting of the three-detector sites plus a LIGO India detector, was able to localize the sky-locations
+to within \carl{[QUOTE REAL DEG2 HERE, NOT RA AND DEC]}.
 
@@
 See \carl{[CITE]} for a better description of the systematic uncertainties present in the most common waveform families.
+Additionally, there are several astrophysical assumptions that can potentially contribute
+to systematic uncertainties in the waveforms, such as the neutron-star equation of state, possible modifications to 
+General Relativity, etc.
 
-Secondly, as stated above, the noise realization that we have employed here is an substaintial idealization.
-In practice the noise levels of Advanced LIGO and Advanced VIRGO will be highly variable over time, and will \emph{not} be stationary or Gaussian, as is commonly assumed.
+Secondly, as stated above, the noise realization that we have employed here is an substantial idealization.
+In practice the noise levels of Advanced LIGO and Advanced Virgo will be highly variable over time, and will \emph{not} be stationary or Gaussian, as is commonly assumed.
 Unfortunately, there is no reliable or simple way to simulate the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.
-Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here, this effect will be critical to properly characterizing gravitational-wave detections \carl{[CITE TYSON AGAIN]}
+Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here \carl{TYSON WILL WRITE}
 
-In this study, we have ignored several of the more interesting parameters that can be included in parameter estimation, such as modifications to general relativity \carl{[CITE]} and the neutron star equation-of-state \carl{[CITE]}.
-We elected to focus on the basic parameters that will be measured routinely in the Advanced Detector era.
-Future work will explore how well these specific questions can be answered using \texttt{LALInferece}, and what prospects such parameter estimation will have for answering longstanding questions in relativistic astrophysics.
+In this study, we have also neglected the effects of spin in the parameter space, electing to focus on the absolute basic
+ parameters that will be measured routinely in the Advanced Detector era.  Given the high degree of coupling
+between the spin and the mass of objects in the gravitational-wave parameter space, it remains unclear
+if the mass measurement alone will be sufficient to distinguish non-spinning neutron stars from highly-spinning low-mass
+black holes.  Future work will explore this potential mass/spin degeneracy, with the aim of definitively answering this question.
+
+\carl{
+\section{TODO}
+ \begin{itemize}
+ \item Discuss the problem of no-spin/how that screws up our ability to constrain masses (BH vs NS)
+ \item Be sure to add links to the 1d credible intervals in the abstract, introduction, conclusion, and at the end of each subsection
+ \item Also point out how this is a idealization, not an average case (SNR 20 vs reality, again NS vs BH)
+ \item Finish adding bibliography/sources
+ \item double check the distribution of sources in Distance/Iota; make sure iota is actually uniform in cos(i)
+ \item also, check the relative SNRs in each detector for the D-i plots, see if you can tell what's making them double peaked 
+ \end{itemize}
+ }
 

### 2013-05-24 DistIotaComp.py

@@ -9,7 +9,7 @@ injected = [(100.8422,1.5548),(124.73,1.782),(170.41,2.135),(145.78,1.671)]
 #injected = [(100.8422,1.5548),(124.73,1.782),(145.78,1.671)]
 
 for j in range(4):
-		file = open('1.4_1.4/' + filenumbers[j] + '/post/posterior_samples.dat')
+		file = open('HLVI/1.4_1.4/' + filenumbers[j] + '/post/posterior_samples.dat')
 		filedata = file.readlines()
 		file.close()
 

### 2013-05-28 doc/paper.tex
finished addressing tysons comments, updating text and figures, and finalizing results with the completed runs

@@
      We also report the average uncertainties on the sky-locations, luminosity distance, and orbital inclinations of randomly 
-     distributed sources that can be achieved by different network configurations. \carl{[PUT IN SA VALUES FOR SKY LOCATION]}
+     distributed sources that can be achieved by different network configurations.
 \end{abstract}
@@
         \ref{noiseSection} we provide an example of parameter estimation in several non-zero noise realizations
-compared to the zero-noise equivelant.
+compared to the zero-noise equivalent \carl{[TYSON WILL WRITE]}.
 
@@
   \centering
- \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{1414masses2D.pdf}
+ \includegraphics[trim=1cm 0cm 2cm 0cm, clip=false,scale=0.63]{1414masses2D.pdf}
  \caption{2D marginalized posterior probability density functions for the mass parameters recovered in typical a $1.4M_{\odot}/1.4M_{\odot}$ system.
@@
   \centering
- \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{125masses2D.pdf}
+ \includegraphics[trim=1cm 0cm 2cm 0cm, clip=false,scale=0.63]{125masses2D.pdf}
  \caption{Similar to Figure~\ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.
@@
 The average is reported since, in practice, there was quantitatively no difference between the recovered PDFs for different systems with identical masses and SNRs.
-Notice how the PDFs for systems with identical mass ratios but different total masses are identical when normalized to the true total mass.}
+Systems with identical mass ratios but different total masses have quantitatively identical PDFs when normalized to the true total mass.}
   \label{metaMassPDFs}
@@
  If one assumes that the threshold between black
-   holes and neutron stars lies at approximately $3M_{\odot}$ \carl{[CITE WILL]}, then it might be assumed that
+   holes and neutron stars lies at approximately $3M_{\odot}$, then it might be assumed that
    the mass recovery would allow one to discriminate between black holes and neutron stars.
@@
   \centering
- \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.8]{distIota2D.pdf}
- \caption{Typical marginalized 2D mass PDFs for luminosity distance $D$ and orbital inclination $\iota$. }
+ \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.75]{distIota2D.pdf}
+ \caption{Typical marginalized 2D mass PDFs for luminosity distance $D$ and orbital inclination $\iota$. Notice the bimodal 
+ distribution on the first PDF, that can occur when a system is detected nearly ``edge-on'' ($\iota \approx \pi/2$).  In general,
+ the degeneracy between distance and inclination forces the PDF into one of these two paths when the system is not edge-on,
+  as seen in the second and third PDFs.}
  \label{distIotaPDF}
@@
 
-Binary neutron star systems (along with neutron star/black hole systems) are one of the best candidates for progenitors of short gamma-ray bursts \carl{CITE}.
-After merger, the remnant is believed to emit the burst along the axis of orbital angular momentum, making the inclination of the binary system of particular interest to gamma-ray astronomy \carl{[CITE]}.
+Binary neutron star systems (along with neutron star/black hole systems) are one of the best candidates for progenitors of short-hard gamma-ray bursts \citep[and references therein]{Nakar2007}.
+After merger, the remnant is believed to emit the burst along the axis of orbital angular momentum, making the inclination of the binary system of particular interest to gamma-ray astronomy \citep{LSCGRB2010,Corsi2012}.
 The inclination is detected as a relative amplitude difference between the two gravitational-wave polarization, such that to lowest order
@@
 
-\noindent It should be apparent that the luminosity distance $D$ and the inclination $\iota$ can be highly correlated in any parameter estimation study, given that both terms modulate the amplitude of a gravitational wave \carl{[QUANTIFY THIS]},
+\noindent It should be apparent that the luminosity distance $D$ and the inclination $\iota$ can be highly correlated in any parameter estimation study.
 
@@
  and inclination are the worst of the six physically interesting parameters.  Four typical 2D PDFs are
-  presented in Figure~\ref{distIotaPDF}.  Notice the large, bimodal uncertainties 
-present in some of the 2D PDFs along the $\iota$ axis, due to the similarity between the evaluated
+  presented in Figure~\ref{distIotaPDF}.  Notice the bimodal uncertainty 
+present in the top 2D PDF along the $\iota$ axis, due to the similarity between the evaluated
  likelihoods at $\iota$ and $\iota + \pi/2$.  As the majority of the information extracted via parameter 
@@
 equal support in the probability density functions near true location and near the 
-point reflected through the plane formed by the three detectors.  See  \carl{[CITE FAIRHURST]} for
+point reflected through the plane formed by the three detectors.  See  \cite{Fairhurst2011} for
  a global analysis of time-of-arrival accuracy for various network configurations, including those considered
@@
   \centering
- \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.59]{noisePDF.pdf}
+ \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.52]{noisePDF.pdf}
  \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the Advanced LIGO noise curve.
@@
 
-We have performed the current analysis on zero-noise injections for two reason.  First, the results of a zero-noise realization
+We have performed the current analysis on zero-noise injections for two reason.  First, the results of a zero-noise 
 analysis are identical to those that would be achieved by averaging the results of multiple identical injections 
@@
 
-As a demonstration of this, we injected a single $1.4M_{\odot}/1.4M_{\odot}$ system, 
+As a demonstration of this, we injected a single $1M_{\odot}/2.5M_{\odot}$ system, 
 detected in HLVI,  into 5 separate realizations of Gaussian noise colored by the Advanced LIGO PSD, 
@@
 detectors (LISA), and is currently being implemented in \texttt{lalinference\_mcmc} 
-\carl{[CITE TYSON, PROTO-TYSON]}.
+\carl{[TYSON WILL WRITE]}.
 
@@
 \centering
-\caption{\carl{65\% confidence intervals}}
+\caption{Mean 65\% confidence intervals for intrinsic parameters for each of the four systems considered.
+We report the confidence intervals of quantities measured, as well as the component masses and total mass.
+Although the results for the
+HLV and HLVI configurations are quantitatively identical, we report them separately for consistancy.}
 \begin{tabular}{lcccccccccc}
@@
 \centering
-\caption{\carl{65\% confidence intervals ADD SKY LOCATION SOLID ANGLE UNCERTAINTIES}}
-\begin{tabular}{lcccccccc}
+\caption{Mean 65\% confidence intervals of extrinsic parameters for each of the four systems considered.  As expected,
+there exists a substantial improvement in the sky localization capabilities of the four-detector HLVI configuration over
+the three-detector HLV configuration.  Note that the solid-angle sky-location confidence intervals, $\Delta\Omega$, are 
+calculated directly on the 2D sphere, not by combining the $\alpha$ and $\delta$ uncertainties.}
+\begin{tabular}{lcccccccccc}
 
@@
 \hline\hline
- System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(rad)$& \vline &  $\Delta \delta$   $(rad)$\\
+ System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline &  $\Delta \delta$   $(deg)$ & \vline & $\Delta\Omega$ $(deg^2)$\\
 \hline\hline
- $1M_{\odot}-1M_{\odot}$ & \vline & $3.56\times 10^{1}$ & \vline & $2.20\times 10^{-1}$ & \vline & $1.02\times 10^{-1}$ & \vline & $6.22\times 10^{-2}$ \\
+ $1M_{\odot}-1M_{\odot}$ & \vline & $3.64\times 10^{1}$ & \vline & $2.23\times 10^{-1}$ & \vline & $1.45$ & \vline & $1.48$ & \vline & $1.88$\\
 \hline
- $1.4M_{\odot}-1.4M_{\odot}$ & \vline & $5.52\times 10^{1}$ & \vline & $2.56\times 10^{-1}$ & \vline & $2.60\times 10^{-2}$ & \vline & $2.62\times 10^{-2}$ \\
+ $1.4M_{\odot}-1.4M_{\odot}$ & \vline & $5.52\times 10^{1}$ & \vline & $2.56\times 10^{-1}$ & \vline & $1.49$ & \vline & $1.50$ & \vline & $2.26$\\
 \hline
- $1M_{\odot}-2.5M_{\odot}$  & \vline & $6.48\times 10^{1}$ & \vline & $2.93\times 10^{-1}$ & \vline & $2.68\times 10^{-2}$ & \vline & $2.87\times 10^{-2}$ \\\hline
- $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.06\times 10^{2}$ & \vline & $2.99\times 10^{-1}$ & \vline & $1.80\times 10^{-1}$ & \vline & $2.80\times 10^{-2}$ \\
+ $1M_{\odot}-2.5M_{\odot}$  & \vline & $6.48\times 10^{1}$ & \vline & $2.93\times 10^{-1}$ & \vline & $1.54$ & \vline & $1.64$ & \vline & $2.10$\\
+ \hline
+ $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.06\times 10^{2}$ & \vline & $2.99\times 10^{-1}$ & \vline & $1.03\times 10^{1}$ & \vline & $1.61$ & \vline & $2.22$\\
 \hline\hline
@@
 \hline\hline
- System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(rad)$& \vline &  $\Delta \delta$   $(rad)$\\
+ System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline &  $\Delta \delta$   $(deg)$ & \vline & $\Delta\Omega$ $(deg^2)$\\
 \hline\hline
- $1M_{\odot}-1M_{\odot}$ & \vline & $4.34\times 10^{1}$ & \vline & $3.04\times 10^{-1}$ & \vline & $2.53\times 10^{-1}$ & \vline & $1.09\times 10^{-1}$ \\
+ $1M_{\odot}-1M_{\odot}$ & \vline & $4.34\times 10^{1}$ & \vline & $3.04\times 10^{-1}$ & \vline & $1.45\times 10^{1}$ & \vline & $6.24$ & \vline & $5.57$\\
 \hline
- $1.4M_{\odot}-1.4M_{\odot}$  & \vline & $5.32\times 10^{1}$ & \vline & $2.87\times 10^{-1}$ & \vline & $1.21\times 10^{-1}$ & \vline & $1.24\times 10^{-1}$ \\
+ $1.4M_{\odot}-1.4M_{\odot}$  & \vline & $5.32\times 10^{1}$ & \vline & $2.87\times 10^{-1}$ & \vline & $6.92$ & \vline & $7.11$ & \vline & $8.35$\\
 \hline
-  $1M_{\odot}-2.5M_{\odot}$& \vline & $6.13\times 10^{1}$ & \vline & $3.12\times 10^{-1}$ & \vline & $4.68\times 10^{-2}$ & \vline & $7.44\times 10^{-2}$ \\
+  $1M_{\odot}-2.5M_{\odot}$& \vline & $6.11\times 10^{1}$ & \vline & $3.11\times 10^{-1}$ & \vline & $2.67$ & \vline & $4.20$ & \vline & $7.39$\\
 \hline
- $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.04\times 10^{2}$ & \vline & $3.42\times 10^{-1}$ & \vline & $1.97\times 10^{-1}$ & \vline & $5.77\times 10^{-2}$ \\
+ $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.04\times 10^{2}$ & \vline & $3.42\times 10^{-1}$ & \vline & $1.13\times 10^{1}$ & \vline & $3.31$ & \vline & $6.27$\\
 \hline\hline
@@
 Finally, we reported the ability of advanced networks to constrain the sky location of BNS signals.  It was found that 
-the three detector configuration, consisting of the Washington and Louisiana LIGO sites plus the Italian Virgo site,
- was able to constrain all signals with within 50 $deg^2$ on the sky, while the four-detector
+the three-detector configuration, consisting of the Washington and Louisiana LIGO sites plus the Italian Virgo site,
+ was able to constrain all signals with within 60 $deg^2$ on the sky at the 65\% confidence interval, with an average
+65\% confidence interval of $\sim 7$ $deg^2$.  Meanwhile, the four-detector
 configuration, consisting of the three-detector sites plus a LIGO India detector, was able to localize the sky-locations
-to within \carl{[QUOTE REAL DEG2 HERE, NOT RA AND DEC]}.
+to within  13 $deg^2$ on the sky at the 65\% confidence interval, with an average
+65\% confidence interval of $\sim 2$ $deg^2$.
 
@@
 to systematic uncertainties in the waveforms, such as the neutron-star equation of state, possible modifications to 
-General Relativity, etc.
+General Relativity, eccentricity, etc.
 
@@
 Unfortunately, there is no reliable or simple way to simulate the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.
-Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here \carl{TYSON WILL WRITE}
+Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here \carl{[TYSON WILL WRITE]}
 
@@
  \begin{itemize}
- \item Discuss the problem of no-spin/how that screws up our ability to constrain masses (BH vs NS)
- \item Be sure to add links to the 1d credible intervals in the abstract, introduction, conclusion, and at the end of each subsection
- \item Also point out how this is a idealization, not an average case (SNR 20 vs reality, again NS vs BH)
  \item Finish adding bibliography/sources
  \item double check the distribution of sources in Distance/Iota; make sure iota is actually uniform in cos(i)
- \item also, check the relative SNRs in each detector for the D-i plots, see if you can tell what's making them double peaked 
  \end{itemize}

### 2013-05-28 CIcomputer.py

@@ -1,0 +1,92 @@
+#!/software/enthought/python/epd_free-7.3.2-rh6-x86_64/bin/python
+import os.path
+import numpy as np
+
+def m1m2fromMcq(Mc,q):
+
+    m1 = Mc*((1+q)/q**3)**0.2
+    m2 = Mc*(q**2 * (1+q))**0.2
+    if m1<m2:
+        m1,m2 = m2,m1
+
+    return m1, m2
+
+def ciInterval(samples, ciInt):
+	percent = (100. - ciInt) / 2.
+	numSamplesToRemove = int(round(len(samples)*percent/100.))
+	sortedSamples = sorted(samples)
+	lower = sortedSamples[numSamplesToRemove]
+	upper = sortedSamples[-numSamplesToRemove]
+	return (upper , lower)
+
+injectM1 = [1.,1.4,2.5,2.5]
+injectM2 = [1.,1.4,1.,2.5]
+injectQ = [1.,1.,0.4,1.]
+injectMC = [0.8705506,1.218771,1.348809,2.176376]
+params = ['mc','m1','m2','mtot','q','dist','iota','ra','dec','sa']
+masses = ['1_1/','1.4_1.4/','1_2.5/','2.5_2.5/']
+
+l = 0
+
+for mass in masses:
+	posteriorSamples = [[[]for i in range(40)]for k in range(10)]
+
+	for i in range(40):
+		filename = mass + str(i) + '/posterior_samples.dat'
+		if os.path.exists(filename):
+			file = open(filename)
+			filedata = file.readlines()
+			for j in range(1,len(filedata)):
+				[cycle,logpost,logprior,iota,psi,dec,ra,dist,phi_orb,time,q,mc,logl,loglh1,logll1,loglv1,logli1,f_lower,chain] = filedata[j].split()
+				posteriorSamples[0][i].append(float(mc)/injectMC[l])
+				m1, m2 = m1m2fromMcq(float(mc),float(q))
+				posteriorSamples[1][i].append(float(m1)/injectM1[l])
+				posteriorSamples[2][i].append(float(m2)/injectM2[l])
+				posteriorSamples[3][i].append((float(m1) + float(m2))/(injectM1[l] + injectM2[l]))
+				posteriorSamples[4][i].append(float(q))
+				posteriorSamples[5][i].append(float(dist))
+				posteriorSamples[6][i].append(abs(np.cos(float(iota))))
[…]

### 2013-05-28 DistIotaComp.py

@@ -3,9 +3,9 @@ from numpy import *
 
 Dist= [[] for i in range(5)]
 Iota= [[] for i in range(5)]
-filenumbers = ['5','27','40','36']
+filenumbers = ['15','26','38','39']
 #filenumbers = ['5','27','36']
-injected = [(100.8422,1.5548),(124.73,1.782),(170.41,2.135),(145.78,1.671)]
+injected = [(102.81124,1.67304),(119.14434,1.961056),(131.2679,0.9685463),(51.905911,1.489843)]
 #injected = [(100.8422,1.5548),(124.73,1.782),(145.78,1.671)]
 
 for j in range(4):
@@ -13,15 +13,15 @@ for j in range(4):
 		filedata = file.readlines()
 		file.close()
 
-		for i in range(1,len(filedata)):
-			[dist,chain,v1_end_time,f_lower,logll1,logl,loglh1,loglh2,v1h1_delay,l1v1_delay,l1h1_delay,loglv1,m1,ra,l1_end_time,m2,iota,v1l1_delay,psi,post,cycle,mc,h1v1_delay,logprior,phi_orb,h1l1_delay,q,prior,h1_end_time,eta,time,cosiota,dec] = filedata[i].split()
+		for i in range(100,len(filedata)):
+			[dist,chain,v1_end_time,f_lower,logll1,logl,loglh1,v1h1_delay,l1v1_delay,l1h1_delay,loglv1,m1,ra,l1_end_time,m2,iota,v1l1_delay,psi,post,cycle,mc,h1v1_delay,logprior,phi_orb,h1l1_delay,q,prior,h1_end_time,eta,li1,time,cosiota,dec] = filedata[i].split()
 			Dist[j].append(float(dist))
 			Iota[j].append(float(iota))
 
 
 subplots_adjust(left=0.15, bottom=None, right=None, top=0.92, wspace=None, hspace=0.5)
+suptitle("Distance/Inclination PDFs", fontsize=20)
 for j in range(1,5):
-		suptitle("Distance/Inclination PDFs", fontsize=20)
 		subplot(4,1,j)
 		#ax.set_xticks([1.3484,1.3486,1.3488, 1.3490,1.3492])
 		gridsize = 60
@@ -29,8 +29,8 @@ for j in range(1,5):
 		plot(injected[j-1][0],injected[j-1][1],marker='o', color='w',markersize=18)
 		pyplot.colorbar()
[…]

### 2013-05-28 McEtaComp.py

@@ -6,37 +6,38 @@ Q = []
 M1 = []
 M2 = []
 
-file = open('postSamp125.dat')
+file = open('HLVI/1.4_1.4/10/post/posterior_samples.dat')
 filedata = file.readlines()
 file.close()
 
 for i in range(1,len(filedata)):
-	[dist,chain,v1_end_time,f_lower,logll1,logl,loglh1,loglh2,v1h1_delay,l1v1_delay,l1h1_delay,loglv1,m1,ra,l1_end_time,m2,iota,v1l1_delay,psi,post,cycle,mc,h1v1_delay,logprior,phi_orb,h1l1_delay,q,prior,h1_end_time,eta,time,cosiota,dec] = filedata[i].split()
+	[dist,chain,v1_end_time,f_lower,logll1,logl,loglh1,v1h1_delay,l1v1_delay,l1h1_delay,loglv1,m1,ra,l1_end_time,m2,iota,v1l1_delay,psi,post,cycle,mc,h1v1_delay,logprior,phi_orb,h1l1_delay,q,prior,h1_end_time,eta,li1,time,cosiota,dec] = filedata[i].split()
 	Q.append(float(q))
 	Mc.append(float(mc))
 	M1.append(float(m1))
 	M2.append(float(m2))
 
 
-suptitle("Mass PDFs for $1M_{\odot}/2.5M_{\odot}$ System", fontsize=20)
-subplots_adjust(left=None, bottom=None, right=None, top=None,
-                  wspace=None, hspace=1)
+suptitle("Mass PDFs for $1.4M_{\odot}/1.4M_{\odot}$ System", fontsize=20)
+subplots_adjust(left=0.15, bottom=None, right=None, top=0.88, wspace=None, hspace=0.5)
 ax = subplot(2,1,1)
-ax.set_xticks([1.3484,1.3486,1.3488, 1.3490,1.3492])
+#ax.set_xticks([1.3484,1.3486,1.3488, 1.3490,1.3492])
+ax.set_xticks([1.2185,1.2186,1.2187, 1.2188,1.2189])
 subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=None, hspace=0.3)
 gridsize = 60
 hexbin(Mc,Q, gridsize=gridsize, cmap=cm.gist_stern, bins=None)
-plot(1.348809,0.4,marker='o', color='w',markersize=18)
[…]

### 2013-05-28 massPDFs.py

@@ -10,8 +10,8 @@ def m1m2fromMcq(Mc,q):
 
 	return m1, m2
 
-massBins = ['11','114','125','2525']
-chirpMasses = [0.870661, 1.218771, 1.348809, 2.176374]
+massBins = ['11','1414','125','2525']
+chirpMasses = [0.8705506, 1.218771, 1.348809, 2.176376]
 massRatios = [1,1,0.4,1]
 indivMasses = [(1.,1.),(1.4,1.4),(1.,2.5),(2.5,2.5)]
 Bin = 0
@@ -32,19 +32,20 @@ for number in massBins:
 		M  = []
 		k = 0
 
-		for i in range(0,len(mcdata),50):
-			q.append(float(qdata[i].rstrip())*massRatios[Bin])
-			mc.append(float(mcdata[i].rstrip()))
+		for i in range(0,len(mcdata),20):
+			q.append(float(qdata[i].rstrip()))
+			mc.append(float(mcdata[i].rstrip())/chirpMasses[Bin])
 			m1Temp, m2Temp = m1m2fromMcq(mc[k]*chirpMasses[Bin],q[k])
 			m1.append(m1Temp / indivMasses[Bin][1])
 			m2.append(m2Temp / indivMasses[Bin][0])
 			M.append((m1Temp + m2Temp)/sum(indivMasses[Bin]))
 			k += 1
+		print min(M)
 
 		m1KDE = scipy.stats.gaussian_kde(m1)
 		m2KDE = scipy.stats.gaussian_kde(m2)
 		mcKDE = scipy.stats.gaussian_kde(mc)
-		mKDE  = scipy.stats.gaussian_kde(mc)
+		mKDE  = scipy.stats.gaussian_kde(M)
 		qKDE  = scipy.stats.gaussian_kde(q)
 
 		Xm1 = []
@@ -93,7 +94,7 @@ for number in massBins:
 		l2=legend([lb1,lb2,lb3,lb4],["$1M_{\odot} - 1M_{\odot}$","$1.4M_{\odot} - 1.4M_{\odot}$","$1M_{\odot} - 2.5M_{\odot}$","$2.5M_{\odot} - 2.5M_{\odot}$"], loc='upper left', title="Neutron Star Masses")
 		gca().add_artist(l1)
 		xlabel('Component Masses ($M_{\odot}/M_{\odot}^{inject}$)', fontsize=18)
[…]

### 2013-06-11 doc/paper.tex
added bens comments

@@
 %\email{rodriguez@u.northwestern.edu}
-,Benjamin Farr \altaffilmark{1}
+Benjamin Farr \altaffilmark{1}
 %\email{bfarr@u.northwestern.edu} 
@@
 Within the next five years, the Advanced LIGO/Virgo network will have reached a sensitivity sufficient to enable the routine
- detection of gravitational waves.  Beyond the initial detection, the scientific promise of these instruments relies the 
- parameter estimation techniques being currently developed.  The majority of this effort has been towards the detection
-   and characterization of gravitational waves from compact binary coalescence, i.e. the coalescence of black holes and/or 
+ detection of gravitational waves.
+Beyond the initial detection, the scientific promise of these instruments relies on the ability to perform parameter estimation.
+The majority of this effort has been towards the detection
+   and characterization of gravitational waves from compact binary coalescence, e.g. the coalescence of binary 
    neutron stars.  While several previous studies have focused on the parameter estimation abilities of advanced detectors, 
-   the majority have relied on approximation techniques such as the Fisher Matrix.  Here, we report the statistical 
-   uncertainties that will be achievable, in practice, using the parameter estimation techniques which will be applied to 
-   detections of binary neutron star systems.  We find the recovery of the individual masses to be within fractionally within 
-   10\% at the 65\% confidence level for equal-mass systems, and within 2\% for unequal-mass systems.
+   the majority have relied on approximation techniques such as the Fisher Matrix.  We report the statistical 
+   uncertainties that will be achievable, in practice, using the full parameter estimation machinery developed by the  
+   LIGO/Virgo Collaboration.  We find the recovery of the individual masses to be fractionally within 
+   10\% at the 65\% credible intervals for equal-mass systems, and within 2\% for unequal-mass systems.
      We also report the average uncertainties on the sky-locations, luminosity distance, and orbital inclinations of randomly 
@@
 
- By the end of the decade, the field of gravitational-wave astrophysics will
- mature into an ideal tool for 
- exploring the gravitational side of the universe. Within the next few
+Within the next few
  years, the first generation of gravitational-wave detectors capable 
- of regularly resolving astrophysical sources will come online \carl{[CITE]}.
+ of regularly resolving astrophysical sources will come online \citep{AdvLIGO,AdvVirgo}.
  The Advanced LIGO and Virgo detectors will provide the first insights
@@
 
-The mergers of binary neutron stars are expected to be the most common
-source in the advanced detector era \carl{[CITE]}.   Models from stellar 
-evolution suggest that the number of binary neutron star mergers within 
-Advanced LIGO/Virgo's detection horizon could reach into the hundreds per 
-year \carl{[CITE]}.  Although the peak sensitivity of ground-based detectors
+The mergers of binary neutron stars (BNS) are expected to be the most common
+compact binary source in the advanced detector era.   Models from stellar 
+evolution and observations of binary pulsars suggest that the number of binary neutron star mergers within 
+Advanced LIGO/Virgo's detection horizon could reach into the hundreds each 
+year, with an expected mean of $\sim 40$ per year \citep{RatesPaper}. 
+Although the peak sensitivity of ground-based detectors
 is not focused on the frequency at which BNS systems merge, it could still
@@
 of state of nuclear matter) \carl{[CITE]}.  Furthermore, the observations of multiple BNS
-systems will provide key insight into the evolution of binary systems in the field \carl{[CITE]},
-and in globular clusters \carl{[CITE]}. As such, BNS systems will likely 
+systems will provide key insight into the evolution of binary systems in the field \citep{VickyRates,KimRates}
+. As such, BNS systems will likely 
 form the ``bread and butter'' of the compact binary coalescence detection effort in the coming 
@@
 perform a full exploration of the parameter space for each detection.  By 
-analyzing the parameter space of each candidate with a Bayesian inference technique 
+analyzing the parameter space of each candidate with a Bayesian inference technique, 
  we will be able to make precise, scientifically meaningful
-statements about the physics of these detectible systems.  To 
+statements about the physics of these systems.  To 
 that end, we employ a Markov-Chain Monte Carlo sampling algorithm, 
 \texttt{lalinference\_mcmc}, included in the LIGO Application Library parameter
-estimation code, \texttt{LALInference}, to analyze the parameter space of binary neutron star systems.
+estimation code, \texttt{LALInference}, to analyze the parameter space of BNS systems.
 
 By employing the full parameter-estimation machinery that will eventually be
-used in the Advanced LIGO/Virgo era, our results give the first estimate at the 
+used in the Advanced LIGO/Virgo era, our results give the first estimates at the 
 realistic capabilities of advanced ground-based detectors to characterize BNS systems.
@@
 first adapted for gravitational-wave parameter estimation by \citep{FinnDetection}.
-While each of these studies (\cite{PoissonWill,CutlerFlanagan,ArunPE}, among 
-many others) have pointed out the limitations 
+While each of these studies \citep{PoissonWill,CutlerFlanagan,ArunPE} have pointed out the limitations 
 and flaws of the Fisher Information Matrix, there has been no study which investigates
-the BNS parameter estimation capabilities of Advanced LIGO/Virgo via the techniques
+the BNS parameter estimation capabilities of Advanced LIGO/Virgo using the techniques
 that will eventually be employed.  The recent work of \cite{Vallisneri} and our 
@@
 which the Advanced LIGO/Virgo network will be able to measure the basic parameters of 
-binary neutron stars.  In Section \ref{PEsection}, we describe
+BNS mergers.  In Section \ref{PEsection}, we describe
 the machinery of our parameter estimation code, \texttt{LALInference}, and the associated
@@
 inclination and luminosity distance (Section \ref{idSection}), and the localization of sources 
-in the sky (Section \ref{skySection}).   Finally we provide quantitative 1-dimensional confidence
- intervals on the parameter recovery in Section \ref{ciSection}.  These results, contained
+on the sky (Section \ref{skySection}).   Finally we provide quantitative 1-dimensional confidence
+ intervals on each parameter in Section \ref{ciSection}.  These results, contained
  in Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}, are intended as a reference for the 
@@
 \end{equation}
-Since our noise model is Gaussian, we can write the
+Since the noise model is Gaussian, we can write the
 probability of a specific signal realization $s$ as proportional to the probability
-that our residual is Gaussian distributed once the waveform has been subtracted
+that the residual is Gaussian distributed once the waveform has been subtracted
 \begin{align}
@@
 \end{align}
-where $\thpara$ is the set of parameters for our template
+where $\thpara$ is the set of parameters for the template
 waveforms, and $p(s | \thpara)$ is the likelihood of the signal $s$ given the parameters $\thpara$.
@@
 \end{equation}
-where $S_n(f)$ is the one-sided power spectral density as a function
+where $S_n(f)$ is the one-sided power spectral density (PSD) as a function
 of frequency, and $\tilde{a}(f)$ and $\tilde{b}(f)$ are the Fourier
-transforms of the time-domain signals $a(t)$ and $b(t)$.
+transforms of the time-domain data $a(t)$ and $b(t)$.  If we pick a set of parameters $\thpara$ such that
+$h(\thpara) = h_0$, then the posterior \eqref{posterior}
+will be near a global maximum; however, the presence of noise will in
+general deflect the maximum of our posterior away from the value at
+$\thpara_0$. That is, in the presence of noise, there is
+no guarantee that the maximum-likelihood of our signal corresponds to
+the true parameters of the system.
 
@@
 
-We are interested in the posterior $p(\thpara | s)$ as it encodes information about
-prior state of knowledge about the problem.  For instance, since it is assumed that compact binaries
-form homogeneously in the local universe, we can safely assume that the population of
+We are interested in the posterior $p(\thpara | s)$ as it encodes information about the
+prior state of knowledge about the problem in addition to the likelihood of the signal.
+  For instance, since it is assumed that compact binaries
+form homogeneously in the local universe observable by advanced detectors,
+ we can safely assume that the population of
 sources will be distributed homogeneously in volume, or evenly in $D^2$. 
@@
 
-If we pick a set of parameters $\thpara$ such that
-$h(\thpara) = h_0$, then the posterior \eqref{posterior}
-will be near a global maximum; however, the presence of noise will in
-general deflect the maximum of our posterior away from the value at
-$\thpara_0$. That is, in the presence of noise, there is
-no guarantee that the maximum-likelihood of our signal corresponds to
-the true parameters of the system.
+\noindent  The mass priors listed here are the generic priors used in follow-up analysis, not specifically for BNS systems.
+While we could have used a prior with a lower component mass cutoff for the present study, in practice the higher prior boundary does not effect our current analysis.
 
@@
 
-The LIGO Algorithm Library parameter estimation code, \texttt{LALInference}, is designed as 
+The LIGO Algorithm Library Bayesian inference code, \texttt{LALInference}, is designed as 
 a unified framework for gravitational-wave parameter estimation.  By using a common setup for 
-waveform generation, PSD estimation, data handling, and other associated techniques from gravitational-wave parameter estimation, \texttt{LALInference} allows the implementation of multiple parameter samplers in using identical parameter setups, including Nested Sampling (\texttt{lalinference\_nest})\carl{[CITE]} and Markov-Chain Monte Carlo (\texttt{lalinference\_mcmc}).
+waveform generation, PSD estimation, data handling, and other associated techniques from gravitational-wave parameter estimation, \texttt{LALInference} allows the implementation of multiple samplers of the parameter space, including Nested Sampling (\texttt{lalinference\_nest}, described in \cite{nestedsampling2010}) and Markov-Chain Monte Carlo (\texttt{lalinference\_mcmc}).
 We elect to use the MCMC sampler for this study.
@@
 The above procedure is designed to record a chain of samples whose
-distribution is $p\left(\thpara|s\right)$.  By drawing a sufficient ($\sim 1000$) number
- of effective samples from the posterior, the chains traces out the functional form of the posterior,
- gathering more samples from regions with high posterior probability.  Depending on
+distribution is $p\left(\thpara|s\right)$.  By drawing a sufficient ($\sim1000$) number
+ of effectively independent samples from the posterior, the chains traces out the functional form of the posterior,
+ gathering more samples from regions with high posterior probability density.  Depending on
 the proposal distribution, $q$, the convergence (mixing) of the chain
 may be rapid or slow.  We employ multiple optimization techniques,
-including both specially-crafted $q$ and parallel tempering, to ensure
+including both specially-crafted jump proposals ($q$) and parallel tempering, to ensure
 adequate mixing of the Markov Chains throughout our parameter space.
-The details of the algorithm can be found in
-\citep{Sluys08,spinspiral2009, spinspiral2010}.  Both samplers were tuned and 
+Both samplers were tuned and 
 developed during the last science run of the Initial LIGO/Virgo network.  
 A description of the parameter estimation capabilities of these two samplers with respect to
-real gravitational-wave data, as well as a more detailed description of the algorithms and
+real interferometer data, as well as a more detailed description of the algorithms and
 checks for convergence, can be found in \cite{S6PE}.
@@
 
-We use a frequency domain waveform accurate up to $3.5$
-post-Newtonian (pN) order in phase and amplitude.  We restrict ourselves to
+We use a frequency-domain waveform accurate up to $3.5$
+post-Newtonian (pN) order in phase and 3 pN order in amplitude.  We restrict ourselves to
 quasi-circular, non-spinning waveforms as a simplifying assumption.  The standard
@@
 where $a(t_f)$ is the amplitude evaluated at a stationary-phase reference point, which to lowest order
-takes the form $A \propto f^{-7/6} \chmass^{5/6}\Theta(\text{angle})/D$, $D$ is
+takes the form $a(t_f) \propto f^{-7/6} \chmass^{5/6}\Theta(\text{angle})/D$, where $D$ is
 the luminosity distance of the binary, and $\psi(f)$ is the pN phase.
@@
 mass, $M_{tot}\equiv M_1+M_2$, it is convenient to work with the
-\textit{mass ratio} and \textit{chirp mass}, defined by
+mass ratio and chirp mass, defined by
 \begin{equation}
-  q\equiv M_1/M_2~~~~\text{and}~~~~\chmass = (M_1 M_2)^{3/5} M^{-1/5},
+  q\equiv M_1/M_2~~~~\text{and}~~~~\chmass = (M_1 M_2)^{3/5} M_{tot}^{-1/5},
   \label{eqRatioCM}
@@
 We elect to use $q$ as it is more physically intuitive, and the prior $p(q)$ is uniform when the component
-mass priors are uniform.}  The stationary phase then becomes an expansion in the 
-Newtonian orbital velocity, $v=(\pi M f)^{1/3}$, 
+mass priors are uniform.}  By convention, $M_1 \geq M_2$.  The stationary phase then becomes an expansion in the 
+Newtonian orbital velocity, $v=(\pi M_{tot} f)^{1/3}$, 
 \begin{equation}
-\psi(f) = 2 \pi f t_c - \phi_0 + \frac{\pi}{4} + \frac{3}{128}\left(\frac{M}{\chmass}\right)^{5/3}\sum^{n}_{k=0}\alpha_{k}v^{k-5}
+\psi(f) = 2 \pi f t_c - \phi_0 + \frac{\pi}{4} + \frac{3}{128}\left(\frac{M_{tot}}{\chmass}\right)^{5/3}\sum^{n}_{k=0}\alpha_{k}v^{k-5}
 \label{phase}
@@
 (in Hanford, WA and Livingston, LA) and the Virgo site (in Pisa, Italy), and a 
-four-detector configuration with adds the proposed LIGO-India detector
+four-detector configuration that adds the proposed LIGO-India detector
 (in Chitradurga, KA).  For simplicity, we assume each detector to be 
@@
 \begin{equation}
-  \pi f_{\text{ISCO}} = \frac{1}{6^{3/2}M}.
+  \pi f_{\text{ISCO}} = \frac{1}{6^{3/2}M_{tot}}.
   \label{ISCOFrequency}
@@
 modulate the amplitude of the signal in an independent fashion for each detector.  
-Combining these leads to our 9-dimensional parameter space for non-spinning systems:
+Combining these leads to our 9-dimensional parameter space for non-spinning systems,
 \begin{equation}
-\thpara =  (\chmass, q, \phi_0,t_c,D,\iota,\psi,\alpha,\delta)
+\thpara =  (\chmass, q, \phi_0,t_c,D,\iota,\psi,\alpha,\delta),
 \label{parameterspace}
 \end{equation}
-where to summarize
+where
 
@@
 \item $D$ is the luminosity distance to the binary,
-\item $\iota$ is the orbital inclination, 
-\item $\psi$ the gravitational-wave polarization, and
-\item $\alpha$ and $\delta$ the right ascension and declination of the
+\item $\iota$ is the orbital inclination (the angle between the orbital angular momentum and the line of sight), 
+\item $\psi$ is the gravitational-wave polarization, and
+\item $\alpha$ and $\delta$ are the right ascension and declination of the
 source on the sky.
@@
 binary with respect to each detector, most of the information about these extrinsic
-parameters comes from two sources: the time-of-arrival triangulation of 
+parameters comes from two quantities: the time-of-arrival triangulation of 
 the source locations, and the relative amplitudes within the detector network.
@@
 \begin{equation}
-  \rho \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{| \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df
+  \rho \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{| \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df,
   \label{formalSNR}
@@
 where $\rho$ is the SNR and $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
-the frequency-domain signal and template, respectively, and the normalization $\sigma$ is
+the frequency-domain data and template, respectively, and the normalization $\sigma$ is
 given by
@@
 
-When dealing with network of gravitational-wave detectors, the SNRs of the individual detectors add in quadrature.  That is, the network SNR for a detection is
+When dealing with network a of gravitational-wave detectors, the SNRs of the individual detectors add in quadrature.  That is, the network SNR for a detection is
 
@@
 distance, $D$, was selected to provide a network SNR of $\rho_{\text{network}}=20$ for each source.
-While unphysical from an astrophysical perspective (binary sources should be 
+While unphysical from an astrophysics perspective (binary sources should be 
 distributed evenly in comoving volume), this choice allows us to explore the parameter estimation
@@
 While this may initially seem disconcerting, it is to be expected.
-Recall that of the BNS signals were injected with a network SNR of 20 into a zero-noise detector realization.
+Recall that all of the BNS signals were injected with a network SNR of 20 into a zero-noise detector realization.
 Furthermore, note that the mass parameters are the only two which directly effect the phase of the TaylorF2 waveform \eqref{phase}.
@@
 To condense the results into a single figure of merit, we average the 1-dimensional mass PDFs into a single 
-posterior probability for system.  See Figure~\ref{metaMassPDFs}.  Notice how when averaged and
+posterior probability for the system.  See Figure~\ref{metaMassPDFs}.  Notice how when averaged and
  normalized to the injected values, the recovery of the component masses depends only on the mass ratio.  
- Furthermore, for systems of equal masses, the posterior barely extends beyond 15\% of the injected values.  
+ Furthermore, for systems with equal component masses, the posterior barely extends beyond 15\% of the injected values.  
  If one assumes that the threshold between black
@@
 correlated to the masses.  This coupling means that a higher-massed spinning black hole systems can produce
- waveforms very similar to non-spinning, low-mass, making it impossible to discern between non-spinning neutron stars
- and spinning, more massive black holes.  However, the situation is not hopeless: if the spins are misaligned, the spin 
+ waveforms very similar to non-spinning, low-mass systems, making it extremely difficult to discern between non-spinning 
+ neutron stars
+ and spinning, more massive black holes \citep{Baird2013,Hannam2013}.  However, the situation is not hopeless: if the spins are misaligned, the spin 
  vectors will couple to the orientation of the binary (encoded in the three angles $\phi_0$, $\iota$, and $\psi$) via
@@
 
-In Table \ref{ciTableIntrinsic}, we list the 65\% fractional confidence intervals for the mass parameters.  We find that the 
-component masses for equal mass systems can be isolated to between 6\% and 9\% fractional uncertainty at the 65\% confidence interval.
-This value drops to less than 2\$ for the components of the unequal mass systems.
+In Table \ref{ciTableIntrinsic}, we list the 65\% fractional credible intervals for the mass parameters.  We find that the 
+component masses for equal mass systems can be isolated to between 6\% and 9\% fractional uncertainty at the 65\% credible interval.
+This value drops to less than 2\% for the components of the unequal mass systems.
 Again, this
@@
 After merger, the remnant is believed to emit the burst along the axis of orbital angular momentum, making the inclination of the binary system of particular interest to gamma-ray astronomy \citep{LSCGRB2010,Corsi2012}.
-The inclination is detected as a relative amplitude difference between the two gravitational-wave polarization, such that to lowest order
+The inclination is detected as a relative amplitude difference between the two gravitational-wave polarizations, such that to lowest order
 
@@
 Given this degeneracy, it should come as no surprise that the 2D marginalized posteriors of distance
- and inclination are the worst of the six physically interesting parameters.  Four typical 2D PDFs are
+ and inclination are the broadest of the six physically interesting parameters.  Four typical 2D PDFs are
   presented in Figure~\ref{distIotaPDF}.  Notice the bimodal uncertainty 
@@
  estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$ space will be 
- limited, even during the Advanced LIGO/Virgo era; however, there will be cases (such as the first 
- PDF in Figure~\ref{distIotaPDF})  that will prove copacetic to simultaneous measurements accurate 
- enough for coincidence measurements with GRB observers.  Conversely, if a gravitational-wave signal is 
- matched to a detected GRB counterpart, the optical information about the orbital inclination
- will provide an additional constraint on the D-$\iota$ space to vastly improve the results quoted here.
+ limited, even during the Advanced LIGO/Virgo era; however, there if a gravitational-wave signal is 
+ matched to a detected SGRB counterpart (which may occur at the rate of $\sim 3 yr^{-1}$ in Advanced LIGO/Virgo, 
+ according to \cite{Metzger2013}), the optical information about the orbital inclination
+ will provide an additional constraint on the D-$\iota$ space, vastly improving the luminosity distance recovery
+ quoted here.
 
 In Table \ref{ciTableExtrinsic}, we list the averaged 65\% confidence intervals for distance and inclination.  
-Notice that, while the uncertainties on distance can be extreme, from tens to hundreds of $mpc$, the uncertainties
-on inclination are reasonably small\carl{[QUANTIFY THIS WITH CORRECT JACOBIAN]}.  If it is assumed that a
- compact object generated GRB maintains bipolar symmetry, the the quantity of interest is $|\cos(\iota)|$, not 
- $\iota$, since observing a compact merger at $\iota$ and $\iota + \pi/2$ should produce identical optical counterparts.  
-Since $|\cos(\iota)|$ maps the bi-modal structure in the inclination PDFs seen in Figure \ref{distIotaPDF} to a single
-mode, the uncertainties in $\iota$ will sufficiently small \carl{[QUANTIFY]} to provide coincident information on
-GRB beaming angles.
+Notice that the uncertainties on distance can be extreme, from tens to hundreds of $mpc$.  When discussing
+the inclination angle, we elected to use $|\cos(\iota)|$, as this maps the occasional bimodal structure into
+a single PDF, 
+ and observing a compact merger at $\iota$ and $\iota + \pi/2$ should yield identical physics.  
+%Since $|\cos(\iota)|$ maps the bi-modal structure in the inclination PDFs seen in Figure \ref{distIotaPDF} to a single
+%mode, the uncertainties in $\iota$ will sufficiently small \carl{[QUANTIFY]} to provide coincident information on
+%GRB beaming angles.
 
@@
 
-  In practice, however, additional information from the wave polarization, can break this plane-reflected degeneracy,
+  In practice, however, additional information from the wave polarization and the relative difference
+  in SNR between individual detectors can break this plane-reflected degeneracy,
    leading to a bi-modal distribution with significantly more support in one mode of the PDF.
-     By fitting for the sky location and the polarization simultaneously, the MCMC can identify
+     By fitting for the sky location and the polarization simultaneously, the MCMC can often identify
    the correct mode on the sky.  For the four-detector configuration, this concern is irrelevant: even with time-of-arrival
@@
 glitches have a variety of well-known and not-so-well-known physical causes in the instrument,
-and can cause substantially greater errors in parameter recovery than any specific realization noise realizations.  This has already been addressed for the case of space-based gravitational-wave
+and can cause substantially greater errors in parameter recovery than any specific noise realizations.  This has already been addressed for the case of space-based gravitational-wave
 detectors (LISA), and is currently being implemented in \texttt{lalinference\_mcmc} 
@@
 
-\section{Confidence Intervals}
+\section{Credible Intervals}
 \label{ciSection}
 
-When quoting parameter estimation results, it is often convienant to reduce the full parameter space to
-confidence intervals about single, marginalized parameters..  To that end, we state the averaged 65\% 
+When quoting parameter estimation results, it is often convenient to reduce the full parameter space to
+credible intervals about single, marginalized parameters..  To that end, we state the averaged 65\% 
 confidence intervals about the single parameters for each of the three parameter pairs of interest.  These were already
@@
 
-There are several different ways of computing the width of a confidence interval in this setup.  If one considers the points in
- the MCMC as random draws from the true posterior, then the $\alpha$-level confidence interval can be computed by simply
+There are several different ways of computing the width of a credible interval in this setup.  If one considers the points in
+ the MCMC as random draws from the true posterior, then the $\alpha$-level credible interval can be computed by simply
   ordering the points, removing $N(1-\alpha )/2$ points from both sides of the posterior samples symmetrically, and measuring
@@
 In this paper, we performed an MCMC parameter estimation analysis on the recoverability of basic information about binary 
-neutron stars, using two projected version of the Advanced LIGO/Virgo network.  We focused on the recovery of the two 
+neutron stars, using two projected versions of the Advanced LIGO/Virgo network.  We focused on the recovery of the two 
 masses, the luminosity distance, orbital inclination, and the sky location, as these are the six basic parameters of physical 
-interest to the problem.  We found that, neglecting the effects of spin, the component masses can be constrained to less
- than 10\% of their true value to a confidence of 65\%.  This value drops below 2\% for systems with an asymmetric mass ratio.
- These results were summarized in Table \ref{ciTableIntrinsic}
+interest to the problem.  We found that, neglecting the effects of spin, the component masses can be constrained to within
+ 10\% of their true value to a confidence of 65\%.  This value drops below 2\% for systems with an asymmetric mass ratio.
+ These results were summarized in Table \ref{ciTableIntrinsic}.
 
@@
 the three-detector configuration, consisting of the Washington and Louisiana LIGO sites plus the Italian Virgo site,
- was able to constrain all signals with within 60 $deg^2$ on the sky at the 65\% confidence interval, with an average
+ was able to constrain all signals within 60 $deg^2$ on the sky at the 65\% confidence interval, with an average
 65\% confidence interval of $\sim 7$ $deg^2$.  Meanwhile, the four-detector
@@
 if the mass measurement alone will be sufficient to distinguish non-spinning neutron stars from highly-spinning low-mass
-black holes.  Future work will explore this potential mass/spin degeneracy, with the aim of definitively answering this question.
+black holes.  Future work will explore this potential mass/spin degeneracy, including the effects of orbital precession, with the aim of definitively answering this question.
 

### 2013-06-20 doc/paper.tex
Added half of Vivien's comments (still want to add a couple of the suggestions) and added Tyson's paragraps

@@
 that end, we employ a Markov-Chain Monte Carlo sampling algorithm, 
-\texttt{lalinference\_mcmc}, included in the LIGO Application Library parameter
+\texttt{lalinference\_mcmc}, included in the LIGO Algorithm Library parameter
 estimation code, \texttt{LALInference}, to analyze the parameter space of BNS systems.
@@
 $h(\thpara) = h_0$, then the posterior \eqref{posterior}
-will be near a global maximum; however, the presence of noise will in
+will be near a global maximum; however, our choice of prior the presence of noise will in
 general deflect the maximum of our posterior away from the value at
-$\thpara_0$. That is, in the presence of noise, there is
-no guarantee that the maximum-likelihood of our signal corresponds to
-the true parameters of the system.
+$\thpara_0$.  Therefore, the maximum posterior parameters do not necessarily 
+correspond to the true parameters of the source, so when interpreting parameter
+ estimation results we must consider the full posterior distribution function.
 
@@
 \item uniform in component masses from $0.8M_{\odot} \leq M_{1,2} \leq 30M_{\odot}$, with a minimum chirp mass  \eqref{eqRatioCM} of 0.6 $M_{\odot}$,
-\item uniform in volume, which implies a luminosity distance prior of $p(D) = D^2 dD$, and
-\item uniform in all other parameters.
+\item uniform in volume, which implies a luminosity distance prior of $p(D) = D^2 dD$,
+\item uniform in coalescence time over the segment of data being analyzed, and
+\item uniform in all other parameters, with angular parameters being flat over their corresponding domains.
 \end{itemize}
@@
  any stretch of data should contain a specific noise realization drawn from a Gaussian colored by the PSD.
-   However, what we are interested in is not the parameter estimation that can occur in a specific draw
-    from this probability of noises, but the uncertainties averaged over all possible noise
-     realizations.\footnote{Similarly to how the Fisher matrix formalism can provide the Cramer-Rao bound averaged over
-     all noise realizations} Since our noise model is assumed to be Gaussian, it is unnecessary to recover the
-      parameters from a large sample of identical waveforms in different noise; we can simply assume the 
-      noise \emph{is} the mean defined by the power-spectral density.  This ``zero-noise'' parameter estimation
-       provides a statistical statement on the measurable uncertainties, and is what is reported here.  In Section
-        \ref{noiseSection} we provide an example of parameter estimation in several non-zero noise realizations
-compared to the zero-noise equivalent \carl{[TYSON WILL WRITE]}.
+%   However, what we are interested in is not the parameter estimation that can occur in a specific draw
+  %  from this probability of noises, but the uncertainties averaged over all possible noise
+     realizations. Without a realistic model including the actual instrument sensitivity,
+      non stationary noise, and uncertainty in the PSD we cannot 
+     accurately simulate GW data to the point of making precise predictions about parameter 
+     estimation capabilities.  Furthermore, the posterior distribution from a future 
+     detection will be influenced by 
+     the realization of the noise at the time of the detection.  Because of this, we 
+     elect to focus only on the statistical 
+     errors due to the flexibility of the waveforms and the expected sensitivity of 
+     the advanced era detectors and suppress 
+     any effects of detector noise by not including a noise realization in our simulated data.
+       Consequently, what we recover with the MCMC  
+     could be interpreted as the posterior distribution function for each source averaged over all
+      possible (Gaussian) noise realizations 
+     assuming we have the correct PSD.    \footnote{Similarly to how the Fisher matrix formalism can
+      provide the Cramer-Rao bound averaged over
+     all noise realizations.  Unlike a Fisher matrix study, we make no assumptions about the 
+     shape of the posterior distribution function, nor the location of the peak, while still requiring a
+      feasible number of MCMC runs 
+     to sufficiently cover parameter space, which would not be the case had we needed to 
+     average several noise-dependent results.} To check that our reported statistical errors
+     are not in gross disagreement with those obtained in the presence of noise,  we selected a 
+       particular simulated signal to perform parameter estimation in several noise realizations.  
+       The comparison of the noise-dependent and noise-free results
+       can be found in \ref{noiseSection}.
 
@@
 marginalization of a single dimension from the full 9D posterior space.  To better see this effect, 
-compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in Figure~\label{9dPDF}}
+compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in Figure~\ref{1414masses}}
 \end{figure*}
@@
 $t_c$, and the wave polarization $\psi$ must be included in any parameter estimation of the 
-waveform, they do not encode any information of particular astrophysical interest.
-\footnote{For systems whose components are non-spinning.  The presence of intrinsic angular 
+waveform, they do not encode any information of particular astrophysical interest.\footnote{For systems
+ whose components are non-spinning.  The presence of intrinsic angular 
 momentum will, in general, couple to the coalescence phase and wave polarization.}
@@
 probability density functions recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system. 
- These PDFs are the typical of the type of results that will be produced by parameter estimation
+ These PDFs are typical of the type of results that will be produced by parameter estimation
   studies in the advanced  detector era.  Notice that the peak of several parameters, including the 
@@
  estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$ space will be 
- limited, even during the Advanced LIGO/Virgo era; however, there if a gravitational-wave signal is 
+ limited, even during the Advanced LIGO/Virgo era; however, if a gravitational-wave signal is 
  matched to a detected SGRB counterpart (which may occur at the rate of $\sim 3 yr^{-1}$ in Advanced LIGO/Virgo, 
@@
    data alone, the HLVI network can constrain any source to a single mode on the sky.  Even then, there are still locations 
-   on the sky in which two or more detectors are not sensitive to the gravitational-wave signal, distorted, non-Gaussian PDFs.
+   on the sky in which two or more detectors are not sensitive to the gravitational-wave signal, yielding
+    distorted, non-Gaussian PDFs.
 
@@
  and \ref{2525SkyLocHLVI} respectively.  We show all four mass bins together, since in practice
-  the mass of the signals has no effect on the recovery of the sky location.  Only the location on 
+  the mass of the signals has no effect on the recovery of the sky location for the considered BNS systems.
+    Only the location on 
   the sky, the network configuration, and the other extrinsic parameters were found to be relevant.  
@@
  \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.52]{noisePDF.pdf}
- \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the Advanced LIGO noise curve.
-Each PDF represents the recovery of the same $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked at random from the Gaussian colored noise defined by the Advanced LIGO power spectral density.
-Notice how the curve is relatively unchanged, but usually assumes a Gaussian PDF displaced from the true value.
-This only holds true for glitch-free data, which is an unrealistic idealization when compared to real data.}
+ \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the 
+ Advanced LIGO noise curve.  Each PDF represents the recovery of the same $1M_{\odot}/2.5M_{\odot}$ signal in a
+  different noise curve, picked at random from the Gaussian colored noise defined by the Advanced LIGO power
+   spectral density, while the gray-shaded curve is the zero-noise PDF.  Notice how the curve is relatively unchanged,
+    but usually assumes a Gaussian PDF displaced from the true value.  This only holds true for glitch-free data, which
+     is an unrealistic idealization when compared to real data.}
  \label{noisePDFs}
@@
 analysis are identical to those that would be achieved by averaging the results of multiple identical injections 
-in different Gaussian noise realizations, as was argued in Section \ref{waveformSection}.  The second reason is simply
-that no good model exists for the true (decidedly non-Gaussian) noise that will arrive with a single detection candidate,
-Each detection will occur in noisy data, with a specific realization of the PSD provided and with 
-possible instrumentation and environmental glitches.  In the case of a unique Gaussian realization
+in different Gaussian noise realizations, as was argued in Section \ref{waveformSection}.  The second reason is 
+we are not able to predict the characteristics of realistic (often non-Gaussian) advanced detector noise.  
+Attempting to do so would have little chance of being accurate while requiring a huge computational 
+burden to combine the results of many MCMC runs in different noise realizations.
+
+ In the case of a unique Gaussian realization
 of the Advanced-LIGO noise curve, each realization causes the maximum likelihood of the posterior probability 
@@
 Of course, the largest concern for gravitational-wave parameter estimation will not be the specific
-realization of Gaussian noise, but the effects of glitches in the data.  These time-series 
-glitches have a variety of well-known and not-so-well-known physical causes in the instrument,
-and can cause substantially greater errors in parameter recovery than any specific noise realizations.  This has already been addressed for the case of space-based gravitational-wave
-detectors (LISA), and is currently being implemented in \texttt{lalinference\_mcmc} 
-\carl{[TYSON WILL WRITE]}.
+realization of Gaussian noise, but the effects of non-Gaussianities in the data.  Techniques which build
+ off of the theoretical progress made in~\cite{Allen:2002jw,Rover:2011qd,Littenberg:2010gf} for including
+  glitches in our model for the data, and therefore relaxing the assumptions about stationary and Gaussian
+   noise, are currently under investigation.
 
@@
 Although the results for the
-HLV and HLVI configurations are quantitatively identical, we report them separately for consistancy.}
+HLV and HLVI configurations are quantitatively identical, we report them separately for consistency.}
 \begin{tabular}{lcccccccccc}
@@
 
-Secondly, as stated above, the noise realization that we have employed here is an substantial idealization.
-In practice the noise levels of Advanced LIGO and Advanced Virgo will be highly variable over time, and will \emph{not} be stationary or Gaussian, as is commonly assumed.
-Unfortunately, there is no reliable or simple way to simulate the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.
-Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here \carl{[TYSON WILL WRITE]}
+Secondly, as stated above, we have performed our study under idealized detector-noise conditions.
+In practice the noise levels of Advanced LIGO and Advanced Virgo can vary with time and contain occasional excursions which are highly non-Gaussian.
+Unfortunately, there is no reliable way to predict the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.
+Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here.
 

### 2013-06-28 doc/paper.tex
Re-formatting paper.tex.

@@
 %\IfFileExists{revtex4.cls}{\documentclass[prd, twocolumn, lengthcheck, superscriptaddress, showpacs, letterpaper]{revtex4}}{}}
-\documentclass[11pt,a4paper]{emulateapj}
-\bibliographystyle{apj}
+\documentclass[11pt,a4paper]{emulateapj} \bibliographystyle{apj}
 
@@
 %\documentclass[lengthcheck,superscriptaddress,showpacs,letterpaper,nofootinbib]{article}
-\usepackage{ifpdf}
-\usepackage[bookmarks=false]{hyperref}
-\pdfoutput=1
-\usepackage[usenames,dvipsnames]{color}
-\usepackage{graphicx}
-\usepackage{graphics}  
-  \usepackage{float}
+\usepackage{ifpdf} \usepackage[bookmarks=false]{hyperref} \pdfoutput=1
+\usepackage[usenames,dvipsnames]{color} \usepackage{graphicx}
+\usepackage{graphics} \usepackage{float}
 %\restylefloat{table}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{acronym}
-\usepackage{comment}
-\usepackage{multirow}
-\usepackage{xspace}
+\usepackage{amsmath} \usepackage{amssymb} \usepackage{acronym}
+\usepackage{comment} \usepackage{multirow} \usepackage{xspace}
 %\restylefloat{figure}
-\usepackage{units}
-\usepackage{dcolumn}
-\usepackage{ulem}
+\usepackage{units} \usepackage{dcolumn} \usepackage{ulem}
 
 \def\aj{Astron. J.}  % Astronomical Journal 
-\def\apj{Astrophys. J.}                % Astrophysical Journal
+\def\apj{Astrophys. J.}  %Astrophysical Journal 
 \def\apjl{Astrophys. J. Lett.}  % Astrophysical Journal, Letters 
@@
 \def\nat{Nature} % Nature
-\def\aap{Astron. Astrophys.}                % Astronomy and
-                                % Astrophysics
+\def\aap{Astron. Astrophys.}  % Astronomy and % Astrophysics
 \def\jasa{J. Am. Stat. Assoc.}  
@@
 \begin{document}
-\title{Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network}
-\author{Carl L. Rodriguez \altaffilmark{1}
+\title{Basic Parameter estimation of Binary Neutron Star Systems by
+  the Advanced LIGO/Virgo Network} \author{Carl L. Rodriguez
+  \altaffilmark{1}
 %\email{rodriguez@u.northwestern.edu}
@@
 %\email{bfarr@u.northwestern.edu} 
-Vivien Raymond \altaffilmark{1,2}
-Will M. Farr \altaffilmark{1}
+Vivien Raymond \altaffilmark{1,2} Will M. Farr \altaffilmark{1}
 %\email{w-farr@northwestern.edu} 
@@
 
-\altaffiltext{1}{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) \& Dept.~of Physics and Astronomy, Northwestern University, 2145 Sheridan Rd, Evanston, IL 60208, USA; [e-mail: {\tt cr@u.northwestern.edu}]}
-\altaffiltext{2}{California Institute of Technology, Pasadena, CA 92215, USA}
+\altaffiltext{1}{Center for Interdisciplinary Exploration and Research
+  in Astrophysics (CIERA) \& Dept.~of Physics and Astronomy,
+  Northwestern University, 2145 Sheridan Rd, Evanston, IL 60208, USA;
+  [e-mail: {\tt cr@u.northwestern.edu}]} \altaffiltext{2}{California
+  Institute of Technology, Pasadena, CA 92215, USA}
 
@@
 
-Within the next five years, the Advanced LIGO/Virgo network will have reached a sensitivity sufficient to enable the routine
- detection of gravitational waves.
-Beyond the initial detection, the scientific promise of these instruments relies on the ability to perform parameter estimation.
-The majority of this effort has been towards the detection
-   and characterization of gravitational waves from compact binary coalescence, e.g. the coalescence of binary 
-   neutron stars.  While several previous studies have focused on the parameter estimation abilities of advanced detectors, 
-   the majority have relied on approximation techniques such as the Fisher Matrix.  We report the statistical 
-   uncertainties that will be achievable, in practice, using the full parameter estimation machinery developed by the  
-   LIGO/Virgo Collaboration.  We find the recovery of the individual masses to be fractionally within 
-   10\% at the 65\% credible intervals for equal-mass systems, and within 2\% for unequal-mass systems.
-     We also report the average uncertainties on the sky-locations, luminosity distance, and orbital inclinations of randomly 
-     distributed sources that can be achieved by different network configurations.
+Within the next five years, the Advanced LIGO/Virgo network will have
+reached a sensitivity sufficient to enable the routine detection of
+gravitational waves.  Beyond the initial detection, the scientific
+promise of these instruments relies on the ability to perform
+parameter estimation. The majority of this effort has been towards the
+detection and characterization of gravitational waves from compact
+binary coalescence, e.g. the coalescence of binary neutron stars.
+While several previous studies have focused on the parameter
+estimation abilities of advanced detectors, the majority have relied
+on approximation techniques such as the Fisher Matrix.  We report the
+statistical uncertainties that will be achievable, in practice, using
+the full parameter estimation machinery developed by the LIGO/Virgo
+Collaboration.  We find the recovery of the individual masses to be
+fractionally within 10\% at the 65\% credible intervals for equal-mass
+systems, and within 2\% for unequal-mass systems.  We also report the
+average uncertainties on the sky-locations, luminosity distance, and
+orbital inclinations of randomly distributed sources that can be
+achieved by different network configurations.
 \end{abstract}
@@
 
-Within the next few
- years, the first generation of gravitational-wave detectors capable 
- of regularly resolving astrophysical sources will come online \citep{AdvLIGO,AdvVirgo}.
- The Advanced LIGO and Virgo detectors will provide the first insights
- into the final moment of binary compact object mergers, including the 
- merger of binary neutron star systems.  Intense preparations are underway
- to characterize and extract as much physical 
- information as possible from these signals.
-
-The mergers of binary neutron stars (BNS) are expected to be the most common
-compact binary source in the advanced detector era.   Models from stellar 
-evolution and observations of binary pulsars suggest that the number of binary neutron star mergers within 
-Advanced LIGO/Virgo's detection horizon could reach into the hundreds each 
-year, with an expected mean of $\sim 40$ per year \citep{RatesPaper}. 
-Although the peak sensitivity of ground-based detectors
-is not focused on the frequency at which BNS systems merge, it could still
-be possible to extract information about both strong field gravitational 
-physics \carl{[CITE]} and the hydrodynamics of dense matter (e.g. the equation 
-of state of nuclear matter) \carl{[CITE]}.  Furthermore, the observations of multiple BNS
-systems will provide key insight into the evolution of binary systems in the field \citep{VickyRates,KimRates}
-. As such, BNS systems will likely 
-form the ``bread and butter'' of the compact binary coalescence detection effort in the coming 
-years.
-
-Of course one must distinguish between the detection of 
-such events, and the precision measurement of the relevant physical parameters.
-The detection of BNS systems will be performed with a matched filtering approach.  
-By comparing the data stream with a bank of theoretical templates, the 
- time-series data can be searched for candidate signals at a sufficiently
-  rapid rate to analyze months of data.  When the overlap between one of the template waveforms and the 
-detector output is sufficiently large (97\%), a detection candidate is found.  However,
-the parameter space of these signals can be highly degenerate, with several 
-locations in parameter space corresponding to nearly identical waveforms.  In 
-order to fully realize the science potential of these instruments, we must 
-perform a full exploration of the parameter space for each detection.  By 
-analyzing the parameter space of each candidate with a Bayesian inference technique, 
- we will be able to make precise, scientifically meaningful
-statements about the physics of these systems.  To 
-that end, we employ a Markov-Chain Monte Carlo sampling algorithm, 
-\texttt{lalinference\_mcmc}, included in the LIGO Algorithm Library parameter
-estimation code, \texttt{LALInference}, to analyze the parameter space of BNS systems.
-
-By employing the full parameter-estimation machinery that will eventually be
-used in the Advanced LIGO/Virgo era, our results give the first estimates at the 
-realistic capabilities of advanced ground-based detectors to characterize BNS systems.
-  Until recently, the majority of studies have employed the Fisher matrix formalism which was 
-first adapted for gravitational-wave parameter estimation by \citep{FinnDetection}.
-While each of these studies \citep{PoissonWill,CutlerFlanagan,ArunPE} have pointed out the limitations 
-and flaws of the Fisher Information Matrix, there has been no study which investigates
-the BNS parameter estimation capabilities of Advanced LIGO/Virgo using the techniques
-that will eventually be employed.  The recent work of \cite{Vallisneri} and our 
-own work \citep{Inadequacies} has demonstrated that the Fisher matrix cannot even
-be treated as a lower bound on the standard deviations of certain parameters
-(particularly the masses) measurable in gravitational-wave detectors.
-
-In this paper, we perform a systematic study of the statistical uncertainties with
-which the Advanced LIGO/Virgo network will be able to measure the basic parameters of 
-BNS mergers.  In Section \ref{PEsection}, we describe
-the machinery of our parameter estimation code, \texttt{LALInference}, and the associated
-MCMC sampler, \texttt{lalinference\_mcmc}, as well as the frequency-domain 
-gravitational-wave template we employ.   In Section \ref{resultsSection}, we qualitatively 
-analyze the posterior probability density functions for BNS systems with different masses 
-and extrinsic parameters.  The results are divided into three parameter sets of interest: the
-recovery of the mass parameters (Section \ref{massSection}), the recovery of the orbital
-inclination and luminosity distance (Section \ref{idSection}), and the localization of sources 
-on the sky (Section \ref{skySection}).   Finally we provide quantitative 1-dimensional confidence
- intervals on each parameter in Section \ref{ciSection}.  These results, contained
- in Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}, are intended as a reference for the 
- optimal BNS parameter estimation capabilities of Advanced LIGO/Virgo.
-   We assume that $G=c=1$ throughout.
+Within the next few years, the first generation of gravitational-wave
+detectors capable of regularly resolving astrophysical sources will
+come online \citep{AdvLIGO,AdvVirgo}.  The Advanced LIGO and Virgo
+detectors will provide the first insights into the final moment of
+binary compact object mergers, including the merger of binary neutron
+star systems.  Intense preparations are underway to characterize and
+extract as much physical information as possible from these signals.
+
+The mergers of binary neutron stars (BNS) are expected to be the most
+common compact binary source in the advanced detector era.  Models
+from stellar evolution and observations of binary pulsars suggest that
+the number of binary neutron star mergers within Advanced LIGO/Virgo's
+detection horizon could reach into the hundreds each year, with an
+expected mean of $\sim 40$ per year \citep{RatesPaper}.  Although the
+peak sensitivity of ground-based detectors is not focused on the
+frequency at which BNS systems merge, it could still be possible to
+extract information about both strong field gravitational physics
+\carl{[CITE]} and the hydrodynamics of dense matter (e.g. the equation
+of state of nuclear matter) \carl{[CITE]}.  Furthermore, the
+observations of multiple BNS systems will provide key insight into the
+evolution of binary systems in the field \citep{VickyRates,KimRates}
+. As such, BNS systems will likely form the ``bread and butter'' of
+the compact binary coalescence detection effort in the coming years.
+
+Of course one must distinguish between the detection of such events,
+and the precision measurement of the relevant physical parameters.
+The detection of BNS systems will be performed with a matched
+filtering approach.  By comparing the data stream with a bank of
+theoretical templates, the time-series data can be searched for
+candidate signals at a sufficiently rapid rate to analyze months of
+data.  When the overlap between one of the template waveforms and the
+detector output is sufficiently large (97\%), a detection candidate is
+found.  However, the parameter space of these signals can be highly
+degenerate, with several locations in parameter space corresponding to
+nearly identical waveforms.  In order to fully realize the science
+potential of these instruments, we must perform a full exploration of
+the parameter space for each detection.  By analyzing the parameter
+space of each candidate with a Bayesian inference technique, we will
+be able to make precise, scientifically meaningful statements about
+the physics of these systems.  To that end, we employ a Markov-Chain
+Monte Carlo sampling algorithm, \texttt{lalinference\_mcmc}, included
+in the LIGO Algorithm Library parameter estimation code,
+\texttt{LALInference}, to analyze the parameter space of BNS systems.
+
+By employing the full parameter-estimation machinery that will
+eventually be used in the Advanced LIGO/Virgo era, our results give
+the first estimates at the realistic capabilities of advanced
+ground-based detectors to characterize BNS systems.  Until recently,
+the majority of studies have employed the Fisher matrix formalism
+which was first adapted for gravitational-wave parameter estimation by
+\citep{FinnDetection}.  While each of these studies
+\citep{PoissonWill,CutlerFlanagan,ArunPE} have pointed out the
+limitations and flaws of the Fisher Information Matrix, there has been
+no study which investigates the BNS parameter estimation capabilities
+of Advanced LIGO/Virgo using the techniques that will eventually be
+employed.  The recent work of \cite{Vallisneri} and our own work
+\citep{Inadequacies} has demonstrated that the Fisher matrix cannot
+even be treated as a lower bound on the standard deviations of certain
+parameters (particularly the masses) measurable in gravitational-wave
+detectors.
+
+In this paper, we perform a systematic study of the statistical
+uncertainties with which the Advanced LIGO/Virgo network will be able
+to measure the basic parameters of BNS mergers.  In Section
+\ref{PEsection}, we describe the machinery of our parameter estimation
+code, \texttt{LALInference}, and the associated MCMC sampler,
+\texttt{lalinference\_mcmc}, as well as the frequency-domain
+gravitational-wave template we employ.  In Section
+\ref{resultsSection}, we qualitatively analyze the posterior
+probability density functions for BNS systems with different masses
+and extrinsic parameters.  The results are divided into three
+parameter sets of interest: the recovery of the mass parameters
+(Section \ref{massSection}), the recovery of the orbital inclination
+and luminosity distance (Section \ref{idSection}), and the
+localization of sources on the sky (Section \ref{skySection}).
+Finally we provide quantitative 1-dimensional confidence intervals on
+each parameter in Section \ref{ciSection}.  These results, contained
+in Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}, are
+intended as a reference for the optimal BNS parameter estimation
+capabilities of Advanced LIGO/Virgo.  We assume that $G=c=1$
+throughout.
 
@@
 %techniques must be introduced.  First,
-We assume that the time-domain signal in a gravitational-wave
-network can be written as a combination of a gravitational
-waveform $h_0$ and the noise of the detector $n$.  We further assume
-that this noise is stationary and Gaussian with zero mean.  Therefore,
-the detector output is simply
+We assume that the time-domain signal in a gravitational-wave network
+can be written as a combination of a gravitational waveform $h_0$ and
+the noise of the detector $n$.  We further assume that this noise is
+stationary and Gaussian with zero mean.  Therefore, the detector
+output is simply
 \begin{equation}
@@
 \end{equation}
-Since the noise model is Gaussian, we can write the
-probability of a specific signal realization $s$ as proportional to the probability
-that the residual is Gaussian distributed once the waveform has been subtracted
+Since the noise model is Gaussian, we can write the probability of a
+specific signal realization $s$ as proportional to the probability
+that the residual is Gaussian distributed once the waveform has been
+subtracted
 \begin{align}
@@
 \end{align}
-where $\thpara$ is the set of parameters for the template
-waveforms, and $p(s | \thpara)$ is the likelihood of the signal $s$ given the parameters $\thpara$.
-  The inner product, $\left< ~|~ \right> $, is defined using the noise
-spectrum of the detectors as
-\begin{equation}
-  \left<a|b\right> \equiv 4 \Re \int \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df ,
+where $\thpara$ is the set of parameters for the template waveforms,
+and $p(s | \thpara)$ is the likelihood of the signal $s$ given the
+parameters $\thpara$.  The inner product, $\left< ~|~ \right> $, is
+defined using the noise spectrum of the detectors as
+\begin{equation}
+  \left<a|b\right> \equiv 4 \Re \int
+  \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df ,
   \label{innerProduct}
 \end{equation}
-where $S_n(f)$ is the one-sided power spectral density (PSD) as a function
-of frequency, and $\tilde{a}(f)$ and $\tilde{b}(f)$ are the Fourier
-transforms of the time-domain data $a(t)$ and $b(t)$.  If we pick a set of parameters $\thpara$ such that
-$h(\thpara) = h_0$, then the posterior \eqref{posterior}
-will be near a global maximum; however, our choice of prior the presence of noise will in
-general deflect the maximum of our posterior away from the value at
-$\thpara_0$.  Therefore, the maximum posterior parameters do not necessarily 
-correspond to the true parameters of the source, so when interpreting parameter
- estimation results we must consider the full posterior distribution function.
+where $S_n(f)$ is the one-sided power spectral density (PSD) as a
+function of frequency, and $\tilde{a}(f)$ and $\tilde{b}(f)$ are the
+Fourier transforms of the time-domain data $a(t)$ and $b(t)$.  If we
+pick a set of parameters $\thpara$ such that $h(\thpara) = h_0$, then
+the posterior \eqref{posterior} will be near a global maximum;
+however, our choice of prior the presence of noise will in general
+deflect the maximum of our posterior away from the value at
+$\thpara_0$.  Therefore, the maximum posterior parameters do not
+necessarily correspond to the true parameters of the source, so when
+interpreting parameter estimation results we must consider the full
+posterior distribution function.
 
@@
 \begin{align}
-  p(\thpara | s) &= \frac{p(\thpara)p(s | \thpara)}{p(s)} \nonumber\\
-  & \propto p(\thpara) \exp\left[-\frac{1}{2}\big < s - h(\thpara) | s-h(\thpara) \big > \right] ,
+  p(\thpara | s) &= \frac{p(\thpara)p(s | \thpara)}{p(s)}
+  \nonumber\\ & \propto p(\thpara) \exp\left[-\frac{1}{2}\big < s -
+    h(\thpara) | s-h(\thpara) \big > \right] ,
   \label{posterior}
 \end{align}
-where $p(\thpara)$ are the prior probabilities on our
-source parameters and $p(s)$ is a normalization constant.
-
-We are interested in the posterior $p(\thpara | s)$ as it encodes information about the
-prior state of knowledge about the problem in addition to the likelihood of the signal.
-  For instance, since it is assumed that compact binaries
-form homogeneously in the local universe observable by advanced detectors,
- we can safely assume that the population of
-sources will be distributed homogeneously in volume, or evenly in $D^2$. 
- Our prior information can come from mathematical limits in the parameter space or
-from our \textit{a priori} knowledge of astrophysical systems.  We employ priors which are
+where $p(\thpara)$ are the prior probabilities on our source
+parameters and $p(s)$ is a normalization constant.
+
+We are interested in the posterior $p(\thpara | s)$ as it encodes
+information about the prior state of knowledge about the problem in
+addition to the likelihood of the signal.  For instance, since it is
+assumed that compact binaries form homogeneously in the local universe
+observable by advanced detectors, we can safely assume that the
+population of sources will be distributed homogeneously in volume, or
+evenly in $D^2$.  Our prior information can come from mathematical
+limits in the parameter space or from our \textit{a priori} knowledge
+of astrophysical systems.  We employ priors which are
 
 \begin{itemize}
-\item uniform in component masses from $0.8M_{\odot} \leq M_{1,2} \leq 30M_{\odot}$, with a minimum chirp mass  \eqref{eqRatioCM} of 0.6 $M_{\odot}$,
-\item uniform in volume, which implies a luminosity distance prior of $p(D) = D^2 dD$,
-\item uniform in coalescence time over the segment of data being analyzed, and
-\item uniform in all other parameters, with angular parameters being flat over their corresponding domains.
+\item uniform in component masses from $0.8M_{\odot} \leq M_{1,2} \leq
+  30M_{\odot}$, with a minimum chirp mass \eqref{eqRatioCM} of 0.6
+  $M_{\odot}$,
+\item uniform in volume, which implies a luminosity distance prior of
+  $p(D) = D^2 dD$,
+\item uniform in coalescence time over the segment of data being
+  analyzed, and
+\item uniform in all other parameters, with angular parameters being
+  flat over their corresponding domains.
 \end{itemize}
 
-\noindent  The mass priors listed here are the generic priors used in follow-up analysis, not specifically for BNS systems.
-While we could have used a prior with a lower component mass cutoff for the present study, in practice the higher prior boundary does not effect our current analysis.
+\noindent The mass priors listed here are the generic priors used in
+follow-up analysis, not specifically for BNS systems.  While we could
+have used a prior with a lower component mass cutoff for the present
+study, in practice the higher prior boundary does not effect our
+current analysis.
 
@@
 
-The LIGO Algorithm Library Bayesian inference code, \texttt{LALInference}, is designed as 
-a unified framework for gravitational-wave parameter estimation.  By using a common setup for 
-waveform generation, PSD estimation, data handling, and other associated techniques from gravitational-wave parameter estimation, \texttt{LALInference} allows the implementation of multiple samplers of the parameter space, including Nested Sampling (\texttt{lalinference\_nest}, described in \cite{nestedsampling2010}) and Markov-Chain Monte Carlo (\texttt{lalinference\_mcmc}).
-We elect to use the MCMC sampler for this study.
-\texttt{lalinference\_mcmc} is based upon the previously described code,
-\texttt{SpinSpiral} \citep{spinspiral2009, spinspiral2010}.  The MCMC employs a Metropolis-Hastings sampling algorithm, which can be described as follows \citep{Gilks99}:
+The LIGO Algorithm Library Bayesian inference code,
+\texttt{LALInference}, is designed as a unified framework for
+gravitational-wave parameter estimation.  By using a common setup for
+waveform generation, PSD estimation, data handling, and other
+associated techniques from gravitational-wave parameter estimation,
+\texttt{LALInference} allows the implementation of multiple samplers
+of the parameter space, including Nested Sampling
+(\texttt{lalinference\_nest}, described in \cite{nestedsampling2010})
+and Markov-Chain Monte Carlo (\texttt{lalinference\_mcmc}).  We elect
+to use the MCMC sampler for this study.  \texttt{lalinference\_mcmc}
+is based upon the previously described code, \texttt{SpinSpiral}
+\citep{spinspiral2009, spinspiral2010}.  The MCMC employs a
+Metropolis-Hastings sampling algorithm, which can be described as
+follows \citep{Gilks99}:
 
@@
   \begin{equation}
-    p_\mathrm{accept} = \min \left[ 1, \frac{p(\boldsymbol{\theta_{\text{new}}}|s) q\left(\boldsymbol{\theta_{\text{old}}} | \boldsymbol{\theta_{\text{new}}} \right)}{p(\boldsymbol{\theta_{\text{old}}}|s) q\left(\boldsymbol{\theta_{\text{new}}} | \boldsymbol{\theta_{\text{old}}} \right)} \right].
+    p_\mathrm{accept} = \min \left[ 1,
+      \frac{p(\boldsymbol{\theta_{\text{new}}}|s)
+        q\left(\boldsymbol{\theta_{\text{old}}} |
+        \boldsymbol{\theta_{\text{new}}}
+        \right)}{p(\boldsymbol{\theta_{\text{old}}}|s)
+        q\left(\boldsymbol{\theta_{\text{new}}} |
+        \boldsymbol{\theta_{\text{old}}} \right)} \right].
   \end{equation}
@@
 The above procedure is designed to record a chain of samples whose
-distribution is $p\left(\thpara|s\right)$.  By drawing a sufficient ($\sim1000$) number
- of effectively independent samples from the posterior, the chains traces out the functional form of the posterior,
- gathering more samples from regions with high posterior probability density.  Depending on
-the proposal distribution, $q$, the convergence (mixing) of the chain
-may be rapid or slow.  We employ multiple optimization techniques,
-including both specially-crafted jump proposals ($q$) and parallel tempering, to ensure
-adequate mixing of the Markov Chains throughout our parameter space.
-Both samplers were tuned and 
-developed during the last science run of the Initial LIGO/Virgo network.  
-A description of the parameter estimation capabilities of these two samplers with respect to
-real interferometer data, as well as a more detailed description of the algorithms and
+distribution is $p\left(\thpara|s\right)$.  By drawing a sufficient
+($\sim1000$) number of effectively independent samples from the
+posterior, the chains traces out the functional form of the posterior,
+gathering more samples from regions with high posterior probability
+density.  Depending on the proposal distribution, $q$, the convergence
+(mixing) of the chain may be rapid or slow.  We employ multiple
+optimization techniques, including both specially-crafted jump
+proposals ($q$) and parallel tempering, to ensure adequate mixing of
+the Markov Chains throughout our parameter space.  Both samplers were
+tuned and developed during the last science run of the Initial
+LIGO/Virgo network.  A description of the parameter estimation
+capabilities of these two samplers with respect to real interferometer
+data, as well as a more detailed description of the algorithms and
 checks for convergence, can be found in \cite{S6PE}.
@@
 
-We use a frequency-domain waveform accurate up to $3.5$
-post-Newtonian (pN) order in phase and 3 pN order in amplitude.  We restrict ourselves to
-quasi-circular, non-spinning waveforms as a simplifying assumption.  The standard
-form of our waveform model, known as the \textit{TaylorF2}
-approximant, is calculated via the stationary-phase approximation.
-  In this setup, the gravitational-wave
-amplitude is given by
+We use a frequency-domain waveform accurate up to $3.5$ post-Newtonian
+(pN) order in phase and 3 pN order in amplitude.  We restrict
+ourselves to quasi-circular, non-spinning waveforms as a simplifying
+assumption.  The standard form of our waveform model, known as the
+\textit{TaylorF2} approximant, is calculated via the stationary-phase
+approximation.  In this setup, the gravitational-wave amplitude is
+given by
 \begin{equation}
@@
 \end{equation}
-where $a(t_f)$ is the amplitude evaluated at a stationary-phase reference point, which to lowest order
-takes the form $a(t_f) \propto f^{-7/6} \chmass^{5/6}\Theta(\text{angle})/D$, where $D$ is
-the luminosity distance of the binary, and $\psi(f)$ is the pN phase.
+where $a(t_f)$ is the amplitude evaluated at a stationary-phase
+reference point, which to lowest order takes the form $a(t_f) \propto
+f^{-7/6} \chmass^{5/6}\Theta(\text{angle})/D$, where $D$ is the
+luminosity distance of the binary, and $\psi(f)$ is the pN phase.
 $\Theta(\text{angle})$ is a function of the orbital orientation with
@@
 inclination, and the wave polarization.  In addition to the total
-mass, $M_{tot}\equiv M_1+M_2$, it is convenient to work with the
-mass ratio and chirp mass, defined by
-\begin{equation}
-  q\equiv M_1/M_2~~~~\text{and}~~~~\chmass = (M_1 M_2)^{3/5} M_{tot}^{-1/5},
+mass, $M_{tot}\equiv M_1+M_2$, it is convenient to work with the mass
+ratio and chirp mass, defined by
+\begin{equation}
+  q\equiv M_1/M_2~~~~\text{and}~~~~\chmass = (M_1 M_2)^{3/5}
+  M_{tot}^{-1/5},
   \label{eqRatioCM}
 \end{equation}
-respectively.\footnote{Most gravitational-wave literature instead uses the \textit{symmetric mass ratio}, defined as $\eta \equiv M_1 M_2 / M^2$.
-We elect to use $q$ as it is more physically intuitive, and the prior $p(q)$ is uniform when the component
-mass priors are uniform.}  By convention, $M_1 \geq M_2$.  The stationary phase then becomes an expansion in the 
-Newtonian orbital velocity, $v=(\pi M_{tot} f)^{1/3}$, 
-\begin{equation}
-\psi(f) = 2 \pi f t_c - \phi_0 + \frac{\pi}{4} + \frac{3}{128}\left(\frac{M_{tot}}{\chmass}\right)^{5/3}\sum^{n}_{k=0}\alpha_{k}v^{k-5}
+respectively.\footnote{Most gravitational-wave literature instead uses
+  the \textit{symmetric mass ratio}, defined as $\eta \equiv M_1 M_2 /
+  M^2$.  We elect to use $q$ as it is more physically intuitive, and
+  the prior $p(q)$ is uniform when the component mass priors are
+  uniform.}  By convention, $M_1 \geq M_2$.  The stationary phase then
+becomes an expansion in the Newtonian orbital velocity, $v=(\pi
+M_{tot} f)^{1/3}$,
+\begin{equation}
+\psi(f) = 2 \pi f t_c - \phi_0 + \frac{\pi}{4} +
+\frac{3}{128}\left(\frac{M_{tot}}{\chmass}\right)^{5/3}\sum^{n}_{k=0}\alpha_{k}v^{k-5}
 \label{phase}
@@
 
-\noindent where the $\alpha_{k}$ coefficients are taken from the pN expansion to order $n/2$.
-See \cite{BuonannoWaveform} for a description and comparison of different waveform families.
-The terms $t_c$ and $\phi_0$ in equation (\ref{phase}) are constants of integration, referred to as the chirp time and coalescence phase, respectively.
-
-To perform the integral defined in \eqref{innerProduct}, we used as our power-spectral
-density the best estimate for a high-power, zero-detuning configuration of Advanced 
-LIGO, provided by the LIGO Scientific Collaboration.  Both the noise curve and technical 
-reports describing it can be found in \cite{ADVLIGONoise}.
-We consider two configurations of the advanced detector
-network: a three-detector configuation consistanting of the two LIGO sites 
-(in Hanford, WA and Livingston, LA) and the Virgo site (in Pisa, Italy), and a 
+\noindent where the $\alpha_{k}$ coefficients are taken from the pN
+expansion to order $n/2$.  See \cite{BuonannoWaveform} for a
+description and comparison of different waveform families.  The terms
+$t_c$ and $\phi_0$ in equation (\ref{phase}) are constants of
+integration, referred to as the chirp time and coalescence phase,
+respectively.
+
+To perform the integral defined in \eqref{innerProduct}, we used as
+our power-spectral density the best estimate for a high-power,
+zero-detuning configuration of Advanced LIGO, provided by the LIGO
+Scientific Collaboration.  Both the noise curve and technical reports
+describing it can be found in \cite{ADVLIGONoise}.  We consider two
+configurations of the advanced detector network: a three-detector
+configuation consistanting of the two LIGO sites (in Hanford, WA and
+Livingston, LA) and the Virgo site (in Pisa, Italy), and a
 four-detector configuration that adds the proposed LIGO-India detector
@@
 from a lower-frequency cutoff of $20\text{Hz}$ to the
-innermost-stable-circular orbit of the systems in question, which for a
-non-spinning binary is a function only of the total mass:
+innermost-stable-circular orbit of the systems in question, which for
+a non-spinning binary is a function only of the total mass:
 
@@
 
-We consier the mass parameters ($\chmass,q$) and the phasing parameters,
-($\phi_0,t_c$), to be the intrinsic parameters of a gravitational-wave signal.  There 
-are an additional 5 extrinsic parameters, independent of the pN orbital phase, which can
-modulate the amplitude of the signal in an independent fashion for each detector.  
-Combining these leads to our 9-dimensional parameter space for non-spinning systems,
+We consier the mass parameters ($\chmass,q$) and the phasing
+parameters, ($\phi_0,t_c$), to be the intrinsic parameters of a
+gravitational-wave signal.  There are an additional 5 extrinsic
+parameters, independent of the pN orbital phase, which can modulate
+the amplitude of the signal in an independent fashion for each
+detector.  Combining these leads to our 9-dimensional parameter space
+for non-spinning systems,
 \begin{equation}
@@
 \item $q$ is the mass ratio,
-\item $\phi_0$ and $t_c$ are the chirp phase and chirp time, arbitrary phasing parameters,
+\item $\phi_0$ and $t_c$ are the chirp phase and chirp time, arbitrary
+  phasing parameters,
 \item $D$ is the luminosity distance to the binary,
-\item $\iota$ is the orbital inclination (the angle between the orbital angular momentum and the line of sight), 
+\item $\iota$ is the orbital inclination (the angle between the
+  orbital angular momentum and the line of sight),
 \item $\psi$ is the gravitational-wave polarization, and
-\item $\alpha$ and $\delta$ are the right ascension and declination of the
-source on the sky.
+\item $\alpha$ and $\delta$ are the right ascension and declination of
+  the source on the sky.
 \end{itemize}
-  Since the wave amplitude depends on the orientation of the
-binary with respect to each detector, most of the information about these extrinsic
-parameters comes from two quantities: the time-of-arrival triangulation of 
-the source locations, and the relative amplitudes within the detector network.
+  Since the wave amplitude depends on the orientation of the binary
+  with respect to each detector, most of the information about these
+  extrinsic parameters comes from two quantities: the time-of-arrival
+  triangulation of the source locations, and the relative amplitudes
+  within the detector network.
 
@@
 \begin{equation}
-  \rho \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{| \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df,
+  \rho \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{|
+    \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df,
   \label{formalSNR}
@@
 where $\rho$ is the SNR and $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
-the frequency-domain data and template, respectively, and the normalization $\sigma$ is
-given by
+the frequency-domain data and template, respectively, and the
+normalization $\sigma$ is given by
 \begin{equation}
@@
 
-When dealing with network a of gravitational-wave detectors, the SNRs of the individual detectors add in quadrature.  That is, the network SNR for a detection is
+When dealing with network a of gravitational-wave detectors, the SNRs
+of the individual detectors add in quadrature.  That is, the network
+SNR for a detection is
 
@@
 
-\noindent where $\rho_i$ is the SNR, given by \eqref{formalSNR}, of the $i^{\text{th}}$ detector.
-
-For this study, we consider four seperate populations of BNS systems, with component mass 
-combinations of $1M_{\odot}/1M_{\odot}$, $1.4M_{\odot}/1.4M_{\odot}$, $1M_{\odot}/2.5M_{\odot}$, 
-and $2.5M_{\odot}/2.5M_{\odot}$.  Each population consisted of 40 signals distributed randomly
-in sky location, polarization, inclination, time-of-arrival, and coalescence phase.  The luminosity 
-distance, $D$, was selected to provide a network SNR of $\rho_{\text{network}}=20$ for each source.
-While unphysical from an astrophysics perspective (binary sources should be 
-distributed evenly in comoving volume), this choice allows us to explore the parameter estimation
-in the context of optimal detection candidates.
-
-Finally, note that the power-spectral density that defines the inner product \eqref{innerProduct} is simply 
-the time-averaged sensitivity of a given detector to a specific frequency.  Ignoring non-Gaussian glitches,
- any stretch of data should contain a specific noise realization drawn from a Gaussian colored by the PSD.
+\noindent where $\rho_i$ is the SNR, given by \eqref{formalSNR}, of
+the $i^{\text{th}}$ detector.
+
+For this study, we consider four seperate populations of BNS systems,
+with component mass combinations of $1M_{\odot}/1M_{\odot}$,
+$1.4M_{\odot}/1.4M_{\odot}$, $1M_{\odot}/2.5M_{\odot}$, and
+$2.5M_{\odot}/2.5M_{\odot}$.  Each population consisted of 40 signals
+distributed randomly in sky location, polarization, inclination,
+time-of-arrival, and coalescence phase.  The luminosity distance, $D$,
+was selected to provide a network SNR of $\rho_{\text{network}}=20$
+for each source.  While unphysical from an astrophysics perspective
+(binary sources should be distributed evenly in comoving volume), this
+choice allows us to explore the parameter estimation in the context of
+optimal detection candidates.
+
+Finally, note that the power-spectral density that defines the inner
+product \eqref{innerProduct} is simply the time-averaged sensitivity
+of a given detector to a specific frequency.  Ignoring non-Gaussian
+glitches, any stretch of data should contain a specific noise
+realization drawn from a Gaussian colored by the PSD.
 %   However, what we are interested in is not the parameter estimation that can occur in a specific draw
-  %  from this probability of noises, but the uncertainties averaged over all possible noise
-     realizations. Without a realistic model including the actual instrument sensitivity,
-      non stationary noise, and uncertainty in the PSD we cannot 
-     accurately simulate GW data to the point of making precise predictions about parameter 
-     estimation capabilities.  Furthermore, the posterior distribution from a future 
-     detection will be influenced by 
-     the realization of the noise at the time of the detection.  Because of this, we 
-     elect to focus only on the statistical 
-     errors due to the flexibility of the waveforms and the expected sensitivity of 
-     the advanced era detectors and suppress 
-     any effects of detector noise by not including a noise realization in our simulated data.
-       Consequently, what we recover with the MCMC  
-     could be interpreted as the posterior distribution function for each source averaged over all
-      possible (Gaussian) noise realizations 
-     assuming we have the correct PSD.    \footnote{Similarly to how the Fisher matrix formalism can
-      provide the Cramer-Rao bound averaged over
-     all noise realizations.  Unlike a Fisher matrix study, we make no assumptions about the 
-     shape of the posterior distribution function, nor the location of the peak, while still requiring a
-      feasible number of MCMC runs 
-     to sufficiently cover parameter space, which would not be the case had we needed to 
-     average several noise-dependent results.} To check that our reported statistical errors
-     are not in gross disagreement with those obtained in the presence of noise,  we selected a 
-       particular simulated signal to perform parameter estimation in several noise realizations.  
-       The comparison of the noise-dependent and noise-free results
-       can be found in \ref{noiseSection}.
+  % from this probability of noises, but the uncertainties averaged
+over all possible noise realizations. Without a realistic model
+including the actual instrument sensitivity, non stationary noise, and
+uncertainty in the PSD we cannot accurately simulate GW data to the
+point of making precise predictions about parameter estimation
+capabilities.  Furthermore, the posterior distribution from a future
+detection will be influenced by the realization of the noise at the
+time of the detection.  Because of this, we elect to focus only on the
+statistical errors due to the flexibility of the waveforms and the
+expected sensitivity of the advanced era detectors and suppress any
+effects of detector noise by not including a noise realization in our
+simulated data.  Consequently, what we recover with the MCMC could be
+interpreted as the posterior distribution function for each source
+averaged over all possible (Gaussian) noise realizations assuming we
+have the correct PSD.  \footnote{Similarly to how the Fisher matrix
+  formalism can provide the Cramer-Rao bound averaged over all noise
+  realizations.  Unlike a Fisher matrix study, we make no assumptions
+  about the shape of the posterior distribution function, nor the
+  location of the peak, while still requiring a feasible number of
+  MCMC runs to sufficiently cover parameter space, which would not be
+  the case had we needed to average several noise-dependent results.}
+To check that our reported statistical errors are not in gross
+disagreement with those obtained in the presence of noise, we selected
+a particular simulated signal to perform parameter estimation in
+several noise realizations.  The comparison of the noise-dependent and
+noise-free results can be found in \ref{noiseSection}.
 
@@
 
-Each set of MCMC samples is tested for convergence by examining both the Gelman-Rubin diagnostic and the auto-correlation length of the MCMC chains, the details of which can be found in \carl{[CITE]} and \carl{[CITE]}, respectively.
-However, there is an additional check we can consider: the standard matched filtering searches employed by the LIGO/Virgo collaboration assume that a detection will occur when one of the template waveforms matches the detector data with a signal overlap of 97\% or better \carl{[CITE]}.
-That is, for a template waveform $h^{t}(f)$ and detector output $s(f)$, an overlap of
-
-\begin{equation}
-\left< s | h^{t}\right> \geq 97\%
-\nonumber
-\end{equation}
-
-\noindent  yields a detection candidate.  This requirement provides us with a convenient test for the effectiveness 
-of our parameter estimation.  First, we note that maximizing our likelihood function, \eqref{likelihood},
-is identical to maximizing the SNR \eqref{formalSNR} of our template waveform in a given stretch of data.
-Therefore, the better the match between the template waveform and the data, the higher the SNR.  Since we
-assume, quite tautologically, that our parameter estimation code should estimate parameters at least as 
-well as a matched filtering approach, we would be immediately suspicious of any MCMC run whose 
-maximum-likelihood waveform had an SNR below that of our pipeline trigger.   In that case, we would perform
-the MCMC with a much longer runtime, until the maximum likelihood of our posterior distribution had an SNR
-at least as high as the detection.
-
-For the purposes of our present study, we reproduce this information as follows: since we know the true SNR
-of the signal we are simulating, we assume that the ``trigger'' SNR returned by our detection pipeline is 
-97\% of the true SNR.  We then assume any posterior distribution whose maximum likelihood satisfies
-
-\begin{equation}
-\text{Maximum Likelihood} \leq 0.97 \times \left(\frac{\rho_{inj}^2}{2}\right) 
-\nonumber
-\end{equation}
-
-\noindent has not converged.  As one would expect, the lower-mass, longer waveform systems require longer 
-to converge.  With our original runtime of one week over 8 processors, we found that seven of our 
-$1M_{\odot}/1M_{\odot}$ systems had not converged, while all but one system for our $1.4M_{\odot}/1.4M_{\odot}$
-and $1M_{\odot}/2.5M_{\odot}$ systems had converged.  All of the $2.5M_{\odot}/2.5M_{\odot}$ systems 
-converged within one week.
-
-\carl{[THIS SECTION INCOMPLETE  WILL REQUIRE THE FINISHED HLV/HLVI RUNS BEFORE I CAN COMPLETE IT]}
+Each set of MCMC samples is tested for convergence by examining both
+the Gelman-Rubin diagnostic and the auto-correlation length of the
+MCMC chains, the details of which can be found in \carl{[CITE]} and
+\carl{[CITE]}, respectively.  However, there is an additional check we
+can consider: the standard matched filtering searches employed by the
+LIGO/Virgo collaboration assume that a detection will occur when one
+of the template waveforms matches the detector data with a signal
+overlap of 97\% or better \carl{[CITE]}.  That is, for a template
+waveform $h^{t}(f)$ and detector output $s(f)$, an overlap of
+
+\begin{equation}
+\left< s | h^{t}\right> \geq 97\% \nonumber
+\end{equation}
+
+\noindent yields a detection candidate.  This requirement provides us
+with a convenient test for the effectiveness of our parameter
+estimation.  First, we note that maximizing our likelihood function,
+\eqref{likelihood}, is identical to maximizing the SNR
+\eqref{formalSNR} of our template waveform in a given stretch of data.
+Therefore, the better the match between the template waveform and the
+data, the higher the SNR.  Since we assume, quite tautologically, that
+our parameter estimation code should estimate parameters at least as
+well as a matched filtering approach, we would be immediately
+suspicious of any MCMC run whose maximum-likelihood waveform had an
+SNR below that of our pipeline trigger.  In that case, we would
+perform the MCMC with a much longer runtime, until the maximum
+likelihood of our posterior distribution had an SNR at least as high
+as the detection.
+
+For the purposes of our present study, we reproduce this information
+as follows: since we know the true SNR of the signal we are
+simulating, we assume that the ``trigger'' SNR returned by our
+detection pipeline is 97\% of the true SNR.  We then assume any
+posterior distribution whose maximum likelihood satisfies
+
+\begin{equation}
+\text{Maximum Likelihood} \leq 0.97 \times
+\left(\frac{\rho_{inj}^2}{2}\right) \nonumber
+\end{equation}
+
+\noindent has not converged.  As one would expect, the lower-mass,
+longer waveform systems require longer to converge.  With our original
+runtime of one week over 8 processors, we found that seven of our
+$1M_{\odot}/1M_{\odot}$ systems had not converged, while all but one
+system for our $1.4M_{\odot}/1.4M_{\odot}$ and
+$1M_{\odot}/2.5M_{\odot}$ systems had converged.  All of the
+$2.5M_{\odot}/2.5M_{\odot}$ systems converged within one week.
+
+\carl{[THIS SECTION INCOMPLETE WILL REQUIRE THE FINISHED HLV/HLVI RUNS
+    BEFORE I CAN COMPLETE IT]}
 \end{comment}
@@
 \begin{figure*}[t!]
-\centering
-\includegraphics[trim=7cm 0cm 0cm 0cm, clip=true,scale=0.55]{9dpdf.pdf}
+\centering \includegraphics[trim=7cm 0cm 0cm 0cm,
+  clip=true,scale=0.55]{9dpdf.pdf}
 %\begin{array}{ccc} 
@@
 %\end{array}$
-\caption{Marginalized 1D posterior probability density functions taken from a typical 
-$1.4M_{\odot}/1.4M_{\odot}$ BNS system.  We have plotted each of the 9 parameters for 
-our non-spinning BNS problem as stated in section \ref{waveformSection}.  Note how, 
-even for parameters with excellent recovery, the peak of the 1D Gaussian is displaced from 
-the injected value (in dashed red).  This is not due to a systematic bias, but is caused by the 
-marginalization of a single dimension from the full 9D posterior space.  To better see this effect, 
-compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in Figure~\ref{1414masses}}
+\caption{Marginalized 1D posterior probability density functions taken
+  from a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS system.  We have
+  plotted each of the 9 parameters for our non-spinning BNS problem as
+  stated in section \ref{waveformSection}.  Note how, even for
+  parameters with excellent recovery, the peak of the 1D Gaussian is
+  displaced from the injected value (in dashed red).  This is not due
+  to a systematic bias, but is caused by the marginalization of a
+  single dimension from the full 9D posterior space.  To better see
+  this effect, compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with
+  the 2D marginalized PDF in Figure~\ref{1414masses}}
 \end{figure*}
 
-Of the nine parameters in the domain of the waveform, only six are particularly physically
-interesting: the masses of the two binaries, $M_1$ and $M_2$, the orbital inclination,
-$\iota$, the angular position on the sky, $\alpha$ and $\delta$, and the luminosity 
-distance of the source, $D$.  While the coalescence phase $\phi_c$, the coalescence time
-$t_c$, and the wave polarization $\psi$ must be included in any parameter estimation of the 
-waveform, they do not encode any information of particular astrophysical interest.\footnote{For systems
- whose components are non-spinning.  The presence of intrinsic angular 
-momentum will, in general, couple to the coalescence phase and wave polarization.}
-
-In Figure~\ref{9dPDF}, we provide an example of the nine, 1-dimensional marginalized posterior 
-probability density functions recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system. 
- These PDFs are typical of the type of results that will be produced by parameter estimation
-  studies in the advanced  detector era.  Notice that the peak of several parameters, including the 
-  chirp mass, $\chmass$,  appears to be displaced from the true values in red.  This effect is due to 
-  the reduction of the  9-dimensional PDF to a series of marginalized 1-dimensional PDFs. 
-   For instance, the 1-dimensional PDF for chirp mass is marginalized via
-
-\begin{equation}
-p(\chmass | s) = \int _{\thpara \setminus \chmass} p(\thpara | s)~d(\thpara \setminus \chmass)
+Of the nine parameters in the domain of the waveform, only six are
+particularly physically interesting: the masses of the two binaries,
+$M_1$ and $M_2$, the orbital inclination, $\iota$, the angular
+position on the sky, $\alpha$ and $\delta$, and the luminosity
+distance of the source, $D$.  While the coalescence phase $\phi_c$,
+the coalescence time $t_c$, and the wave polarization $\psi$ must be
+included in any parameter estimation of the waveform, they do not
+encode any information of particular astrophysical
+interest.\footnote{For systems whose components are non-spinning.  The
+  presence of intrinsic angular momentum will, in general, couple to
+  the coalescence phase and wave polarization.}
+
+In Figure~\ref{9dPDF}, we provide an example of the nine,
+1-dimensional marginalized posterior probability density functions
+recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system.  These
+PDFs are typical of the type of results that will be produced by
+parameter estimation studies in the advanced detector era.  Notice
+that the peak of several parameters, including the chirp mass,
+$\chmass$, appears to be displaced from the true values in red.  This
+effect is due to the reduction of the 9-dimensional PDF to a series of
+marginalized 1-dimensional PDFs.  For instance, the 1-dimensional PDF
+for chirp mass is marginalized via
+
+\begin{equation}
+p(\chmass | s) = \int _{\thpara \setminus \chmass} p(\thpara |
+s)~d(\thpara \setminus \chmass)
 \label{mcMarginalization}
@@
 \noindent where the notation $\thpara \setminus \chmass$ implies all
-parameter of \eqref{parameterspace} except $\chmass$.  Other parameter and higher-dimensional marginalizations follow
- a similar convention.  In practice, the MCMC samples make this integral trivial: since the samples are distributed according 
-to the posterior, \eqref{mcMarginalization} can be calculated by simply reading off the relevant samples in a single parameter, 
-implicitly calculating a Monte-Carlo integral over all other parameters.
+parameter of \eqref{parameterspace} except $\chmass$.  Other parameter
+and higher-dimensional marginalizations follow a similar convention.
+In practice, the MCMC samples make this integral trivial: since the
+samples are distributed according to the posterior,
+\eqref{mcMarginalization} can be calculated by simply reading off the
+relevant samples in a single parameter, implicitly calculating a
+Monte-Carlo integral over all other parameters.
 
@@
 \begin{figure}[h!]
-  \centering
- \includegraphics[trim=1cm 0cm 2cm 0cm, clip=false,scale=0.63]{1414masses2D.pdf}
- \caption{2D marginalized posterior probability density functions for the mass parameters recovered in typical a $1.4M_{\odot}/1.4M_{\odot}$ system.
-The posteriors are plotted in terms of parameters used in the waveform, chirp mass ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual component masses of the binary ($M_1$ and $M_2$).
-In the $\chmass$-$q$ space, the posterior would resemble a Gaussian if not for the limitation of $q \leq 1$.
-The presence of the $q$ cutoff and the convention that $M_1 \geq M_2$ inform the non-Gaussian features present.
-When projected as 1D marginalized posteriors, the component masses resemble the posterior PDFs shown in figure \ref{metaMassPDFs}.}
+  \centering \includegraphics[trim=1cm 0cm 2cm 0cm,
+    clip=false,scale=0.63]{1414masses2D.pdf}
+ \caption{2D marginalized posterior probability density functions for
+   the mass parameters recovered in typical a
+   $1.4M_{\odot}/1.4M_{\odot}$ system.  The posteriors are plotted in
+   terms of parameters used in the waveform, chirp mass
+   ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual
+   component masses of the binary ($M_1$ and $M_2$).  In the
+   $\chmass$-$q$ space, the posterior would resemble a Gaussian if not
+   for the limitation of $q \leq 1$.  The presence of the $q$ cutoff
+   and the convention that $M_1 \geq M_2$ inform the non-Gaussian
+   features present.  When projected as 1D marginalized posteriors,
+   the component masses resemble the posterior PDFs shown in figure
+   \ref{metaMassPDFs}.}
   \label{1414masses}
@@
 \begin{figure}[h!]
-  \centering
- \includegraphics[trim=1cm 0cm 2cm 0cm, clip=false,scale=0.63]{125masses2D.pdf}
- \caption{Similar to Figure~\ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.
-The unequal mass ratio displaces the posterior PDFs from the $q \leq 1$ present in the equal mass case, yielding a Gaussian PDF in both the $\chmass$-$q$ and $M_1$-$M_2$ spaces.}
+  \centering \includegraphics[trim=1cm 0cm 2cm 0cm,
+    clip=false,scale=0.63]{125masses2D.pdf}
+ \caption{Similar to Figure~\ref{1414masses}, for a typical
+   $1M_{\odot}/2.5M_{\odot}$ system.  The unequal mass ratio displaces
+   the posterior PDFs from the $q \leq 1$ present in the equal mass
+   case, yielding a Gaussian PDF in both the $\chmass$-$q$ and
+   $M_1$-$M_2$ spaces.}
   \label{125masses}
@@
 \begin{figure*}[ht!]
-  \centering
- \includegraphics[trim=2cm 0cm 2cm 0cm, clip=false,scale=0.7]{newMasses.pdf}
- \caption{Mass PDFs for the four BNS systems, averaged over each of the 40 injections.
-The average is reported since, in practice, there was quantitatively no difference between the recovered PDFs for different systems with identical masses and SNRs.
-Systems with identical mass ratios but different total masses have quantitatively identical PDFs when normalized to the true total mass.}
+  \centering \includegraphics[trim=2cm 0cm 2cm 0cm,
+    clip=false,scale=0.7]{newMasses.pdf}
+ \caption{Mass PDFs for the four BNS systems, averaged over each of
+   the 40 injections.  The average is reported since, in practice,
+   there was quantitatively no difference between the recovered PDFs
+   for different systems with identical masses and SNRs.  Systems with
+   identical mass ratios but different total masses have
+   quantitatively identical PDFs when normalized to the true total
+   mass.}
   \label{metaMassPDFs}
@@
 
-Of the nine variables in our parameter space \eqref{parameterspace}, the two of immediate physical
-interest are the two parameters, $\chmass$ and $q$, or correspondingly the direct masses 
-of the two companions, $M_1$ and $M_2$.    As stated above, the ability of
-Advanced LIGO/Virgo to construct a population of BNS masses will be one of the more useful applications
-of gravitational-wave astronomy.
-
-We find that there is virtually no difference between the mass PDFs of our different injected signals
-within each mass bin.
-While this may initially seem disconcerting, it is to be expected.
-Recall that all of the BNS signals were injected with a network SNR of 20 into a zero-noise detector realization.
-Furthermore, note that the mass parameters are the only two which directly effect the phase of the TaylorF2 waveform \eqref{phase}.
-Therefore, as long as the injected mass parameters are identical within each mass system, and as long as the injected SNR is identical, the amount of recoverable information in each mass parameter should be almost identical, and for a sufficiently converged MCMC chain, the recovered posterior PDF should be identical.
-
-This effect can be summarized as follows: for non-spinning systems, the posterior probability of the masses,
-$p(\chmass, q | s)$, does not depend strongly on the recovery of the extrinsic parameters, $\phi_0$ or $t_c$.  Therefore, 
-systems with identical masses will produce identical mass PDFs.  The only noticeable difference will come from
- the specific realization of noise produced by the detector, which we address in Section \ref{noiseSection}.
+Of the nine variables in our parameter space \eqref{parameterspace},
+the two of immediate physical interest are the two parameters,
+$\chmass$ and $q$, or correspondingly the direct masses of the two
+companions, $M_1$ and $M_2$.  As stated above, the ability of Advanced
+LIGO/Virgo to construct a population of BNS masses will be one of the
+more useful applications of gravitational-wave astronomy.
+
+We find that there is virtually no difference between the mass PDFs of
+our different injected signals within each mass bin.  While this may
+initially seem disconcerting, it is to be expected.  Recall that all
+of the BNS signals were injected with a network SNR of 20 into a
+zero-noise detector realization.  Furthermore, note that the mass
+parameters are the only two which directly effect the phase of the
+TaylorF2 waveform \eqref{phase}.  Therefore, as long as the injected
+mass parameters are identical within each mass system, and as long as
+the injected SNR is identical, the amount of recoverable information
+in each mass parameter should be almost identical, and for a
+sufficiently converged MCMC chain, the recovered posterior PDF should
+be identical.
+
+This effect can be summarized as follows: for non-spinning systems,
+the posterior probability of the masses, $p(\chmass, q | s)$, does not
+depend strongly on the recovery of the extrinsic parameters, $\phi_0$
+or $t_c$.  Therefore, systems with identical masses will produce
+identical mass PDFs.  The only noticeable difference will come from
+the specific realization of noise produced by the detector, which we
+address in Section \ref{noiseSection}.
 
@@
 
-In Figures~\ref{1414masses} and~\ref{125masses}, we show the marginalized 2D posterior PDFs of our
- mass parameters for  prototypical equal mass and unequal mass binaries.  We include the PDF in both
-  the $\chmass$-$q$ space (relevant for the waveform and the MCMC algorithm), and the more physically 
-  interesting component mass space ($M_1$-$M_2$).  Although only the $1.4M_{\odot}/1.4M_{\odot}$ system
-   is included in Figure \ref{1414masses}, the PDF is quantitatively identical to the other equal mass cases, 
-   modulo a scaling factor.
-
-To condense the results into a single figure of merit, we average the 1-dimensional mass PDFs into a single 
-posterior probability for the system.  See Figure~\ref{metaMassPDFs}.  Notice how when averaged and
- normalized to the injected values, the recovery of the component masses depends only on the mass ratio.  
- Furthermore, for systems with equal component masses, the posterior barely extends beyond 15\% of the injected values.  
- If one assumes that the threshold between black
-   holes and neutron stars lies at approximately $3M_{\odot}$, then it might be assumed that
-   the mass recovery would allow one to discriminate between black holes and neutron stars.
-
-Unfortunately, this will not be feasible in practice.  We have neglected the spin of the binaries, which will be highly
-correlated to the masses.  This coupling means that a higher-massed spinning black hole systems can produce
- waveforms very similar to non-spinning, low-mass systems, making it extremely difficult to discern between non-spinning 
- neutron stars
- and spinning, more massive black holes \citep{Baird2013,Hannam2013}.  However, the situation is not hopeless: if the spins are misaligned, the spin 
- vectors will couple to the orientation of the binary (encoded in the three angles $\phi_0$, $\iota$, and $\psi$) via
- relativistic precession.  It remains to be seen if using fully spinning waveforms will make it possible for Advanced\
-  LIGO/Virgo to discern binary neutron stars from their spinning black hole counterparts.
-
-In Table \ref{ciTableIntrinsic}, we list the 65\% fractional credible intervals for the mass parameters.  We find that the 
-component masses for equal mass systems can be isolated to between 6\% and 9\% fractional uncertainty at the 65\% credible interval.
-This value drops to less than 2\% for the components of the unequal mass systems.
-Again, this
-neglects the effects of spin which can substantially increase these values.
+In Figures~\ref{1414masses} and~\ref{125masses}, we show the
+marginalized 2D posterior PDFs of our mass parameters for prototypical
+equal mass and unequal mass binaries.  We include the PDF in both the
+$\chmass$-$q$ space (relevant for the waveform and the MCMC
+algorithm), and the more physically interesting component mass space
+($M_1$-$M_2$).  Although only the $1.4M_{\odot}/1.4M_{\odot}$ system
+is included in Figure \ref{1414masses}, the PDF is quantitatively
+identical to the other equal mass cases, modulo a scaling factor.
+
+To condense the results into a single figure of merit, we average the
+1-dimensional mass PDFs into a single posterior probability for the
+system.  See Figure~\ref{metaMassPDFs}.  Notice how when averaged and
+normalized to the injected values, the recovery of the component
+masses depends only on the mass ratio.  Furthermore, for systems with
+equal component masses, the posterior barely extends beyond 15\% of
+the injected values.  If one assumes that the threshold between black
+holes and neutron stars lies at approximately $3M_{\odot}$, then it
+might be assumed that the mass recovery would allow one to
+discriminate between black holes and neutron stars.
+
+Unfortunately, this will not be feasible in practice.  We have
+neglected the spin of the binaries, which will be highly correlated to
+the masses.  This coupling means that a higher-massed spinning black
+hole systems can produce waveforms very similar to non-spinning,
+low-mass systems, making it extremely difficult to discern between
+non-spinning neutron stars and spinning, more massive black holes
+\citep{Baird2013,Hannam2013}.  However, the situation is not hopeless:
+if the spins are misaligned, the spin vectors will couple to the
+orientation of the binary (encoded in the three angles $\phi_0$,
+$\iota$, and $\psi$) via relativistic precession.  It remains to be
+seen if using fully spinning waveforms will make it possible for
+Advanced\ LIGO/Virgo to discern binary neutron stars from their
+spinning black hole counterparts.
+
+In Table \ref{ciTableIntrinsic}, we list the 65\% fractional credible
+intervals for the mass parameters.  We find that the component masses
+for equal mass systems can be isolated to between 6\% and 9\%
+fractional uncertainty at the 65\% credible interval.  This value
+drops to less than 2\% for the components of the unequal mass systems.
+Again, this neglects the effects of spin which can substantially
+increase these values.
 
@@
 \begin{figure}[h!]
-  \centering
- \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.75]{distIota2D.pdf}
- \caption{Typical marginalized 2D mass PDFs for luminosity distance $D$ and orbital inclination $\iota$. Notice the bimodal 
- distribution on the first PDF, that can occur when a system is detected nearly ``edge-on'' ($\iota \approx \pi/2$).  In general,
- the degeneracy between distance and inclination forces the PDF into one of these two paths when the system is not edge-on,
-  as seen in the second and third PDFs.}
+  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
+    clip=true,scale=0.75]{distIota2D.pdf}
+ \caption{Typical marginalized 2D mass PDFs for luminosity distance
+   $D$ and orbital inclination $\iota$. Notice the bimodal
+   distribution on the first PDF, that can occur when a system is
+   detected nearly ``edge-on'' ($\iota \approx \pi/2$).  In general,
+   the degeneracy between distance and inclination forces the PDF into
+   one of these two paths when the system is not edge-on, as seen in
+   the second and third PDFs.}
  \label{distIotaPDF}
@@
 
-Binary neutron star systems (along with neutron star/black hole systems) are one of the best candidates for progenitors of short-hard gamma-ray bursts \citep[and references therein]{Nakar2007}.
-After merger, the remnant is believed to emit the burst along the axis of orbital angular momentum, making the inclination of the binary system of particular interest to gamma-ray astronomy \citep{LSCGRB2010,Corsi2012}.
-The inclination is detected as a relative amplitude difference between the two gravitational-wave polarizations, such that to lowest order
+Binary neutron star systems (along with neutron star/black hole
+systems) are one of the best candidates for progenitors of short-hard
+gamma-ray bursts \citep[and references therein]{Nakar2007}.  After
+merger, the remnant is believed to emit the burst along the axis of
+orbital angular momentum, making the inclination of the binary system
+of particular interest to gamma-ray astronomy
+\citep{LSCGRB2010,Corsi2012}.  The inclination is detected as a
+relative amplitude difference between the two gravitational-wave
+polarizations, such that to lowest order
 
 \begin{align}
-h_+(f) &= \frac{1+\cos^2(\iota)}{2 D} \tilde{h}(f) \nonumber \\
-h_\times(f) &= i \frac{\cos(\iota)}{D}\tilde{h}(f)
+h_+(f) &= \frac{1+\cos^2(\iota)}{2 D} \tilde{h}(f) \nonumber
+\\ h_\times(f) &= i \frac{\cos(\iota)}{D}\tilde{h}(f)
 \end{align}
 
-\noindent It should be apparent that the luminosity distance $D$ and the inclination $\iota$ can be highly correlated in any parameter estimation study.
-
-Given this degeneracy, it should come as no surprise that the 2D marginalized posteriors of distance
- and inclination are the broadest of the six physically interesting parameters.  Four typical 2D PDFs are
-  presented in Figure~\ref{distIotaPDF}.  Notice the bimodal uncertainty 
-present in the top 2D PDF along the $\iota$ axis, due to the similarity between the evaluated
- likelihoods at $\iota$ and $\iota + \pi/2$.  As the majority of the information extracted via parameter 
- estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$ space will be 
- limited, even during the Advanced LIGO/Virgo era; however, if a gravitational-wave signal is 
- matched to a detected SGRB counterpart (which may occur at the rate of $\sim 3 yr^{-1}$ in Advanced LIGO/Virgo, 
- according to \cite{Metzger2013}), the optical information about the orbital inclination
- will provide an additional constraint on the D-$\iota$ space, vastly improving the luminosity distance recovery
- quoted here.
-
-In Table \ref{ciTableExtrinsic}, we list the averaged 65\% confidence intervals for distance and inclination.  
-Notice that the uncertainties on distance can be extreme, from tens to hundreds of $mpc$.  When discussing
-the inclination angle, we elected to use $|\cos(\iota)|$, as this maps the occasional bimodal structure into
-a single PDF, 
- and observing a compact merger at $\iota$ and $\iota + \pi/2$ should yield identical physics.  
+\noindent It should be apparent that the luminosity distance $D$ and
+the inclination $\iota$ can be highly correlated in any parameter
+estimation study.
+
+Given this degeneracy, it should come as no surprise that the 2D
+marginalized posteriors of distance and inclination are the broadest
+of the six physically interesting parameters.  Four typical 2D PDFs
+are presented in Figure~\ref{distIotaPDF}.  Notice the bimodal
+uncertainty present in the top 2D PDF along the $\iota$ axis, due to
+the similarity between the evaluated likelihoods at $\iota$ and $\iota
++ \pi/2$.  As the majority of the information extracted via parameter
+estimation is from the phase of the signal, the recovery of a
+posterior in $D$-$\iota$ space will be limited, even during the
+Advanced LIGO/Virgo era; however, if a gravitational-wave signal is
+matched to a detected SGRB counterpart (which may occur at the rate of
+$\sim 3 yr^{-1}$ in Advanced LIGO/Virgo, according to
+\cite{Metzger2013}), the optical information about the orbital
+inclination will provide an additional constraint on the D-$\iota$
+space, vastly improving the luminosity distance recovery quoted here.
+
+In Table \ref{ciTableExtrinsic}, we list the averaged 65\% confidence
+intervals for distance and inclination.  Notice that the uncertainties
+on distance can be extreme, from tens to hundreds of $mpc$.  When
+discussing the inclination angle, we elected to use $|\cos(\iota)|$,
+as this maps the occasional bimodal structure into a single PDF, and
+observing a compact merger at $\iota$ and $\iota + \pi/2$ should yield
+identical physics.
 %Since $|\cos(\iota)|$ maps the bi-modal structure in the inclination PDFs seen in Figure \ref{distIotaPDF} to a single
@@
 
-Unlike the mass parameters, the recovery of the position on the sky is highly dependent 
-on the location of the source with respect to the detector network in question. 
-For the HLV configuration, the three-detector network can only localize signals to one of
-two points in the sky.  That is, when using only time-of-arrival information, there is 
-equal support in the probability density functions near true location and near the 
-point reflected through the plane formed by the three detectors.  See  \cite{Fairhurst2011} for
- a global analysis of time-of-arrival accuracy for various network configurations, including those considered
- here.
-
-  In practice, however, additional information from the wave polarization and the relative difference
-  in SNR between individual detectors can break this plane-reflected degeneracy,
-   leading to a bi-modal distribution with significantly more support in one mode of the PDF.
-     By fitting for the sky location and the polarization simultaneously, the MCMC can often identify
-   the correct mode on the sky.  For the four-detector configuration, this concern is irrelevant: even with time-of-arrival
-   data alone, the HLVI network can constrain any source to a single mode on the sky.  Even then, there are still locations 
-   on the sky in which two or more detectors are not sensitive to the gravitational-wave signal, yielding
+Unlike the mass parameters, the recovery of the position on the sky is
+highly dependent on the location of the source with respect to the
+detector network in question.  For the HLV configuration, the
+three-detector network can only localize signals to one of two points
+in the sky.  That is, when using only time-of-arrival information,
+there is equal support in the probability density functions near true
+location and near the point reflected through the plane formed by the
+three detectors.  See \cite{Fairhurst2011} for a global analysis of
+time-of-arrival accuracy for various network configurations, including
+those considered here.
+
+  In practice, however, additional information from the wave
+  polarization and the relative difference in SNR between individual
+  detectors can break this plane-reflected degeneracy, leading to a
+  bi-modal distribution with significantly more support in one mode of
+  the PDF.  By fitting for the sky location and the polarization
+  simultaneously, the MCMC can often identify the correct mode on the
+  sky.  For the four-detector configuration, this concern is
+  irrelevant: even with time-of-arrival data alone, the HLVI network
+  can constrain any source to a single mode on the sky.  Even then,
+  there are still locations on the sky in which two or more detectors
+  are not sensitive to the gravitational-wave signal, yielding
   distorted, non-Gaussian PDFs.
 
-The sky location uncertainties for HLV and HLVI are shown in Figures \ref{2525SkyLocHLV}
- and \ref{2525SkyLocHLVI} respectively.  We show all four mass bins together, since in practice
-  the mass of the signals has no effect on the recovery of the sky location for the considered BNS systems.
-    Only the location on 
-  the sky, the network configuration, and the other extrinsic parameters were found to be relevant.  
-  In particular, notice the increase in efficiency between the HLV configuration and the HLVI 
-  configuration.  In the HLV configuration, there exist points on the sky in which the signal was injected
-  near the plane of the detector network.  This causes the elongated, ``banana-shaped'' PDFs seen in
-  Figure \ref{2525SkyLocHLV}.  In the HLVI configuration, the plane is no longer relevant, and there are substantially
-  less regions in which only two detectors see a sufficiently strong signal.  
-  See \cite{Veitch2012} for a more detailed comparison of the sky-localization benefits of the HLVI 
-  configuration verses the three-detector network.  As previously, the quantitative results for the two network configurations
-  are reported in Table \ref{ciTableExtrinsic}.
+The sky location uncertainties for HLV and HLVI are shown in Figures
+\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI} respectively.  We show
+all four mass bins together, since in practice the mass of the signals
+has no effect on the recovery of the sky location for the considered
+BNS systems.  Only the location on the sky, the network configuration,
+and the other extrinsic parameters were found to be relevant.  In
+particular, notice the increase in efficiency between the HLV
+configuration and the HLVI configuration.  In the HLV configuration,
+there exist points on the sky in which the signal was injected near
+the plane of the detector network.  This causes the elongated,
+``banana-shaped'' PDFs seen in Figure \ref{2525SkyLocHLV}.  In the
+HLVI configuration, the plane is no longer relevant, and there are
+substantially less regions in which only two detectors see a
+sufficiently strong signal.  See \cite{Veitch2012} for a more detailed
+comparison of the sky-localization benefits of the HLVI configuration
+verses the three-detector network.  As previously, the quantitative
+results for the two network configurations are reported in Table
+\ref{ciTableExtrinsic}.
 
 \begin{figure*}[ht!]
-  \centering
- \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm 0cm]{HLVsky.pdf}
- \caption{The uncertainty on the sky of 160 BNS systems in the HLV detector configuration.
-Each region represents a single injection, with the colored central region representing the 65\% uncertainty region on the sphere, and the gray region representing the 90\% uncertainty region.
-The color scheme indicates the total solid angle size of the 65\% region.
-Note the similar shape of the uncertainty regions at particular points; this is due to the specific realization of our network pattern sensitivity.}
+  \centering \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm
+    0cm]{HLVsky.pdf}
+ \caption{The uncertainty on the sky of 160 BNS systems in the HLV
+   detector configuration.  Each region represents a single injection,
+   with the colored central region representing the 65\% uncertainty
+   region on the sphere, and the gray region representing the 90\%
+   uncertainty region.  The color scheme indicates the total solid
+   angle size of the 65\% region.  Note the similar shape of the
+   uncertainty regions at particular points; this is due to the
+   specific realization of our network pattern sensitivity.}
  \label{2525SkyLocHLV}
@@
 \begin{figure*}[ht!]
-  \centering
- \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm 0cm]{HLVIsky.pdf}
- \caption{The same as Fig \ref{2525SkyLocHLV}, except for the HLVI detector configuration.
-Note the substaintally lower average uncertainties on the skies for the majority of the injections.
-Also note the lack of large, ``banana-shaped'' uncertainties that were recovered by the HLV configuration.
-The two improvements are due to the breaking of the degeneracy in sky location recovery that is facilitated by the transition to a four-detector network.}
+  \centering \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm
+    0cm]{HLVIsky.pdf}
+ \caption{The same as Fig \ref{2525SkyLocHLV}, except for the HLVI
+   detector configuration.  Note the substaintally lower average
+   uncertainties on the skies for the majority of the injections.
+   Also note the lack of large, ``banana-shaped'' uncertainties that
+   were recovered by the HLV configuration.  The two improvements are
+   due to the breaking of the degeneracy in sky location recovery that
+   is facilitated by the transition to a four-detector network.}
  \label{2525SkyLocHLVI}
@@
 \begin{figure}[ht!]
-  \centering
- \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.52]{noisePDF.pdf}
- \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the 
- Advanced LIGO noise curve.  Each PDF represents the recovery of the same $1M_{\odot}/2.5M_{\odot}$ signal in a
-  different noise curve, picked at random from the Gaussian colored noise defined by the Advanced LIGO power
-   spectral density, while the gray-shaded curve is the zero-noise PDF.  Notice how the curve is relatively unchanged,
-    but usually assumes a Gaussian PDF displaced from the true value.  This only holds true for glitch-free data, which
-     is an unrealistic idealization when compared to real data.}
+  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
+    clip=true,scale=0.52]{noisePDF.pdf}
+ \caption{The effects of a non-zero noise realization on the recovered
+   PDF for five different Gaussian realizations of the Advanced LIGO
+   noise curve.  Each PDF represents the recovery of the same
+   $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked
+   at random from the Gaussian colored noise defined by the Advanced
+   LIGO power spectral density, while the gray-shaded curve is the
+   zero-noise PDF.  Notice how the curve is relatively unchanged, but
+   usually assumes a Gaussian PDF displaced from the true value.  This
+   only holds true for glitch-free data, which is an unrealistic
+   idealization when compared to real data.}
  \label{noisePDFs}
@@
 
-We have performed the current analysis on zero-noise injections for two reason.  First, the results of a zero-noise 
-analysis are identical to those that would be achieved by averaging the results of multiple identical injections 
-in different Gaussian noise realizations, as was argued in Section \ref{waveformSection}.  The second reason is 
-we are not able to predict the characteristics of realistic (often non-Gaussian) advanced detector noise.  
-Attempting to do so would have little chance of being accurate while requiring a huge computational 
-burden to combine the results of many MCMC runs in different noise realizations.
-
- In the case of a unique Gaussian realization
-of the Advanced-LIGO noise curve, each realization causes the maximum likelihood of the posterior probability 
-distribution to be translated away from the true value; however, these displacements are drawn
-according to the zero-noise distribution \citep{Inadequacies}.  Once averaged, the mean
-uncertainties should be equal to the uncertainty drawn from the zero-noise runs.
-
-As a demonstration of this, we injected a single $1M_{\odot}/2.5M_{\odot}$ system, 
-detected in HLVI,  into 5 separate realizations of Gaussian noise colored by the Advanced LIGO PSD, 
-and compared the results to the same MCMC recovery in the zero-noise case.  This example
-can be seen for one-dimensional marginalization of $\chmass$ and $q$ in Fig. \ref{noisePDFs}.  In effect, the ``real answer'' that will be recovered is a single PDF with similar 
-width to the zero-noise PDF, but with the peak likelihood displaced from the true value.
-
-Of course, the largest concern for gravitational-wave parameter estimation will not be the specific
-realization of Gaussian noise, but the effects of non-Gaussianities in the data.  Techniques which build
- off of the theoretical progress made in~\cite{Allen:2002jw,Rover:2011qd,Littenberg:2010gf} for including
-  glitches in our model for the data, and therefore relaxing the assumptions about stationary and Gaussian
-   noise, are currently under investigation.
+We have performed the current analysis on zero-noise injections for
+two reason.  First, the results of a zero-noise analysis are identical
+to those that would be achieved by averaging the results of multiple
+identical injections in different Gaussian noise realizations, as was
+argued in Section \ref{waveformSection}.  The second reason is we are
+not able to predict the characteristics of realistic (often
+non-Gaussian) advanced detector noise.  Attempting to do so would have
+little chance of being accurate while requiring a huge computational
+burden to combine the results of many MCMC runs in different noise
+realizations.
+
+ In the case of a unique Gaussian realization of the Advanced-LIGO
+ noise curve, each realization causes the maximum likelihood of the
+ posterior probability distribution to be translated away from the
+ true value; however, these displacements are drawn according to the
+ zero-noise distribution \citep{Inadequacies}.  Once averaged, the
+ mean uncertainties should be equal to the uncertainty drawn from the
+ zero-noise runs.
+
+As a demonstration of this, we injected a single
+$1M_{\odot}/2.5M_{\odot}$ system, detected in HLVI, into 5 separate
+realizations of Gaussian noise colored by the Advanced LIGO PSD, and
+compared the results to the same MCMC recovery in the zero-noise case.
+This example can be seen for one-dimensional marginalization of
+$\chmass$ and $q$ in Fig. \ref{noisePDFs}.  In effect, the ``real
+answer'' that will be recovered is a single PDF with similar width to
+the zero-noise PDF, but with the peak likelihood displaced from the
+true value.
+
+Of course, the largest concern for gravitational-wave parameter
+estimation will not be the specific realization of Gaussian noise, but
+the effects of non-Gaussianities in the data.  Techniques which build
+off of the theoretical progress made
+in~\cite{Allen:2002jw,Rover:2011qd,Littenberg:2010gf} for including
+glitches in our model for the data, and therefore relaxing the
+assumptions about stationary and Gaussian noise, are currently under
+investigation.
 
@@
 \begin{figure*}[h!]
-  \centering
- \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.65]{HLVRuntimes.pdf}
+  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
+    clip=true,scale=0.65]{HLVRuntimes.pdf}
  \label{HLVRuntimes}
- \caption{Typical Runtimes for the HLV Network Configuration.  Each run was done on the local Northwestern supercomputer}
+ \caption{Typical Runtimes for the HLV Network Configuration.  Each
+   run was done on the local Northwestern supercomputer}
 \end{figure*}
@@
 \begin{figure*}[h!]
-  \centering
- \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.65]{HLVIRuntimes.pdf}
+  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
+    clip=true,scale=0.65]{HLVIRuntimes.pdf}
  \label{HLVIRuntimes}
- \caption{\carl{this is superfluous; combine this into one figure with two colors.} }
+ \caption{\carl{this is superfluous; combine this into one figure with
+     two colors.} }
 \end{figure*}
 
-The parameter estimation techniques described here will be performed as a follow-up analysis
-to the detections returned by various on-line analyses in the Advanced LIGO/Virgo era.  While
-there exist specific PE analyses that will be performed in real-time for time sensitive signals 
-(i.e. extrinsic parameters for signals with a potential optimal counterpart \carl{[CITE PROTO-BEN
-OR LEO SINGER]}), most PE will require several days to weeks to complete the analysis upon a 
-single event.  We display the distribution of runtimes for the two network configuration in Figures~\ref{HLVRuntimes} and ~\ref{HLVIRuntimes} 
+The parameter estimation techniques described here will be performed
+as a follow-up analysis to the detections returned by various on-line
+analyses in the Advanced LIGO/Virgo era.  While there exist specific
+PE analyses that will be performed in real-time for time sensitive
+signals (i.e. extrinsic parameters for signals with a potential
+optimal counterpart \carl{[CITE PROTO-BEN OR LEO SINGER]}), most PE
+will require several days to weeks to complete the analysis upon a
+single event.  We display the distribution of runtimes for the two
+network configuration in Figures~\ref{HLVRuntimes} and
+~\ref{HLVIRuntimes}
 \end{comment}
@@
 
-When quoting parameter estimation results, it is often convenient to reduce the full parameter space to
-credible intervals about single, marginalized parameters..  To that end, we state the averaged 65\% 
-confidence intervals about the single parameters for each of the three parameter pairs of interest.  These were already
- plotted for the sky locations in Figures~\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI}.
-
-There are several different ways of computing the width of a credible interval in this setup.  If one considers the points in
- the MCMC as random draws from the true posterior, then the $\alpha$-level credible interval can be computed by simply
-  ordering the points, removing $N(1-\alpha )/2$ points from both sides of the posterior samples symmetrically, and measuring
-   the width of the remaining points.  While this procedure can prove hazardous for multi-modal distributions, it is 
-   straightforward and reliable for single-peaked distributions as reported here.
-
-In Table~\ref{ciTableIntrinsic}, we list the mean 65\% confidence intervals recovered for the four mass configurations in both 
-network configurations. This essentially quantifies the widths of the posteriors plotted throughout Section~\ref{resultsSection}.
-  The purpose of Tables~\ref{ciTableIntrinsic} and \ref{ciTableExtrinsic} is to provide a quantitative and quotable source for studies seeking to determine how 
-  well a physical question about BNS systems can be answered with the Advanced LIGO/Virgo network.
+When quoting parameter estimation results, it is often convenient to
+reduce the full parameter space to credible intervals about single,
+marginalized parameters..  To that end, we state the averaged 65\%
+confidence intervals about the single parameters for each of the three
+parameter pairs of interest.  These were already plotted for the sky
+locations in Figures~\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI}.
+
+There are several different ways of computing the width of a credible
+interval in this setup.  If one considers the points in the MCMC as
+random draws from the true posterior, then the $\alpha$-level credible
+interval can be computed by simply ordering the points, removing
+$N(1-\alpha )/2$ points from both sides of the posterior samples
+symmetrically, and measuring the width of the remaining points.  While
+this procedure can prove hazardous for multi-modal distributions, it
+is straightforward and reliable for single-peaked distributions as
+reported here.
+
+In Table~\ref{ciTableIntrinsic}, we list the mean 65\% confidence
+intervals recovered for the four mass configurations in both network
+configurations. This essentially quantifies the widths of the
+posteriors plotted throughout Section~\ref{resultsSection}.  The
+purpose of Tables~\ref{ciTableIntrinsic} and \ref{ciTableExtrinsic} is
+to provide a quantitative and quotable source for studies seeking to
+determine how well a physical question about BNS systems can be
+answered with the Advanced LIGO/Virgo network.
 
@@
 \centering
-\caption{Mean 65\% confidence intervals for intrinsic parameters for each of the four systems considered.
-We report the confidence intervals of quantities measured, as well as the component masses and total mass.
-Although the results for the
-HLV and HLVI configurations are quantitatively identical, we report them separately for consistency.}
+\caption{Mean 65\% confidence intervals for intrinsic parameters for
+  each of the four systems considered.  We report the confidence
+  intervals of quantities measured, as well as the component masses
+  and total mass.  Although the results for the HLV and HLVI
+  configurations are quantitatively identical, we report them
+  separately for consistency.}
 \begin{tabular}{lcccccccccc}
 
-\\HLVI\\
-\hline\hline
-System & \vline &  $\Delta \chmass / \chmass$ & \vline & $\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline & $\Delta M_{tot}/M_{tot}$ & \vline & $\Delta q$\\
-\hline\hline
-$1M_{\odot}-1M_{\odot}$ & \vline & $4.70\times 10^{-5}$ & \vline & $6.83\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline & $3.67\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$\\
-\hline
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.27\times 10^{-5}$ & \vline & $7.27\times 10^{-2}$ & \vline & $6.45\times 10^{-2}$ & \vline & $4.10\times 10^{-3}$ & \vline & $1.24\times 10^{-1}$ \\
-\hline
-$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline & $1.74\times 10^{-2}$ & \vline & $1.49\times 10^{-2}$ & \vline & $8.15\times 10^{-3}$ & \vline & $1.29\times 10^{-2}$\\\hline
-$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.29\times 10^{-4}$ & \vline & $8.52\times 10^{-2}$ & \vline & $7.41\times 10^{-2}$ & \vline & $5.51\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$\\
-\hline\hline
-
-\\
-HLV\\
-
-\hline\hline
-System & \vline &  $\Delta \chmass / \chmass$ & \vline & $\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline & $\Delta M_{tot}/M_{tot}$ & \vline & $\Delta q$\\
-\hline\hline
-$1M_{\odot}-1M_{\odot}$ & \vline & $4.66\times 10^{-5}$ & \vline & $6.82\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline & $3.64\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$ \\
-\hline
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.31\times 10^{-5}$ & \vline & $7.35\times 10^{-2}$ & \vline & $6.51\times 10^{-2}$ & \vline & $4.18\times 10^{-3}$ & \vline & $1.25\times 10^{-1}$\\
-\hline
-$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline & $1.75\times 10^{-2}$ & \vline & $1.50\times 10^{-2}$ & \vline & $8.19\times 10^{-3}$ & \vline & $1.30\times 10^{-2}$ \\
-\hline
-$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.30\times 10^{-4}$ & \vline & $8.53\times 10^{-2}$ & \vline & $7.42\times 10^{-2}$ & \vline & $5.52\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$ \\
-\hline\hline
+\\HLVI\\ \hline\hline System & \vline & $\Delta \chmass / \chmass$ &
+\vline & $\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline &
+$\Delta M_{tot}/M_{tot}$ & \vline & $\Delta q$\\ \hline\hline
+$1M_{\odot}-1M_{\odot}$ & \vline & $4.70\times 10^{-5}$ & \vline &
+$6.83\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline &
+$3.67\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$\\ \hline
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.27\times 10^{-5}$ & \vline &
+$7.27\times 10^{-2}$ & \vline & $6.45\times 10^{-2}$ & \vline &
+$4.10\times 10^{-3}$ & \vline & $1.24\times 10^{-1}$ \\ \hline
+$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline &
+$1.74\times 10^{-2}$ & \vline & $1.49\times 10^{-2}$ & \vline &
+$8.15\times 10^{-3}$ & \vline & $1.29\times 10^{-2}$\\\hline
+$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.29\times 10^{-4}$ & \vline &
+$8.52\times 10^{-2}$ & \vline & $7.41\times 10^{-2}$ & \vline &
+$5.51\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$\\ \hline\hline
+
+\\ HLV\\
+
+\hline\hline System & \vline & $\Delta \chmass / \chmass$ & \vline &
+$\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline & $\Delta
+M_{tot}/M_{tot}$ & \vline & $\Delta q$\\ \hline\hline
+$1M_{\odot}-1M_{\odot}$ & \vline & $4.66\times 10^{-5}$ & \vline &
+$6.82\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline &
+$3.64\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$ \\ \hline
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.31\times 10^{-5}$ & \vline &
+$7.35\times 10^{-2}$ & \vline & $6.51\times 10^{-2}$ & \vline &
+$4.18\times 10^{-3}$ & \vline & $1.25\times 10^{-1}$\\ \hline
+$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline &
+$1.75\times 10^{-2}$ & \vline & $1.50\times 10^{-2}$ & \vline &
+$8.19\times 10^{-3}$ & \vline & $1.30\times 10^{-2}$ \\ \hline
+$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.30\times 10^{-4}$ & \vline &
+$8.53\times 10^{-2}$ & \vline & $7.42\times 10^{-2}$ & \vline &
+$5.52\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$ \\ \hline\hline
 
@@
 \centering
-\caption{Mean 65\% confidence intervals of extrinsic parameters for each of the four systems considered.  As expected,
-there exists a substantial improvement in the sky localization capabilities of the four-detector HLVI configuration over
-the three-detector HLV configuration.  Note that the solid-angle sky-location confidence intervals, $\Delta\Omega$, are 
-calculated directly on the 2D sphere, not by combining the $\alpha$ and $\delta$ uncertainties.}
+\caption{Mean 65\% confidence intervals of extrinsic parameters for
+  each of the four systems considered.  As expected, there exists a
+  substantial improvement in the sky localization capabilities of the
+  four-detector HLVI configuration over the three-detector HLV
+  configuration.  Note that the solid-angle sky-location confidence
+  intervals, $\Delta\Omega$, are calculated directly on the 2D sphere,
+  not by combining the $\alpha$ and $\delta$ uncertainties.}
 \begin{tabular}{lcccccccccc}
 
-\\HLVI\\
-\hline\hline
- System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline &  $\Delta \delta$   $(deg)$ & \vline & $\Delta\Omega$ $(deg^2)$\\
-\hline\hline
- $1M_{\odot}-1M_{\odot}$ & \vline & $3.64\times 10^{1}$ & \vline & $2.23\times 10^{-1}$ & \vline & $1.45$ & \vline & $1.48$ & \vline & $1.88$\\
-\hline
- $1.4M_{\odot}-1.4M_{\odot}$ & \vline & $5.52\times 10^{1}$ & \vline & $2.56\times 10^{-1}$ & \vline & $1.49$ & \vline & $1.50$ & \vline & $2.26$\\
-\hline
- $1M_{\odot}-2.5M_{\odot}$  & \vline & $6.48\times 10^{1}$ & \vline & $2.93\times 10^{-1}$ & \vline & $1.54$ & \vline & $1.64$ & \vline & $2.10$\\
- \hline
- $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.06\times 10^{2}$ & \vline & $2.99\times 10^{-1}$ & \vline & $1.03\times 10^{1}$ & \vline & $1.61$ & \vline & $2.22$\\
-\hline\hline
-
-\\
-HLV\\
-
-\hline\hline
- System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline &  $\Delta \delta$   $(deg)$ & \vline & $\Delta\Omega$ $(deg^2)$\\
-\hline\hline
- $1M_{\odot}-1M_{\odot}$ & \vline & $4.34\times 10^{1}$ & \vline & $3.04\times 10^{-1}$ & \vline & $1.45\times 10^{1}$ & \vline & $6.24$ & \vline & $5.57$\\
-\hline
- $1.4M_{\odot}-1.4M_{\odot}$  & \vline & $5.32\times 10^{1}$ & \vline & $2.87\times 10^{-1}$ & \vline & $6.92$ & \vline & $7.11$ & \vline & $8.35$\\
-\hline
-  $1M_{\odot}-2.5M_{\odot}$& \vline & $6.11\times 10^{1}$ & \vline & $3.11\times 10^{-1}$ & \vline & $2.67$ & \vline & $4.20$ & \vline & $7.39$\\
-\hline
- $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.04\times 10^{2}$ & \vline & $3.42\times 10^{-1}$ & \vline & $1.13\times 10^{1}$ & \vline & $3.31$ & \vline & $6.27$\\
-\hline\hline
+\\HLVI\\ \hline\hline System & \vline & $\Delta D$ $(mpc)$ & \vline &
+$\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline &
+$\Delta \delta$ $(deg)$ & \vline & $\Delta\Omega$
+$(deg^2)$\\ \hline\hline $1M_{\odot}-1M_{\odot}$ & \vline &
+$3.64\times 10^{1}$ & \vline & $2.23\times 10^{-1}$ & \vline & $1.45$
+& \vline & $1.48$ & \vline & $1.88$\\ \hline
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $5.52\times 10^{1}$ & \vline &
+$2.56\times 10^{-1}$ & \vline & $1.49$ & \vline & $1.50$ & \vline &
+$2.26$\\ \hline $1M_{\odot}-2.5M_{\odot}$ & \vline & $6.48\times
+10^{1}$ & \vline & $2.93\times 10^{-1}$ & \vline & $1.54$ & \vline &
+$1.64$ & \vline & $2.10$\\ \hline $2.5M_{\odot}-2.5M_{\odot}$ & \vline
+& $1.06\times 10^{2}$ & \vline & $2.99\times 10^{-1}$ & \vline &
+$1.03\times 10^{1}$ & \vline & $1.61$ & \vline & $2.22$\\ \hline\hline
+
+\\ HLV\\
+
+\hline\hline System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta
+|\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline & $\Delta
+\delta$ $(deg)$ & \vline & $\Delta\Omega$ $(deg^2)$\\ \hline\hline
+$1M_{\odot}-1M_{\odot}$ & \vline & $4.34\times 10^{1}$ & \vline &
+$3.04\times 10^{-1}$ & \vline & $1.45\times 10^{1}$ & \vline & $6.24$
+& \vline & $5.57$\\ \hline $1.4M_{\odot}-1.4M_{\odot}$ & \vline &
+$5.32\times 10^{1}$ & \vline & $2.87\times 10^{-1}$ & \vline & $6.92$
+& \vline & $7.11$ & \vline & $8.35$\\ \hline
+$1M_{\odot}-2.5M_{\odot}$& \vline & $6.11\times 10^{1}$ & \vline &
+$3.11\times 10^{-1}$ & \vline & $2.67$ & \vline & $4.20$ & \vline &
+$7.39$\\ \hline $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.04\times
+10^{2}$ & \vline & $3.42\times 10^{-1}$ & \vline & $1.13\times 10^{1}$
+& \vline & $3.31$ & \vline & $6.27$\\ \hline\hline
 
@@
 
-In this paper, we performed an MCMC parameter estimation analysis on the recoverability of basic information about binary 
-neutron stars, using two projected versions of the Advanced LIGO/Virgo network.  We focused on the recovery of the two 
-masses, the luminosity distance, orbital inclination, and the sky location, as these are the six basic parameters of physical 
-interest to the problem.  We found that, neglecting the effects of spin, the component masses can be constrained to within
- 10\% of their true value to a confidence of 65\%.  This value drops below 2\% for systems with an asymmetric mass ratio.
- These results were summarized in Table \ref{ciTableIntrinsic}.
-
-We also reported on the ability of the two network configurations to constrain the
-luminosity distance and orbital inclination.  For distance, it was found that the uncertainties
-will fall anywhere from 40 to 100 MPC at 65\% confidence, making the uncertainties frequently larger than the luminosity
-distances themselves.  However, it was found that the cosine of the orbital inclination can be constrained to within 
-0.3 at the 65\% level, suggesting that Advanced LIGO/Virgo will be able to offer some information on GRB beaming
-angles in coincidence with electromagnetic observations.
-
-Finally, we reported the ability of advanced networks to constrain the sky location of BNS signals.  It was found that 
-the three-detector configuration, consisting of the Washington and Louisiana LIGO sites plus the Italian Virgo site,
- was able to constrain all signals within 60 $deg^2$ on the sky at the 65\% confidence interval, with an average
-65\% confidence interval of $\sim 7$ $deg^2$.  Meanwhile, the four-detector
-configuration, consisting of the three-detector sites plus a LIGO India detector, was able to localize the sky-locations
-to within  13 $deg^2$ on the sky at the 65\% confidence interval, with an average
-65\% confidence interval of $\sim 2$ $deg^2$.
-
-It should be noted that there are two distinct types of systematic error, highly relevant to the gravitational-wave parameter estimation problem, that we have not addressed in this study.
-First, we have studied the parameter estimation uncertainties under the assumption that the waveform template we use to recover the signal template exactly matches the fully relativistic waveforms nature provides.
-In practice, these waveforms are only approximations to the fully general-relativistic physics required to solve the problem.
-See \carl{[CITE]} for a better description of the systematic uncertainties present in the most common waveform families.
-Additionally, there are several astrophysical assumptions that can potentially contribute
-to systematic uncertainties in the waveforms, such as the neutron-star equation of state, possible modifications to 
-General Relativity, eccentricity, etc.
-
-Secondly, as stated above, we have performed our study under idealized detector-noise conditions.
-In practice the noise levels of Advanced LIGO and Advanced Virgo can vary with time and contain occasional excursions which are highly non-Gaussian.
-Unfortunately, there is no reliable way to predict the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.
-Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here.
-
-In this study, we have also neglected the effects of spin in the parameter space, electing to focus on the absolute basic
- parameters that will be measured routinely in the Advanced Detector era.  Given the high degree of coupling
-between the spin and the mass of objects in the gravitational-wave parameter space, it remains unclear
-if the mass measurement alone will be sufficient to distinguish non-spinning neutron stars from highly-spinning low-mass
-black holes.  Future work will explore this potential mass/spin degeneracy, including the effects of orbital precession, with the aim of definitively answering this question.
+In this paper, we performed an MCMC parameter estimation analysis on
+the recoverability of basic information about binary neutron stars,
+using two projected versions of the Advanced LIGO/Virgo network.  We
+focused on the recovery of the two masses, the luminosity distance,
+orbital inclination, and the sky location, as these are the six basic
+parameters of physical interest to the problem.  We found that,
+neglecting the effects of spin, the component masses can be
+constrained to within 10\% of their true value to a confidence of
+65\%.  This value drops below 2\% for systems with an asymmetric mass
+ratio.  These results were summarized in Table \ref{ciTableIntrinsic}.
+
+We also reported on the ability of the two network configurations to
+constrain the luminosity distance and orbital inclination.  For
+distance, it was found that the uncertainties will fall anywhere from
+40 to 100 MPC at 65\% confidence, making the uncertainties frequently
+larger than the luminosity distances themselves.  However, it was
+found that the cosine of the orbital inclination can be constrained to
+within 0.3 at the 65\% level, suggesting that Advanced LIGO/Virgo will
+be able to offer some information on GRB beaming angles in coincidence
+with electromagnetic observations.
+
+Finally, we reported the ability of advanced networks to constrain the
+sky location of BNS signals.  It was found that the three-detector
+configuration, consisting of the Washington and Louisiana LIGO sites
+plus the Italian Virgo site, was able to constrain all signals within
+60 $deg^2$ on the sky at the 65\% confidence interval, with an average
+65\% confidence interval of $\sim 7$ $deg^2$.  Meanwhile, the
+four-detector configuration, consisting of the three-detector sites
+plus a LIGO India detector, was able to localize the sky-locations to
+within 13 $deg^2$ on the sky at the 65\% confidence interval, with an
+average 65\% confidence interval of $\sim 2$ $deg^2$.
+
+It should be noted that there are two distinct types of systematic
+error, highly relevant to the gravitational-wave parameter estimation
+problem, that we have not addressed in this study.  First, we have
+studied the parameter estimation uncertainties under the assumption
+that the waveform template we use to recover the signal template
+exactly matches the fully relativistic waveforms nature provides.  In
+practice, these waveforms are only approximations to the fully
+general-relativistic physics required to solve the problem.  See
+\carl{[CITE]} for a better description of the systematic uncertainties
+present in the most common waveform families.  Additionally, there are
+several astrophysical assumptions that can potentially contribute to
+systematic uncertainties in the waveforms, such as the neutron-star
+equation of state, possible modifications to General Relativity,
+eccentricity, etc.
+
+Secondly, as stated above, we have performed our study under idealized
+detector-noise conditions.  In practice the noise levels of Advanced
+LIGO and Advanced Virgo can vary with time and contain occasional
+excursions which are highly non-Gaussian.  Unfortunately, there is no
+reliable way to predict the sort of non-Gaussian detector glitches and
+instrumentation effects that will arise in any advanced
+gravitational-wave detector.  Since the realization of noise will be
+the primary factor in the deflection of true signal PDFs from the
+averages quoted here.
+
+In this study, we have also neglected the effects of spin in the
+parameter space, electing to focus on the absolute basic parameters
+that will be measured routinely in the Advanced Detector era.  Given
+the high degree of coupling between the spin and the mass of objects
+in the gravitational-wave parameter space, it remains unclear if the
+mass measurement alone will be sufficient to distinguish non-spinning
+neutron stars from highly-spinning low-mass black holes.  Future work
+will explore this potential mass/spin degeneracy, including the
+effects of orbital precession, with the aim of definitively answering
+this question.
 
@@
  \item Finish adding bibliography/sources
- \item double check the distribution of sources in Distance/Iota; make sure iota is actually uniform in cos(i)
+ \item double check the distribution of sources in Distance/Iota; make
+   sure iota is actually uniform in cos(i)
  \end{itemize}
@@
 
-\bibliographystyle{apj}
-\bibliography{paper}{}
+\bibliographystyle{apj} \bibliography{paper}{}
 

### 2013-06-28 doc/paper.tex
Edits and comments from Will.

@@
 orbital inclinations of randomly distributed sources that can be
-achieved by different network configurations.
+achieved by different network configurations.  \will{I'm not sure that
+  we want to say this exactly this way---the sources in this study are
+  not randomly distributed in SNR, but rather cluster at rather loud
+  signals.}
 \end{abstract}
@@
 come online \citep{AdvLIGO,AdvVirgo}.  The Advanced LIGO and Virgo
-detectors will provide the first insights into the final moment of
+detectors will provide the first insights into the final moments of
 binary compact object mergers, including the merger of binary neutron
@@
 The mergers of binary neutron stars (BNS) are expected to be the most
-common compact binary source in the advanced detector era.  Models
-from stellar evolution and observations of binary pulsars suggest that
-the number of binary neutron star mergers within Advanced LIGO/Virgo's
-detection horizon could reach into the hundreds each year, with an
-expected mean of $\sim 40$ per year \citep{RatesPaper}.  Although the
-peak sensitivity of ground-based detectors is not focused on the
-frequency at which BNS systems merge, it could still be possible to
-extract information about both strong field gravitational physics
-\carl{[CITE]} and the hydrodynamics of dense matter (e.g. the equation
-of state of nuclear matter) \carl{[CITE]}.  Furthermore, the
-observations of multiple BNS systems will provide key insight into the
-evolution of binary systems in the field \citep{VickyRates,KimRates}
-. As such, BNS systems will likely form the ``bread and butter'' of
-the compact binary coalescence detection effort in the coming years.
+common compact binary source in the advanced detector era.  \will{This
+  is technically true (thanks to the word ``expected''), but the
+  uncertainty in rates is so large that it would not be surprising at
+  all for it to be wrong.  Re-word or eliminate.} Models from stellar
+evolution and observations of binary pulsars suggest that the number
+of binary neutron star mergers within Advanced LIGO/Virgo's detection
+horizon could reach \will{several tens to hundreds} each year
+\citep{RatesPaper}.  Although the peak sensitivity of ground-based
+detectors is not focused on the frequency at which BNS systems merge,
+it could still be possible to extract information about both strong
+field gravitational physics \carl{[CITE]} and the hydrodynamics of
+dense matter (e.g. the equation of state of nuclear matter)
+\carl{[CITE]}.  Furthermore, the observations of multiple BNS systems
+will provide key insight into the evolution of binary systems in the
+field \citep{VickyRates,KimRates} . As such, BNS systems will likely
+form the ``bread and butter'' of the compact binary coalescence
+detection effort in the coming years.
 
@@
 detector output is sufficiently large (97\%), a detection candidate is
-found.  However, the parameter space of these signals can be highly
-degenerate, with several locations in parameter space corresponding to
-nearly identical waveforms.  In order to fully realize the science
-potential of these instruments, we must perform a full exploration of
-the parameter space for each detection.  By analyzing the parameter
-space of each candidate with a Bayesian inference technique, we will
-be able to make precise, scientifically meaningful statements about
-the physics of these systems.  To that end, we employ a Markov-Chain
-Monte Carlo sampling algorithm, \texttt{lalinference\_mcmc}, included
-in the LIGO Algorithm Library parameter estimation code,
-\texttt{LALInference}, to analyze the parameter space of BNS systems.
+found.  \will{This is not true.  The \emph{templates} are chosen so
+  that any signal should have 97\% overlap with at least one template,
+  but detection depends on the intrinsic strength of the signal, not
+  its degree of overlap with templates.}  However, the parameter space
+of these signals can be highly degenerate, with several locations in
+parameter space corresponding to nearly identical waveforms.  In order
+to fully realize the science potential of these instruments, we must
+perform a full exploration of the parameter space for each detection.
+By analyzing the parameter space of each candidate with a Bayesian
+inference technique, we will be able to make precise, scientifically
+meaningful statements about the physics of these systems.  To that
+end, we employ a Markov-Chain Monte Carlo sampling algorithm,
+\texttt{lalinference\_mcmc}, included in the LIGO Algorithm Library
+parameter estimation code, \texttt{LALInference}, to analyze the
+parameter space of BNS systems.
 
@@
 eventually be used in the Advanced LIGO/Virgo era, our results give
-the first estimates at the realistic capabilities of advanced
-ground-based detectors to characterize BNS systems.  Until recently,
-the majority of studies have employed the Fisher matrix formalism
-which was first adapted for gravitational-wave parameter estimation by
-\citep{FinnDetection}.  While each of these studies
+\will{\sout{the first}} estimates at the realistic capabilities of
+advanced ground-based detectors to characterize BNS systems.  Until
+recently, the majority of studies have employed the Fisher matrix
+formalism which was first adapted for gravitational-wave parameter
+estimation by \citet{FinnDetection}.  While each of these studies
 \citep{PoissonWill,CutlerFlanagan,ArunPE} have pointed out the
@@
 probability density functions for BNS systems with different masses
-and extrinsic parameters.  The results are divided into three
-parameter sets of interest: the recovery of the mass parameters
-(Section \ref{massSection}), the recovery of the orbital inclination
-and luminosity distance (Section \ref{idSection}), and the
+and extrinsic parameters.  \will{Here would be a good place to have a
+  sentence or two about the distribution of source parameters---the
+  choices of masses, angles, and distances.}  The results are divided
+into three parameter sets of interest: the recovery of the mass
+parameters (Section \ref{massSection}), the recovery of the orbital
+inclination and luminosity distance (Section \ref{idSection}), and the
 localization of sources on the sky (Section \ref{skySection}).
@@
 the noise of the detector $n$.  We further assume that this noise is
-stationary and Gaussian with zero mean.  Therefore, the detector
-output is simply
+stationary and Gaussian with zero mean.  The detector output is
 \begin{equation}
@@
 Since the noise model is Gaussian, we can write the probability of a
-specific signal realization $s$ as proportional to the probability
-that the residual is Gaussian distributed once the waveform has been
-subtracted
+specific signal realization $s$ given an input waveform as
+proportional to the probability that the residual is Gaussian
+distributed once the waveform has been subtracted
 \begin{align}
@@
 \end{align}
-where $\thpara$ is the set of parameters for the template waveforms,
-and $p(s | \thpara)$ is the likelihood of the signal $s$ given the
-parameters $\thpara$.  The inner product, $\left< ~|~ \right> $, is
-defined using the noise spectrum of the detectors as
+where $\thpara$ is the set of parameters for the template waveforms.
+The quantity $p(s | \thpara)$ is the likelihood of the signal $s$
+given the parameters $\thpara$.  The inner product, $\left< ~|~
+\right> $, is defined using the noise spectrum of the detectors as
 \begin{equation}
@@
 the posterior \eqref{posterior} will be near a global maximum;
-however, our choice of prior the presence of noise will in general
-deflect the maximum of our posterior away from the value at
-$\thpara_0$.  Therefore, the maximum posterior parameters do not
-necessarily correspond to the true parameters of the source, so when
-interpreting parameter estimation results we must consider the full
-posterior distribution function.
+however, the presence of noise will in general deflect the maximum of
+our posterior away from the value at $\thpara_0$.  Therefore, the
+maximum posterior parameters do not necessarily correspond to the true
+parameters of the source; when interpreting parameter estimation
+results it is important to consider the full posterior distribution
+function.
 
@@
 population of sources will be distributed homogeneously in volume, or
-evenly in $D^2$.  Our prior information can come from mathematical
-limits in the parameter space or from our \textit{a priori} knowledge
-of astrophysical systems.  We employ priors which are
-
+with a density proportional to $D^2$.  Our prior information can come
+from mathematical limits in the parameter space or from our \textit{a
+  priori} knowledge of astrophysical systems.  We employ priors which
+are
 \begin{itemize}
 \item uniform in component masses from $0.8M_{\odot} \leq M_{1,2} \leq
-  30M_{\odot}$, with a minimum chirp mass \eqref{eqRatioCM} of 0.6
-  $M_{\odot}$,
+  30M_{\odot}$, with a minimum chirp mass (see Eq.~\eqref{eqRatioCM})
+  of 0.6 $M_{\odot}$,
 \item uniform in volume, which implies a luminosity distance prior of
-  $p(D) = D^2 dD$,
+  $p(D)dD = D^2 dD$,
 \item uniform in coalescence time over the segment of data being
   analyzed, and
-\item uniform in all other parameters, with angular parameters being
-  flat over their corresponding domains.
+\item a delta function at zero spin (i.e.\ we use waveforms without
+  spin)
+\item isotropic in all angles
 \end{itemize}
-
-\noindent The mass priors listed here are the generic priors used in
-follow-up analysis, not specifically for BNS systems.  While we could
-have used a prior with a lower component mass cutoff for the present
-study, in practice the higher prior boundary does not effect our
-current analysis.
+The mass priors listed here are the generic priors used in follow-up
+analysis, not specifically for BNS systems.  While we could have used
+a prior with a lower component mass cutoff for the present study, in
+practice the higher prior boundary does not effect our current
+analysis.
 
@@
   the prior $p(q)$ is uniform when the component mass priors are
-  uniform.}  By convention, $M_1 \geq M_2$.  The stationary phase then
+  uniform.  \will{This is not true.  I calculate (could be a bug, so
+    check it)
+    \begin{equation}
+      p(\chmass, q) = \frac{\chmass}{q} \left(\frac{\left(1+q\right)^2}{q}\right)^{\frac{1}{5}}
+    \end{equation}
+    when 
+    \begin{equation}
+      p\left(m_1, m_2\right) \propto \mathrm{const}
+    \end{equation}
+    The reasons to use $q$ instead of $\eta$
+    \begin{itemize}
+      \item It is more intuitive to astronomers (you mention this
+        above).
+      \item As $m_1 \to m_2$, or $q \to 1$, or $\eta \to 1/4$, the
+        prior on $\eta$ for equal mass systems diverges (it is an
+        integrable singularity, but still singular), while the prior
+        on $q$ is well-behaved.  This doesn't matter for sampling
+        purposes, since the divergence in integrable, but it is
+        disconcerting for near-equal-mass systems to see a large peak
+        in the histogram for $\eta$ near $\eta = 1/4$.
+    \end{itemize}}}  By convention, $M_1 \geq M_2$.  The stationary phase then
 becomes an expansion in the Newtonian orbital velocity, $v=(\pi
@@
 choice allows us to explore the parameter estimation in the context of
-optimal detection candidates.
+\will{\sout{optimal}} \will{loud, but plausible} detection candidates.
 
@@
 glitches, any stretch of data should contain a specific noise
-realization drawn from a Gaussian colored by the PSD.
-%   However, what we are interested in is not the parameter estimation that can occur in a specific draw
-  % from this probability of noises, but the uncertainties averaged
-over all possible noise realizations. Without a realistic model
-including the actual instrument sensitivity, non stationary noise, and
-uncertainty in the PSD we cannot accurately simulate GW data to the
-point of making precise predictions about parameter estimation
-capabilities.  Furthermore, the posterior distribution from a future
-detection will be influenced by the realization of the noise at the
-time of the detection.  Because of this, we elect to focus only on the
-statistical errors due to the flexibility of the waveforms and the
-expected sensitivity of the advanced era detectors and suppress any
-effects of detector noise by not including a noise realization in our
-simulated data.  Consequently, what we recover with the MCMC could be
-interpreted as the posterior distribution function for each source
-averaged over all possible (Gaussian) noise realizations assuming we
-have the correct PSD.  \footnote{Similarly to how the Fisher matrix
-  formalism can provide the Cramer-Rao bound averaged over all noise
-  realizations.  Unlike a Fisher matrix study, we make no assumptions
-  about the shape of the posterior distribution function, nor the
-  location of the peak, while still requiring a feasible number of
-  MCMC runs to sufficiently cover parameter space, which would not be
-  the case had we needed to average several noise-dependent results.}
+realization drawn from a Gaussian colored by the PSD.  Without a
+realistic model including the actual instrument sensitivity, non
+stationary noise, and uncertainty in the PSD we cannot accurately
+simulate GW data to the point of making precise predictions about
+parameter estimation capabilities.  Furthermore, the posterior
+distribution from a future detection will be influenced by the
+realization of the noise at the time of the detection.  Because of
+this, we elect to focus only on the statistical errors due to the
+flexibility of the waveforms and the expected sensitivity of the
+advanced era detectors and suppress any effects of detector noise by
+picking the (most likely) noise realization that has $n(t) \equiv 0$.
+Consequently, what we recover with the MCMC could be interpreted as
+the posterior distribution function for each source averaged over all
+possible (Gaussian) noise realizations assuming we have the correct
+PSD.  \will{This is not true because the map from noise realization to
+  posterior is not linear.}
+
 To check that our reported statistical errors are not in gross
@@
 \centering \includegraphics[trim=7cm 0cm 0cm 0cm,
-  clip=true,scale=0.55]{9dpdf.pdf}
+  clip=true,scale=0.55]{9dpdf}
 %\begin{array}{ccc} 
@@
 %\end{array}$
-\caption{Marginalized 1D posterior probability density functions taken
-  from a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS system.  We have
-  plotted each of the 9 parameters for our non-spinning BNS problem as
-  stated in section \ref{waveformSection}.  Note how, even for
-  parameters with excellent recovery, the peak of the 1D Gaussian is
-  displaced from the injected value (in dashed red).  This is not due
-  to a systematic bias, but is caused by the marginalization of a
-  single dimension from the full 9D posterior space.  To better see
-  this effect, compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with
-  the 2D marginalized PDF in Figure~\ref{1414masses}}
+\caption{\label{9dPDF} Marginalized 1D posterior probability density
+  functions taken from a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS
+  system.  We have plotted each of the 9 parameters for our
+  non-spinning BNS problem as stated in section \ref{waveformSection}.
+  Note how, even for parameters with excellent recovery, the peak of
+  the 1D Gaussian is displaced from the injected value (in dashed
+  red).  This is not due to a systematic bias, but is caused by the
+  marginalization of a single dimension from the full 9D posterior
+  space.  To better see this effect, compare the 1D PDF for
+  $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in
+  Figure~\ref{1414masses}}
 \end{figure*}
@@
   presence of intrinsic angular momentum will, in general, couple to
-  the coalescence phase and wave polarization.}
+  the coalescence phase and wave polarization.  \will{But those
+    parameters are still physically uninteresting.  They couple to
+    interesting parameters in both the spinning and non-spinning
+    cases, which is why they must be included.  I would just eliminate
+    this footnote.}}
 
@@
 for chirp mass is marginalized via
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent where the notation $\thpara \setminus \chmass$ implies all
-parameter of \eqref{parameterspace} except $\chmass$.  Other parameter
-and higher-dimensional marginalizations follow a similar convention.
-In practice, the MCMC samples make this integral trivial: since the
+where the notation $\thpara \setminus \chmass$ implies all parameter
+of \eqref{parameterspace} except $\chmass$.  Other parameter and
+higher-dimensional marginalizations follow a similar convention.  In
+practice, the MCMC samples make this integral trivial: since the
 samples are distributed according to the posterior,
@@
 Of the nine variables in our parameter space \eqref{parameterspace},
-the two of immediate physical interest are the two parameters,
-$\chmass$ and $q$, or correspondingly the direct masses of the two
-companions, $M_1$ and $M_2$.  As stated above, the ability of Advanced
-LIGO/Virgo to construct a population of BNS masses will be one of the
-more useful applications of gravitational-wave astronomy.
+the mass parameters, $\chmass$ and $q$, or, correspondingly, $M_1$ and
+$M_2$ are the most astrophysically interesting.  The ability of
+Advanced LIGO/Virgo to construct a population of BNS masses will be
+one of the more useful applications of gravitational-wave astronomy.
 
@@
 zero-noise detector realization.  Furthermore, note that the mass
-parameters are the only two which directly effect the phase of the
+parameters are the only two which directly affect the phase of the
 TaylorF2 waveform \eqref{phase}.  Therefore, as long as the injected
@@
 ($M_1$-$M_2$).  Although only the $1.4M_{\odot}/1.4M_{\odot}$ system
-is included in Figure \ref{1414masses}, the PDF is quantitatively
+is included in Figure \ref{1414masses}, the PDF is qualitatively
 identical to the other equal mass cases, modulo a scaling factor.
@@
 intervals for distance and inclination.  Notice that the uncertainties
-on distance can be extreme, from tens to hundreds of $mpc$.  When
+on distance can be extreme, from tens to hundreds of Mpc.  When
 discussing the inclination angle, we elected to use $|\cos(\iota)|$,
@@
 highly dependent on the location of the source with respect to the
-detector network in question.  For the HLV configuration, the
+detector network in question.  Much of the information about the sky
+position of the source comes from the relative timing of the signals
+in each detector.  For the HLV configuration, timing in the
 three-detector network can only localize signals to one of two points
@@
 simultaneously, the MCMC can often identify the correct mode on the
-  sky.  For the four-detector configuration, this concern is
-  irrelevant: even with time-of-arrival data alone, the HLVI network
-  can constrain any source to a single mode on the sky.  Even then,
-  there are still locations on the sky in which two or more detectors
-  are not sensitive to the gravitational-wave signal, yielding
-  distorted, non-Gaussian PDFs.
+sky.  For the four-detector configuration, this concern is irrelevant:
+even with time-of-arrival data alone, the HLVI network can constrain
+any source to a single mode on the sky.  Even then, there are still
+locations on the sky in which two or more detectors are not sensitive
+to the gravitational-wave signal, yielding distorted, non-Gaussian
+PDFs.
 
@@
 all four mass bins together, since in practice the mass of the signals
-has no effect on the recovery of the sky location for the considered
-BNS systems.  Only the location on the sky, the network configuration,
-and the other extrinsic parameters were found to be relevant.  In
-particular, notice the increase in efficiency between the HLV
-configuration and the HLVI configuration.  In the HLV configuration,
-there exist points on the sky in which the signal was injected near
-the plane of the detector network.  This causes the elongated,
-``banana-shaped'' PDFs seen in Figure \ref{2525SkyLocHLV}.  In the
-HLVI configuration, the plane is no longer relevant, and there are
-substantially less regions in which only two detectors see a
+has little effect on the recovery of the sky location for the
+considered BNS systems.  Only the location on the sky, the network
+configuration, and the other extrinsic parameters were found to be
+relevant.  In particular, notice the increase in efficiency between
+the HLV configuration and the HLVI configuration.  In the HLV
+configuration, there exist points on the sky in which the signal was
+injected near the plane of the detector network.  This causes the
+elongated, ``banana-shaped'' PDFs seen in Figure \ref{2525SkyLocHLV}.
+In the HLVI configuration, the plane is no longer relevant, and there
+are substantially fewer regions in which only two detectors see a
 sufficiently strong signal.  See \cite{Veitch2012} for a more detailed
@@
 We have performed the current analysis on zero-noise injections for
-two reason.  First, the results of a zero-noise analysis are identical
-to those that would be achieved by averaging the results of multiple
-identical injections in different Gaussian noise realizations, as was
-argued in Section \ref{waveformSection}.  The second reason is we are
-not able to predict the characteristics of realistic (often
-non-Gaussian) advanced detector noise.  Attempting to do so would have
-little chance of being accurate while requiring a huge computational
-burden to combine the results of many MCMC runs in different noise
-realizations.
+two reasons.  First, the results of a zero-noise analysis are
+identical to those that would be achieved by averaging the results of
+multiple identical injections in different Gaussian noise
+realizations, as was argued in Section \ref{waveformSection}.
+\will{Again, this is not true!}  The second reason is we are not able
+to predict the characteristics of realistic (often non-Gaussian)
+advanced detector noise.  Attempting to do so would have little chance
+of being accurate while requiring a huge computational burden to
+combine the results of many MCMC runs in different noise realizations.
 
@@
 noise curve, each realization causes the maximum likelihood of the
- posterior probability distribution to be translated away from the
- true value; however, these displacements are drawn according to the
- zero-noise distribution \citep{Inadequacies}.  Once averaged, the
- mean uncertainties should be equal to the uncertainty drawn from the
- zero-noise runs.
+posterior probability distribution to be translated away from the true
+value; however, these displacements are drawn according to the
+zero-noise distribution \citep{Inadequacies} \will{I don't understand
+  what ``drawn according to the zero-noise distribution'' means.  I
+  don't think this sentence makes sense.}.  Once averaged, the mean
+uncertainties should be equal to the uncertainty drawn from the
+zero-noise runs.  \will{Again, not strictly true.}
 
@@
 ratio.  These results were summarized in Table \ref{ciTableIntrinsic}.
+\will{You should mention the fact that our signals were chosen to be
+  loud, but plausible here.  Make sure to note that the average
+  uncertainties below do not necessarily reflect the average
+  uncertainty expected in the analysis of advanced detector era
+  detections.}
 
@@
 be able to offer some information on GRB beaming angles in coincidence
-with electromagnetic observations.
+with electromagnetic observations.  \will{Are you sure about this?
+  Beaming angles about 10 degrees would have $\Delta \cos i \simeq
+  0.01$.}
 
@@
 plus the Italian Virgo site, was able to constrain all signals within
-60 $deg^2$ on the sky at the 65\% confidence interval, with an average
-65\% confidence interval of $\sim 7$ $deg^2$.  Meanwhile, the
-four-detector configuration, consisting of the three-detector sites
-plus a LIGO India detector, was able to localize the sky-locations to
-within 13 $deg^2$ on the sky at the 65\% confidence interval, with an
-average 65\% confidence interval of $\sim 2$ $deg^2$.
+60 $\mathrm{deg}^2$ on the sky at the 65\% confidence interval, with
+an average 65\% confidence interval of $\sim 7$ $\mathrm{deg}^2$.
+Meanwhile, the four-detector configuration, consisting of the
+three-detector sites plus a LIGO India detector, was able to localize
+the sky-locations to within 13 $\mathrm{deg}^2$ on the sky at the 65\%
+confidence interval, with an average 65\% confidence interval of $\sim
+2$ $\mathrm{deg}^2$.
 
@@
 instrumentation effects that will arise in any advanced
-gravitational-wave detector.  Since the realization of noise will be
-the primary factor in the deflection of true signal PDFs from the
-averages quoted here.
+gravitational-wave detector.  The realization of noise will be the a
+major factor in the deflection of signal PDFs from the idealized cases
+presented here.
 

### 2013-07-05 doc/paper.tex
Included the rest of will's comments and a couple of vivien's comments. Need to settle argument about 0-noise realization before sending to Vicky

@@
   [e-mail: {\tt cr@u.northwestern.edu}]} \altaffiltext{2}{California
-  Institute of Technology, Pasadena, CA 92215, USA}
+  Institute of Technology, Pasadena, CA 91125, USA}
 
@@
 average uncertainties on the sky-locations, luminosity distance, and
-orbital inclinations of randomly distributed sources that can be
-achieved by different network configurations.  \will{I'm not sure that
-  we want to say this exactly this way---the sources in this study are
-  not randomly distributed in SNR, but rather cluster at rather loud
-  signals.}
+orbital inclinations of ideal detection candidates  sources that can be
+achieved by different network configurations.
+% \will{I'm not sure that
+  %we want to say this exactly this way---the sources in this study are
+ % not randomly distributed in SNR, but rather cluster at rather loud
+  %signals.}
 \end{abstract}
@@
 
-The mergers of binary neutron stars (BNS) are expected to be the most
-common compact binary source in the advanced detector era.  \will{This
-  is technically true (thanks to the word ``expected''), but the
-  uncertainty in rates is so large that it would not be surprising at
-  all for it to be wrong.  Re-word or eliminate.} Models from stellar
+The mergers of binary neutron stars (BNS) are expected to be the one of the most
+common compact binary source in the advanced detector era.  %\will{This
+  %is technically true (thanks to the word ``expected''), but the
+ % uncertainty in rates is so large that it would not be surprising at
+ % all for it to be wrong.  Re-word or eliminate.} Added "one of the "
+  Models from stellar
 evolution and observations of binary pulsars suggest that the number
 of binary neutron star mergers within Advanced LIGO/Virgo's detection
-horizon could reach \will{several tens to hundreds} each year
+horizon could reach several tens to hundreds each year
 \citep{RatesPaper}.  Although the peak sensitivity of ground-based
@@
 it could still be possible to extract information about both strong
-field gravitational physics \carl{[CITE]} and the hydrodynamics of
-dense matter (e.g. the equation of state of nuclear matter)
-\carl{[CITE]}.  Furthermore, the observations of multiple BNS systems
+field gravitational physics \citep{Li2012} and the hydrodynamics of
+dense matter (e.g. the equation of state of nuclear matter,
+\citep{HindererBNS2010}).  Furthermore, the observations of multiple BNS systems
 will provide key insight into the evolution of binary systems in the
@@
 candidate signals at a sufficiently rapid rate to analyze months of
-data.  When the overlap between one of the template waveforms and the
-detector output is sufficiently large (97\%), a detection candidate is
-found.  \will{This is not true.  The \emph{templates} are chosen so
-  that any signal should have 97\% overlap with at least one template,
-  but detection depends on the intrinsic strength of the signal, not
-  its degree of overlap with templates.}  However, the parameter space
+data.  However, the parameter space
 of these signals can be highly degenerate, with several locations in
-parameter space corresponding to nearly identical waveforms.  In order
+parameter space corresponding to waveforms with nearly identical overlap.  In order
 to fully realize the science potential of these instruments, we must
@@
 By analyzing the parameter space of each candidate with a Bayesian
-inference technique, we will be able to make precise, scientifically
+inference technique, we will be able to make informative, scientifically
 meaningful statements about the physics of these systems.  To that
@@
 eventually be used in the Advanced LIGO/Virgo era, our results give
-\will{\sout{the first}} estimates at the realistic capabilities of
+ estimates at the realistic capabilities of
 advanced ground-based detectors to characterize BNS systems.  Until
@@
 probability density functions for BNS systems with different masses
-and extrinsic parameters.  \will{Here would be a good place to have a
-  sentence or two about the distribution of source parameters---the
-  choices of masses, angles, and distances.}  The results are divided
-into three parameter sets of interest: the recovery of the mass
+and extrinsic parameters.  We select three equal-mass an one unequal-mass
+ binary systems as fiducal examples of BNS systems.  Each system was then analyzed 40 
+ times with isotropically selected sky locations and binary orientations, and with a distance
+ such that each signal was injected with a signal-to-noise ratio of 20.
+  The results are divided into three parameter sets of interest: the recovery of the mass
 parameters (Section \ref{massSection}), the recovery of the orbital
@@
   M^2$.  We elect to use $q$ as it is more physically intuitive, and
-  the prior $p(q)$ is uniform when the component mass priors are
-  uniform.  \will{This is not true.  I calculate (could be a bug, so
-    check it)
-    \begin{equation}
-      p(\chmass, q) = \frac{\chmass}{q} \left(\frac{\left(1+q\right)^2}{q}\right)^{\frac{1}{5}}
-    \end{equation}
-    when 
-    \begin{equation}
-      p\left(m_1, m_2\right) \propto \mathrm{const}
-    \end{equation}
-    The reasons to use $q$ instead of $\eta$
-    \begin{itemize}
-      \item It is more intuitive to astronomers (you mention this
-        above).
-      \item As $m_1 \to m_2$, or $q \to 1$, or $\eta \to 1/4$, the
-        prior on $\eta$ for equal mass systems diverges (it is an
-        integrable singularity, but still singular), while the prior
-        on $q$ is well-behaved.  This doesn't matter for sampling
-        purposes, since the divergence in integrable, but it is
-        disconcerting for near-equal-mass systems to see a large peak
-        in the histogram for $\eta$ near $\eta = 1/4$.
-    \end{itemize}}}  By convention, $M_1 \geq M_2$.  The stationary phase then
+  because avoids an integrable singularity that can appear for
+  equal-mass systems when employing a prior on $p(\eta)$.  
+  %\will{This is not true.  I calculate (could be a bug, so
+   % check it)
+   % \begin{equation}
+   %   p(\chmass, q) = \frac{\chmass}{q} \left(\frac{\left(1+q\right)^2}{q}\right)^{\frac{1}{5}}
+   % \end{equation}
+  %  when 
+   % \begin{equation}
+    %  p\left(m_1, m_2\right) \propto \mathrm{const}
+   % \end{equation}
+   % The reasons to use $q$ instead of $\eta$
+   % \begin{itemize}
+     % \item It is more intuitive to astronomers (you mention this
+      %  above).
+     % \item As $m_1 \to m_2$, or $q \to 1$, or $\eta \to 1/4$, the
+      %  prior on $\eta$ for equal mass systems diverges (it is an
+      %  integrable singularity, but still singular), while the prior
+       % on $q$ is well-behaved.  This doesn't matter for sampling
+      %  purposes, since the divergence in integrable, but it is
+      %  disconcerting for near-equal-mass systems to see a large peak
+       % in the histogram for $\eta$ near $\eta = 1/4$.
+    %\end{itemize}}
+    }  By convention, $M_1 \geq M_2$.  The stationary phase then
 becomes an expansion in the Newtonian orbital velocity, $v=(\pi
@@
 choice allows us to explore the parameter estimation in the context of
-\will{\sout{optimal}} \will{loud, but plausible} detection candidates.
+loud, but plausible detection candidates.
 
@@
 realization drawn from a Gaussian colored by the PSD.  Without a
-realistic model including the actual instrument sensitivity, non
-stationary noise, and uncertainty in the PSD we cannot accurately
+realistic model including the actual instrument sensitivity, non-stationary
+ noise, and uncertainty in the PSD we cannot accurately
 simulate GW data to the point of making precise predictions about
@@
 encode any information of particular astrophysical
-interest.\footnote{For systems whose components are non-spinning.  The
-  presence of intrinsic angular momentum will, in general, couple to
-  the coalescence phase and wave polarization.  \will{But those
-    parameters are still physically uninteresting.  They couple to
-    interesting parameters in both the spinning and non-spinning
-    cases, which is why they must be included.  I would just eliminate
-    this footnote.}}
+interest.%\footnote{For systems whose components are non-spinning.  The
+  %presence of intrinsic angular momentum will, in general, couple to
+  %the coalescence phase and wave polarization.  \will{But those
+   % parameters are still physically uninteresting.  They couple to
+   % interesting parameters in both the spinning and non-spinning
+  %  cases, which is why they must be included.  I would just eliminate
+   % this footnote.}}
 
@@
 posterior probability distribution to be translated away from the true
-value; however, these displacements are drawn according to the
-zero-noise distribution \citep{Inadequacies} \will{I don't understand
+value; however, these displacements are drawn from the same probability
+distribution we are attempting to sample with the MCMC \citep{Inadequacies}.
+ \will{I don't understand
   what ``drawn according to the zero-noise distribution'' means.  I
-  don't think this sentence makes sense.}.  Once averaged, the mean
-uncertainties should be equal to the uncertainty drawn from the
-zero-noise runs.  \will{Again, not strictly true.}
+  don't think this sentence makes sense.} \carl{Changed the sentence, but
+   I think you, Tyson, and I will need to chat about this}.  These displacements average to 
+   zero over many runs, ensuring that the mean uncertainties should be equal to 
+   the uncertainty drawn from the zero-noise runs.  \will{Again, not strictly true.}
 
@@
 ratio.  These results were summarized in Table \ref{ciTableIntrinsic}.
-\will{You should mention the fact that our signals were chosen to be
-  loud, but plausible here.  Make sure to note that the average
-  uncertainties below do not necessarily reflect the average
-  uncertainty expected in the analysis of advanced detector era
-  detections.}
+It should be remembered that these signals were injected at high, 
+but not unrealistic, SNRs.  Thus, the results quoted can be thought of as the
+average uncertainties for a ``good'' Advanced LIGO/Virgo detection.
+
+%\will{You should mention the fact that our signals were chosen to be
+%  loud, but plausible here.  Make sure to note that the average
+  %uncertainties below do not necessarily reflect the average
+ % uncertainty expected in the analysis of advanced detector era
+ % detections.}
 
@@
 40 to 100 MPC at 65\% confidence, making the uncertainties frequently
-larger than the luminosity distances themselves.  However, it was
+larger than the luminosity distances themselves.  Furthermore, it was
 found that the cosine of the orbital inclination can be constrained to
-within 0.3 at the 65\% level, suggesting that Advanced LIGO/Virgo will
-be able to offer some information on GRB beaming angles in coincidence
-with electromagnetic observations.  \will{Are you sure about this?
-  Beaming angles about 10 degrees would have $\Delta \cos i \simeq
-  0.01$.}
+within 0.3 at the 65\% level, suggesting that Advanced LIGO/Virgo will not
+be able to offer constraining information on GRB beaming angles in coincidence
+with electromagnetic observations.  Coincidence detections will still be possible, but
+the orbital orientation information from gravitational-waves will 
+not provide astropysically relevant constrains.
+%  \will{Are you sure about this?
+ % Beaming angles about 10 degrees would have $\Delta \cos i \simeq
+ % 0.01$.}
 
@@
 general-relativistic physics required to solve the problem.  See
-\carl{[CITE]} for a better description of the systematic uncertainties
+\cite{BuonannoWaveform} for a better description of the systematic uncertainties
 present in the most common waveform families.  Additionally, there are
@@
 
-\carl{
-\section{TODO}
- \begin{itemize}
- \item Finish adding bibliography/sources
- \item double check the distribution of sources in Distance/Iota; make
-   sure iota is actually uniform in cos(i)
- \end{itemize}
- }
-
 \bibliographystyle{apj} \bibliography{paper}{}

### 2013-07-05 doc/paper.tex
proof-read almost-final version

@@
 gravitational waves.  Beyond the initial detection, the scientific
-promise of these instruments relies on the ability to perform
-parameter estimation. The majority of this effort has been towards the
+promise of these instruments relies on the effectiveness of our
+parameter estimation techniques. The majority of this effort has been towards the
 detection and characterization of gravitational waves from compact
@@
 systems, and within 2\% for unequal-mass systems.  We also report the
-average uncertainties on the sky-locations, luminosity distance, and
-orbital inclinations of ideal detection candidates  sources that can be
+average uncertainties on the sky-locations, luminosity distances, and
+orbital inclinations of ideal detection candidates that can be
 achieved by different network configurations.
@@
 detectors capable of regularly resolving astrophysical sources will
-come online \citep{AdvLIGO,AdvVirgo}.  The Advanced LIGO and Virgo
+come online \citep{AdvLIGO,AdvVirgo}.  The Advanced LIGO and Advanced Virgo
 detectors will provide the first insights into the final moments of
-binary compact object mergers, including the merger of binary neutron
+binary compact object mergers, including the mergers of binary neutron
 star systems.  Intense preparations are underway to characterize and
@@
 The mergers of binary neutron stars (BNS) are expected to be the one of the most
-common compact binary source in the advanced detector era.  %\will{This
+common compact binary sources in the advanced detector era.  %\will{This
   %is technically true (thanks to the word ``expected''), but the
@@
 evolution and observations of binary pulsars suggest that the number
-of binary neutron star mergers within Advanced LIGO/Virgo's detection
+of BNS mergers within Advanced LIGO/Virgo's detection
 horizon could reach several tens to hundreds each year
@@
 it could still be possible to extract information about both strong
-field gravitational physics \citep{Li2012} and the hydrodynamics of
-dense matter (e.g. the equation of state of nuclear matter,
-\citep{HindererBNS2010}).  Furthermore, the observations of multiple BNS systems
-will provide key insight into the evolution of binary systems in the
+field gravitational physics \citep{Li2012} and the the equation of state of
+dense nuclear matter
+\citep{HindererBNS2010}.  Furthermore, the observations of multiple BNS systems
+will provide key insights into the evolution of binary systems in the
 field \citep{VickyRates,KimRates} . As such, BNS systems will likely
@@
 
-Of course one must distinguish between the detection of such events,
-and the precision measurement of the relevant physical parameters.
+Of course one must distinguish between the detection of such events
+and the precision measurement of their relevant physical parameters.
 The detection of BNS systems will be performed with a matched
@@
 candidate signals at a sufficiently rapid rate to analyze months of
-data.  However, the parameter space
+data.  See \cite{S6search}.  However, the parameter space
 of these signals can be highly degenerate, with several locations in
@@
 advanced ground-based detectors to characterize BNS systems.  Until
-recently, the majority of studies have employed the Fisher matrix
+recently, the majority of studies have employed the Fisher-matrix
 formalism which was first adapted for gravitational-wave parameter
@@
 probability density functions for BNS systems with different masses
-and extrinsic parameters.  We select three equal-mass an one unequal-mass
+and extrinsic parameters.  We select three equal-mass and one unequal-mass
  binary systems as fiducal examples of BNS systems.  Each system was then analyzed 40 
- times with isotropically selected sky locations and binary orientations, and with a distance
+ times with isotropically selected sky locations and orbital orientations, and with a distance
  such that each signal was injected with a signal-to-noise ratio of 20.
-  The results are divided into three parameter sets of interest: the recovery of the mass
+  The results are divided into three subsections of interest: the recovery of the mass
 parameters (Section \ref{massSection}), the recovery of the orbital
@@
 localization of sources on the sky (Section \ref{skySection}).
-Finally we provide quantitative 1-dimensional confidence intervals on
+Finally we provide quantitative 1-dimensional credible intervals on
 each parameter in Section \ref{ciSection}.  These results, contained
@@
 the noise of the detector $n$.  We further assume that this noise is
-stationary and Gaussian with zero mean.  The detector output is
+stationary and Gaussian with zero mean.  The detector output is simply
 \begin{equation}
@@
 \end{equation}
-where $S_n(f)$ is the one-sided power spectral density (PSD) as a
+where $S_n(f)$ is the one-sided power-spectral density (PSD) as a
 function of frequency, and $\tilde{a}(f)$ and $\tilde{b}(f)$ are the
@@
 however, the presence of noise will in general deflect the maximum of
-our posterior away from the value at $\thpara_0$.  Therefore, the
+our posterior away from the value at $h(\thpara) = h_0$.  Therefore, the
 maximum posterior parameters do not necessarily correspond to the true
@@
 observable by advanced detectors, we can safely assume that the
-population of sources will be distributed homogeneously in volume, or
+population of sources will be distributed homogeneously in volume, i.e.\
 with a density proportional to $D^2$.  Our prior information can come
@@
 \item uniform in coalescence time over the segment of data being
-  analyzed, and
-\item a delta function at zero spin (i.e.\ we use waveforms without
-  spin)
+  analyzed,
+  \item a delta function at zero spin, and
 \item isotropic in all angles
@@
   $\boldsymbol{\theta_{\text{new}}}$.  The jump follows the
-  (conditional) probability distribution $q\left(
+  proposal distribution $q\left(
   \boldsymbol{\theta_{\text{new}}} | \boldsymbol{\theta_{\text{old}}}
@@
   $\boldsymbol{\theta_\text{new}}$ and repeat with
-  $\boldsymbol{\theta_\text{old}} \gets
-  \boldsymbol{\theta_\text{new}}$; otherwise, record
+  $\boldsymbol{\theta_\text{new}} \rightarrow
+  \boldsymbol{\theta_\text{old}}$; otherwise, record
   $\boldsymbol{\theta_\text{old}}$, and repeat.
@@
 \begin{equation}
-  q\equiv M_1/M_2~~~~\text{and}~~~~\chmass = (M_1 M_2)^{3/5}
+  q\equiv M_2/M_1~~~~\text{and}~~~~\chmass = (M_1 M_2)^{3/5}
   M_{tot}^{-1/5},
@@
   M^2$.  We elect to use $q$ as it is more physically intuitive, and
-  because avoids an integrable singularity that can appear for
+  because it avoids an integrable singularity that can appear for
   equal-mass systems when employing a prior on $p(\eta)$.  
@@
 from a lower-frequency cutoff of $20\text{Hz}$ to the
-innermost-stable-circular orbit of the systems in question, which for
+innermost-stable-circular orbit of the systems, which for
 a non-spinning binary is a function only of the total mass:
@@
 We consier the mass parameters ($\chmass,q$) and the phasing
-parameters, ($\phi_0,t_c$), to be the intrinsic parameters of a
+parameters, ($\phi_0,t_c$), to be the intrinsic parameters of the
 gravitational-wave signal.  There are an additional 5 extrinsic
 parameters, independent of the pN orbital phase, which can modulate
-the amplitude of the signal in an independent fashion for each
+the amplitude of the signal independently in each
 detector.  Combining these leads to our 9-dimensional parameter space
@@
   with respect to each detector, most of the information about these
-  extrinsic parameters comes from two quantities: the time-of-arrival
-  triangulation of the source locations, and the relative amplitudes
-  within the detector network.
+  extrinsic parameters comes from two sources: the time-of-arrival
+  triangulation of the signal, and the relative amplitudes
+  in each detector in the network.
 
@@
 choice allows us to explore the parameter estimation in the context of
-loud, but plausible detection candidates.
-
-Finally, note that the power-spectral density that defines the inner
+loud but plausible detection candidates.
+
+Finally, note that the PSD that defines the inner
 product \eqref{innerProduct} is simply the time-averaged sensitivity
@@
  noise, and uncertainty in the PSD we cannot accurately
-simulate GW data to the point of making precise predictions about
+simulate gravitational-wave data to the point of making precise predictions about
 parameter estimation capabilities.  Furthermore, the posterior
@@
 the posterior distribution function for each source averaged over all
-possible (Gaussian) noise realizations assuming we have the correct
+possible (Gaussian) noise realizations, assuming we have the correct
 PSD.  \will{This is not true because the map from noise realization to
@@
 several noise realizations.  The comparison of the noise-dependent and
-noise-free results can be found in \ref{noiseSection}.
-
-\begin{comment}
-\subsection{Testing MCMC Convergence}
-
-Each set of MCMC samples is tested for convergence by examining both
-the Gelman-Rubin diagnostic and the auto-correlation length of the
-MCMC chains, the details of which can be found in \carl{[CITE]} and
-\carl{[CITE]}, respectively.  However, there is an additional check we
-can consider: the standard matched filtering searches employed by the
-LIGO/Virgo collaboration assume that a detection will occur when one
-of the template waveforms matches the detector data with a signal
-overlap of 97\% or better \carl{[CITE]}.  That is, for a template
-waveform $h^{t}(f)$ and detector output $s(f)$, an overlap of
-
-\begin{equation}
-\left< s | h^{t}\right> \geq 97\% \nonumber
-\end{equation}
-
-\noindent yields a detection candidate.  This requirement provides us
-with a convenient test for the effectiveness of our parameter
-estimation.  First, we note that maximizing our likelihood function,
-\eqref{likelihood}, is identical to maximizing the SNR
-\eqref{formalSNR} of our template waveform in a given stretch of data.
-Therefore, the better the match between the template waveform and the
-data, the higher the SNR.  Since we assume, quite tautologically, that
-our parameter estimation code should estimate parameters at least as
-well as a matched filtering approach, we would be immediately
-suspicious of any MCMC run whose maximum-likelihood waveform had an
-SNR below that of our pipeline trigger.  In that case, we would
-perform the MCMC with a much longer runtime, until the maximum
-likelihood of our posterior distribution had an SNR at least as high
-as the detection.
-
-For the purposes of our present study, we reproduce this information
-as follows: since we know the true SNR of the signal we are
-simulating, we assume that the ``trigger'' SNR returned by our
-detection pipeline is 97\% of the true SNR.  We then assume any
-posterior distribution whose maximum likelihood satisfies
-
-\begin{equation}
-\text{Maximum Likelihood} \leq 0.97 \times
-\left(\frac{\rho_{inj}^2}{2}\right) \nonumber
-\end{equation}
-
-\noindent has not converged.  As one would expect, the lower-mass,
-longer waveform systems require longer to converge.  With our original
-runtime of one week over 8 processors, we found that seven of our
-$1M_{\odot}/1M_{\odot}$ systems had not converged, while all but one
-system for our $1.4M_{\odot}/1.4M_{\odot}$ and
-$1M_{\odot}/2.5M_{\odot}$ systems had converged.  All of the
-$2.5M_{\odot}/2.5M_{\odot}$ systems converged within one week.
-
-\carl{[THIS SECTION INCOMPLETE WILL REQUIRE THE FINISHED HLV/HLVI RUNS
-    BEFORE I CAN COMPLETE IT]}
-\end{comment}
+noise-free results can be found in Section \ref{noiseSection}.
 
@@
   $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in
-  Figure~\ref{1414masses}}
+  Figure~\ref{1414masses}.}
 \end{figure*}
@@
 position on the sky, $\alpha$ and $\delta$, and the luminosity
-distance of the source, $D$.  While the coalescence phase $\phi_c$,
+distance of the source, $D$.  While the coalescence phase $\phi_0$,
 the coalescence time $t_c$, and the wave polarization $\psi$ must be
@@
 that the peak of several parameters, including the chirp mass,
-$\chmass$, appears to be displaced from the true values in red.  This
+$\chmass$, appears to be displaced from the true values in dashed red.  This
 effect is due to the reduction of the 9-dimensional PDF to a series of
@@
    component masses of the binary ($M_1$ and $M_2$).  In the
-   $\chmass$-$q$ space, the posterior would resemble a Gaussian if not
+   $\chmass$-$q$ space, the posterior would almost resemble a Gaussian if not
    for the limitation of $q \leq 1$.  The presence of the $q$ cutoff
@@
    features present.  When projected as 1D marginalized posteriors,
-   the component masses resemble the posterior PDFs shown in figure
+   the component masses resemble the posterior PDFs shown in Figure
    \ref{metaMassPDFs}.}
@@
     clip=false,scale=0.63]{125masses2D.pdf}
- \caption{Similar to Figure~\ref{1414masses}, for a typical
+ \caption{Similar to Figure~\ref{1414masses}, but for a typical
    $1M_{\odot}/2.5M_{\odot}$ system.  The unequal mass ratio displaces
-   the posterior PDFs from the $q \leq 1$ present in the equal mass
+   the posterior PDFs from the $q \leq 1$ boundary present in the equal-mass
    case, yielding a Gaussian PDF in both the $\chmass$-$q$ and
@@
    identical mass ratios but different total masses have
-   quantitatively identical PDFs when normalized to the true total
+   quantitatively identical PDFs when normalized to the total
    mass.}
@@
 Advanced LIGO/Virgo to construct a population of BNS masses will be
-one of the more useful applications of gravitational-wave astronomy.
+one of the more useful and immediate applications of gravitational-wave astronomy.
 
@@
 marginalized 2D posterior PDFs of our mass parameters for prototypical
-equal mass and unequal mass binaries.  We include the PDF in both the
+equal-mass and unequal-mass binaries.  We include the PDF in both the
 $\chmass$-$q$ space (relevant for the waveform and the MCMC
@@
 1-dimensional mass PDFs into a single posterior probability for the
-system.  See Figure~\ref{metaMassPDFs}.  Notice how when averaged and
+system in Figure~\ref{metaMassPDFs}.  Notice how, when averaged and
 normalized to the injected values, the recovery of the component
@@
 holes and neutron stars lies at approximately $3M_{\odot}$, then it
-might be assumed that the mass recovery would allow one to
+might be naively assumed that the mass recovery would allow one to
 discriminate between black holes and neutron stars.
@@
 relative amplitude difference between the two gravitational-wave
-polarizations, such that to lowest order
+polarizations, such that to lowest order:
 
@@
 h_+(f) &= \frac{1+\cos^2(\iota)}{2 D} \tilde{h}(f) \nonumber
-\\ h_\times(f) &= i \frac{\cos(\iota)}{D}\tilde{h}(f)
+\\ h_\times(f) &= i \frac{\cos(\iota)}{D}\tilde{h}(f) .
 \end{align}
@@
 the inclination $\iota$ can be highly correlated in any parameter
-estimation study.
+estimation recovery.
 
@@
 + \pi/2$.  As the majority of the information extracted via parameter
-estimation is from the phase of the signal, the recovery of a
+estimation is from the phase of the signal, the recovery of the
 posterior in $D$-$\iota$ space will be limited, even during the
@@
 polarization and the relative difference in SNR between individual
-detectors can break this plane-reflected degeneracy, leading to a
+detectors can break this plane-reflection degeneracy, leading to a
 bi-modal distribution with significantly more support in one mode of
@@
 comparison of the sky-localization benefits of the HLVI configuration
-verses the three-detector network.  As previously, the quantitative
-results for the two network configurations are reported in Table
+verses the three-detector network.  The quantitative
+results for the two network configurations are again reported in Table
 \ref{ciTableExtrinsic}.
@@
     0cm]{HLVsky.pdf}
- \caption{The uncertainty on the sky of 160 BNS systems in the HLV
+ \caption{The uncertainties on the sky of 160 BNS systems in the HLV
    detector configuration.  Each region represents a single injection,
    with the colored central region representing the 65\% uncertainty
-   region on the sphere, and the gray region representing the 90\%
+   region on the sphere, and the gray shade representing the 90\%
    uncertainty region.  The color scheme indicates the total solid
@@
    uncertainty regions at particular points; this is due to the
-   specific realization of our network pattern sensitivity.}
+   specific pattern of sensitivity over the sky for the three-detector network.}
  \label{2525SkyLocHLV}
@@
    were recovered by the HLV configuration.  The two improvements are
-   due to the breaking of the degeneracy in sky location recovery that
+   due to the breaking of the plane degeneracy that
    is facilitated by the transition to a four-detector network.}
@@
    LIGO power spectral density, while the gray-shaded curve is the
-   zero-noise PDF.  Notice how the curve is relatively unchanged, but
-   usually assumes a Gaussian PDF displaced from the true value.  This
+   zero-noise PDF.  Notice how each curve is a Gaussian PDF with roughly similar shape,
+   but different mean, to the zero-noise PDF.  This
    only holds true for glitch-free data, which is an unrealistic
@@
 
-In the case of a unique Gaussian realization of the Advanced-LIGO
+In the case of a unique Gaussian realization of the Advanced LIGO
 noise curve, each realization causes the maximum likelihood of the
@@
 compared the results to the same MCMC recovery in the zero-noise case.
-This example can be seen for one-dimensional marginalization of
+This example can be seen for one-dimensional marginalizations of
 $\chmass$ and $q$ in Fig. \ref{noisePDFs}.  In effect, the ``real
@@
 When quoting parameter estimation results, it is often convenient to
-reduce the full parameter space to credible intervals about single,
+reduce the full parameter space to credible intervals about single
 marginalized parameters..  To that end, we state the averaged 65\%
-confidence intervals about the single parameters for each of the three
+intervals about the single parameters for each of the three
 parameter pairs of interest.  These were already plotted for the sky
@@
 with electromagnetic observations.  Coincidence detections will still be possible, but
-the orbital orientation information from gravitational-waves will 
+the orbital orientation information from gravitational waves will 
 not provide astropysically relevant constrains.
@@
 three-detector sites plus a LIGO India detector, was able to localize
-the sky-locations to within 13 $\mathrm{deg}^2$ on the sky at the 65\%
+all the sky locations to within 13 $\mathrm{deg}^2$ on the sky at the 65\%
 confidence interval, with an average 65\% confidence interval of $\sim
@@
 that will be measured routinely in the Advanced Detector era.  Given
-the high degree of coupling between the spin and the mass of objects
+the high degree of coupling between the spin and mass of objects
 in the gravitational-wave parameter space, it remains unclear if the

### 2013-07-09 doc/paper.tex
fixed rest of wills comments

@@
 advanced era detectors and suppress any effects of detector noise by
-picking the (most likely) noise realization that has $n(t) \equiv 0$.
+picking $n(t) \equiv 0$.
 Consequently, what we recover with the MCMC could be interpreted as
@@
 possible (Gaussian) noise realizations, assuming we have the correct
-PSD.  \will{This is not true because the map from noise realization to
-  posterior is not linear.}
+PSD and that the signal is sufficiently powerful for the linearized-signal
+approximation \citep{Vallisneri} to be valid.
 
@@
 two reasons.  First, the results of a zero-noise analysis are
-identical to those that would be achieved by averaging the results of
+similar to those that would be achieved by averaging the results of
 multiple identical injections in different Gaussian noise
-realizations, as was argued in Section \ref{waveformSection}.
-\will{Again, this is not true!}  The second reason is we are not able
+realizations, as was argued in Section \ref{waveformSection}.  The second reason 
+is we are not able
 to predict the characteristics of realistic (often non-Gaussian)
@@
 posterior probability distribution to be translated away from the true
-value; however, these displacements are drawn from the same probability
-distribution we are attempting to sample with the MCMC \citep{Inadequacies}.
- \will{I don't understand
-  what ``drawn according to the zero-noise distribution'' means.  I
-  don't think this sentence makes sense.} \carl{Changed the sentence, but
-   I think you, Tyson, and I will need to chat about this}.  These displacements average to 
-   zero over many runs, ensuring that the mean uncertainties should be equal to 
-   the uncertainty drawn from the zero-noise runs.  \will{Again, not strictly true.}
+value.  These displacements tend to cancel 
+    over many runs, ensuring that the mean uncertainties should be nearly identical to 
+   the uncertainty drawn from the zero-noise runs.  Again, this only holds in the case
+  where a signal is sufficiently loud that the posterior is linear in the parameters 
+  $\thpara$.
 

### 2013-07-09 massPDFs.py

@@ -80,7 +80,7 @@ for number in massBins:
 			n += dx
 
 		ax1 = subplot(3,1,1)
-		fill_between(Xm1,Ym1,zeros(len(Ym1)), alpha=0.4, color=colors[Bin])
+		fill_between(Xm1,Ym1,zeros(len(Ym1)), alpha=0.3, color=colors[Bin])
 		plot(Xm1,Ym1, color=colors[Bin], linestyle='solid', lw=3)
 		fill_between(Xm2,Ym2,zeros(len(Ym2)), alpha=0.4, color=colors[Bin])
 		plot(Xm2,Ym2, color=colors[Bin], linestyle='dashed', lw=3)
@@ -124,8 +124,8 @@ for number in massBins:
 			n += dx
 
 		ax3 = subplot(3,1,2)
-		plot(Xm,Ym, color=colors[Bin], lw=1)
-		fill_between(Xm,Ym,zeros(len(Ym)), alpha=0.4, color=colors[Bin])
+		plot(Xm,Ym, color=colors[Bin], lw=3)
+		fill_between(Xm,Ym,zeros(len(Ym)), alpha=0.3, color=colors[Bin])
 		axvline(1,0,max(Ym),color='black', lw=3)
 		ax3.grid(True)
 		ylabel('Probability Densities',fontsize=22)
@@ -143,8 +143,8 @@ for number in massBins:
 			n += dx
 
 		ax4 = subplot(3,1,3)
-		plot(Xq,Yq, color=colors[Bin], lw=1)
-		fill_between(Xq,Yq,zeros(len(Yq)), alpha=0.4, color=colors[Bin])
+		plot(Xq,Yq, color=colors[Bin], lw=3)
+		fill_between(Xq,Yq,zeros(len(Yq)), alpha=0.3, color=colors[Bin])
 #		axvline(1,0,max(Yq),color='black', lw=3)
 		ax4.grid(True)
 		xlabel('Mass Ratios ($q$)', fontsize=18)

### 2013-07-25 doc/paper.tex
Fixed a few typos and made a few minor modifications.

@@
 
-The mergers of binary neutron stars (BNS) are expected to be the one of the most
+The mergers of binary neutron stars (BNS) are expected to be one of the most
 common compact binary sources in the advanced detector era.  %\will{This
@@
 and extrinsic parameters.  We select three equal-mass and one unequal-mass
- binary systems as fiducal examples of BNS systems.  Each system was then analyzed 40 
+ binary systems as fiducial examples of BNS systems.  Each system was then analyzed 40 
  times with isotropically selected sky locations and orbital orientations, and with a distance
@@
 We assume that the time-domain signal in a gravitational-wave network
-can be written as a combination of a gravitational waveform $h_0$ and
+can be written as the sum of a gravitational waveform $h_0$ and
 the noise of the detector $n$.  We further assume that this noise is
@@
 Since the noise model is Gaussian, we can write the probability of a
-specific signal realization $s$ given an input waveform as
+specific signal realization $s$ given an input waveform $h(\thpara)$ as
 proportional to the probability that the residual is Gaussian
@@
 population of sources will be distributed homogeneously in volume, i.e.\
-with a density proportional to $D^2$.  Our prior information can come
-from mathematical limits in the parameter space or from our \textit{a
-  priori} knowledge of astrophysical systems.  We employ priors which
-are
+with a density proportional to the square of the luminosity distance $D^2$.  
+Our prior information can come from mathematical limits in the parameter space 
+or from our \textit{a priori} knowledge of astrophysical systems.  
+We employ priors which are
 \begin{itemize}
@@
 a prior with a lower component mass cutoff for the present study, in
-practice the higher prior boundary does not effect our current
+practice the higher prior boundary does not affect our current
 analysis.
@@
 
-When dealing with network a of gravitational-wave detectors, the SNRs
+When dealing with a network of gravitational-wave detectors, the SNRs
 of the individual detectors add in quadrature.  That is, the network
@@
 
-For this study, we consider four seperate populations of BNS systems,
+For this study, we consider four separate populations of BNS systems,
 with component mass combinations of $1M_{\odot}/1M_{\odot}$,
@@
 recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system.  These
-PDFs are typical of the type of results that will be produced by
+PDFs are representative of the type of results that will be produced by
 parameter estimation studies in the advanced detector era.  Notice
@@
 comparison of the sky-localization benefits of the HLVI configuration
-verses the three-detector network.  The quantitative
+versus the three-detector network.  The quantitative
 results for the two network configurations are again reported in Table
@@
 instrumentation effects that will arise in any advanced
-gravitational-wave detector.  The realization of noise will be the a
+gravitational-wave detector.  The realization of noise will be a
 major factor in the deflection of signal PDFs from the idealized cases

### 2013-07-30 doc/paper.tex
added vicky's and diego's comments, and finalized the draft

@@
 
-Within the next five years, the Advanced LIGO/Virgo network will have
+Within the next five years, it is expected that the Advanced LIGO/Virgo network will have
 reached a sensitivity sufficient to enable the routine detection of
 gravitational waves.  Beyond the initial detection, the scientific
-promise of these instruments relies on the effectiveness of our
-parameter estimation techniques. The majority of this effort has been towards the
+promise of these instruments relies on the effectiveness of our physical
+parameter estimation capabilities. The majority of this effort has been towards the
 detection and characterization of gravitational waves from compact
 binary coalescence, e.g. the coalescence of binary neutron stars.
-While several previous studies have focused on the parameter
-estimation abilities of advanced detectors, the majority have relied
-on approximation techniques such as the Fisher Matrix.  We report the
-statistical uncertainties that will be achievable, in practice, using
+While several previous studies have investigated the accuracy of parameter
+estimation with advanced detectors, the majority have relied
+on approximation techniques such as the Fisher Matrix.  Here we report the
+statistical uncertainties that will be achievable using
 the full parameter estimation machinery developed by the LIGO/Virgo
-Collaboration.  We find the recovery of the individual masses to be
-fractionally within 10\% at the 65\% credible intervals for equal-mass
-systems, and within 2\% for unequal-mass systems.  We also report the
-average uncertainties on the sky-locations, luminosity distances, and
+Collaboration via Markov-Chain Monte Carlo methods. 
+ We find the recovery of the individual masses to be
+fractionally within 8.5\% (13.4\%) at the 65\% (90\%) credible intervals for equal-mass
+systems, and within 2\% (3.1\%) for unequal-mass systems.  We also find that the Advanced
+LIGO/Virgo network will constrain the locations of binary neutron star mergers to an average
+ uncertainty of $7.4$ $\mathrm{deg}^2$ (18.6 $\mathrm{deg}^2$) on the sky.
+This region is improved to  2.2 $\mathrm{deg}^2$ $(5$ $\mathrm{deg}^2)$ with the addition of the proposed LIGO India detector to the network.
+We also report the
+average uncertainties on the luminosity distances and
 orbital inclinations of ideal detection candidates that can be
@@
 Within the next few years, the first generation of gravitational-wave
-detectors capable of regularly resolving astrophysical sources will
+interferometers capable of regularly detecting astrophysical sources will
 come online \citep{AdvLIGO,AdvVirgo}.  The Advanced LIGO and Advanced Virgo
-detectors will provide the first insights into the final moments of
+detectors (and the anticipated LIGO India detector)
+ will provide the first insights into the final moments of
 binary compact object mergers, including the mergers of binary neutron
@@
 will provide key insights into the evolution of binary systems in the
-field \citep{VickyRates,KimRates} . As such, BNS systems will likely
+field \citep{VickyRates,KimRates,OsowskiRates2011,RichardRates2010} . As such, BNS systems will likely
 form the ``bread and butter'' of the compact binary coalescence
@@
 By employing the full parameter-estimation machinery that will
-eventually be used in the Advanced LIGO/Virgo era, our results give
- estimates at the realistic capabilities of
+eventually be used in the Advanced LIGO/Virgo era, our results
+ give estimates of the realistic capabilities of
 advanced ground-based detectors to characterize BNS systems.  Until
@@
 and extrinsic parameters.  We select three equal-mass and one unequal-mass
- binary systems as fiducial examples of BNS systems.  Each system was then analyzed 40 
+ binary systems as prototypical examples of BNS systems.  Each system is analyzed 40 
  times with isotropically selected sky locations and orbital orientations, and with a distance
- such that each signal was injected with a signal-to-noise ratio of 20.
+ such that each signal was injected with a network signal-to-noise ratio of 20.
   The results are divided into three subsections of interest: the recovery of the mass
@@
 pick a set of parameters $\thpara$ such that $h(\thpara) = h_0$, then
-the posterior \eqref{posterior} will be near a global maximum;
+the likelihood \eqref{likelihood} will be near a global maximum;
 however, the presence of noise will in general deflect the maximum of
-our posterior away from the value at $h(\thpara) = h_0$.  Therefore, the
-maximum posterior parameters do not necessarily correspond to the true
-parameters of the source; when interpreting parameter estimation
-results it is important to consider the full posterior distribution
-function.
+our likelood away from the value at $h(\thpara) = h_0$.  Therefore, the
+maximum likelihood parameters do not necessarily correspond to the true
+parameters of the source.
 
@@
 
-To perform the integral defined in \eqref{innerProduct}, we used as
-our power-spectral density the best estimate for a high-power,
-zero-detuning configuration of Advanced LIGO, provided by the LIGO
-Scientific Collaboration.  Both the noise curve and technical reports
-describing it can be found in \cite{ADVLIGONoise}.  We consider two
-configurations of the advanced detector network: a three-detector
-configuation consistanting of the two LIGO sites (in Hanford, WA and
-Livingston, LA) and the Virgo site (in Pisa, Italy), and a
-four-detector configuration that adds the proposed LIGO-India detector
-(in Chitradurga, KA).  For simplicity, we assume each detector to be
-operating at the Advanced LIGO sensitivity.
-
-For a multi-detector network, the noise-weighted inner products
-\eqref{innerProduct} combine linearly, allowing us to use the above
-formalism with minimal modification.  We integrate the inner product
-from a lower-frequency cutoff of $20\text{Hz}$ to the
-innermost-stable-circular orbit of the systems, which for
-a non-spinning binary is a function only of the total mass:
-
-\begin{equation}
-  \pi f_{\text{ISCO}} = \frac{1}{6^{3/2}M_{tot}}.
-  \label{ISCOFrequency}
-\end{equation}
-
 We consier the mass parameters ($\chmass,q$) and the phasing
@@
 
+  \subsection{Detector Configuration and Noise Models}
+  \label{detectorSection}
+
+To perform the integral defined in \eqref{innerProduct}, we used as
+our power-spectral density the best estimate for a high-power,
+zero-detuning configuration of Advanced LIGO, provided by the LIGO
+Scientific Collaboration.  Both the noise curve and technical reports
+describing it can be found in \cite{ADVLIGONoise}.  We consider two
+configurations of the advanced detector network: a three-detector
+configuation consistanting of the two LIGO sites (in Hanford, WA and
+Livingston, LA) and the Virgo site (in Pisa, Italy), and a
+four-detector configuration that adds the proposed LIGO-India detector
+(in Chitradurga, KA).  For simplicity, we assume each detector to be
+operating at the Advanced LIGO sensitivity.
+
+For a multi-detector network, the noise-weighted inner products
+\eqref{innerProduct} combine linearly, allowing us to use the above
+formalism with minimal modification.  We integrate the inner product
+from a lower-frequency cutoff of $20\text{Hz}$ to the
+innermost-stable-circular orbit of the systems, which for
+a non-spinning binary is a function only of the total mass:
+
+\begin{equation}
+  \pi f_{\text{ISCO}} = \frac{1}{6^{3/2}M_{tot}}.
+  \label{ISCOFrequency}
+\end{equation}
+
 We define the signal-to-noise ratio (SNR) of a gravitational wave in a
@@
 
-When dealing with a network of gravitational-wave detectors, the SNRs
+\noindent When dealing with a network of gravitational-wave detectors, the SNRs
 of the individual detectors add in quadrature.  That is, the network
@@
 for each source.  While unphysical from an astrophysics perspective
-(binary sources should be distributed evenly in comoving volume), this
+(binary sources are expected to be distributed uniformly in comoving volume), this
 choice allows us to explore the parameter estimation in the context of
@@
 our different injected signals within each mass bin.  While this may
-initially seem disconcerting, it is to be expected.  Recall that all
+initially seem disconcerting, it is to be expected for the analysis presented here.
+  Recall that all
 of the BNS signals were injected with a network SNR of 20 into a
@@
 
-Unfortunately, this will not be feasible in practice.  We have
+In practice, there is a physical complication to this claim: we have
 neglected the spin of the binaries, which will be highly correlated to
-the masses.  This coupling means that a higher-massed spinning black
+the masses.  This coupling means that, in the case where the black hole spins
+are parallel to the orbital angular momentum, a higher-massed spinning black
 hole systems can produce waveforms very similar to non-spinning,
-low-mass systems, making it extremely difficult to discern between
-non-spinning neutron stars and spinning, more massive black holes
+low-mass systems.  This effect makes it extremely difficult to discern between
+non-spinning neutron stars and spin-aligned, more massive black holes
 \citep{Baird2013,Hannam2013}.  However, the situation is not hopeless:
@@
 comparison of the sky-localization benefits of the HLVI configuration
-versus the three-detector network.  The quantitative
-results for the two network configurations are again reported in Table
-\ref{ciTableExtrinsic}.
+versus the three-detector network.  For the HLV configuration, we find that
+ all of the signals are recovered with
+a solid angle uncertainty of less than 60 $\mathrm{deg}^2$ (120 $\mathrm{deg}^2$)
+at the 65\% (90\%) credible interval, while the HLVI configuration 
+recovers all signals to less than 13 $\mathrm{deg}^2$ (34 $\mathrm{deg}^2$).
+The mean quantitative results for the two network configurations show a similar
+ benefit with the addition of LIGO India, and are again reported in
+  Table \ref{ciTableExtrinsic}.
 
@@
 multiple identical injections in different Gaussian noise
-realizations, as was argued in Section \ref{waveformSection}.  The second reason 
+realizations, as was argued in Section \ref{detectorSection}.  The second reason 
 is we are not able
@@
 of being accurate while requiring a huge computational burden to
-combine the results of many MCMC runs in different noise realizations.
+combine the results of many MCMC runs in many different noise realizations.
 
@@
 reduce the full parameter space to credible intervals about single
-marginalized parameters..  To that end, we state the averaged 65\%
+marginalized parameters..  To that end, we state the averaged 65\% and 90\% credible
 intervals about the single parameters for each of the three
@@
 
-In Table~\ref{ciTableIntrinsic}, we list the mean 65\% confidence
+In Table~\ref{ciTableIntrinsic}, we list the mean 65\% and 90\% credible
 intervals recovered for the four mass configurations in both network
@@
 
+Given the previous reliance of parameter estimation studies on the Fisher
+Information Matrix, it is informative to compare the credible intervals quoted here 
+to previously reported values in the literature.  We recompute the credible intervals 
+of the chirp mass and the symmetric mass ratio ($\eta \equiv m_1 m_2 / M_{tot}^2$)
+at the 68\% level (1-$\sigma$) for the $1.4M_{\odot}/1.4M_{\odot}$ system presented 
+here.  We then compare the findings of the MCMC to the Fisher matrix predictions using
+an identical network configuration (HLV), noise curve, and waveform model.  
+We compute the Fisher matrix uncertainties 
+using a code previously described in \cite{Inadequacies}.  We find that the MCMC credible
+ intervals vary significantly from
+the estimates of the Fisher matrix, with the Fisher matrix underestimating the 
+fractional uncertainties by as much as a factor of three.  See Table~\ref{FIMvsMCMC}.
+   This disagreement, while 
+   unsurprising, emphasizes the importance of employing the full parameter estimation
+    machinery of an MCMC when making physically relevant claims.
+
 \begin{table*}[t!]
 \centering
-\caption{Mean 65\% confidence intervals for intrinsic parameters for
-  each of the four systems considered.  We report the confidence
+\caption{Mean 65\% and 90\% credible intervals for intrinsic parameters for
+  each of the four systems considered.  We report the credible
   intervals of quantities measured, as well as the component masses
@@
   separately for consistency.}
-\begin{tabular}{lcccccccccc}
-
-\\HLVI\\ \hline\hline System & \vline & $\Delta \chmass / \chmass$ &
-\vline & $\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline &
-$\Delta M_{tot}/M_{tot}$ & \vline & $\Delta q$\\ \hline\hline
-$1M_{\odot}-1M_{\odot}$ & \vline & $4.70\times 10^{-5}$ & \vline &
-$6.83\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline &
-$3.67\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$\\ \hline
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.27\times 10^{-5}$ & \vline &
-$7.27\times 10^{-2}$ & \vline & $6.45\times 10^{-2}$ & \vline &
-$4.10\times 10^{-3}$ & \vline & $1.24\times 10^{-1}$ \\ \hline
-$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline &
-$1.74\times 10^{-2}$ & \vline & $1.49\times 10^{-2}$ & \vline &
-$8.15\times 10^{-3}$ & \vline & $1.29\times 10^{-2}$\\\hline
-$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.29\times 10^{-4}$ & \vline &
-$8.52\times 10^{-2}$ & \vline & $7.41\times 10^{-2}$ & \vline &
-$5.51\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$\\ \hline\hline
+  \tabcolsep=0.11cm
+      {\renewcommand{\arraystretch}{1.3} 
+\begin{tabular}{lcccccccccccccccccccc}
+
+\\HLVI\\
+
+ \hline\hline System & \vline & \multicolumn{3}{c}{$\Delta \chmass / \chmass$} &
+\vline & \multicolumn{3}{c}{$\Delta M_1 / M_1$} & \vline & \multicolumn{3}{c}{$\Delta M_2 / M_2$} & \vline &
+\multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
+Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
+\hline\hline
+
+$1M_{\odot}-1M_{\odot}$ & \vline &$0.00465\%$ & \vline &$0.00863\%$ & \vline & $6.78\%$ & \vline &$10.6\%$ & \vline & $6.06\%$ & \vline &$9.28\%$ & \vline & $0.362\%$ & \vline &$0.633\%$ & \vline & $0.117$ & \vline &$0.178$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00827\%$ & \vline &$0.0154\%$ & \vline & $7.27\%$ & \vline &$11.4\%$ & \vline & $6.45\%$ & \vline &$9.90\%$ & \vline & $0.410\%$ & \vline &$0.724\%$ & \vline & $0.124$ & \vline &$0.189$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0165\%$ & \vline &$0.0294\%$ & \vline & $1.74\%$ & \vline &$3.10\%$ & \vline & $1.49\%$ & \vline &$2.67\%$ & \vline & $0.815\%$ & \vline &$1.46\%$ & \vline & $0.0129$ & \vline &$0.0231$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.0229\%$ & \vline &$0.0424\%$ & \vline & $8.52\%$ & \vline &$13.3\%$ & \vline & $7.42\%$ & \vline &$11.4\%$ & \vline & $0.551\%$ & \vline &$0.958\%$ & \vline & $0.141$ & \vline &$0.215$\\
+
+\hline
+\hline
 
@@
 
-\hline\hline System & \vline & $\Delta \chmass / \chmass$ & \vline &
-$\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline & $\Delta
-M_{tot}/M_{tot}$ & \vline & $\Delta q$\\ \hline\hline
-$1M_{\odot}-1M_{\odot}$ & \vline & $4.66\times 10^{-5}$ & \vline &
-$6.82\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline &
-$3.64\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$ \\ \hline
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.31\times 10^{-5}$ & \vline &
-$7.35\times 10^{-2}$ & \vline & $6.51\times 10^{-2}$ & \vline &
-$4.18\times 10^{-3}$ & \vline & $1.25\times 10^{-1}$\\ \hline
-$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline &
-$1.75\times 10^{-2}$ & \vline & $1.50\times 10^{-2}$ & \vline &
-$8.19\times 10^{-3}$ & \vline & $1.30\times 10^{-2}$ \\ \hline
-$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.30\times 10^{-4}$ & \vline &
-$8.53\times 10^{-2}$ & \vline & $7.42\times 10^{-2}$ & \vline &
-$5.52\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$ \\ \hline\hline
-
-\end{tabular}
+ \hline\hline System & \vline & \multicolumn{3}{c}{$\Delta \chmass / \chmass$} &
+\vline & \multicolumn{3}{c}{$\Delta M_1 / M_1$} & \vline & \multicolumn{3}{c}{$\Delta M_2 / M_2$} & \vline &
+\multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
+Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
+\hline\hline
+
+$1M_{\odot}-1M_{\odot}$ & \vline &$0.00466\%$ & \vline &$0.00865\%$ & \vline & $6.82\%$ & \vline &$10.5\%$ & \vline & $6.09\%$ & \vline &$9.25\%$ & \vline & $0.364\%$ & \vline &$0.633\%$ & \vline & $0.117$ & \vline &$0.177$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00831\%$ & \vline &$0.0155\%$ & \vline & $7.35\%$ & \vline &$11.5\%$ & \vline & $6.51\%$ & \vline &$10.0\%$ & \vline & $0.418\%$ & \vline &$0.743\%$ & \vline & $0.125$ & \vline &$0.191$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0165\%$ & \vline &$0.0295\%$ & \vline & $1.75\%$ & \vline &$3.11\%$ & \vline & $1.50\%$ & \vline &$2.67\%$ & \vline & $0.819\%$ & \vline &$1.46\%$ & \vline & $0.0130$ & \vline &$0.0232$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.023\%$ & \vline &$0.0428\%$ & \vline & $8.53\%$ & \vline &$13.4\%$ & \vline & $7.42\%$ & \vline &$11.4\%$ & \vline & $0.552\%$ & \vline &$0.968\%$ & \vline & $0.141$ & \vline &$0.216$\\
+
+\hline
+\hline
+
+\end{tabular}}
 \label{ciTableIntrinsic}
@@
 \centering
-\caption{Mean 65\% confidence intervals of extrinsic parameters for
+\caption{Mean 65\% and 90\% credible intervals of extrinsic parameters for
   each of the four systems considered.  As expected, there exists a
@@
   not by combining the $\alpha$ and $\delta$ uncertainties.}
-\begin{tabular}{lcccccccccc}
-
-\\HLVI\\ \hline\hline System & \vline & $\Delta D$ $(mpc)$ & \vline &
-$\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline &
-$\Delta \delta$ $(deg)$ & \vline & $\Delta\Omega$
-$(deg^2)$\\ \hline\hline $1M_{\odot}-1M_{\odot}$ & \vline &
-$3.64\times 10^{1}$ & \vline & $2.23\times 10^{-1}$ & \vline & $1.45$
-& \vline & $1.48$ & \vline & $1.88$\\ \hline
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $5.52\times 10^{1}$ & \vline &
-$2.56\times 10^{-1}$ & \vline & $1.49$ & \vline & $1.50$ & \vline &
-$2.26$\\ \hline $1M_{\odot}-2.5M_{\odot}$ & \vline & $6.48\times
-10^{1}$ & \vline & $2.93\times 10^{-1}$ & \vline & $1.54$ & \vline &
-$1.64$ & \vline & $2.10$\\ \hline $2.5M_{\odot}-2.5M_{\odot}$ & \vline
-& $1.06\times 10^{2}$ & \vline & $2.99\times 10^{-1}$ & \vline &
-$1.03\times 10^{1}$ & \vline & $1.61$ & \vline & $2.22$\\ \hline\hline
+
+  \tabcolsep=0.11cm
+      {\renewcommand{\arraystretch}{1.3} 
+\begin{tabular}{lcccccccccccccccccccc}
+
+\\HLVI\\ 
+\hline\hline System & \vline & \multicolumn{3}{c}{$\Delta D$ $(mpc)$} & \vline &
+\multicolumn{3}{c}{$\Delta |\cos(\iota)|$} & \vline & \multicolumn{3}{c}{$\Delta \alpha$ $(deg)$} & \vline &
+\multicolumn{3}{c}{$\Delta \delta$ $(deg)$} & \vline & \multicolumn{3}{c}{$\Delta\Omega$
+$(deg^2)$}\\\hline
+Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
+ \hline\hline 
+$1M_{\odot}-1M_{\odot}$ & \vline &$36.4$ & \vline &$58.6$ & \vline & $0.223$ & \vline &$0.359$ & \vline & $1.45$ & \vline &$2.58$ & \vline & $1.48$ & \vline &$2.62$ & \vline & $1.88$ & \vline &$4.28$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$55.2$ & \vline &$89.8$ & \vline & $0.256$ & \vline &$0.413$ & \vline & $1.49$ & \vline &$2.67$ & \vline & $1.50$ & \vline &$2.71$ & \vline & $2.26$ & \vline &$5.38$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$64.8$ & \vline &$101$ & \vline & $0.293$ & \vline &$0.451$ & \vline & $1.54$ & \vline &$2.73$ & \vline & $1.64$ & \vline &$2.92$ & \vline & $2.10$ & \vline &$4.84$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$106$ & \vline &$170$ & \vline & $0.299$ & \vline &$0.473$ & \vline & $1.35$ & \vline &$2.36$ & \vline & $1.61$ & \vline &$2.86$ & \vline & $2.23$ & \vline &$5.04$\\\hline
 
@@
 
-\hline\hline System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta
-|\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline & $\Delta
-\delta$ $(deg)$ & \vline & $\Delta\Omega$ $(deg^2)$\\ \hline\hline
-$1M_{\odot}-1M_{\odot}$ & \vline & $4.34\times 10^{1}$ & \vline &
-$3.04\times 10^{-1}$ & \vline & $1.45\times 10^{1}$ & \vline & $6.24$
-& \vline & $5.57$\\ \hline $1.4M_{\odot}-1.4M_{\odot}$ & \vline &
-$5.32\times 10^{1}$ & \vline & $2.87\times 10^{-1}$ & \vline & $6.92$
-& \vline & $7.11$ & \vline & $8.35$\\ \hline
-$1M_{\odot}-2.5M_{\odot}$& \vline & $6.11\times 10^{1}$ & \vline &
-$3.11\times 10^{-1}$ & \vline & $2.67$ & \vline & $4.20$ & \vline &
-$7.39$\\ \hline $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.04\times
-10^{2}$ & \vline & $3.42\times 10^{-1}$ & \vline & $1.13\times 10^{1}$
-& \vline & $3.31$ & \vline & $6.27$\\ \hline\hline
-
-\end{tabular}
+\hline\hline System & \vline & \multicolumn{3}{c}{$\Delta D$ $(mpc)$} & \vline &
+\multicolumn{3}{c}{$\Delta |\cos(\iota)|$} & \vline & \multicolumn{3}{c}{$\Delta \alpha$ $(deg)$} & \vline &
+\multicolumn{3}{c}{$\Delta \delta$ $(deg)$} & \vline & \multicolumn{3}{c}{$\Delta\Omega$
+$(deg^2)$}\\\hline
+Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
+ \hline\hline
+
+$1M_{\odot}-1M_{\odot}$ & \vline &$43.4$ & \vline &$70.8$ & \vline & $0.304$ & \vline &$0.501$ & \vline & $5.56$ & \vline &$12.0$ & \vline & $6.24$ & \vline &$11.8$ & \vline & $5.57$ & \vline &$12.4$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$53.2$ & \vline &$87.0$ & \vline & $0.287$ & \vline &$0.485$ & \vline & $6.92$ & \vline &$9.90$ & \vline & $7.11$ & \vline &$10.4$ & \vline & $8.35$ & \vline &$18.6$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$61.1$ & \vline &$100$ & \vline & $0.311$ & \vline &$0.508$ & \vline & $2.67$ & \vline &$11.9$ & \vline & $4.20$ & \vline &$15.1$ & \vline & $7.39$ & \vline &$16.9$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$104$ & \vline &$161$ & \vline & $0.342$ & \vline &$0.543$ & \vline & $2.42$ & \vline &$9.00$ & \vline & $3.31$ & \vline &$6.18$ & \vline & $6.27$ & \vline &$14.1$\\
+
+\hline\hline
+
+\end{tabular}}
 \label{ciTableExtrinsic}
 \end{table*}
+
+\begin{table}[b!]
+\centering
+\caption{68\% Credible intervals versus 1-$\sigma$ Fisher matrix uncertainties for each system in the HLV configuration.}
+  \tabcolsep=0.11cm
+    {\renewcommand{\arraystretch}{1.3} 
+\begin{tabular}{lcccccccc}
+
+\hline\hline Parameter & \vline & \multicolumn{3}{c}{$\Delta\mathcal{M}_c / \mathcal{M}_c$} & \vline & \multicolumn{3}{c}{$\Delta \eta / \eta$} \\ \hline \hline
+
+Estimate & \vline & MCMC & \vline & FIM & \vline & MCMC & \vline & FIM \\ \hline
+
+$1M_{\odot}-1M_{\odot}$ & \vline &  0.00497\% & \vline & 0.00205\% & \vline & 0.645\% & \vline & 0.321\% \\
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline &  0.00890\% & \vline & 0.00384\% & \vline & 0.745\% & \vline & 0.380\% \\
+$1M_{\odot}-2.5M_{\odot}$& \vline &  0.0176\% & \vline & 0.00457\% & \vline & 1.475\% & \vline & 0.400\% \\
+$2.5M_{\odot}-2.5M_{\odot}$& \vline &  0.0245\% & \vline & 0.0114\% & \vline & 1.000\% & \vline & 0.612\% \\
+
+\hline\hline
+
+\end{tabular}}
+\label{FIMvsMCMC}
+\end{table}
 
@@
 neglecting the effects of spin, the component masses can be
-constrained to within 10\% of their true value to a confidence of
-65\%.  This value drops below 2\% for systems with an asymmetric mass
+constrained to within 8.5\% (13.4\%) of their true value to a credible level of
+65\% (90\%).  This value drops below 2\% (3.1\%) for systems with an asymmetric mass
 ratio.  These results were summarized in Table \ref{ciTableIntrinsic}.
@@
 
-%\will{You should mention the fact that our signals were chosen to be
-%  loud, but plausible here.  Make sure to note that the average
-  %uncertainties below do not necessarily reflect the average
- % uncertainty expected in the analysis of advanced detector era
- % detections.}
-
 We also reported on the ability of the two network configurations to
 constrain the luminosity distance and orbital inclination.  For
-distance, it was found that the uncertainties will fall anywhere from
-40 to 100 MPC at 65\% confidence, making the uncertainties frequently
-larger than the luminosity distances themselves.  Furthermore, it was
+distance, it was found that the uncertainties will average anywhere from
+40 to 100 MPC at 65\% credible levels, and from 60 to 170 MPC at 90\% credible levels,
+ making the uncertainties 
+larger than the luminosity distances themselves in many cases.  Furthermore, it was
 found that the cosine of the orbital inclination can be constrained to
-within 0.3 at the 65\% level, suggesting that Advanced LIGO/Virgo will not
+within 0.3 (0.5) at the 65\% (90\%) level on average,
+ suggesting that Advanced LIGO/Virgo will not
 be able to offer constraining information on GRB beaming angles in coincidence
@@
 the orbital orientation information from gravitational waves will 
-not provide astropysically relevant constrains.
-%  \will{Are you sure about this?
- % Beaming angles about 10 degrees would have $\Delta \cos i \simeq
- % 0.01$.}
+not provide astrophysically relevant constrains.
 
@@
 plus the Italian Virgo site, was able to constrain all signals within
-60 $\mathrm{deg}^2$ on the sky at the 65\% confidence interval, with
-an average 65\% confidence interval of $\sim 7$ $\mathrm{deg}^2$.
+60 $\mathrm{deg}^2$ (120 $\mathrm{deg}^2$) on the sky at the 65\% (90\%) credible level, with
+an average 65\% (90\%) credible interval of $7.4$ $\mathrm{deg}^2$ (18.6 $\mathrm{deg}^2$).
 Meanwhile, the four-detector configuration, consisting of the
 three-detector sites plus a LIGO India detector, was able to localize
-all the sky locations to within 13 $\mathrm{deg}^2$ on the sky at the 65\%
-confidence interval, with an average 65\% confidence interval of $\sim
-2$ $\mathrm{deg}^2$.
+all the sky locations to within 13 $\mathrm{deg}^2$ (34 $\mathrm{deg}^2$) on the sky at the 65\% (90\%)
+credible interval, with an average 65\% (90\%) credible interval of 
+2.2 $\mathrm{deg}^2$ $(5$ $\mathrm{deg}^2)$.
 

### 2013-07-30 CIcomputer.py

@@ -37,7 +37,7 @@ for mass in masses:
 			file = open(filename)
 			filedata = file.readlines()
 			for j in range(1,len(filedata)):
-				[cycle,logpost,logprior,iota,psi,dec,ra,dist,phi_orb,time,q,mc,logl,loglh1,logll1,loglv1,logli1,f_lower,chain] = filedata[j].split()
+				[cycle,logpost,logprior,iota,psi,dec,ra,dist,phi_orb,time,q,mc,logl,loglh1,logll1,loglv1,f_lower,chain] = filedata[j].split()
 				posteriorSamples[0][i].append(float(mc)/injectMC[l])
 				m1, m2 = m1m2fromMcq(float(mc),float(q))
 				posteriorSamples[1][i].append(float(m1)/injectM1[l])
@@ -63,6 +63,7 @@ for mass in masses:
 
 	l += 1
 	intervals = [[]for i in range(10)]
+	intervals90 = [[]for i in range(10)]
 	lowers = [[]for i in range(10)]
 	uppers = [[]for i in range(10)]
 	print 'mass Bin: ' + mass
@@ -71,16 +72,19 @@ for mass in masses:
 			if posteriorSamples[i][j] != []:
 				interval = ciInterval(posteriorSamples[i][j],65)
 				intervals[i].append(interval[0] - interval[1])
+				interval90 = ciInterval(posteriorSamples[i][j],90)
+				intervals90[i].append(interval90[0] - interval90[1])
 				lowers[i].append(interval[1])
 				uppers[i].append(interval[0])
 		print params[i] + ': mean:' + str(np.mean(intervals[i])) + ': lower:' + str(np.mean(lowers[i])) + ': upper:' + str(np.mean(uppers[i]))
 
 	for i in range(40):
 		intervals[9].append(posteriorSamples[9][i])
+		intervals90[9].append(posteriorSamples[9][i])
 	print params[9] + ': mean:' + str(np.mean(intervals[9])) + ': max:' + str(max(intervals[9])) + ': min:' + str(min(intervals[9])) 
 	string = ''
 	for i in range(5,10):
-		string += "$%.2e}$" % (np.mean(intervals[i])) +  " & \\vlin & " 
+		string += "$%.2e (%.2e)}$" % (np.mean(intervals[i])) % (np.mean(intervals90[i])) +  " & \\vlin & " 
 	string = string.replace('e','\\times 10^{')
 	string = string.replace('vlin','vline')
 	string = string.replace('+0','')

### 2013-07-30 fullSkyPlot.py

@@ -24,8 +24,7 @@ ra = []
 dec= []
 sa = []
 deg= []
-for prefix in ['2.5_2.5']:
-#for prefix in ['1_1','1.4_1.4','1_2.5','2.5_2.5']:
+for prefix in ['1_1','1.4_1.4','1_2.5','2.5_2.5']:
 	for run in range(1,41):
 		filename = prefix + '/' + str(run) + '/post/ranked_sky_pixels.dat'
 		try: 
@@ -77,8 +76,7 @@ ra = []
 dec= []
 sa = []
 deg= []
-for prefix in ['2.5_2.5']:
-#for prefix in ['1_1','1.4_1.4','1_2.5','2.5_2.5']:
+for prefix in ['1_1','1.4_1.4','1_2.5','2.5_2.5']:
 	for run in range(1,41):
 		filename = prefix + '/' + str(run) + '/post/ranked_sky_pixels.dat'
 		try: 

### 2013-08-03 doc/paper.tex
Corrected a bug in the KDE estimates that caused a decrease in measured probability near the boundaries

@@
 %\end{array}$
-\caption{\label{9dPDF} Marginalized 1D posterior probability density
-  functions taken from a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS
+\caption{\label{9dPDF} Marginalized 1D  posterior probability densities
+  of a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS
   system.  We have plotted each of the 9 parameters for our
@@
   $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in
-  Figure~\ref{1414masses}.}
+  Figure~\ref{1414masses}.  The plots here represent the Gaussian kernel density
+  estimator of each PDF.  The estimate for $q$ was 
+  computed by reflecting the highest $10\%$ of samples across the $q=1$ boundary.  
+  This was done to avoid a false decrease in estimated probability density near
+  the boundary.}
 \end{figure*}
@@
    quantitatively identical PDFs when normalized to the total
-   mass.}
+   mass.  Similarly to Fig. \ref{9dPDF}, we plot the Gaussian kernel density
+   estimates, and reflect $10\%$ of the points across the $q = 1$ and $M_1 = M_2$ boundaries (for the three equal-mass cases).}
   \label{metaMassPDFs}
@@
 \centering
-\caption{68\% Credible intervals versus 1-$\sigma$ Fisher matrix uncertainties for each system in the HLV configuration.}
+\caption{68\% Credible intervals versus 1-$\sigma$ Fisher matrix uncertainties for mass parameters in each system in the HLV configuration.}
   \tabcolsep=0.11cm

### 2013-08-03 9oneDpdfs.py

@@ -18,7 +18,7 @@ postSamp = [[] for i in range(9)]
 num = [11, 10, 8, 6,5,7,3,4,9]
 names = ["$\mathcal{M}_c$","$q$","$\phi_c$","$\\alpha$","$\delta$","$D$","$\iota$","$\psi$","$Time$"]
 xaxis = ["Chirp Mass $(M_{\odot})$","Mass Ratio","Chirp Phase $(rad.)$","Right Ascension $(rad.)$","Declination $(rad.)$","Distance $(MPC)$","Inclination $(rad.)$","Polarization $(rad.)$","Time $(msec.)$"]
-inject = [1.21877,1.,2.68833,4.662361,-0.4254096,99.15952,2.353028,2.153679,0.]
+inject = [1.21877,.999,2.68833,4.662361,-0.4254096,99.15952,2.353028,2.153679,0.]
 ticks = [[1.2183,1.2185,1.2187,1.2189],
          [0.7,0.75,0.8,0.85,0.9,0.95,1],
 		 [0,1,2,3,4,5,6],
@@ -39,6 +39,19 @@ for i in range(1,len(filedata)):
 			if j == 8:
 				postSamp[j][i-1] = (postSamp[j][i-1] - 894429279.)*1000
 
+for j in range(9):
+	postSamp[j].sort()
+
+#this part reflects the data across boundares for the purposes of the KDE.
+#for q, it reflects across the q=1 boundary, while it wraps data around for the 
+# phi_0 and psi boundaries
+for i in range(1,1200):  
+	postSamp[1].append(2-postSamp[1][-2*i + 1])  
+for i in range(1,2000):  
+	postSamp[2].insert(0, -(2*pi - postSamp[2][-2*i + 1]))
+	postSamp[2].append(2*pi + postSamp[2][2*i - 1 ]) 
+	postSamp[7].insert(0, -(pi - postSamp[7][-2*i + 1]))
+	postSamp[7].append(pi + postSamp[7][2*i - 1 ])
 
 KDEdataX = []
 KDEdataY = []
@@ -46,8 +59,17 @@ KDEdataY = []
 suptitle("Example 1D Posterior Probability Densities for $1.4M_{\odot}/1.4M_{\odot}$ System", fontsize=26)
 for i in range(9):
 		KDE = scipy.stats.gaussian_kde(postSamp[i])
[…]

### 2013-08-03 massPDFs.py

@@ -32,7 +32,7 @@ for number in massBins:
 		M  = []
 		k = 0
 
-		for i in range(0,len(mcdata),20):
+		for i in range(0,len(mcdata),10):
 			q.append(float(qdata[i].rstrip()))
 			mc.append(float(mcdata[i].rstrip())/chirpMasses[Bin])
 			m1Temp, m2Temp = m1m2fromMcq(mc[k]*chirpMasses[Bin],q[k])
@@ -40,7 +40,28 @@ for number in massBins:
 			m2.append(m2Temp / indivMasses[Bin][0])
 			M.append((m1Temp + m2Temp)/sum(indivMasses[Bin]))
 			k += 1
-		print min(M)
+
+		m1.sort()
+		m2.sort()
+		q.sort()
+		M.sort()
+
+		m1Min = min(m1)
+		m1Max = max(m1)
+		m2Min = min(m2)
+		m2Max = max(m2)
+		mMin = min(M)
+		mMax = max(M)
+		qMin = min(q)
+		qMax = max(q)
+
+		if not number == '125':
+			for i in range(1,330):  
+				q.append(2-q[-2*i + 1])  
+				m2.append(2-m2[-2*i + 1])  
+				m1.insert(0,2-m1[2*i - 1])  
+				#M.insert(0,2-M[2*i - 1])  
+
 
 		m1KDE = scipy.stats.gaussian_kde(m1)
 		m2KDE = scipy.stats.gaussian_kde(m2)
@@ -59,8 +80,6 @@ for number in massBins:
 		Xq  = []
 		Yq  = []
 
-		m1Min = min(m1)
-		m1Max = max(m1)
 		dx = (m1Max- m1Min) / 1000.
 		n = m1Min
 
@@ -69,8 +88,6 @@ for number in massBins:
 			Ym1.append(float(m1KDE(n)))
 			n += dx
 
-		m2Min = min(m2)
-		m2Max = max(m2)
 		dx = (m2Max - m2Min) / 1000.
 		n = m2Min
 
@@ -113,8 +130,6 @@ for number in massBins:
 #		ax2.grid(True)
 #		xlabel('Chirp Masses ($M_{\odot}/M_{\odot}^{inject}$)', fontsize=18)
 
-		mMin = min(M)
-		mMax = max(M)
 		dx = (mMax - mMin) / 1000.
 		n = mMin
 
@@ -132,8 +147,6 @@ for number in massBins:
[…]

### 2013-08-16 doc/paper.tex
adding new pdfs

@@
 
-In Table \ref{ciTableIntrinsic}, we list the 65\% fractional credible
+In Table \ref{ciTableIntrinsic}, we list the 65\% and 90\% fractional credible
 intervals for the mass parameters.  We find that the component masses
@@
 
-In Table \ref{ciTableExtrinsic}, we list the averaged 65\% confidence
+In Table \ref{ciTableExtrinsic}, we list the averaged 65\% and 90\% credible
 intervals for distance and inclination.  Notice that the uncertainties
@@
   four-detector HLVI configuration over the three-detector HLV
-  configuration.  Note that the solid-angle sky-location confidence
+  configuration.  Note that the solid-angle sky-location credible
   intervals, $\Delta\Omega$, are calculated directly on the 2D sphere,

### 2013-08-16 doc/paper.tex
testbranch2

@@
 
-In this study, we have also neglected the effects of spin in the
-parameter space, electing to focus on the absolute basic parameters
-that will be measured routinely in the Advanced Detector era.  Given
+%In this study, we have also neglected the effects of spin in the
+%parameter space, electing to focus on the absolute basic parameters
+%that will be measured routinely in the Advanced Detector era.  Given
 the high degree of coupling between the spin and mass of objects

### 2013-08-22 doc/paper.tex
quick test
quick test 2
added most of the comments from the CBC call

--- 2013-08-16 doc/paper.tex
@@
 on approximation techniques such as the Fisher Matrix.  Here we report the
-statistical uncertainties that will be achievable using
+statistical uncertainties that will be achievable for optimal detection candidates
+ ($\text{SNR}=20$) using
 the full parameter estimation machinery developed by the LIGO/Virgo
@@
  We find the recovery of the individual masses to be
-fractionally within 8.5\% (13.4\%) at the 65\% (90\%) credible intervals for equal-mass
-systems, and within 2\% (3.1\%) for unequal-mass systems.  We also find that the Advanced
-LIGO/Virgo network will constrain the locations of binary neutron star mergers to an average
- uncertainty of $7.4$ $\mathrm{deg}^2$ (18.6 $\mathrm{deg}^2$) on the sky.
-This region is improved to  2.2 $\mathrm{deg}^2$ $(5$ $\mathrm{deg}^2)$ with the addition of the proposed LIGO India detector to the network.
+fractionally within 9\% (15\%) at the 68\% (95\%) credible intervals for equal-mass
+systems, and within 1.9\% (3.7\%) for unequal-mass systems.  We also find that the Advanced
+LIGO/Virgo network will constrain the locations of binary neutron star mergers to a median
+ uncertainty of $5.1$ $\mathrm{deg}^2$ (13.5 $\mathrm{deg}^2$) on the sky.
+This region is improved to  2.3 $\mathrm{deg}^2$ $(6$ $\mathrm{deg}^2)$ with the addition of the proposed LIGO India detector to the network.
 We also report the
@@
 eventually be used in the Advanced LIGO/Virgo era, our results
- give estimates of the realistic capabilities of
+ give realistic estimates of the capabilities of
 advanced ground-based detectors to characterize BNS systems.  Until
@@
 limitations and flaws of the Fisher Information Matrix, there has been
-no study which investigates the BNS parameter estimation capabilities
+relatively few studies which investigate the BNS parameter estimation capabilities
 of Advanced LIGO/Virgo using the techniques that will eventually be
@@
 parameters (particularly the masses) measurable in gravitational-wave
-detectors.
+detectors.  While previous studies have employed MCMC techniques for specific
+parameters,  \citep{Nissanke2011,Nissanke2013,Veitch2012}, none have considered 
+the full range of parameters, in particular the neutron star masses.
 
@@
 \item uniform in volume, which implies a luminosity distance prior of
-  $p(D)dD = D^2 dD$,
+  $p(D)dD \propto D^2 dD$,
 \item uniform in coalescence time over the segment of data being
@@
 We use a frequency-domain waveform accurate up to $3.5$ post-Newtonian
-(pN) order in phase and 3 pN order in amplitude.  We restrict
+(pN) order in phase and 3 pN order in amplitude of the lowest ($l=m=2$) spatial mode.
+  We restrict
 ourselves to quasi-circular, non-spinning waveforms as a simplifying
@@
 
-We consier the mass parameters ($\chmass,q$) and the phasing
+We consider the mass parameters ($\chmass,q$) and the phasing
 parameters, ($\phi_0,t_c$), to be the intrinsic parameters of the
@@
 was selected to provide a network SNR of $\rho_{\text{network}}=20$
-for each source.  While unphysical from an astrophysics perspective
-(binary sources are expected to be distributed uniformly in comoving volume), this
+for each source in each network configuration. 
+ While unphysical from an astrophysics perspective
+(binary sources are expected to be distributed uniformly in co-moving volume), this
 choice allows us to explore the parameter estimation in the context of
@@
 advanced era detectors and suppress any effects of detector noise by
-picking $n(t) \equiv 0$.
+picking $n(t) \equiv 0$.  It can be shown that this ``zero-noise'' injection
+represents the geometric mean of the same experiment over many different
+noise realizations drawn from the same PSD.  See \cite{Nissanke2010}, c.f. equation
+53.
+
 Consequently, what we recover with the MCMC could be interpreted as
@@
 PSD and that the signal is sufficiently powerful for the linearized-signal
-approximation \citep{Vallisneri} to be valid.
+approximation \citep{Vallisneri} to be valid.  By selecting a source population
+with an artificial distribution in SNR, we ensure that the ``zero-noise'' as
+average uncertainty
 
@@
 \centering \includegraphics[trim=7cm 0cm 0cm 0cm,
-  clip=true,scale=0.55]{9dpdf}
+  clip=true,scale=0.58]{9dpdf}
 %\begin{array}{ccc} 
@@
 \begin{figure*}[ht!]
-  \centering \includegraphics[trim=2cm 0cm 2cm 0cm,
-    clip=false,scale=0.7]{newMasses.pdf}
+  \centering \includegraphics[trim=3cm 0cm 2cm 0cm,
+    clip=false,scale=0.75]{newMasses.pdf}
  \caption{Mass PDFs for the four BNS systems, averaged over each of
@@
 
-In Table \ref{ciTableIntrinsic}, we list the 65\% and 90\% fractional credible
+In Table \ref{ciTableIntrinsic}, we list the 68\% and 95\% credible
 intervals for the mass parameters.  We find that the component masses
-for equal mass systems can be isolated to between 6\% and 9\%
-fractional uncertainty at the 65\% credible interval.  This value
-drops to less than 2\% for the components of the unequal mass systems.
+for equal mass systems can be isolated to between 6.4\% and 9\% (10.3\% and 15\%)
+fractional uncertainty at the 68\% (95\%) credible interval.  This value
+drops to less than 1.9\% (3.7\%) for the components of the unequal mass systems.
 Again, this neglects the effects of spin which can substantially
@@
 inclination will provide an additional constraint on the D-$\iota$
-space, vastly improving the luminosity distance recovery quoted here.
-
-In Table \ref{ciTableExtrinsic}, we list the averaged 65\% and 90\% credible
+space, vastly improving the luminosity distance recovery quoted here.  These results
+qualitatively agree with those of \cite{Nissanke2011}, who studied in detail
+MCMC estimation of $D$-$\iota$ measurements from gravitational-wave detectors with 
+coincident GRB detections.
+
+In Table \ref{ciTableExtrinsic}, we list the averaged 68\% and 95\% credible
 intervals for distance and inclination.  Notice that the uncertainties
@@
  all of the signals are recovered with
-a solid angle uncertainty of less than 60 $\mathrm{deg}^2$ (120 $\mathrm{deg}^2$)
-at the 65\% (90\%) credible interval, while the HLVI configuration 
-recovers all signals to less than 13 $\mathrm{deg}^2$ (34 $\mathrm{deg}^2$).
-The mean quantitative results for the two network configurations show a similar
- benefit with the addition of LIGO India, and are again reported in
-  Table \ref{ciTableExtrinsic}.
+a solid angle uncertainty of less than 64 $\mathrm{deg}^2$ (136 $\mathrm{deg}^2$)
+at the 68\% (95\%) credible interval, while the HLVI configuration 
+recovers all signals to less than 14 $\mathrm{deg}^2$ (45 $\mathrm{deg}^2$).
+The median quantitative results for the two network configurations show a similar
+ benefit with the addition of LIGO India, and are again reported in Table \ref{ciTableExtrinsic}.
+
+Two previous studies have considered the increase in sensitivity from the addition of the LIGO India site. \carl{[INCOMPLETE]}
 
@@
    detector configuration.  Each region represents a single injection,
-   with the colored central region representing the 65\% uncertainty
-   region on the sphere, and the gray shade representing the 90\%
+   with the colored central region representing the 68\% uncertainty
+   region on the sphere, and the gray shade representing the 95\%
    uncertainty region.  The color scheme indicates the total solid
-   angle size of the 65\% region.  Note the similar shape of the
+   angle size of the 68\% region.  Note the similar shape of the
    uncertainty regions at particular points; this is due to the
@@
 reduce the full parameter space to credible intervals about single
-marginalized parameters..  To that end, we state the averaged 65\% and 90\% credible
+marginalized parameters..  To that end, we state the averaged 68\% and 95\% credible
 intervals about the single parameters for each of the three
@@
 
-In Table~\ref{ciTableIntrinsic}, we list the mean 65\% and 90\% credible
+In Table~\ref{ciTableIntrinsic}, we list the mean 68\% and 95\% credible
 intervals recovered for the four mass configurations in both network
@@
 \centering
-\caption{Mean 65\% and 90\% credible intervals for intrinsic parameters for
+\caption{Median 68\% and 95\% credible intervals for intrinsic parameters for
   each of the four systems considered.  We report the credible
@@
 
-\\HLVI\\
+\\ HLV\\
 
@@
 \multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
-Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
+Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
 \hline\hline
 
-$1M_{\odot}-1M_{\odot}$ & \vline &$0.00465\%$ & \vline &$0.00863\%$ & \vline & $6.78\%$ & \vline &$10.6\%$ & \vline & $6.06\%$ & \vline &$9.28\%$ & \vline & $0.362\%$ & \vline &$0.633\%$ & \vline & $0.117$ & \vline &$0.178$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00827\%$ & \vline &$0.0154\%$ & \vline & $7.27\%$ & \vline &$11.4\%$ & \vline & $6.45\%$ & \vline &$9.90\%$ & \vline & $0.410\%$ & \vline &$0.724\%$ & \vline & $0.124$ & \vline &$0.189$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0165\%$ & \vline &$0.0294\%$ & \vline & $1.74\%$ & \vline &$3.10\%$ & \vline & $1.49\%$ & \vline &$2.67\%$ & \vline & $0.815\%$ & \vline &$1.46\%$ & \vline & $0.0129$ & \vline &$0.0231$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.0229\%$ & \vline &$0.0424\%$ & \vline & $8.52\%$ & \vline &$13.3\%$ & \vline & $7.42\%$ & \vline &$11.4\%$ & \vline & $0.551\%$ & \vline &$0.958\%$ & \vline & $0.141$ & \vline &$0.215$\\
+$1M_{\odot}-1M_{\odot}$ & \vline &$0.00497\%$ & \vline &$0.0104\%$ & \vline & $7.17\%$ & \vline &$11.9\%$ & \vline & $6.39\%$ & \vline &$10.3\%$ & \vline & $0.643\%$ & \vline &$1.25\%$ & \vline & $0.123$ & \vline &$0.197$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00883\%$ & \vline &$0.0188\%$ & \vline & $7.77\%$ & \vline &$13\%$ & \vline & $6.87\%$ & \vline &$11.1\%$ & \vline & $0.746\%$ & \vline &$1.47\%$ & \vline & $0.132$ & \vline &$0.212$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0176\%$ & \vline &$0.0355\%$ & \vline & $1.86\%$ & \vline &$3.74\%$ & \vline & $1.59\%$ & \vline &$3.23\%$ & \vline & $1.48\%$ & \vline &$2.99\%$ & \vline & $0.0138$ & \vline &$0.028$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.0246\%$ & \vline &$0.0522\%$ & \vline & $9.02\%$ & \vline &$15\%$ & \vline & $7.82\%$ & \vline &$12.6\%$ & \vline & $1.01\%$ & \vline &$1.94\%$ & \vline & $0.149$ & \vline &$0.239$\\
 
@@
 
-\\ HLV\\
+\\HLVI\\
 
@@
 \multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
-Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
+Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
 \hline\hline
 
-$1M_{\odot}-1M_{\odot}$ & \vline &$0.00466\%$ & \vline &$0.00865\%$ & \vline & $6.82\%$ & \vline &$10.5\%$ & \vline & $6.09\%$ & \vline &$9.25\%$ & \vline & $0.364\%$ & \vline &$0.633\%$ & \vline & $0.117$ & \vline &$0.177$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00831\%$ & \vline &$0.0155\%$ & \vline & $7.35\%$ & \vline &$11.5\%$ & \vline & $6.51\%$ & \vline &$10.0\%$ & \vline & $0.418\%$ & \vline &$0.743\%$ & \vline & $0.125$ & \vline &$0.191$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0165\%$ & \vline &$0.0295\%$ & \vline & $1.75\%$ & \vline &$3.11\%$ & \vline & $1.50\%$ & \vline &$2.67\%$ & \vline & $0.819\%$ & \vline &$1.46\%$ & \vline & $0.0130$ & \vline &$0.0232$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.023\%$ & \vline &$0.0428\%$ & \vline & $8.53\%$ & \vline &$13.4\%$ & \vline & $7.42\%$ & \vline &$11.4\%$ & \vline & $0.552\%$ & \vline &$0.968\%$ & \vline & $0.141$ & \vline &$0.216$\\
+$1M_{\odot}-1M_{\odot}$ & \vline &$0.00497\%$ & \vline &$0.0106\%$ & \vline & $7.15\%$ & \vline &$11.9\%$ & \vline & $6.38\%$ & \vline &$10.4\%$ & \vline & $0.646\%$ & \vline &$1.27\%$ & \vline & $0.123$ & \vline &$0.198$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00884\%$ & \vline &$0.0188\%$ & \vline & $7.67\%$ & \vline &$12.8\%$ & \vline & $6.79\%$ & \vline &$11.1\%$ & \vline & $0.733\%$ & \vline &$1.46\%$ & \vline & $0.13$ & \vline &$0.211$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0176\%$ & \vline &$0.0352\%$ & \vline & $1.85\%$ & \vline &$3.72\%$ & \vline & $1.59\%$ & \vline &$3.2\%$ & \vline & $1.47\%$ & \vline &$2.96\%$ & \vline & $0.0137$ & \vline &$0.0277$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.0243\%$ & \vline &$0.0515\%$ & \vline & $9.03\%$ & \vline &$14.9\%$ & \vline & $7.84\%$ & \vline &$12.6\%$ & \vline & $0.998\%$ & \vline &$1.92\%$ & \vline & $0.149$ & \vline &$0.238$\\
 
@@
 \centering
-\caption{Mean 65\% and 90\% credible intervals of extrinsic parameters for
+\caption{Median 68\% and 95\% credible intervals of extrinsic parameters for
   each of the four systems considered.  As expected, there exists a
@@
 
+\\ HLV\\
+
+\hline\hline System & \vline & \multicolumn{3}{c}{$\Delta D$ $(mpc)$} & \vline &
+\multicolumn{3}{c}{$\Delta |\cos(\iota)|$} & \vline & \multicolumn{3}{c}{$\Delta \alpha$ $(deg)$} & \vline &
+\multicolumn{3}{c}{$\Delta \delta$ $(deg)$} & \vline & \multicolumn{3}{c}{$\Delta\Omega$
+$(deg^2)$}\\\hline
+Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
+ \hline\hline
+
+$1M_{\odot}-1M_{\odot}$ & \vline &$49.4$ & \vline &$89.9$ & \vline & $0.323$ & \vline &$0.611$ & \vline & $1.73$ & \vline &$4.09$ & \vline & $2.51$ & \vline &$5.52$ & \vline & $5.12$ & \vline &$13.5$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$61.4$ & \vline &$107$ & \vline & $0.314$ & \vline &$0.588$ & \vline & $2.63$ & \vline &$5.42$ & \vline & $2.53$ & \vline &$5.27$ & \vline & $4.12$ & \vline &$11.2$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$68.8$ & \vline &$127$ & \vline & $0.31$ & \vline &$0.549$ & \vline & $2.41$ & \vline &$4.6$ & \vline & $2.77$ & \vline &$6.2$ & \vline & $4.37$ & \vline &$12.1$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$116$ & \vline &$198$ & \vline & $0.349$ & \vline &$0.613$ & \vline & $1.75$ & \vline &$4.51$ & \vline & $2.42$ & \vline &$5.01$ & \vline & $4.62$ & \vline &$12$\\
+
+\hline\hline
+
 \\HLVI\\ 
@@
 $(deg^2)$}\\\hline
-Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
+Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
  \hline\hline 
-$1M_{\odot}-1M_{\odot}$ & \vline &$36.4$ & \vline &$58.6$ & \vline & $0.223$ & \vline &$0.359$ & \vline & $1.45$ & \vline &$2.58$ & \vline & $1.48$ & \vline &$2.62$ & \vline & $1.88$ & \vline &$4.28$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$55.2$ & \vline &$89.8$ & \vline & $0.256$ & \vline &$0.413$ & \vline & $1.49$ & \vline &$2.67$ & \vline & $1.50$ & \vline &$2.71$ & \vline & $2.26$ & \vline &$5.38$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$64.8$ & \vline &$101$ & \vline & $0.293$ & \vline &$0.451$ & \vline & $1.54$ & \vline &$2.73$ & \vline & $1.64$ & \vline &$2.92$ & \vline & $2.10$ & \vline &$4.84$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$106$ & \vline &$170$ & \vline & $0.299$ & \vline &$0.473$ & \vline & $1.35$ & \vline &$2.36$ & \vline & $1.61$ & \vline &$2.86$ & \vline & $2.23$ & \vline &$5.04$\\\hline
-
-\\ HLV\\
-
-\hline\hline System & \vline & \multicolumn{3}{c}{$\Delta D$ $(mpc)$} & \vline &
-\multicolumn{3}{c}{$\Delta |\cos(\iota)|$} & \vline & \multicolumn{3}{c}{$\Delta \alpha$ $(deg)$} & \vline &
-\multicolumn{3}{c}{$\Delta \delta$ $(deg)$} & \vline & \multicolumn{3}{c}{$\Delta\Omega$
-$(deg^2)$}\\\hline
-Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
- \hline\hline
-
-$1M_{\odot}-1M_{\odot}$ & \vline &$43.4$ & \vline &$70.8$ & \vline & $0.304$ & \vline &$0.501$ & \vline & $5.56$ & \vline &$12.0$ & \vline & $6.24$ & \vline &$11.8$ & \vline & $5.57$ & \vline &$12.4$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$53.2$ & \vline &$87.0$ & \vline & $0.287$ & \vline &$0.485$ & \vline & $6.92$ & \vline &$9.90$ & \vline & $7.11$ & \vline &$10.4$ & \vline & $8.35$ & \vline &$18.6$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$61.1$ & \vline &$100$ & \vline & $0.311$ & \vline &$0.508$ & \vline & $2.67$ & \vline &$11.9$ & \vline & $4.20$ & \vline &$15.1$ & \vline & $7.39$ & \vline &$16.9$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$104$ & \vline &$161$ & \vline & $0.342$ & \vline &$0.543$ & \vline & $2.42$ & \vline &$9.00$ & \vline & $3.31$ & \vline &$6.18$ & \vline & $6.27$ & \vline &$14.1$\\
-
-\hline\hline
+$1M_{\odot}-1M_{\odot}$ & \vline &$42.7$ & \vline &$76.2$ & \vline & $0.267$ & \vline &$0.455$ & \vline & $1.13$ & \vline &$2.25$ & \vline & $1.48$ & \vline &$3.01$ & \vline & $1.87$ & \vline &$5.37$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$66.6$ & \vline &$121$ & \vline & $0.285$ & \vline &$0.509$ & \vline & $1.27$ & \vline &$2.48$ & \vline & $1.49$ & \vline &$3.01$ & \vline & $2$ & \vline &$5.12$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$73.7$ & \vline &$130$ & \vline & $0.297$ & \vline &$0.499$ & \vline & $1.29$ & \vline &$2.42$ & \vline & $1.42$ & \vline &$2.89$ & \vline & $1.75$ & \vline &$4.87$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$120$ & \vline &$213$ & \vline & $0.301$ & \vline &$0.517$ & \vline & $1.18$ & \vline &$2.34$ & \vline & $1.55$ & \vline &$3.14$ & \vline & $2.25$ & \vline &$5.99$\\ \hline
 
@@
 neglecting the effects of spin, the component masses can be
-constrained to within 8.5\% (13.4\%) of their true value to a credible level of
-65\% (90\%).  This value drops below 2\% (3.1\%) for systems with an asymmetric mass
+constrained to within 9\% (15\%) of their true value to a credible level of
+68\% (95\%).  This value drops below 1.9\% (3.7\%) for systems with an asymmetric mass
 ratio.  These results were summarized in Table \ref{ciTableIntrinsic}.
@@
 distance, it was found that the uncertainties will average anywhere from
-40 to 100 MPC at 65\% credible levels, and from 60 to 170 MPC at 90\% credible levels,
+43 to 120 MPC at 68\% credible levels, and from 76 to 213 MPC at 96\% credible levels,
  making the uncertainties 
@@
 found that the cosine of the orbital inclination can be constrained to
-within 0.3 (0.5) at the 65\% (90\%) level on average,
+within 0.35 (0.61) at the 68\% (95\%) level on average,
  suggesting that Advanced LIGO/Virgo will not
@@
 plus the Italian Virgo site, was able to constrain all signals within
-60 $\mathrm{deg}^2$ (120 $\mathrm{deg}^2$) on the sky at the 65\% (90\%) credible level, with
-an average 65\% (90\%) credible interval of $7.4$ $\mathrm{deg}^2$ (18.6 $\mathrm{deg}^2$).
+64 $\mathrm{deg}^2$ (136 $\mathrm{deg}^2$) on the sky at the 68\% (95\%) 
+credible level, with
+an average median 68\% (95\%) credible interval of 
+$4.6$ $\mathrm{deg}^2$ (12.2 $\mathrm{deg}^2$).
 Meanwhile, the four-detector configuration, consisting of the
 three-detector sites plus a LIGO India detector, was able to localize
-all the sky locations to within 13 $\mathrm{deg}^2$ (34 $\mathrm{deg}^2$) on the sky at the 65\% (90\%)
-credible interval, with an average 65\% (90\%) credible interval of 
-2.2 $\mathrm{deg}^2$ $(5$ $\mathrm{deg}^2)$.
+all the sky locations to within 14 $\mathrm{deg}^2$ (45 $\mathrm{deg}^2$) on the sky at the 68\% (95\%)
+credible interval, with an average median 68\% (95\%) credible interval of 
+2 $\mathrm{deg}^2$ $(5.3$ $\mathrm{deg}^2)$.
 

### 2013-08-22 9oneDpdfs.py

@@ -1,4 +1,7 @@
 import scipy.stats
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+rc('text', usetex=True)
 from matplotlib import pyplot as plt,cm as mpl_cm,lines as mpl_lines,colorbar
 
 def m1m2fromMcq(Mc,q):
@@ -16,7 +19,8 @@ file.close()
 
 postSamp = [[] for i in range(9)]
 num = [11, 10, 8, 6,5,7,3,4,9]
-names = ["$\mathcal{M}_c$","$q$","$\phi_c$","$\\alpha$","$\delta$","$D$","$\iota$","$\psi$","$Time$"]
+names = ["$\mathcal{M}_c$","$q$","$\phi_c$","$\\alpha$","$\delta$","$D$","$\iota$","$\psi$",
+'Time']
 xaxis = ["Chirp Mass $(M_{\odot})$","Mass Ratio","Chirp Phase $(rad.)$","Right Ascension $(rad.)$","Declination $(rad.)$","Distance $(MPC)$","Inclination $(rad.)$","Polarization $(rad.)$","Time $(msec.)$"]
 inject = [1.21877,.999,2.68833,4.662361,-0.4254096,99.15952,2.353028,2.153679,0.]
 ticks = [[1.2183,1.2185,1.2187,1.2189],
@@ -86,7 +90,11 @@ for i in range(9):
 		ax1.grid("on")
 		ax1.set_xticks(ticks[i])
 		axvline(inject[i],color='red', lw=3,linestyle="--")
-		title(names[i], fontsize = 22)
+		if i==8:
+			title(names[i], fontsize = 18)
+		else:
+			title(names[i], fontsize = 22)
+			
 		KDEdataX = []
 		KDEdataY = []
 

### 2013-08-22 massPDFs.py

@@ -1,4 +1,7 @@
 import scipy.stats
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+rc('text', usetex=True)
 from matplotlib import pyplot as plt,cm as mpl_cm,lines as mpl_lines,colorbar
 
 def m1m2fromMcq(Mc,q):
@@ -110,7 +113,7 @@ for number in massBins:
 		lb4 = Rectangle((0, 0), 1, 1, fc='green')
 		l2=legend([lb1,lb2,lb3,lb4],["$1M_{\odot} - 1M_{\odot}$","$1.4M_{\odot} - 1.4M_{\odot}$","$1M_{\odot} - 2.5M_{\odot}$","$2.5M_{\odot} - 2.5M_{\odot}$"], loc='upper left', title="Neutron Star Masses")
 		gca().add_artist(l1)
-		xlabel('Component Masses ($M_{\odot}/M_{\odot}^{inject}$)', fontsize=18)
+		xlabel('Component Masses ($M/M_{inject}$)', fontsize=18)
 		title('Mass Posterior PDFs', fontsize=26)
 
 #		mcMin = min(mc)
@@ -144,7 +147,7 @@ for number in massBins:
 		axvline(1,0,max(Ym),color='black', lw=3)
 		ax3.grid(True)
 		ylabel('Probability Densities',fontsize=22)
-		xlabel('Total Mass ($M_{\odot}/M_{\odot}^{inject}$)', fontsize=18)
+		xlabel('Total Mass ($M/M_{inject}$)', fontsize=18)
 
 
 		dx = (qMax - qMin) / 1000.

### 2013-09-04 doc/paper.tex
quick git test
ALMOST fixed everything

@@
 
-Two previous studies have considered the increase in sensitivity from the addition of the LIGO India site. \carl{[INCOMPLETE]}
+Two previous studies have considered the increase in sensitivity from the addition of the 
+LIGO India site. \cite{Veitch2012} and \cite{Nissanke2013} studied the decrease in
+sky-location uncertainties obtained by the inclusion of the LIGO India site
+into the advanced detector network.  Both studies employed an MCMC sampling technique 
+(Veitch et al.\ via \texttt{LALInference}, Nissanke et al. via a modified version of CosmoMC),
+to determine the average parameter estimation uncertainties for a realistic distribution
+of sources in co-moving volume.  As the current study is interested in the uncertainties
+of optimal sources at $\text{SNR}_{network}=20$, ignoring the effects of less viable 
+detection candidates, it is instructive to compare the $95\%$ credible intervals
+between the three studies.  The cumulative distributions of sky-area uncertainties
+for both network configurations in each study are plotted in Fig. \ref{compSky}.
 
@@
 
+\begin{figure}[ht!]
+  \centering \includegraphics[angle=0,scale=0.58, trim=0.5cm 1cm 0cm 0cm]{comparitiveSkyAreas.pdf}
+
+ \caption{The cumulative fraction of sources found within $deg^2$ at the 95\% credible
+ interval.  This plot contains results from three separate studies: the current study, in
+ which optimal detection candidates are considered ($SNR_{network}=20$), 
+ \cite{Veitch2012}, which employs several \texttt{LALInference} samplers (including the
+ MCMC sampler used here) on an source population evenly distributed in co-moving 
+ volume, and \cite{Nissanke2013}, which employs a separate MCMC code on a
+ realistic source population.  The optimal detection candidates are constrained
+ to substantially smaller solid angles on the sky, as is expected for such ``gold-plated''
+ events.}
+ \label{compSky}
+\end{figure}
+
 \subsection{Varied Noise Realizations}
@@
    PDF for five different Gaussian realizations of the Advanced LIGO
-   noise curve.  Each PDF represents the recovery of the same
+   noise curve.  Each blue-dashed PDF represents the recovery of the same
    $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked

### 2013-09-04 doc/paper.tex
ALMOST THERE

--- 2013-08-22 doc/paper.tex
@@
 parameters,  \citep{Nissanke2011,Nissanke2013,Veitch2012}, none have considered 
-the full range of parameters, in particular the neutron star masses.
+the full range of parameters measurable for an optimal detection candidate.
 
@@
 noise realizations drawn from the same PSD.  See \cite{Nissanke2010}, c.f. equation
-53.
+(53), for a proof that the geometric mean of the posteriors over many realizations of the 
+noise is identical to the $n(t) = 0$ selection, given a sufficiently loud gravitational-wave
+event.
 
@@
 PSD and that the signal is sufficiently powerful for the linearized-signal
-approximation \citep{Vallisneri} to be valid.  By selecting a source population
-with an artificial distribution in SNR, we ensure that the ``zero-noise'' as
-average uncertainty
+approximation to be valid\footnote{This can also be seen in \cite{Vallisneri}, equation (74).
+  By expanding the posterior variance as a series in $1/\text{SNR}$, it can be seen that the 
+  $n(t) = 0$ posterior variance is identical to the frequentist average 
+  over noise realizations of the posterior variance up to third order in $1/\text{SNR}$. }.
+    By selecting a source population with an artificial distribution in SNR, we ensure that the
+     ``zero-noise'' as average uncertainty approximation is valid.
 
@@
 are substantially fewer regions in which only two detectors see a
-sufficiently strong signal.  See \cite{Veitch2012} for a more detailed
-comparison of the sky-localization benefits of the HLVI configuration
-versus the three-detector network.  For the HLV configuration, we find that
+sufficiently strong signal.  For the HLV configuration, we find that
  all of the signals are recovered with
@@
 
-Two previous studies have considered the increase in sensitivity from the addition of the LIGO India site. \carl{[INCOMPLETE]}
+Previous studies have considered the increase in sensitivity from the addition of the 
+LIGO India site.  \cite{Nissanke2013} studied the decrease in
+sky-location uncertainties obtained by the inclusion of the LIGO India site
+into the advanced detector network.  Their study also employed an MCMC sampling technique 
+ (a modified version of CosmoMC),
+to determine the average parameter estimation uncertainties for a realistic distribution
+of sources.  As the current study is interested in the uncertainties
+of optimal sources at $\text{SNR}_{network}=20$, ignoring the effects of less viable 
+detection candidates, it is instructive to compare the $95\%$ credible intervals
+between the two studies.  The cumulative distributions of sky-area uncertainties
+for both network configurations in each study are plotted in Fig. \ref{compSky}.
+
+The difference in uncertainties between the two studies is illustrative.  \cite{Nissanke2013}
+considered a realistic distribution of sources motivated by a local galaxy catalogue for
+ sources where $D\leq 200\text{Mpc}$, and homogeneously distributed in co-moving
+ volume for sources where $D > 200\text{Mpc}$.  These were then limited to those signals
+ where $\text{SNR}_{network} \geq 8.5$ (the threshold for detection candidates in the
+ current LIGO/Virgo software framework) for the MCMC parameter estimation.
+   The current study considers a source
+ population isotropically distributed on the sky, but at distances such that each signal
+ represents an optimal case for parameter estimation.   Fig. \ref{compSky} compares
+ the sky-area uncertainties that will be available to those considering ``good 
+ gravitational-wave events'' (e.g. precision source isolation), and the 
+ uncertainties that one can gather by considering all gravitational-wave candidates with 
+ $\text{SNR}_{network}\geq 8.5$ (e.g. electromagnetic follow-up).  As expected, both source
+ populations show a dramatic decrease in parameter estimation uncertainties with the
+ addition of the LIGO India site to the advanced detector network.  This holds true even when
+ considering the increased number of nominal sources available to the HLVI network 
+ configuration in the Nissanke population, where the extension of the network detection 
+ horizon due to the Indian detector increases the number of sources to 130, versus 90 in 
+ the HLV configuration.
 
@@
 
+\begin{figure}[ht!]
+  \centering \includegraphics[angle=0,scale=0.58, trim=0.5cm 1cm 0cm 0cm]{comparitiveSkyAreas.pdf}
+
+ \caption{The cumulative fraction of sources found within $deg^2$ at the 95\% credible
+ interval.  This plot contains results from two separate studies: the current study, in
+ which optimal detection candidates are considered ($\rho_{network}=20$), 
+and \cite{Nissanke2013}, which employs a separate MCMC code on a
+ realistic source population (where $\rho_{trigger} \geq 8.5$ is employed to determine
+ parameter estimation sources).  The optimal detection candidates are constrained
+ to substantially smaller solid angles on the sky, as is expected for such ``gold-plated''
+ events, while both studies show a substantial decrease in sky-area uncertainties for the HLVI configuration.}
+ \label{compSky}
+\end{figure}
+
 \subsection{Varied Noise Realizations}
@@
   where a signal is sufficiently loud that the posterior is linear in the parameters 
-  $\thpara$.
+  $\thpara$.  Meanwhile, the posterior variances, averaged over many noise realizations, 
+  are identical to the $n(t) = 0$ variance, up to third order in $1/\text{SNR}$.
 
@@
 the estimates of the Fisher matrix, with the Fisher matrix underestimating the 
-fractional uncertainties by as much as a factor of three.  See Table~\ref{FIMvsMCMC}.
+fractional uncertainties by as much as a factor of three.  See Table~\ref{FIMvsMCMC}.  This 
+result agrees with the conventional wisdom surrounding the Fisher Matrix accuracy,
+as well as results where the Fisher Matrix is computed to higher order \citep{Vitale2010}
    This disagreement, while 

### 2013-09-05 doc/paper.tex
finished final edits

@@
  will provide the first insights into the final moments of
-binary compact object mergers, including the mergers of binary neutron
+ compact object mergers, including the mergers of binary neutron
 star systems.  Intense preparations are underway to characterize and
@@
 parameters,  \citep{Nissanke2011,Nissanke2013,Veitch2012}, none have considered 
-the full range of parameters measurable for an optimal detection candidate.
+the full range of parameters measurable for an optimal detection candidates.
 
@@
 \ref{PEsection}, we describe the machinery of our parameter estimation
-code, \texttt{LALInference}, and the associated MCMC sampler,
+code, \texttt{LALInference}, and its associated MCMC sampler,
 \texttt{lalinference\_mcmc}, as well as the frequency-domain
@@
 \begin{equation}
-  \rho \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{|
+  \text{SNR} \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{|
     \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df,
@@
 \end{equation}
-where $\rho$ is the SNR and $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
+where $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
 the frequency-domain data and template, respectively, and the
@@
 \begin{equation}
-\rho_{\text{network}} = \sqrt{\sum_i \rho_{i}^2}
+\text{SNR}_{\text{network}} = \sqrt{\sum_i \text{SNR}_{i}^2}
 \label{SNRnetwork}
@@
 
-\noindent where $\rho_i$ is the SNR, given by \eqref{formalSNR}, of
+\noindent where $\text{SNR}_i$ is the SNR, given by \eqref{formalSNR}, of
 the $i^{\text{th}}$ detector.
@@
 time-of-arrival, and coalescence phase.  The luminosity distance, $D$,
-was selected to provide a network SNR of $\rho_{\text{network}}=20$
+was selected to yield a signal strength of $\text{SNR}_{network}=20$
 for each source in each network configuration. 
@@
 advanced era detectors and suppress any effects of detector noise by
-picking $n(t) \equiv 0$.  It can be shown that this ``zero-noise'' injection
+picking $n(t) \equiv 0$.  It can be shown \cite{Nissanke2010} that this ``zero-noise'' injection
 represents the geometric mean of the same experiment over many different
-noise realizations drawn from the same PSD.  See \cite{Nissanke2010}, c.f. equation
-(53), for a proof that the geometric mean of the posteriors over many realizations of the 
-noise is identical to the $n(t) = 0$ selection, given a sufficiently loud gravitational-wave
-event.
+noise realizations drawn from the same PSD.
 
@@
 PSD and that the signal is sufficiently powerful for the linearized-signal
-approximation to be valid\footnote{This can also be seen in \cite{Vallisneri}, equation (74).
-  By expanding the posterior variance as a series in $1/\text{SNR}$, it can be seen that the 
-  $n(t) = 0$ posterior variance is identical to the frequentist average 
-  over noise realizations of the posterior variance up to third order in $1/\text{SNR}$. }.
-    By selecting a source population with an artificial distribution in SNR, we ensure that the
-     ``zero-noise'' as average uncertainty approximation is valid.
-
-To check that our reported statistical errors are not in gross
+approximation to be valid.  By selecting a source population with an
+ artificial distribution in SNR, we ensure that the
+     ``zero-noise'' as average uncertainty approximation is valid.  To check that our
+      reported statistical errors are not in gross
 disagreement with those obtained in the presence of noise, we selected
@@
 time-of-arrival accuracy for various network configurations, including
-those considered here.
+those considered here.  See also \cite{Prospects2013} for a similar analysis,
+applied to each stage of the advanced detector network.
 
@@
 of optimal sources at $\text{SNR}_{network}=20$, ignoring the effects of less viable 
-detection candidates, it is instructive to compare the $95\%$ credible intervals
+detection candidates, it is useful to compare the $95\%$ credible intervals
 between the two studies.  The cumulative distributions of sky-area uncertainties
@@
  where $\text{SNR}_{network} \geq 8.5$ (the threshold for detection candidates in the
- current LIGO/Virgo software framework) for the MCMC parameter estimation.
+ current LIGO/Virgo matched-filtering framework) for the MCMC parameter estimation.
    The current study considers a source
@@
  the sky-area uncertainties that will be available to those considering ``good 
- gravitational-wave events'' (e.g. precision source isolation), and the 
+ gravitational-wave events'' (e.g. precision source localization), and the 
  uncertainties that one can gather by considering all gravitational-wave candidates with 
@@
  considering the increased number of nominal sources available to the HLVI network 
- configuration in the Nissanke population, where the extension of the network detection 
- horizon due to the Indian detector increases the number of sources to 130, versus 90 in 
- the HLV configuration.
+ configuration in the Nissanke population, where the expansion of the network detection 
+ horizon due to LIGO India increases the number of sources to 130, versus 90 in 
+ the HLV configuration.  This trend is similar to that observed in \cite{Veitch2012}, contrasting
+ the originally proposed four-detector configuration (with two co-located Hanford detectors) to 
+ the HLVI configuration.
 
@@
  interval.  This plot contains results from two separate studies: the current study, in
- which optimal detection candidates are considered ($\rho_{network}=20$), 
+ which optimal detection candidates are considered ($\text{SNR}_{network}=20$), 
 and \cite{Nissanke2013}, which employs a separate MCMC code on a
- realistic source population (where $\rho_{trigger} \geq 8.5$ is employed to determine
+ realistic source population (where $\text{SNR}_{trigger} \geq 8.5$ is employed to determine
  parameter estimation sources).  The optimal detection candidates are constrained
@@
    LIGO power spectral density, while the gray-shaded curve is the
-   zero-noise PDF.  Notice how each curve is a Gaussian PDF with roughly similar shape,
-   but different mean, to the zero-noise PDF.  This
+   zero-noise PDF.  Notice how each curve is a Gaussian PDF with different mean and slightly
+   different width
+   , to the zero-noise PDF.  This
    only holds true for glitch-free data, which is an unrealistic
@@
 multiple identical injections in different Gaussian noise
-realizations, as was argued in Section \ref{detectorSection}.  The second reason 
-is we are not able
-to predict the characteristics of realistic (often non-Gaussian)
-advanced detector noise.  Attempting to do so would have little chance
-of being accurate while requiring a huge computational burden to
-combine the results of many MCMC runs in many different noise realizations.
-
-In the case of a unique Gaussian realization of the Advanced LIGO
-noise curve, each realization causes the maximum likelihood of the
+realizations.  For a unique Gaussian realization of the Advanced LIGO
+noise curve, the realization causes the maximum likelihood of the
 posterior probability distribution to be translated away from the true
-value.  These displacements tend to cancel 
-    over many runs, ensuring that the mean uncertainties should be nearly identical to 
-   the uncertainty drawn from the zero-noise runs.  Again, this only holds in the case
-  where a signal is sufficiently loud that the posterior is linear in the parameters 
-  $\thpara$.  Meanwhile, the posterior variances, averaged over many noise realizations, 
-  are identical to the $n(t) = 0$ variance, up to third order in $1/\text{SNR}$.
+value. These displacements tend cancel in the frequentist average over noise
+ realizations, ensuring that the mean uncertainties should be nearly identical to 
+   the uncertainty drawn from the zero-noise runs.  This can be seen in 
+   \cite{Vallisneri}, equations (73) and (74).
+  By expanding the posterior mean and the posterior variance as series in $1/\text{SNR}$,
+   it can be seen that the 
+  $n(t) = 0$ posterior mean is identical to the frequentist average 
+  over noise realizations of the posterior mean to first order in $1/\text{SNR}$.  In similar
+  fashion, the $n(t) = 0$ posterior variance is identical to the noise-realization frequentist 
+  average up to third order in $1/\text{SNR}$.  As the current study operates in a high-SNR 
+  regime, the zero-noise averages (particularly the averages of the posterior variances) are
+   assumed to be valid.
 
@@
 
-Of course, the largest concern for gravitational-wave parameter
-estimation will not be the specific realization of Gaussian noise, but
-the effects of non-Gaussianities in the data.  Techniques which build
+  Of course, this also relies on the assumption that the detector noise is Gaussian.  
+  This is the second reason for employing the zero-noise approximation: it is not feasible
+to predict the characteristics of realistic (i.e. non-Gaussian)
+advanced detector noise.  Attempting to do so would have little chance
+of being accurate while requiring a huge computational burden to
+combine the results of many MCMC runs in many different noise realizations.
+These non-Gaussian excursions will be one of the largest hurdles for parameter estimation
+in the advanced detector era.
+  Techniques which build
 off of the theoretical progress made
 in~\cite{Allen:2002jw,Rover:2011qd,Littenberg:2010gf} for including
-glitches in our model for the data, and therefore relaxing the
+glitches in the model for the data, and therefore relaxing the
 assumptions about stationary and Gaussian noise, are currently under
@@
 credible interval, with an average median 68\% (95\%) credible interval of 
-2 $\mathrm{deg}^2$ $(5.3$ $\mathrm{deg}^2)$.
+2 $\mathrm{deg}^2$ $(5.3$ $\mathrm{deg}^2)$.  These high-SNR results
+were then compared to similar results for a realistic, non-optimal source distribution from
+\cite{Nissanke2013}.
 
@@
 
+\section{Acknowledgements}
+
+The authors would like to thank Samaya Nissanke, John Veitch, and Neil Cornish for useful discussions.  We would also like to thank Samaya Nissanke for the 95\% credible regions
+quoted in Fig. \ref{compSky}. CR and BF were supported by NSF GRFP Fellowships, award DGE-0824162.
+
 \bibliographystyle{apj} \bibliography{paper}{}

### 2013-09-23 doc/paper.tex
final version that was posted on Astro-Ph

@@
 advanced era detectors and suppress any effects of detector noise by
-picking $n(t) \equiv 0$.  It can be shown \cite{Nissanke2010} that this ``zero-noise'' injection
-represents the geometric mean of the same experiment over many different
-noise realizations drawn from the same PSD.
+picking $n(t) \equiv 0$.
 
@@
  artificial distribution in SNR, we ensure that the
-     ``zero-noise'' as average uncertainty approximation is valid.  To check that our
-      reported statistical errors are not in gross
+     ``zero-noise'' as average uncertainty approximation is valid.
+       This approach has been employed in previous studies to similar effect
+        (e.g. \cite{Nissanke2010} and \cite{Sampson2013}).
+ To check that our reported statistical errors are not in gross
 disagreement with those obtained in the presence of noise, we selected
-a particular simulated signal to perform parameter estimation in
+a particular simulated signal to perform parameter estimation upon in
 several noise realizations.  The comparison of the noise-dependent and
@@
  population isotropically distributed on the sky, but at distances such that each signal
- represents an optimal case for parameter estimation.   Fig. \ref{compSky} compares
+ represents an optimal case for parameter estimation.   Fig.\ \ref{compSky} compares
  the sky-area uncertainties that will be available to those considering ``good 
@@
 The authors would like to thank Samaya Nissanke, John Veitch, and Neil Cornish for useful discussions.  We would also like to thank Samaya Nissanke for the 95\% credible regions
-quoted in Fig. \ref{compSky}. CR and BF were supported by NSF GRFP Fellowships, award DGE-0824162.
+quoted in Fig.
+\ref{compSky}.
+CR and BF were supported by NSF GRFP Fellowships, award DGE-0824162.
+All authors were also partially or fully supported by NSF Gravitational Physics grant PHY-0969820, PI: VK.
+Lastly, VK is grateful to the hospitality of the Aspen Center for Physics while she worked on this study.
 

### 2013-09-23 fullSkyPlot.py

@@ -16,7 +16,7 @@ m.drawparallels(np.arange(-90.,90.,45.),labels=[1,0,0,0],labelstyle='+/-')
 # draw parallels
 m.drawmeridians(np.arange(0.,360.,90.),labels=[0,0,0,1],labelstyle='+/-')
 # draw meridians
-plt.title("Sky Location Uncertainty", fontsize=22) # add a title
+plt.title("Sky Location Credible Intervals, HLVI Configuration", fontsize=35) # add a title
 m.drawmapboundary()
 #colorbar.ColorbarBase.set_label(test,'$\log_{10}$($\Omega$)  $(deg)^2$', fontsize=15)
 
@@ -24,6 +24,7 @@ ra = []
 dec= []
 sa = []
 deg= []
+#for prefix in ['2.5_2.5']:
 for prefix in ['1_1','1.4_1.4','1_2.5','2.5_2.5']:
 	for run in range(1,41):
 		filename = prefix + '/' + str(run) + '/post/ranked_sky_pixels.dat'
@@ -45,7 +46,6 @@ for prefix in ['1_1','1.4_1.4','1_2.5','2.5_2.5']:
 		fileSummary.close()
 		gmst = float(fileSummaryData[31].split()[6])
 		gmst = np.mod(gmst/3600.,24.)
-		print gmst
 
 		i = 0
 		cum = float(filedata[1].split()[3]) 
@@ -58,24 +58,26 @@ for prefix in ['1_1','1.4_1.4','1_2.5','2.5_2.5']:
 			i += 1
 		for j in range(i):
 			deg.append(i*(41252.96129655765) / (len(filedata) - 1))
+print max(deg)
 
 ra = np.array(ra)
 dec= np.array(dec)
 sa = np.array(sa)
 
-ra_reverse =  ra*57.296
+ra_reverse =  -ra*57.296
 
 plx,ply=m(
 	  ra_reverse,
 	  (dec)*57.296
 	  )
 
-m.scatter(plx,ply,s=sa,c='gray',edgecolors='none',cmap=plt.cm.gist_rainbow,alpha=0.75)
+m.scatter(plx,ply,s=sa,c='gray',edgecolors='none',cmap=plt.cm.gist_rainbow_r,alpha=0.75)
 
 ra = []
 dec= []
 sa = []
 deg= []
+#for prefix in ['2.5_2.5']:
[…]

### 2013-12-12 doc/Review1Response.txt
Reviewer responses before 12/9 meeting

1st referee

The paper presents a numerical calculation on the measurement of BNS physical parameters, from GW signals to be obtained with the advanced detector array.
The paper is clearly written and the calculation look sound and free of basic errors.
The analysis reported here is a sort of reduced version, at higher SNR, of the analysis reported in Nissanke et al, 2013, Astrophys. J., 767, 124, 124.
Both analyses use the zero-noise, MCMC technique, and their results are consistent.
I am not convinced that the paper, at this stage of the work, provides substantial new information over that of Nissanke. The only piece of information that I find new is to be found in figure 7 and 8, wherein the positional accuracy is reported as a function of the sky location of the source.
As most of methods and procedures are not new, I think the authors, after having substantially shortened the introductory parts and minimized the description of the zero-noise MCMC method, may want to highlight the delta knowledge contributed by this paper relative to the recent literature.

I have also one comment on section 3.4 and the related figure 9.

At face value figure 9 would indicate that by averaging overn many non zero-noise MCMC calculation, the distribution of all parameters would be substantially smeared out . The authors state instead that the figure demonstrates that the distribution stays the same as in the zero-noise case. I think this is confusing and should be clarified.

I think the authors have to respond to these objections before the paper may be considered for publication.

———————————————————————————————————

The reviewer brings up two points where our paper can be improved: the length of the description of our MCMC zero-noise choice, and the difference between our work and the work of Nissanke et al.  We discuss these points below:

Length of the zero-noise sections:

We feel that the length of the description of our MCMC technique is justified for two reasons:

	1.the code employed is distinct from that of Nissanke et al.  While it is certainly true that the two codes use the same technique (an MCMC is an MCMC, after all), the LALInference_MCMC code was specifically developed for the analysis of raw data from the LIGO instrument, and is the only MCMC code to have been tested against real data, and

	2. The description of our Bayesian technique is necessary, due to the difference in priors between our study and Nissanke. In particular, we employ a flat prior in the component masses (versus Nissanke’s flat prior in the chirp mass), which can lead to substantially different recovered posteriors

Delta Knowledge between our work and Nissanke et al:

The second issue is, of course, what additional information is provided by our paper that was not provided by Nissanke at al. 2011 or 2013.  There are two primary areas in which our study differentiates itself from the two of Nissanke, in addition to the figures demonstrating the uncertainties as a function of sky-location:

	1. Our choice of signal population: we consider multiple masses for neutron stars, including one system with an asymmetric mass ratio, and employ a physically uninformative mass prior (that is, flat in component masses).  As Nissanke et al. is primarily interested in recovery of the binary distance, inclination, and sky locations, their work (and all previous MCMC results in the literature) only consider neutron stars of 1.4 solar masses, and employs an unphysical flat prior on the chirp mass (which yields a non-flat prior in component masses).

We have made this distinction clear in the text (see the new paragraph at the end of section 1, and the second paragraph in the conclusion, and the end of section 2.0).

	2. Our choice of signal strength: The high-SNR selection ensures that our reported credible regions are accurate, as it is only in the high-SNR regime that the zero-noise as average posterior assumption becomes valid.  This serves the goal of the study to provide quotable lower-limit estimates on the average parameter recoveries.  This was stated in the last paragraph of section 2.3, and we have modified the text (first paragraph of the conclusion and the new, 5th paragraph of the introduction) to make this goal sufficiently explicit.

Finally, the reviewer points out that the caption for Figure 9 is confusing.  We agree, and have clarified the text (specifically mentioning that the variance and mean of multiple zero-noise results are accurate to different orders in 1/SNR)

### 2013-12-12 doc/Review2Response.txt
Reviewer responses before 12/9 meeting

This paper reports on a competent exercise in the analysis of simulated data for the upcoming "advanced" phase of ground-based gravitational-wave detectors. However, there is a disconnect between what the paper purports to do, and what it actually does. As a consequence, I believe that publishing the paper in its current form would be misleading for the research community. I will give my reasons below why I think this is the case. Once my concerns are adequately addressed by the authors, the resulting paper would be interesting technically, but much less so physically, and may be appropriate for publication in the ApJ supplement series, but probably not in ApJ.

The paper claims to report (I quote) the "statistical uncertainties that will be achievable for optimal detection candidates", to "give realistic estimates of the capabilities of advanced ground-based detectors to characterize BNS systems", to produce PDFs that are "representative of the type of results that will be produced by parameter estimation studies in the advanced detector era", and to provide a "quantitative a quotable source for studies seeking to determine how well a physical question about BNS systems can be answered within the Advanced LIGO/Virgo network." Yet, the paper analyzes detections with network SNR = 20, corresponding to one out of fifteen observations (under the assumption of isotropic source distribution and threshold at 8.5), which it characterizes as "high, but not unrealistic" SNR. By focusing on a non-typical case, the paper overstates the very capabilities that it seeks to represent. Furthermore, the paper notes that it reports on a study performed
under "idealized detector-noise conditions", and that "in practice the realization of noise will be a major factor in the deflection of signal PDFs from the idealized cases presented here." Indeed, most of the parameter-estimation runs discussed in the paper are performed by setting the noise to zero! I have more to say about that, but I believe I have made my case that the paper is misleading in its current form.

Regarding setting the noise to zero: The paper claims it has the virtue of "focusing on statistical errors due to the flexibility of the waveforms"; but that is only one piece of the puzzle in actual parameter estimations. It is true that the zero-noise posterior is equal to the PDF averaged over noise realization when the linearized-signal approximation is valid (i.e., in the high-SNR limit), but that is also the very limit in which the Fisher matrix results are accurate; yet one of the main selling points of the paper is to do a full Bayesian treatment, and later the MCMC and Fisher results are indeed found to be very different.

The justifications for setting the noise to zero given in Sec. 3.4 are not tenable in my opinion. The first is that the O(1/SNR) statistical estimators are correctly reproduced by setting n = 0; but then why do MCMC and not just Fisher, which yields those very O(1/SNR) results? The second is that it is not feasible to predict the characteristic of realistic (non-Gaussian) detector noise. This is a non sequitur (set to zero everything that you can't predict?) Furthermore, if the noise cannot be characterized then the very likelihood [Eq. (4)] that underlies all the MCMC results of this paper would be undermined. (There are reasons to use Gaussian noise statistics even when the noise is not Gaussian, but they need to be argued and implemented very carefully, which is not done here.)

A few minor points:

- The intro seems to imply that the full exploration of parameter space is not "matched filtering". But of course it is, since it uses Eq. (4).
- The priors given at the bottom of p. 2 are not astrophysical, but rather conventional. Astrophysical processes would not result into a uniform distribution for masses, and the distribution of systems out to the horizon distance for LIGO is not homogeneous. The zero-spin assumption also needs justification (it is later called a "simplifying assumption", but is it realistic?)
- In 2.3, noise inner products combine linearly only if noise is uncorrelated among detectors.
- In the caption to Fig. 1, the bit about "reflecting the highest 10% of samples" seems dangerous. What is it about?
- On p. 9, the 8.5 network threshold is a conventional number; the reality is much more complicated (vetos, cuts, etc.) 
- Question: Figs. 6 and 7 show events at the sky position. But is the network SNR set to 20 for both? In that case the HLVI gain is understated, because the sky location would improve even more with the additional SNR that would be available for an SNR = 20 HLV event.

——————————————————————————————————————————

The reviewer brings two large objections to our paper: first, that our choice of source population (SNR = 20) is unrealistic (and correspondingly, that our results do not represent “realistic estimates of parameter estimation”), and secondly, that our choice of setting the noise equal to zero is not sufficiently justified (nor why we would prefer an MCMC over a Fisher matrix analysis for such a case).  We discuss both objections in turn, as well as the minor points the reviewer discusses:

Choice of SNR:

The referee is completely correct: phrasing our results in terms of a typical detection scenario is not supported by our selection of SNR=20.  The goal of our study was to provide a quotable estimate for the community when discussing the parameter estimation capabilities of Advanced LIGO, in effect to update the results of previous Fisher matrix studies while correcting for the limitations of the Fisher Matrix when dealing with a non-trivial posterior.

We have made extensive revisions to the text to correct this point. As such, we have modified the text, particularly in the abstract, introduction, and conclusion to make the intent clear.  See new paragraphs 5 and 7 in the introduction, the new sentence in the abstract, and the modified paragraphs 1 and 2 in the conclusion.  Additionally, we have culled any references to “realistic estimates” from the abstract and introduction.  By describing the results as “averaged lower-bounds”, we believe the information is still physically interesting, while not misleading the reader.

Zero Noise:

There are two distinct reasons for preferring a noise-less averaged MCMC over a Fisher Matrix analysis
	1. The Fisher matrix assumes that each posterior is Gaussian at sufficiently high-SNR.  Several of our posteriors are bounded (e.g. mass ratio), our priors non-Gaussian (e.g. distance), and our likelihoods multimodal (e.g. inclination), nuances that cannot be sufficiently modeled with a Fisher Matrix approach.  The virtue of our approach is that it allows us to update the Fisher-matrix rule—of-thumb estimates in the literature with credible intervals that respect the highly non-Gaussian structure of our posteriors.  We have added this discussion to the text in the paragraphs 5 of the introduction and paragraph 2 of the conclusion.

Additionally, it can be shown (Vallisneri, 2011) that the variance of the zero-noise Bayesian posterior is identical to the averaged variances of multiple noisy runs to O(1/SNR^3), compared to O(1/SNR) for the Fisher Matrix.  This is discussed in the first paragraph of section 3.4

We agree with the reviewer that our choice of n=0 does not account for any non-Gaussian excursions that can occur in any single event.  Unfortunately, it is not possible to model or predict the nature of such glitch events before the instrument has been

We agree with the reviewer that our choice is sub-optimal, but we maintain that it is the most scientifically responsible, given our current limitations.

In response to the few minor points at the end:

1. The intro seems to imply that the full exploration of parameter space is not "matched filtering". But of course it is, since it uses Eq. (4)

Our goal was to contrast our parameter estimation with a template bank detection approach.  We have corrected the text to better reflect this.

2. The priors given at the bottom of p. 2 are not astrophysical, but rather conventional. Astrophysical processes would not result into a uniform distribution for masses, and the distribution of systems out to the horizon distance for LIGO is not homogeneous. The zero-spin assumption also needs justification (it is later called a "simplifying assumption", but is it realistic?)

Of course, the true prior should be the true mass distribution for binary neutron stars, combined with a distance/sky-location prior based on the distribution of baryonic matter in the local universe.  In practice, the observed distribution of neutron star masses from pulsar measurements isn’t sufficiently strong to noticeably influence our recovered posteriors. [DE-SARCASTIC THIS]

The zero-spin assumption is NOT physical, though in practice the maximum possible spin of a neutron star (assuming a reasonable equation of state) is insufficient to induce a large effect in the waveform.

3. In 2.3, noise inner products combine linearly only if noise is uncorrelated among detectors

We have added this to the text .

4. In the caption to Fig. 1, the bit about "reflecting the highest 10% of samples" seems dangerous. What is it about?

At a wall in the parameter space (e.g. q=1), the KDE drops artificially, since the value at q=1 is missing support from points where q>1.  To fix this, it is customary to reflect some of the points across the boundary, so that the KDE resembles the histogram.  As long as dp(x)/dx = 0 at the boundary, this estimator is unbiased.  We elected to use 10% of the points, as it was the minimum number required to get the smooth KDE to match the binned histograms. [SHORTEN THIS AND INSERT IN THE TEXT]

5. On p. 9, the 8.5 network threshold is a conventional number; the reality is much more complicated

We have added a mention that this is a simplification in the text. [ADD IT]

6. Figs. 6 and 7 show events at the sky position. But is the network SNR set to 20 for both?

Correct; we are ignoring the extra contribution from the additional SNR provided by a fourth detector site.  However, the purpose of the figure is to illustrate the increased precision of the parameter estimation regardless of the signal SNR (specifically the shape on the sky, which is vastly improved by a four-detector network).

### 2013-12-12 doc/paper.tex
Reviewer responses before 12/9 meeting

@@
 estimation with advanced detectors, the majority have relied
-on approximation techniques such as the Fisher Matrix.  Here we report the
+on approximation techniques such as the Fisher Matrix\carl{, while ignoring the rich, non-Gaussian
+nature of the gravitational-wave parameter space}.  Here we report the
 statistical uncertainties that will be achievable for optimal detection candidates
@@
 the full parameter estimation machinery developed by the LIGO/Virgo
-Collaboration via Markov-Chain Monte Carlo methods. 
+Collaboration via Markov-Chain Monte Carlo methods\carl{, with the goal of supplanting the previously quoted Fisher Matrix bounds}. 
  We find the recovery of the individual masses to be
@@
 achieved by different network configurations.
-% \will{I'm not sure that
-  %we want to say this exactly this way---the sources in this study are
- % not randomly distributed in SNR, but rather cluster at rather loud
-  %signals.}
 \end{abstract}
@@
 eventually be used in the Advanced LIGO/Virgo era, our results
- give realistic estimates of the capabilities of
-advanced ground-based detectors to characterize BNS systems.  Until
-recently, the majority of studies have employed the Fisher-matrix
+ give \sout{realistic} \carl{lower-bound} estimates of the capabilities of
+advanced ground-based detectors to characterize BNS systems.  
+The majority of studies have employed the Fisher-matrix
 formalism which was first adapted for gravitational-wave parameter
@@
 of Advanced LIGO/Virgo using the techniques that will eventually be
-employed.  The recent work of \cite{Vallisneri} and our own work
-\citep{Inadequacies} has demonstrated that the Fisher matrix cannot
+employed.  \sout{The recent work of} \cite{Vallisneri} \sout{and our own work}
+\citep{Inadequacies} \sout{ has demonstrated that the Fisher matrix cannot
 even be treated as a lower bound on the standard deviations of certain
 parameters (particularly the masses) measurable in gravitational-wave
-detectors.  While previous studies have employed MCMC techniques for specific
-parameters,  \citep{Nissanke2011,Nissanke2013,Veitch2012}, none have considered 
-the full range of parameters measurable for an optimal detection candidates.
+detectors.}
+
+\carl{The Fisher-matrix estimates which the current study seeks to supplant ignore 
+the complicated structure of the gravitational-wave parameter space.  The recovered
+parameter distributions are often highly non-Gaussian, with multiple peaks and correlations, details
+which violate the explicit assumptions of the Fisher-matrix formalism.   By relaxing those constraints, this study
+provides a full exploration of the parameter space in the context of optimal detection candidates.  This picture is
+necessary to understand the }
 
@@
  times with isotropically selected sky locations and orbital orientations, and with a distance
- such that each signal was injected with a network signal-to-noise ratio of 20.
+ such that each signal was injected with a network signal-to-noise ratio of 20, \carl{a loudness selected to
+ ensure the averages }
   The results are divided into three subsections of interest: the recovery of the mass
@@
 Finally we provide quantitative 1-dimensional credible intervals on
-each parameter in Section \ref{ciSection}.  These results, contained
+each parameter in Section \ref{ciSection}.  \sout{These results, contained
 in Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}, are
 intended as a reference for the optimal BNS parameter estimation
-capabilities of Advanced LIGO/Virgo.  We assume that $G=c=1$
-throughout.
+capabilities of Advanced LIGO/Virgo.}
+
+\carl{The goal of the current study is to provide an lower-limit ``rule-of-thumb'' for parameter estimation uncertainties 
+in Advanced LIGO/Virgo which acknowledges the complexity of the parameter space, and separates this from
+ the difficulties introduced by the detector noise for a single event.  These results are collected and summarized in 
+ Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}.  While previous studies have employed 
+ MCMC techniques for specific parameters,  \citep{Nissanke2011,Nissanke2013,Veitch2012}, none have considered 
+the full range of parameters measurable for an optimal detection candidates, nor have they considered neutron stars
+ of masses other than $1.4M_{\odot}$.  We explore
+ the recovery of mass parameters for BNS systems with multiple neutron star masses and mass ratios.  
+ We assume that $G=c=1$.}
 
@@
   30M_{\odot}$, with a minimum chirp mass (see Eq.~\eqref{eqRatioCM})
-  of 0.6 $M_{\odot}$,
+  of 0.6 $M_{\odot}$ 
 \item uniform in volume, which implies a luminosity distance prior of
@@
 practice the higher prior boundary does not affect our current
-analysis.
+analysis.  \carl{Note that the choice of a flat prior in component masses is distinct from \cite{Nissanke2013},
+ which employed a prior flat in chirp mass and reduced mass-ratio.}
 
@@
 For a multi-detector network, the noise-weighted inner products
-\eqref{innerProduct} combine linearly, allowing us to use the above
+\eqref{innerProduct} combine linearly \carl{so long as the noise is
+uncorrelated between detectors}, allowing us to use the above
 formalism with minimal modification.  We integrate the inner product
@@
 advanced era detectors and suppress any effects of detector noise by
-picking $n(t) \equiv 0$.
-
-Consequently, what we recover with the MCMC could be interpreted as
+picking $n(t) \equiv 0$.  Consequently, what we recover with the MCMC could be interpreted as
 the posterior distribution function for each source averaged over all
@@
      ``zero-noise'' as average uncertainty approximation is valid.
-       This approach has been employed in previous studies to similar effect
-        (e.g. \cite{Nissanke2010} and \cite{Sampson2013}).
- To check that our reported statistical errors are not in gross
-disagreement with those obtained in the presence of noise, we selected
-a particular simulated signal to perform parameter estimation upon in
-several noise realizations.  The comparison of the noise-dependent and
-noise-free results can be found in Section \ref{noiseSection}.
+
+     Previous studies have both employed and studied in detail the consequences of this approach.
+   \carl{  In particular, \cite{Nissanke2010} demonstrated that the $n(t)=0$ posterior is equal to the geometric mean over 
+     specific noise realizations of the posterior, while \cite{Sampson2013} performed a numerical experiment to 
+     demonstrate the validity of the assumption.
+We perform a similar numerical experiment in Section \ref{noiseSection}, in which we demonstrate that the uncertainties from a $n(t)=0$ posterior are equivalent to the frequentist
+     average over uncertainties from multiple noise realizations. }
 
@@
  volume for sources where $D > 200\text{Mpc}$.  These were then limited to those signals
- where $\text{SNR}_{network} \geq 8.5$ (the threshold for detection candidates in the
+ where $\text{SNR}_{network} \geq 8.5$ (the \carl{rule-of-thumb} threshold for detection candidates in the
  current LIGO/Virgo matched-filtering framework) for the MCMC parameter estimation.
@@
    LIGO power spectral density, while the gray-shaded curve is the
-   zero-noise PDF.  Notice how each curve is a Gaussian PDF with different mean and slightly
-   different width
-   , to the zero-noise PDF.  This
-   only holds true for glitch-free data, which is an unrealistic
+   zero-noise PDF.  \carl{Notice how each curve is a Gaussian PDF with different mean but similar 
+   width from the zero-noise PDF.  This is to be expected, as the zero-noise mean is identical to the 
+   average to first order in $1/\text{SNR}$, while the zero-noise standard deviation is identical to the average 
+   standard-deviation
+    up to $1/\text{SNR}^3$.  }
+   This only holds true for glitch-free data, which is an unrealistic
    idealization when compared to real data.}
@@
 to predict the characteristics of realistic (i.e. non-Gaussian)
-advanced detector noise.  Attempting to do so would have little chance
-of being accurate while requiring a huge computational burden to
+advanced detector noise.  
+Attempting to do so would have little chance
+\sout{of being accurate while requiring a huge computational burden to
 combine the results of many MCMC runs in many different noise realizations.
 These non-Gaussian excursions will be one of the largest hurdles for parameter estimation
-in the advanced detector era.
+in the advanced detector era} \carl{However, as the current study is focused on the lower-bound average uncertainties,
+ and not the systematics of a single event (for which we must await a true detection), this assumption does not impact 
+ the validity of our results}
 Techniques which build
@@
 of the chirp mass and the symmetric mass ratio ($\eta \equiv m_1 m_2 / M_{tot}^2$)
-at the 68\% level (1-$\sigma$) for the $1.4M_{\odot}/1.4M_{\odot}$ system presented 
+at the 68\% level \carl{NO, FIX ME}(1-$\sigma$) for the $1.4M_{\odot}/1.4M_{\odot}$ system presented 
 here.  We then compare the findings of the MCMC to the Fisher matrix predictions using
@@
 using a code previously described in \cite{Inadequacies}.  We find that the MCMC credible
- intervals vary significantly from
+ intervals \carl{can} vary significantly from
 the estimates of the Fisher matrix, with the Fisher matrix underestimating the 
-fractional uncertainties by as much as a factor of three.  See Table~\ref{FIMvsMCMC}.  This 
+fractional uncertainties by as much as a factor of \sout{three} \carl{two}.  See Table~\ref{FIMvsMCMC}.  This 
 result agrees with the conventional wisdom surrounding the Fisher Matrix accuracy,
@@
 
-\begin{table*}[t!]
+\begin{table*}[h!]
 \centering
@@
 
-\begin{table}[b!]
+\begin{table}[h!]
 \centering
-\caption{68\% Credible intervals versus 1-$\sigma$ Fisher matrix uncertainties for mass parameters in each system in the HLV configuration.}
+\caption{68\% Credible intervals versus \sout{1-$\sigma$} \carl{$2\sigma$} Fisher matrix uncertainties for mass parameters in each system in the HLV configuration.}
   \tabcolsep=0.11cm
@@
 
-$1M_{\odot}-1M_{\odot}$ & \vline &  0.00497\% & \vline & 0.00205\% & \vline & 0.645\% & \vline & 0.321\% \\
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline &  0.00890\% & \vline & 0.00384\% & \vline & 0.745\% & \vline & 0.380\% \\
-$1M_{\odot}-2.5M_{\odot}$& \vline &  0.0176\% & \vline & 0.00457\% & \vline & 1.475\% & \vline & 0.400\% \\
-$2.5M_{\odot}-2.5M_{\odot}$& \vline &  0.0245\% & \vline & 0.0114\% & \vline & 1.000\% & \vline & 0.612\% \\
+$1M_{\odot}-1M_{\odot}$ & \vline &  0.00497\% & \vline & 0.00396\% & \vline & 0.645\% & \vline & 0.704\% \\
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline &  0.00890\% & \vline & 0.00743\% & \vline & 0.745\% & \vline & 0.866\% \\
+$1M_{\odot}-2.5M_{\odot}$& \vline &  0.0176\% & \vline & 0.00880\% & \vline & 1.475\% & \vline & 0.862\% \\
+$2.5M_{\odot}-2.5M_{\odot}$& \vline &  0.0245\% & \vline & 0.0221\% & \vline & 1.000\% & \vline & 1.299\% \\
 
@@
 orbital inclination, and the sky location, as these are the six basic
-parameters of physical interest to the problem.  We found that,
-neglecting the effects of spin, the component masses can be
+parameters of physical interest to the problem.  It should be remembered that these signals were injected at high, 
+but not unrealistic, SNRs \carl{in order to create a reference similar to those found in previous
+Fisher Matrix studies, and to validate the ``$n(t) = 0$ as average'' assumption.
+
+ Unlike the Fisher-matrix studies, an MCMC allows us to relax the flawed assumptions of a Gaussian and uni-modal 
+ distribtion, and to
+fully explore the relevant parameter space.  Given the highly non-Gaussian nature of the explored 
+parameter space (see Figures \ref{9dPDF}, \ref{1414masses}, \ref{metaMassPDFs}-\ref{2525SkyLocHLVI} ), this exploration is critical to a complete 
+understanding of the gravitational-wave BNS parameter estimation problem}.  
+The results quoted can be thought of as the
+average \carl{lower-bound} uncertainties for an \carl{optimal} \sout{``good''} Advanced LIGO/Virgo detection.
+
+\carl{For the mass parameters,} we found that, neglecting the effects of spin, the component masses can be
 constrained to within 9\% (15\%) of their true value to a credible level of
-68\% (95\%).  This value drops below 1.9\% (3.7\%) for systems with an asymmetric mass
-ratio.  These results were summarized in Table \ref{ciTableIntrinsic}.
-It should be remembered that these signals were injected at high, 
-but not unrealistic, SNRs.  Thus, the results quoted can be thought of as the
-average uncertainties for a ``good'' Advanced LIGO/Virgo detection.
+68\% (95\%) \carl{for systems with equal-mass neutron stars.
+}  This value drops below 1.9\% (3.7\%) for systems with an asymmetric masses.
+  \carl{It was also found that the fractional uncertainties for equal-mass binary systems are similar at equal SNR.
+Only when the masses are unequal are the fractional errors effected.}
+These results were summarized in Table \ref{ciTableIntrinsic}.  \carl{The current study is the first 
+to quantify neutron star mass measurements in Advanced LIGO/VIRGO  via an MCMC for neutron star masses
+other than $1.4M_{\odot}$.}
 
@@
 Finally, we reported the ability of advanced networks to constrain the
-sky location of BNS signals.  It was found that the three-detector
+sky location of \carl{optimal} BNS signals.  It was found that the three-detector
 configuration, consisting of the Washington and Louisiana LIGO sites
@@
 gravitational-wave detector.  The realization of noise will be a
-major factor in the deflection of signal PDFs from the idealized cases
+major factor in the deflection of signal PDFs from the idealized, \carl{lower-bound} cases
 presented here.
@@
 
+\pagebreak
+
 \section{Acknowledgements}

### 2013-12-12 doc/Review1Response.txt
Addressed reviewer ones comments, relagating a lot of the information to appendecies

@@
 
-Length of the zero-noise sections:
+Length of the zero-noise and introductory sections:
+	We completely agree with the reviewer that these sections can be substantially paired down.
+We have made extensive modifications to sections 2.1 and 2.2, relegating the majority of the technical details in those sections to Appendecies.
+We find this improves  the flow of Section two.
+Additionally, we have moved the majority of the discussion regarding the zero-noise choice (the end of section 2.3 and all of section 3.4) to a third Appendix.
 
-We feel that the length of the description of our MCMC technique is justified for two reasons:
-
-	1.the code employed is distinct from that of Nissanke et al.
-While it is certainly true that the two codes use the same technique (an MCMC is an MCMC, after all), the LALInference_MCMC code was specifically developed for the analysis of raw data from the LIGO instrument, and is the only MCMC code to have been tested against real data, and
-
-	2.
-The description of our Bayesian technique is necessary, due to the difference in priors between our study and Nissanke.
-In particular, we employ a flat prior in the component masses (versus Nissanke’s flat prior in the chirp mass), which can lead to substantially different recovered posteriors
-
-Delta Knowledge between our work and Nissanke et al:
+Distinction between the current study and Nissanke et al. 2013:
 
 The second issue is, of course, what additional information is provided by our paper that was not provided by Nissanke at al.
-2011 or 2013.
-There are two primary areas in which our study differentiates itself from the two of Nissanke, in addition to the figures demonstrating the uncertainties as a function of sky-location:
+2013; however, we believe that our study is significantly different from Nissanke2013.
+The numbers in Tables 1 and 2, which provide a “rule-of-thumb” estimate for the community, were in many ways the main goal of this paper.
+As Nissanke2013 primarily reports on EM follow-up capabilities, we feel that the current study is significantly different.
 
-	1.
-Our choice of signal population: we consider multiple masses for neutron stars, including one system with an asymmetric mass ratio, and employ a physically uninformative mass prior (that is, flat in component masses).
-As Nissanke et al.
-is primarily interested in recovery of the binary distance, inclination, and sky locations, their work (and all previous MCMC results in the literature) only consider neutron stars of 1.4 solar masses, and employs an unphysical flat prior on the chirp mass (which yields a non-flat prior in component masses).
+The current study is the first to examine the intrinsic properties of neutron star binaries, in particular the masses.
+Our current study focuses heavily on the recovery of the mass parameters for multiple neutron star masses.
+This is reported in our section 3.1, and the tables in section 4.
+Nissanke2013 does not consider the recovery of the BNS mass parameters, and only simulates neutron stars of 1.4 solar masses, as their study is primarily interested in extrinsic parameters relevant to electromagnetic followup.
 
-We have made this distinction clear in the text (see the new paragraph at the end of section 1, and the second paragraph in the conclusion, and the end of section 2.0).
-
-	2.
-Our choice of signal strength: The high-SNR selection ensures that our reported credible regions are accurate, as it is only in the high-SNR regime that the zero-noise as average posterior assumption becomes valid.
-This serves the goal of the study to provide quotable lower-limit estimates on the average parameter recoveries.
-This was stated in the last paragraph of section 2.3, and we have modified the text (first paragraph of the conclusion and the new, 5th paragraph of the introduction) to make this goal sufficiently explicit.
+We also feel that our section 3.3, which concerns the sky-localization, is distinct from Nissanke2013.
+As the reviewer points out, our figures 6 and 7 demonstrate the uncertainties over a large number of sky-locations for each detector network, while Nissanke2013 only demonstrates a handful of injections.
+In fact, the realistic population plotted in Figure 8 is taken directly from Nissanke2013.
 

### 2013-12-12 doc/Review2Response.txt
Addressed reviewer ones comments, relagating a lot of the information to appendecies

@@
 Additionally, we have culled any references to “realistic estimates” from the abstract and introduction.
-By describing the results as “averaged lower-bounds”, we believe the information is still physically interesting, while not misleading the reader.
+By describing the results as “lower-bound average uncertainties”, we believe the information is still physically interesting, while not misleading the reader.
 
@@
 We agree with the reviewer that our choice of n=0 does not account for any non-Gaussian excursions that can occur in any single event.
-Unfortunately, it is not possible to model or predict the nature of such glitch events before the instrument has been
+Unfortunately, it is not possible to model or predict the nature of such glitch events before the instrument has been constructed and characterized.
+While we can simulate a simple non-Gaussian excursion, we have no means to construct a well-motived population of such excursions, which we would require for a statistically reasonable statement.
+We feel that the averages in the current study most adequately satisfies requests from the community for quotable “rule-of-thumb” estimates, while ignoring the systematic effects that will effect a single detection.
 
-We agree with the reviewer that our choice is sub-optimal, but we maintain that it is the most scientifically responsible, given our current limitations.
+The reviewer is completely correct that our choice is sub-optimal, but we maintain that it is the most scientifically responsible one available to us at the moment.
+We have added a discussion of this in the last paragraph of the introduction.
 

### 2013-12-12 doc/paper.tex
Addressed reviewer ones comments, relagating a lot of the information to appendecies

@@
 eventually be used in the Advanced LIGO/Virgo era, our results
- give \sout{realistic} \carl{lower-bound} estimates of the capabilities of
+ give \sout{realistic} \carl{lower-bound average} estimates of the capabilities of
 advanced ground-based detectors to characterize BNS systems.  
@@
 \citep{spinspiral2009, spinspiral2010}.  The MCMC employs a
-Metropolis-Hastings sampling algorithm, which can be described as
-follows \citep{Gilks99}:
+Metropolis-Hastings sampling algorithm \citep{Gilks99}, which is described in 
+Appendix \ref{appendixMCMC}.
+
+\subsection{Parameter Space}
+\label{parameterSection}
+
+\carl{The phase of the gravitational-waveform is primarily determined by four intrinsic parameters.
+They are the two masses ($M_1$ and $M_2$) and two intrinsic constants of integration.}
+For convenience, we instead describe the masses in terms of the chirp mass and mass ratio, defined below.
+ In addition, there are 5 extrinsic
+parameters which do not influence the inspiral of the binary, but can modulate
+the amplitude of the signal independently in each
+detector.  Considering these leads to our 9-dimensional parameter space
+for non-spinning systems as employed in our MCMC:
+\begin{equation}
+\thpara = (\chmass, q, \phi_0,t_c,D,\iota,\psi,\alpha,\delta),
+\label{parameterspace}
+\end{equation}
+where
+
+\begin{itemize}
+\item $\chmass \equiv (M_1 M_2)^{3/5}  M_{tot}^{-1/5}$ is the chirp mass,
+\item $q\equiv M_2 / M_1$ is the mass ratio,
+\item $\phi_0$ and $t_c$ are the chirp phase and chirp time, arbitrary
+  phasing parameters,
+\item $D$ is the luminosity distance to the binary,
+\item $\iota$ is the orbital inclination (the angle between the
+  orbital angular momentum and the line of sight),
+\item $\psi$ is the gravitational-wave polarization, and
+\item $\alpha$ and $\delta$ are the right ascension and declination of
+  the source on the sky.
+\end{itemize}
+  Since the wave amplitude depends on the orientation of the binary
+  with respect to each detector, most of the information about these
+  extrinsic parameters comes from two sources: the time-of-arrival
+  triangulation of the signal, and the relative amplitudes
+  in each detector in the network.
+
+  \subsection{Detector Configuration and Noise Models}
+  \label{detectorSection}
+
+To perform the integral defined in \eqref{innerProduct}, we used as
+our power-spectral density the best estimate for a high-power,
+zero-detuning configuration of Advanced LIGO, provided by the LIGO
+Scientific Collaboration.  Both the noise curve and technical reports
+describing it can be found in \cite{ADVLIGONoise}.  We consider two
+configurations of the advanced detector network: a three-detector
+configuation consistanting of the two LIGO sites (in Hanford, WA and
+Livingston, LA) and the Virgo site (in Pisa, Italy), and a
+four-detector configuration that adds the proposed LIGO-India detector
+(in Chitradurga, KA).  For simplicity, we assume each detector to be
+operating at the Advanced LIGO sensitivity.
+
+For a multi-detector network, the noise-weighted inner products
+\eqref{innerProduct} combine linearly \carl{so long as the noise is
+uncorrelated between detectors}, allowing us to use the above
+formalism with minimal modification.  We integrate the inner product
+from a lower-frequency cutoff of $20\text{Hz}$ to the
+innermost-stable-circular orbit of the systems, which for
+a non-spinning binary is a function only of the total mass:
+
+\begin{equation}
+  \pi f_{\text{ISCO}} = \frac{1}{6^{3/2}M_{tot}}.
+  \label{ISCOFrequency}
+\end{equation}
+
+We define the signal-to-noise ratio (SNR) of a gravitational wave in a
+single detector as
+\begin{equation}
+  \text{SNR} \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{|
+    \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df,
+  \label{formalSNR}
+\end{equation}
+where $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
+the frequency-domain data and template, respectively, and the
+normalization $\sigma$ is given by
+\begin{equation}
+  \sigma^2 = 4\int^{\infty}_{0}\frac{| \tilde{h}(f)|^2}{S_n(f)}df.
+  \label{SNRnorm}
+\end{equation}
+
+\noindent When dealing with a network of gravitational-wave detectors, the SNRs
+of the individual detectors add in quadrature.  That is, the network
+SNR for a detection is
+
+\begin{equation}
+\text{SNR}_{\text{network}} = \sqrt{\sum_i \text{SNR}_{i}^2}
+\label{SNRnetwork}
+\end{equation}
+
+\noindent where $\text{SNR}_i$ is the SNR, given by \eqref{formalSNR}, of
+the $i^{\text{th}}$ detector.
+
+For this study, we consider four separate populations of BNS systems,
+with component mass combinations of $1M_{\odot}/1M_{\odot}$,
+$1.4M_{\odot}/1.4M_{\odot}$, $1M_{\odot}/2.5M_{\odot}$, and
+$2.5M_{\odot}/2.5M_{\odot}$.  Each population consisted of 40 signals
+distributed randomly in sky location, polarization, inclination,
+time-of-arrival, and coalescence phase.  The luminosity distance, $D$,
+was selected to yield a signal strength of $\text{SNR}_{network}=20$
+for each source in each network configuration. 
+ While unphysical from an astrophysics perspective
+(binary sources are expected to be distributed uniformly in co-moving volume), this
+choice allows us to explore the parameter estimation in the context of
+loud but plausible detection candidates.
+
+Finally, note that the PSD that defines the inner
+product \eqref{innerProduct} is simply the time-averaged sensitivity
+of a given detector to a specific frequency.  Ignoring non-Gaussian
+glitches, any stretch of data should contain a specific noise
+realization drawn from a Gaussian colored by the PSD.  Without a
+realistic model including the actual instrument sensitivity, non-stationary
+ noise, and uncertainty in the PSD we cannot accurately
+simulate gravitational-wave data to the point of making precise predictions about
+parameter estimation capabilities.  Furthermore, the posterior
+distribution from a future detection will be influenced by the
+realization of the noise at the time of the detection.  Because of
+this, we elect to focus only on the statistical errors due to the
+flexibility of the waveforms and the expected sensitivity of the
+advanced era detectors and suppress any effects of detector noise by
+picking $n(t) \equiv 0$.  Consequently, what we recover with the MCMC could be interpreted as
+the posterior distribution function for each source averaged over all
+possible (Gaussian) noise realizations, assuming we have the correct
+PSD and that the signal is sufficiently powerful for the linearized-signal
+approximation to be valid.  By selecting a source population with an
+ artificial distribution in SNR, we ensure that the
+     ``zero-noise'' as average uncertainty approximation is valid.
+       We discuss the reasons for this selection in Appendix \ref{noiseSection}.
+
+\section{Results}
+\label{resultsSection}
+
+\begin{figure*}[t!]
+\centering \includegraphics[trim=7cm 0cm 0cm 0cm,
+  clip=true,scale=0.58]{9dpdf}
+%\begin{array}{ccc} 
+%\includegraphics[width=2.2in]{1dpdfs/mc.pdf} &\includegraphics[width=2.2in]{1dpdfs/eta.pdf}  & \includegraphics[width=2.2in]{1dpdfs/m1.pdf}\\
+%\includegraphics[width=2.2in]{1dpdfs/time.pdf} &\includegraphics[width=2.2in]{1dpdfs/dist.pdf}  &\includegraphics[width=2.2in]{1dpdfs/iota.pdf}\\
+%\includegraphics[width=2.2in]{1dpdfs/ra.pdf} & \includegraphics[width=2.2in]{1dpdfs/dec.pdf} & \includegraphics[width=2.2in]{1dpdfs/m2.pdf}
+%\end{array}$
+\caption{\label{9dPDF} Marginalized 1D  posterior probability densities
+  of a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS
+  system.  We have plotted each of the 9 parameters for our
+  non-spinning BNS problem as stated in section \ref{parameterSection}.
+    Note how, even for parameters with excellent recovery, the peak of
+  the 1D Gaussian is displaced from the injected value (in dashed
+  red).  This is not due to a systematic bias, but is caused by the
+  marginalization of a single dimension from the full 9D posterior
+  space.  To better see this effect, compare the 1D PDF for
+  $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in
+  Figure~\ref{1414masses}.  The plots here represent the Gaussian kernel density
+  estimator of each PDF.  The estimate for $q$ was 
+  computed by reflecting the highest $10\%$ of samples across the $q=1$ boundary.  
+  This was done to avoid a false decrease in estimated probability density near
+  the boundary.}
+\end{figure*}
+
+Of the nine parameters in the domain of the waveform, only six are
+particularly physically interesting: the masses of the two binaries,
+$M_1$ and $M_2$, the orbital inclination, $\iota$, the angular
+position on the sky, $\alpha$ and $\delta$, and the luminosity
+distance of the source, $D$.  While the coalescence phase $\phi_0$,
+the coalescence time $t_c$, and the wave polarization $\psi$ must be
+included in any parameter estimation of the waveform, they do not
+encode any information of particular astrophysical
+interest.%\footnote{For systems whose components are non-spinning.  The
+  %presence of intrinsic angular momentum will, in general, couple to
+  %the coalescence phase and wave polarization.  \will{But those
+   % parameters are still physically uninteresting.  They couple to
+   % interesting parameters in both the spinning and non-spinning
+  %  cases, which is why they must be included.  I would just eliminate
+   % this footnote.}}
+
+In Figure~\ref{9dPDF}, we provide an example of the nine,
+1-dimensional marginalized posterior probability density functions
+recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system.  These
+PDFs are representative of the type of results that will be produced by
+parameter estimation studies in the advanced detector era.  Notice
+that the peak of several parameters, including the chirp mass,
+$\chmass$, appears to be displaced from the true values in dashed red.  This
+effect is due to the reduction of the 9-dimensional PDF to a series of
+marginalized 1-dimensional PDFs.  For instance, the 1-dimensional PDF
+for chirp mass is marginalized via
+\begin{equation}
+p(\chmass | s) = \int _{\thpara \setminus \chmass} p(\thpara |
+s)~d(\thpara \setminus \chmass)
+\label{mcMarginalization}
+\end{equation}
+where the notation $\thpara \setminus \chmass$ implies all parameter
+of \eqref{parameterspace} except $\chmass$.  Other parameter and
+higher-dimensional marginalizations follow a similar convention.  In
+practice, the MCMC samples make this integral trivial: since the
+samples are distributed according to the posterior,
+\eqref{mcMarginalization} can be calculated by simply reading off the
+relevant samples in a single parameter, implicitly calculating a
+Monte-Carlo integral over all other parameters.
+
+\subsection{Mass Parameters}
+\label{massSection}
+
+\begin{figure}[h!]
+  \centering \includegraphics[trim=1cm 0cm 2cm 0cm,
+    clip=false,scale=0.63]{1414masses2D.pdf}
+ \caption{2D marginalized posterior probability density functions for
+   the mass parameters recovered in typical a
+   $1.4M_{\odot}/1.4M_{\odot}$ system.  The posteriors are plotted in
+   terms of parameters used in the waveform, chirp mass
+   ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual
+   component masses of the binary ($M_1$ and $M_2$).  In the
+   $\chmass$-$q$ space, the posterior would almost resemble a Gaussian if not
+   for the limitation of $q \leq 1$.  The presence of the $q$ cutoff
+   and the convention that $M_1 \geq M_2$ inform the non-Gaussian
+   features present.  When projected as 1D marginalized posteriors,
+   the component masses resemble the posterior PDFs shown in Figure
+   \ref{metaMassPDFs}.}
+  \label{1414masses}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering \includegraphics[trim=1cm 0cm 2cm 0cm,
+    clip=false,scale=0.63]{125masses2D.pdf}
+ \caption{Similar to Figure~\ref{1414masses}, but for a typical
+   $1M_{\odot}/2.5M_{\odot}$ system.  The unequal mass ratio displaces
+   the posterior PDFs from the $q \leq 1$ boundary present in the equal-mass
+   case, yielding a Gaussian PDF in both the $\chmass$-$q$ and
+   $M_1$-$M_2$ spaces.}
+  \label{125masses}
+\end{figure}
+
+\begin{figure*}[ht!]
+  \centering \includegraphics[trim=3cm 0cm 2cm 0cm,
+    clip=false,scale=0.75]{newMasses.pdf}
+ \caption{Mass PDFs for the four BNS systems, averaged over each of
+   the 40 injections.  The average is reported since, in practice,
+   there was quantitatively no difference between the recovered PDFs
+   for different systems with identical masses and SNRs.  Systems with
+   identical mass ratios but different total masses have
+   quantitatively identical PDFs when normalized to the total
+   mass.  Similarly to Fig. \ref{9dPDF}, we plot the Gaussian kernel density
+   estimates, and reflect $10\%$ of the points across the $q = 1$ and $M_1 = M_2$ boundaries (for the three equal-mass cases).}
+  \label{metaMassPDFs}
+\end{figure*}
+
+Of the nine variables in our parameter space \eqref{parameterspace},
+the mass parameters, $\chmass$ and $q$, or, correspondingly, $M_1$ and
+$M_2$ are the most astrophysically interesting.  The ability of
+Advanced LIGO/Virgo to construct a population of BNS masses will be
+one of the more useful and immediate applications of gravitational-wave astronomy.
+
+We find that there is virtually no difference between the mass PDFs of
+our different injected signals within each mass bin.  While this may
+initially seem disconcerting, it is to be expected for the analysis presented here.
+  Recall that all
+of the BNS signals were injected with a network SNR of 20 into a
+zero-noise detector realization.  Furthermore, note that the mass
+parameters are the only two which directly affect the phase of the
+\sout{TaylorF2} waveform \eqref{phase}.  Therefore, as long as the injected
+mass parameters are identical within each mass system, and as long as
+the injected SNR is identical, the amount of recoverable information
+in each mass parameter should be almost identical, and for a
+sufficiently converged MCMC chain, the recovered posterior PDF should
+be identical.
+
+This effect can be summarized as follows: for non-spinning systems,
+the posterior probability of the masses, $p(\chmass, q | s)$, does not
+depend strongly on the recovery of the extrinsic parameters, $\phi_0$
+or $t_c$.  Therefore, systems with identical masses will produce
+identical mass PDFs.  The only noticeable difference will come from
+the specific realization of noise produced by the detector, which we
+address in Section \ref{noiseSection}.
+
+%The ``almost'' in the previous sentence is to draw attention to one critical, neglected fact: while the mass parameters are independent of the injected signals position with respect to the detector network, the other parameters are certainly not.
+Obviously many of the other parameters (i.e.
+sky location, polarization, distance, inclination, and time-of-arrival) all depend on the orientation of the binary with respect to each of the individual detectors.
+Since our 9-dimensional parameter space can be highly correlated, it is entirely reasonable to assume that cross-correlations between the extrinsic parameters and the mass parameters will cause variation in the recovery of the individual injection PDFs.
+
+%In practice, it was found that the cross-correlations between the extrinsic parameters and signal time-of-arrival were several orders of magnitude \carl{[QUANTIFY]} below the uncertainties in $\chmass$ and $q$.
+It should be noted that, in practice, this will \emph{not} be the case: in reality, the noise power-spectral density of each detector varies as a function of time, including both natural variations in sensitivity and detector glitches \carl{[CITE]}.
+In such a case, the base sensitivity of a gravitational-wave detector to even the easiest to recover parameters will vary as a function of position and time.
+
+In Figures~\ref{1414masses} and~\ref{125masses}, we show the
+marginalized 2D posterior PDFs of our mass parameters for prototypical
+equal-mass and unequal-mass binaries.  We include the PDF in both the
+$\chmass$-$q$ space (relevant for the waveform and the MCMC
+algorithm), and the more physically interesting component mass space
+($M_1$-$M_2$).  Although only the $1.4M_{\odot}/1.4M_{\odot}$ system
+is included in Figure \ref{1414masses}, the PDF is qualitatively
+identical to the other equal mass cases, modulo a scaling factor.
+
+To condense the results into a single figure of merit, we average the
+1-dimensional mass PDFs into a single posterior probability for the
+system in Figure~\ref{metaMassPDFs}.  Notice how, when averaged and
+normalized to the injected values, the recovery of the component
+masses depends only on the mass ratio.  Furthermore, for systems with
+equal component masses, the posterior barely extends beyond 15\% of
+the injected values.  If one assumes that the threshold between black
+holes and neutron stars lies at approximately $3M_{\odot}$, then it
+might be naively assumed that the mass recovery would allow one to
+discriminate between black holes and neutron stars.
+
+In practice, there is a physical complication to this claim: we have
+neglected the spin of the binaries, which will be highly correlated to
+the masses.  This coupling means that, in the case where the black hole spins
+are parallel to the orbital angular momentum, a higher-massed spinning black
+hole systems can produce waveforms very similar to non-spinning,
+low-mass systems.  This effect makes it extremely difficult to discern between
+non-spinning neutron stars and spin-aligned, more massive black holes
+\citep{Baird2013,Hannam2013}.  However, the situation is not hopeless:
+if the spins are misaligned, the spin vectors will couple to the
+orientation of the binary (encoded in the three angles $\phi_0$,
+$\iota$, and $\psi$) via relativistic precession.  It remains to be
+seen if using fully spinning waveforms will make it possible for
+Advanced\ LIGO/Virgo to discern binary neutron stars from their
+spinning black hole counterparts.
+
+In Table \ref{ciTableIntrinsic}, we list the 68\% and 95\% credible
+intervals for the mass parameters.  We find that the component masses
+for equal mass systems can be isolated to between 6.4\% and 9\% (10.3\% and 15\%)
+fractional uncertainty at the 68\% (95\%) credible interval.  This value
+drops to less than 1.9\% (3.7\%) for the components of the unequal mass systems.
+Again, this neglects the effects of spin which can substantially
+increase these values.
+
+\subsection{Inclination and Distance}
+\label{idSection}
+
+\begin{figure}[h!]
+  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
+    clip=true,scale=0.75]{distIota2D.pdf}
+ \caption{Typical marginalized 2D mass PDFs for luminosity distance
+   $D$ and orbital inclination $\iota$. Notice the bimodal
+   distribution on the first PDF, that can occur when a system is
+   detected nearly ``edge-on'' ($\iota \approx \pi/2$).  In general,
+   the degeneracy between distance and inclination forces the PDF into
+   one of these two paths when the system is not edge-on, as seen in
+   the second and third PDFs.}
+ \label{distIotaPDF}
+\end{figure}
+
+Binary neutron star systems (along with neutron star/black hole
+systems) are one of the best candidates for progenitors of short-hard
+gamma-ray bursts \citep[and references therein]{Nakar2007}.  After
+merger, the remnant is believed to emit the burst along the axis of
+orbital angular momentum, making the inclination of the binary system
+of particular interest to gamma-ray astronomy
+\citep{LSCGRB2010,Corsi2012}.  The inclination is detected as a
+relative amplitude difference between the two gravitational-wave
+polarizations, such that to lowest order:
+
+\begin{align}
+h_+(f) &= \frac{1+\cos^2(\iota)}{2 D} \tilde{h}(f) \nonumber
+\\ h_\times(f) &= i \frac{\cos(\iota)}{D}\tilde{h}(f) .
+\end{align}
+
+\noindent It should be apparent that the luminosity distance $D$ and
+the inclination $\iota$ can be highly correlated in any parameter
+estimation recovery.
+
+Given this degeneracy, it should come as no surprise that the 2D
+marginalized posteriors of distance and inclination are the broadest
+of the six physically interesting parameters.  Four typical 2D PDFs
+are presented in Figure~\ref{distIotaPDF}.  Notice the bimodal
+uncertainty present in the top 2D PDF along the $\iota$ axis, due to
+the similarity between the evaluated likelihoods at $\iota$ and $\iota
++ \pi/2$.  As the majority of the information extracted via parameter
+estimation is from the phase of the signal, the recovery of the
+posterior in $D$-$\iota$ space will be limited, even during the
+Advanced LIGO/Virgo era; however, if a gravitational-wave signal is
+matched to a detected SGRB counterpart (which may occur at the rate of
+$\sim 3 yr^{-1}$ in Advanced LIGO/Virgo, according to
+\cite{Metzger2013}), the optical information about the orbital
+inclination will provide an additional constraint on the D-$\iota$
+space, vastly improving the luminosity distance recovery quoted here.  These results
+qualitatively agree with those of \cite{Nissanke2011}, who studied in detail
+MCMC estimation of $D$-$\iota$ measurements from gravitational-wave detectors with 
+coincident GRB detections.
+
+In Table \ref{ciTableExtrinsic}, we list the averaged 68\% and 95\% credible
+intervals for distance and inclination.  Notice that the uncertainties
+on distance can be extreme, from tens to hundreds of Mpc.  When
+discussing the inclination angle, we elected to use $|\cos(\iota)|$,
+as this maps the occasional bimodal structure into a single PDF, and
+observing a compact merger at $\iota$ and $\iota + \pi/2$ should yield
+identical physics.
+%Since $|\cos(\iota)|$ maps the bi-modal structure in the inclination PDFs seen in Figure \ref{distIotaPDF} to a single
+%mode, the uncertainties in $\iota$ will sufficiently small \carl{[QUANTIFY]} to provide coincident information on
+%GRB beaming angles.
+
+\subsection{Sky Localization}
+\label{skySection}
+
+Unlike the mass parameters, the recovery of the position on the sky is
+highly dependent on the location of the source with respect to the
+detector network in question.  Much of the information about the sky
+position of the source comes from the relative timing of the signals
+in each detector.  For the HLV configuration, timing in the
+three-detector network can only localize signals to one of two points
+in the sky.  That is, when using only time-of-arrival information,
+there is equal support in the probability density functions near true
+location and near the point reflected through the plane formed by the
+three detectors.  See \cite{Fairhurst2011} for a global analysis of
+time-of-arrival accuracy for various network configurations, including
+those considered here.  See also \cite{Prospects2013} for a similar analysis,
+applied to each stage of the advanced detector network.
+
+In practice, however, additional information from the wave
+polarization and the relative difference in SNR between individual
+detectors can break this plane-reflection degeneracy, leading to a
+bi-modal distribution with significantly more support in one mode of
+the PDF.  By fitting for the sky location and the polarization
+simultaneously, the MCMC can often identify the correct mode on the
+sky.  For the four-detector configuration, this concern is irrelevant:
+even with time-of-arrival data alone, the HLVI network can constrain
+any source to a single mode on the sky.  Even then, there are still
+locations on the sky in which two or more detectors are not sensitive
+to the gravitational-wave signal, yielding distorted, non-Gaussian
+PDFs.
+
+The sky location uncertainties for HLV and HLVI are shown in Figures
+\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI} respectively.  We show
+all four mass bins together, since in practice the mass of the signals
+has little effect on the recovery of the sky location for the
+considered BNS systems.  Only the location on the sky, the network
+configuration, and the other extrinsic parameters were found to be
+relevant.  In particular, notice the increase in efficiency between
+the HLV configuration and the HLVI configuration.  In the HLV
+configuration, there exist points on the sky in which the signal was
+injected near the plane of the detector network.  This causes the
+elongated, ``banana-shaped'' PDFs seen in Figure \ref{2525SkyLocHLV}.
+In the HLVI configuration, the plane is no longer relevant, and there
+are substantially fewer regions in which only two detectors see a
+sufficiently strong signal.  For the HLV configuration, we find that
+ all of the signals are recovered with
+a solid angle uncertainty of less than 64 $\mathrm{deg}^2$ (136 $\mathrm{deg}^2$)
+at the 68\% (95\%) credible interval, while the HLVI configuration 
+recovers all signals to less than 14 $\mathrm{deg}^2$ (45 $\mathrm{deg}^2$).
+The median quantitative results for the two network configurations show a similar
+ benefit with the addition of LIGO India, and are again reported in Table \ref{ciTableExtrinsic}.
+
+Previous studies have considered the increase in sensitivity from the addition of the 
+LIGO India site.  \cite{Nissanke2013} studied the decrease in
+sky-location uncertainties obtained by the inclusion of the LIGO India site
+into the advanced detector network.  Their study also employed an MCMC sampling technique 
+ (a modified version of CosmoMC),
+to determine the average parameter estimation uncertainties for a realistic distribution
+of sources.  As the current study is interested in the \carl{average} uncertainties
+of optimal sources at $\text{SNR}_{network}=20$, ignoring the effects of less viable 
+detection candidates, it is useful to compare the $95\%$ credible intervals
+between the two studies.  The cumulative distributions of sky-area uncertainties
+for both network configurations in each study are plotted in Fig. \ref{compSky}.
+
+The difference in uncertainties between the two studies is illustrative.  \cite{Nissanke2013}
+considered a realistic distribution of sources motivated by a local galaxy catalogue for
+ sources where $D\leq 200\text{Mpc}$, and homogeneously distributed in co-moving
+ volume for sources where $D > 200\text{Mpc}$.  These were then limited to those signals
+ where $\text{SNR}_{network} \geq 8.5$ (the \carl{rule-of-thumb} threshold for detection candidates in the
+ current LIGO/Virgo matched-filtering framework) for the MCMC parameter estimation.
+   The current study considers a source
+ population isotropically distributed on the sky, but at distances such that each signal
+ represents an optimal case for parameter estimation.   Fig.\ \ref{compSky} compares
+ the sky-area uncertainties that will be available to those considering ``good 
+ gravitational-wave events'' (e.g. precision source localization), and the 
+ uncertainties that one can gather by considering all gravitational-wave candidates with 
+ $\text{SNR}_{network}\geq 8.5$ (e.g. electromagnetic follow-up).  As expected, both source
+ populations show a dramatic decrease in parameter estimation uncertainties with the
+ addition of the LIGO India site to the advanced detector network.  This holds true even when
+ considering the increased number of nominal sources available to the HLVI network 
+ configuration in the Nissanke population, where the expansion of the network detection 
+ horizon due to LIGO India increases the number of sources to 130, versus 90 in 
+ the HLV configuration.  This trend is similar to that observed in \cite{Veitch2012}, contrasting
+ the originally proposed four-detector configuration (with two co-located Hanford detectors) to 
+ the HLVI configuration.
+
+\begin{figure*}[ht!]
+  \centering \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm
+    0cm]{HLVsky.pdf}
+ \caption{The uncertainties on the sky of 160 BNS systems in the HLV
+   detector configuration.  Each region represents a single injection,
+   with the colored central region representing the 68\% uncertainty
+   region on the sphere, and the gray shade representing the 95\%
+   uncertainty region.  The color scheme indicates the total solid
+   angle size of the 68\% region.  Note the similar shape of the
+   uncertainty regions at particular points; this is due to the
+   specific pattern of sensitivity over the sky for the three-detector network.}
+ \label{2525SkyLocHLV}
+\end{figure*}
+
+\begin{figure*}[ht!]
+  \centering \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm
+    0cm]{HLVIsky.pdf}
+ \caption{The same as Fig \ref{2525SkyLocHLV}, except for the HLVI
+   detector configuration.  Note the substaintally lower average
+   uncertainties on the skies for the majority of the injections.
+   Also note the lack of large, ``banana-shaped'' uncertainties that
+   were recovered by the HLV configuration.  The two improvements are
+   due to the breaking of the plane degeneracy that
+   is facilitated by the transition to a four-detector network.}
+ \label{2525SkyLocHLVI}
+\end{figure*}
+
+\begin{figure}[ht!]
+  \centering \includegraphics[angle=0,scale=0.58, trim=0.5cm 1cm 0cm 0cm]{comparitiveSkyAreas.pdf}
+
+ \caption{The cumulative fraction of sources found within $deg^2$ at the 95\% credible
+ interval.  This plot contains results from two separate studies: the current study, in
+ which optimal detection candidates are considered ($\text{SNR}_{network}=20$), 
+and \cite{Nissanke2013}, which employs a separate MCMC code on a
+ realistic source population (where $\text{SNR}_{trigger} \geq 8.5$ is employed to determine
+ parameter estimation sources).  The optimal detection candidates are constrained
+ to substantially smaller solid angles on the sky, as is expected for such ``gold-plated''
+ events, while both studies show a substantial decrease in sky-area uncertainties for the HLVI configuration.}
+ \label{compSky}
+\end{figure}
+
+\section{Credible Intervals}
+\label{ciSection}
+
+When quoting parameter estimation results, it is often convenient to
+reduce the full parameter space to credible intervals about single
+marginalized parameters..  To that end, we state the averaged 68\% and 95\% credible
+intervals about the single parameters for each of the three
+parameter pairs of interest.  These were already plotted for the sky
+locations in Figures~\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI}.
+
+There are several different ways of computing the width of a credible
+interval in this setup.  If one considers the points in the MCMC as
+random draws from the true posterior, then the $\alpha$-level credible
+interval can be computed by simply ordering the points, removing
+$N(1-\alpha )/2$ points from both sides of the posterior samples
+symmetrically, and measuring the width of the remaining points.  While
+this procedure can prove hazardous for multi-modal distributions, it
+is straightforward and reliable for single-peaked distributions as
+reported here.
+
+In Table~\ref{ciTableIntrinsic}, we list the mean 68\% and 95\% credible
+intervals recovered for the four mass configurations in both network
+configurations. This essentially quantifies the widths of the
+posteriors plotted throughout Section~\ref{resultsSection}.  The
+purpose of Tables~\ref{ciTableIntrinsic} and \ref{ciTableExtrinsic} is
+to provide a quantitative and quotable source for studies seeking to
+determine how well a physical question about BNS systems can be
+answered with the Advanced LIGO/Virgo network.
+
+Given the previous reliance of parameter estimation studies on the Fisher
+Information Matrix, it is informative to compare the credible intervals quoted here 
+to previously reported values in the literature.  We recompute the credible intervals 
+of the chirp mass and the symmetric mass ratio ($\eta \equiv m_1 m_2 / M_{tot}^2$)
+at the 68\% level \carl{NO, FIX ME}(1-$\sigma$) for the $1.4M_{\odot}/1.4M_{\odot}$ system presented 
+here.  We then compare the findings of the MCMC to the Fisher matrix predictions using
+an identical network configuration (HLV), noise curve, and waveform model.  
+We compute the Fisher matrix uncertainties 
+using a code previously described in \cite{Inadequacies}.  We find that the MCMC credible
+ intervals \carl{can} vary significantly from
+the estimates of the Fisher matrix, with the Fisher matrix underestimating the 
+fractional uncertainties by as much as a factor of \sout{three} \carl{two}.  See Table~\ref{FIMvsMCMC}.  This 
+result agrees with the conventional wisdom surrounding the Fisher Matrix accuracy,
+as well as results where the Fisher Matrix is computed to higher order \citep{Vitale2010}
+   This disagreement, while 
+   unsurprising, emphasizes the importance of employing the full parameter estimation
+    machinery of an MCMC when making physically relevant claims.
+
+\begin{table*}[h!]
+\centering
+\caption{Median 68\% and 95\% credible intervals for intrinsic parameters for
+  each of the four systems considered.  We report the credible
+  intervals of quantities measured, as well as the component masses
+  and total mass.  Although the results for the HLV and HLVI
+  configurations are quantitatively identical, we report them
+  separately for consistency.}
+  \tabcolsep=0.11cm
+      {\renewcommand{\arraystretch}{1.3} 
+\begin{tabular}{lcccccccccccccccccccc}
+
+\\ HLV\\
+
+ \hline\hline System & \vline & \multicolumn{3}{c}{$\Delta \chmass / \chmass$} &
+\vline & \multicolumn{3}{c}{$\Delta M_1 / M_1$} & \vline & \multicolumn{3}{c}{$\Delta M_2 / M_2$} & \vline &
+\multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
+Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
+\hline\hline
+
+$1M_{\odot}-1M_{\odot}$ & \vline &$0.00497\%$ & \vline &$0.0104\%$ & \vline & $7.17\%$ & \vline &$11.9\%$ & \vline & $6.39\%$ & \vline &$10.3\%$ & \vline & $0.643\%$ & \vline &$1.25\%$ & \vline & $0.123$ & \vline &$0.197$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00883\%$ & \vline &$0.0188\%$ & \vline & $7.77\%$ & \vline &$13\%$ & \vline & $6.87\%$ & \vline &$11.1\%$ & \vline & $0.746\%$ & \vline &$1.47\%$ & \vline & $0.132$ & \vline &$0.212$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0176\%$ & \vline &$0.0355\%$ & \vline & $1.86\%$ & \vline &$3.74\%$ & \vline & $1.59\%$ & \vline &$3.23\%$ & \vline & $1.48\%$ & \vline &$2.99\%$ & \vline & $0.0138$ & \vline &$0.028$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.0246\%$ & \vline &$0.0522\%$ & \vline & $9.02\%$ & \vline &$15\%$ & \vline & $7.82\%$ & \vline &$12.6\%$ & \vline & $1.01\%$ & \vline &$1.94\%$ & \vline & $0.149$ & \vline &$0.239$\\
+
+\hline
+\hline
+
+\\HLVI\\
+
+ \hline\hline System & \vline & \multicolumn{3}{c}{$\Delta \chmass / \chmass$} &
+\vline & \multicolumn{3}{c}{$\Delta M_1 / M_1$} & \vline & \multicolumn{3}{c}{$\Delta M_2 / M_2$} & \vline &
+\multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
+Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
+\hline\hline
+
+$1M_{\odot}-1M_{\odot}$ & \vline &$0.00497\%$ & \vline &$0.0106\%$ & \vline & $7.15\%$ & \vline &$11.9\%$ & \vline & $6.38\%$ & \vline &$10.4\%$ & \vline & $0.646\%$ & \vline &$1.27\%$ & \vline & $0.123$ & \vline &$0.198$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00884\%$ & \vline &$0.0188\%$ & \vline & $7.67\%$ & \vline &$12.8\%$ & \vline & $6.79\%$ & \vline &$11.1\%$ & \vline & $0.733\%$ & \vline &$1.46\%$ & \vline & $0.13$ & \vline &$0.211$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0176\%$ & \vline &$0.0352\%$ & \vline & $1.85\%$ & \vline &$3.72\%$ & \vline & $1.59\%$ & \vline &$3.2\%$ & \vline & $1.47\%$ & \vline &$2.96\%$ & \vline & $0.0137$ & \vline &$0.0277$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.0243\%$ & \vline &$0.0515\%$ & \vline & $9.03\%$ & \vline &$14.9\%$ & \vline & $7.84\%$ & \vline &$12.6\%$ & \vline & $0.998\%$ & \vline &$1.92\%$ & \vline & $0.149$ & \vline &$0.238$\\
+
+\hline
+\hline
+
+\end{tabular}}
+\label{ciTableIntrinsic}
+\end{table*}
+
+\begin{table*}[h!]
+\centering
+\caption{Median 68\% and 95\% credible intervals of extrinsic parameters for
+  each of the four systems considered.  As expected, there exists a
+  substantial improvement in the sky localization capabilities of the
+  four-detector HLVI configuration over the three-detector HLV
+  configuration.  Note that the solid-angle sky-location credible
+  intervals, $\Delta\Omega$, are calculated directly on the 2D sphere,
+  not by combining the $\alpha$ and $\delta$ uncertainties.}
+
+  \tabcolsep=0.11cm
+      {\renewcommand{\arraystretch}{1.3} 
+\begin{tabular}{lcccccccccccccccccccc}
+
+\\ HLV\\
+
+\hline\hline System & \vline & \multicolumn{3}{c}{$\Delta D$ $(mpc)$} & \vline &
+\multicolumn{3}{c}{$\Delta |\cos(\iota)|$} & \vline & \multicolumn{3}{c}{$\Delta \alpha$ $(deg)$} & \vline &
+\multicolumn{3}{c}{$\Delta \delta$ $(deg)$} & \vline & \multicolumn{3}{c}{$\Delta\Omega$
+$(deg^2)$}\\\hline
+Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
+ \hline\hline
+
+$1M_{\odot}-1M_{\odot}$ & \vline &$49.4$ & \vline &$89.9$ & \vline & $0.323$ & \vline &$0.611$ & \vline & $1.73$ & \vline &$4.09$ & \vline & $2.51$ & \vline &$5.52$ & \vline & $5.12$ & \vline &$13.5$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$61.4$ & \vline &$107$ & \vline & $0.314$ & \vline &$0.588$ & \vline & $2.63$ & \vline &$5.42$ & \vline & $2.53$ & \vline &$5.27$ & \vline & $4.12$ & \vline &$11.2$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$68.8$ & \vline &$127$ & \vline & $0.31$ & \vline &$0.549$ & \vline & $2.41$ & \vline &$4.6$ & \vline & $2.77$ & \vline &$6.2$ & \vline & $4.37$ & \vline &$12.1$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$116$ & \vline &$198$ & \vline & $0.349$ & \vline &$0.613$ & \vline & $1.75$ & \vline &$4.51$ & \vline & $2.42$ & \vline &$5.01$ & \vline & $4.62$ & \vline &$12$\\
+
+\hline\hline
+
+\\HLVI\\ 
+\hline\hline System & \vline & \multicolumn{3}{c}{$\Delta D$ $(mpc)$} & \vline &
+\multicolumn{3}{c}{$\Delta |\cos(\iota)|$} & \vline & \multicolumn{3}{c}{$\Delta \alpha$ $(deg)$} & \vline &
+\multicolumn{3}{c}{$\Delta \delta$ $(deg)$} & \vline & \multicolumn{3}{c}{$\Delta\Omega$
+$(deg^2)$}\\\hline
+Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
+ \hline\hline 
+$1M_{\odot}-1M_{\odot}$ & \vline &$42.7$ & \vline &$76.2$ & \vline & $0.267$ & \vline &$0.455$ & \vline & $1.13$ & \vline &$2.25$ & \vline & $1.48$ & \vline &$3.01$ & \vline & $1.87$ & \vline &$5.37$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$66.6$ & \vline &$121$ & \vline & $0.285$ & \vline &$0.509$ & \vline & $1.27$ & \vline &$2.48$ & \vline & $1.49$ & \vline &$3.01$ & \vline & $2$ & \vline &$5.12$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$73.7$ & \vline &$130$ & \vline & $0.297$ & \vline &$0.499$ & \vline & $1.29$ & \vline &$2.42$ & \vline & $1.42$ & \vline &$2.89$ & \vline & $1.75$ & \vline &$4.87$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$120$ & \vline &$213$ & \vline & $0.301$ & \vline &$0.517$ & \vline & $1.18$ & \vline &$2.34$ & \vline & $1.55$ & \vline &$3.14$ & \vline & $2.25$ & \vline &$5.99$\\ \hline
+
+\end{tabular}}
+\label{ciTableExtrinsic}
+\end{table*}
+
+\begin{table}[h!]
+\centering
+\caption{68\% Credible intervals versus \sout{1-$\sigma$} \carl{$2\sigma$} Fisher matrix uncertainties for mass parameters in each system in the HLV configuration.}
+  \tabcolsep=0.11cm
+    {\renewcommand{\arraystretch}{1.3} 
+\begin{tabular}{lcccccccc}
+
+\hline\hline Parameter & \vline & \multicolumn{3}{c}{$\Delta\mathcal{M}_c / \mathcal{M}_c$} & \vline & \multicolumn{3}{c}{$\Delta \eta / \eta$} \\ \hline \hline
+
+Estimate & \vline & MCMC & \vline & FIM & \vline & MCMC & \vline & FIM \\ \hline
+
+$1M_{\odot}-1M_{\odot}$ & \vline &  0.00497\% & \vline & 0.00396\% & \vline & 0.645\% & \vline & 0.704\% \\
+$1.4M_{\odot}-1.4M_{\odot}$ & \vline &  0.00890\% & \vline & 0.00743\% & \vline & 0.745\% & \vline & 0.866\% \\
+$1M_{\odot}-2.5M_{\odot}$& \vline &  0.0176\% & \vline & 0.00880\% & \vline & 1.475\% & \vline & 0.862\% \\
+$2.5M_{\odot}-2.5M_{\odot}$& \vline &  0.0245\% & \vline & 0.0221\% & \vline & 1.000\% & \vline & 1.299\% \\
+
+\hline\hline
+
+\end{tabular}}
+\label{FIMvsMCMC}
+\end{table}
+
+\section{Conclusion}
+\label{conclusionSection}
+
+In this paper, we performed an MCMC parameter estimation analysis on
+the recoverability of basic information about binary neutron stars,
+using two projected versions of the Advanced LIGO/Virgo network.  We
+focused on the recovery of the two masses, the luminosity distance,
+orbital inclination, and the sky location, as these are the six basic
+parameters of physical interest to the problem.  It should be remembered that these signals were injected at high, 
+but not unrealistic, SNRs \carl{in order to create a reference similar to those found in previous
+Fisher Matrix studies, and to validate the ``$n(t) = 0$ as average'' assumption.
+
+ Unlike the Fisher-matrix studies, an MCMC allows us to relax the flawed assumptions of a Gaussian and uni-modal 
+ distribtion, and to
+fully explore the relevant parameter space.  Given the highly non-Gaussian nature of the explored 
+parameter space (see Figures \ref{9dPDF}, \ref{1414masses}, \ref{metaMassPDFs}-\ref{2525SkyLocHLVI} ), this exploration is critical to a complete 
+understanding of the gravitational-wave BNS parameter estimation problem}.  
+The results quoted can be thought of as the
+average \carl{lower-bound} uncertainties for an \carl{optimal} \sout{``good''} Advanced LIGO/Virgo detection.
+
+\carl{For the mass parameters,} we found that, neglecting the effects of spin, the component masses can be
+constrained to within 9\% (15\%) of their true value to a credible level of
+68\% (95\%) \carl{for systems with equal-mass neutron stars.
+}  This value drops below 1.9\% (3.7\%) for systems with an asymmetric masses.
+  \carl{It was also found that the fractional uncertainties for equal-mass binary systems are similar at equal SNR.
+Only when the masses are unequal are the fractional errors effected.}
+These results were summarized in Table \ref{ciTableIntrinsic}.  \carl{The current study is the first 
+to quantify neutron star mass measurements in Advanced LIGO/VIRGO  via an MCMC for neutron star masses
+other than $1.4M_{\odot}$.}
+
+We also reported on the ability of the two network configurations to
+constrain the luminosity distance and orbital inclination.  For
+distance, it was found that the uncertainties will average anywhere from
+43 to 120 MPC at 68\% credible levels, and from 76 to 213 MPC at 96\% credible levels,
+ making the uncertainties 
+larger than the luminosity distances themselves in many cases.  Furthermore, it was
+found that the cosine of the orbital inclination can be constrained to
+within 0.35 (0.61) at the 68\% (95\%) level on average,
+ suggesting that Advanced LIGO/Virgo will not
+be able to offer constraining information on GRB beaming angles in coincidence
+with electromagnetic observations.  Coincidence detections will still be possible, but
+the orbital orientation information from gravitational waves will 
+not provide astrophysically relevant constrains.
+
+Finally, we reported the ability of advanced networks to constrain the
+sky location of \carl{optimal} BNS signals.  It was found that the three-detector
+configuration, consisting of the Washington and Louisiana LIGO sites
+plus the Italian Virgo site, was able to constrain all signals within
+64 $\mathrm{deg}^2$ (136 $\mathrm{deg}^2$) on the sky at the 68\% (95\%) 
+credible level, with
+an average median 68\% (95\%) credible interval of 
+$4.6$ $\mathrm{deg}^2$ (12.2 $\mathrm{deg}^2$).
+Meanwhile, the four-detector configuration, consisting of the
+three-detector sites plus a LIGO India detector, was able to localize
+all the sky locations to within 14 $\mathrm{deg}^2$ (45 $\mathrm{deg}^2$) on the sky at the 68\% (95\%)
+credible interval, with an average median 68\% (95\%) credible interval of 
+2 $\mathrm{deg}^2$ $(5.3$ $\mathrm{deg}^2)$.  These high-SNR results
+were then compared to similar results for a realistic, non-optimal source distribution from
+\cite{Nissanke2013}.
+
+It should be noted that there are two distinct types of systematic
+error, highly relevant to the gravitational-wave parameter estimation
+problem, that we have not addressed in this study.  First, we have
+studied the parameter estimation uncertainties under the assumption
+that the waveform template we use to recover the signal template
+exactly matches the fully relativistic waveforms nature provides.  In
+practice, these waveforms are only approximations to the fully
+general-relativistic physics required to solve the problem.  See
+\cite{BuonannoWaveform} for a better description of the systematic uncertainties
+present in the most common waveform families.  Additionally, there are
+several astrophysical assumptions that can potentially contribute to
+systematic uncertainties in the waveforms, such as the neutron-star
+equation of state, possible modifications to General Relativity,
+eccentricity, etc.
+
+Secondly, as stated above, we have performed our study under idealized
+detector-noise conditions.  In practice the noise levels of Advanced
+LIGO and Advanced Virgo can vary with time and contain occasional
+excursions which are highly non-Gaussian.  Unfortunately, there is no
+reliable way to predict the sort of non-Gaussian detector glitches and
+instrumentation effects that will arise in any advanced
+gravitational-wave detector.  The realization of noise will be a
+major factor in the deflection of signal PDFs from the idealized cases
+presented here.
+
+In this study, we have also neglected the effects of spin in the
+parameter space, electing to focus on the absolute basic parameters
+that will be measured routinely in the Advanced Detector era.  Given
+the high degree of coupling between the spin and mass of objects
+in the gravitational-wave parameter space, it remains unclear if the
+mass measurement alone will be sufficient to distinguish non-spinning
+neutron stars from highly-spinning low-mass black holes.  Future work
+will explore this potential mass/spin degeneracy, including the
+effects of orbital precession, with the aim of definitively answering
+this question.
+
+\pagebreak
+
+\section{Acknowledgements}
+
+The authors would like to thank Samaya Nissanke, John Veitch, and Neil Cornish for useful discussions.  We would also like to thank Samaya Nissanke for the 95\% credible regions
+quoted in Fig.
+\ref{compSky}.
+CR and BF were supported by NSF GRFP Fellowships, award DGE-0824162.
+All authors were also partially or fully supported by NSF Gravitational Physics grant PHY-0969820, PI: VK.
+Lastly, VK is grateful to the hospitality of the Aspen Center for Physics while she worked on this study.
+
+\bibliographystyle{apj} \bibliography{paper}{}
+
+\appendix
+
+\section{Markov Chain Monte-Carlo}
+\label{appendixMCMC}
+
+  The MCMC sampler included in \texttt{LALInference} employs a Metropolis-Hastings sampling algorithm , which is
+   algorithmically described as follows:
 
@@
 
-\subsection{Waveform Model}
-\label{waveformSection}
+\section{Gravitational-Waveform Model}
+\label{appendixWaveform}
 
@@
 \end{equation}
-respectively.\footnote{Most gravitational-wave literature instead uses
+respectively.  Note that most gravitational-wave literature instead uses
   the \textit{symmetric mass ratio}, defined as $\eta \equiv M_1 M_2 /
@@
   equal-mass systems when employing a prior on $p(\eta)$.  
-  %\will{This is not true.  I calculate (could be a bug, so
-   % check it)
-   % \begin{equation}
-   %   p(\chmass, q) = \frac{\chmass}{q} \left(\frac{\left(1+q\right)^2}{q}\right)^{\frac{1}{5}}
-   % \end{equation}
-  %  when 
-   % \begin{equation}
-    %  p\left(m_1, m_2\right) \propto \mathrm{const}
-   % \end{equation}
-   % The reasons to use $q$ instead of $\eta$
-   % \begin{itemize}
-     % \item It is more intuitive to astronomers (you mention this
-      %  above).
-     % \item As $m_1 \to m_2$, or $q \to 1$, or $\eta \to 1/4$, the
-      %  prior on $\eta$ for equal mass systems diverges (it is an
-      %  integrable singularity, but still singular), while the prior
-       % on $q$ is well-behaved.  This doesn't matter for sampling
-      %  purposes, since the divergence in integrable, but it is
-      %  disconcerting for near-equal-mass systems to see a large peak
-       % in the histogram for $\eta$ near $\eta = 1/4$.
-    %\end{itemize}}
-    }  By convention, $M_1 \geq M_2$.  The stationary phase then
+     By convention, $M_1 \geq M_2$.  The stationary phase then
 becomes an expansion in the Newtonian orbital velocity, $v=(\pi
@@
 
-We consider the mass parameters ($\chmass,q$) and the phasing
-parameters, ($\phi_0,t_c$), to be the intrinsic parameters of the
-gravitational-wave signal.  There are an additional 5 extrinsic
-parameters, independent of the pN orbital phase, which can modulate
-the amplitude of the signal independently in each
-detector.  Combining these leads to our 9-dimensional parameter space
-for non-spinning systems,
-\begin{equation}
-\thpara = (\chmass, q, \phi_0,t_c,D,\iota,\psi,\alpha,\delta),
-\label{parameterspace}
-\end{equation}
-where
-
-\begin{itemize}
-\item $\chmass$ is the chirp mass,
-\item $q$ is the mass ratio,
-\item $\phi_0$ and $t_c$ are the chirp phase and chirp time, arbitrary
-  phasing parameters,
-\item $D$ is the luminosity distance to the binary,
-\item $\iota$ is the orbital inclination (the angle between the
-  orbital angular momentum and the line of sight),
-\item $\psi$ is the gravitational-wave polarization, and
-\item $\alpha$ and $\delta$ are the right ascension and declination of
-  the source on the sky.
-\end{itemize}
-  Since the wave amplitude depends on the orientation of the binary
-  with respect to each detector, most of the information about these
-  extrinsic parameters comes from two sources: the time-of-arrival
-  triangulation of the signal, and the relative amplitudes
-  in each detector in the network.
-
-  \subsection{Detector Configuration and Noise Models}
-  \label{detectorSection}
-
-To perform the integral defined in \eqref{innerProduct}, we used as
-our power-spectral density the best estimate for a high-power,
-zero-detuning configuration of Advanced LIGO, provided by the LIGO
-Scientific Collaboration.  Both the noise curve and technical reports
-describing it can be found in \cite{ADVLIGONoise}.  We consider two
-configurations of the advanced detector network: a three-detector
-configuation consistanting of the two LIGO sites (in Hanford, WA and
-Livingston, LA) and the Virgo site (in Pisa, Italy), and a
-four-detector configuration that adds the proposed LIGO-India detector
-(in Chitradurga, KA).  For simplicity, we assume each detector to be
-operating at the Advanced LIGO sensitivity.
-
-For a multi-detector network, the noise-weighted inner products
-\eqref{innerProduct} combine linearly \carl{so long as the noise is
-uncorrelated between detectors}, allowing us to use the above
-formalism with minimal modification.  We integrate the inner product
-from a lower-frequency cutoff of $20\text{Hz}$ to the
-innermost-stable-circular orbit of the systems, which for
-a non-spinning binary is a function only of the total mass:
-
-\begin{equation}
-  \pi f_{\text{ISCO}} = \frac{1}{6^{3/2}M_{tot}}.
-  \label{ISCOFrequency}
-\end{equation}
-
-We define the signal-to-noise ratio (SNR) of a gravitational wave in a
-single detector as
-\begin{equation}
-  \text{SNR} \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{|
-    \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df,
-  \label{formalSNR}
-\end{equation}
-where $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
-the frequency-domain data and template, respectively, and the
-normalization $\sigma$ is given by
-\begin{equation}
-  \sigma^2 = 4\int^{\infty}_{0}\frac{| \tilde{h}(f)|^2}{S_n(f)}df.
-  \label{SNRnorm}
-\end{equation}
-
-\noindent When dealing with a network of gravitational-wave detectors, the SNRs
-of the individual detectors add in quadrature.  That is, the network
-SNR for a detection is
-
-\begin{equation}
-\text{SNR}_{\text{network}} = \sqrt{\sum_i \text{SNR}_{i}^2}
-\label{SNRnetwork}
-\end{equation}
-
-\noindent where $\text{SNR}_i$ is the SNR, given by \eqref{formalSNR}, of
-the $i^{\text{th}}$ detector.
-
-For this study, we consider four separate populations of BNS systems,
-with component mass combinations of $1M_{\odot}/1M_{\odot}$,
-$1.4M_{\odot}/1.4M_{\odot}$, $1M_{\odot}/2.5M_{\odot}$, and
-$2.5M_{\odot}/2.5M_{\odot}$.  Each population consisted of 40 signals
-distributed randomly in sky location, polarization, inclination,
-time-of-arrival, and coalescence phase.  The luminosity distance, $D$,
-was selected to yield a signal strength of $\text{SNR}_{network}=20$
-for each source in each network configuration. 
- While unphysical from an astrophysics perspective
-(binary sources are expected to be distributed uniformly in co-moving volume), this
-choice allows us to explore the parameter estimation in the context of
-loud but plausible detection candidates.
-
-Finally, note that the PSD that defines the inner
-product \eqref{innerProduct} is simply the time-averaged sensitivity
-of a given detector to a specific frequency.  Ignoring non-Gaussian
-glitches, any stretch of data should contain a specific noise
-realization drawn from a Gaussian colored by the PSD.  Without a
-realistic model including the actual instrument sensitivity, non-stationary
- noise, and uncertainty in the PSD we cannot accurately
-simulate gravitational-wave data to the point of making precise predictions about
-parameter estimation capabilities.  Furthermore, the posterior
-distribution from a future detection will be influenced by the
-realization of the noise at the time of the detection.  Because of
-this, we elect to focus only on the statistical errors due to the
-flexibility of the waveforms and the expected sensitivity of the
-advanced era detectors and suppress any effects of detector noise by
-picking $n(t) \equiv 0$.  Consequently, what we recover with the MCMC could be interpreted as
-the posterior distribution function for each source averaged over all
-possible (Gaussian) noise realizations, assuming we have the correct
-PSD and that the signal is sufficiently powerful for the linearized-signal
-approximation to be valid.  By selecting a source population with an
- artificial distribution in SNR, we ensure that the
-     ``zero-noise'' as average uncertainty approximation is valid.
-
-     Previous studies have both employed and studied in detail the consequences of this approach.
-   \carl{  In particular, \cite{Nissanke2010} demonstrated that the $n(t)=0$ posterior is equal to the geometric mean over 
-     specific noise realizations of the posterior, while \cite{Sampson2013} performed a numerical experiment to 
-     demonstrate the validity of the assumption.
-We perform a similar numerical experiment in Section \ref{noiseSection}, in which we demonstrate that the uncertainties from a $n(t)=0$ posterior are equivalent to the frequentist
-     average over uncertainties from multiple noise realizations. }
-
-\section{Results}
-\label{resultsSection}
-
-\begin{figure*}[t!]
-\centering \includegraphics[trim=7cm 0cm 0cm 0cm,
-  clip=true,scale=0.58]{9dpdf}
-%\begin{array}{ccc} 
-%\includegraphics[width=2.2in]{1dpdfs/mc.pdf} &\includegraphics[width=2.2in]{1dpdfs/eta.pdf}  & \includegraphics[width=2.2in]{1dpdfs/m1.pdf}\\
-%\includegraphics[width=2.2in]{1dpdfs/time.pdf} &\includegraphics[width=2.2in]{1dpdfs/dist.pdf}  &\includegraphics[width=2.2in]{1dpdfs/iota.pdf}\\
-%\includegraphics[width=2.2in]{1dpdfs/ra.pdf} & \includegraphics[width=2.2in]{1dpdfs/dec.pdf} & \includegraphics[width=2.2in]{1dpdfs/m2.pdf}
-%\end{array}$
-\caption{\label{9dPDF} Marginalized 1D  posterior probability densities
-  of a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS
-  system.  We have plotted each of the 9 parameters for our
-  non-spinning BNS problem as stated in section \ref{waveformSection}.
-    Note how, even for parameters with excellent recovery, the peak of
-  the 1D Gaussian is displaced from the injected value (in dashed
-  red).  This is not due to a systematic bias, but is caused by the
-  marginalization of a single dimension from the full 9D posterior
-  space.  To better see this effect, compare the 1D PDF for
-  $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in
-  Figure~\ref{1414masses}.  The plots here represent the Gaussian kernel density
-  estimator of each PDF.  The estimate for $q$ was 
-  computed by reflecting the highest $10\%$ of samples across the $q=1$ boundary.  
-  This was done to avoid a false decrease in estimated probability density near
-  the boundary.}
-\end{figure*}
-
-Of the nine parameters in the domain of the waveform, only six are
-particularly physically interesting: the masses of the two binaries,
-$M_1$ and $M_2$, the orbital inclination, $\iota$, the angular
-position on the sky, $\alpha$ and $\delta$, and the luminosity
-distance of the source, $D$.  While the coalescence phase $\phi_0$,
-the coalescence time $t_c$, and the wave polarization $\psi$ must be
-included in any parameter estimation of the waveform, they do not
-encode any information of particular astrophysical
-interest.%\footnote{For systems whose components are non-spinning.  The
-  %presence of intrinsic angular momentum will, in general, couple to
-  %the coalescence phase and wave polarization.  \will{But those
-   % parameters are still physically uninteresting.  They couple to
-   % interesting parameters in both the spinning and non-spinning
-  %  cases, which is why they must be included.  I would just eliminate
-   % this footnote.}}
-
-In Figure~\ref{9dPDF}, we provide an example of the nine,
-1-dimensional marginalized posterior probability density functions
-recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system.  These
-PDFs are representative of the type of results that will be produced by
-parameter estimation studies in the advanced detector era.  Notice
-that the peak of several parameters, including the chirp mass,
-$\chmass$, appears to be displaced from the true values in dashed red.  This
-effect is due to the reduction of the 9-dimensional PDF to a series of
-marginalized 1-dimensional PDFs.  For instance, the 1-dimensional PDF
-for chirp mass is marginalized via
-\begin{equation}
-p(\chmass | s) = \int _{\thpara \setminus \chmass} p(\thpara |
-s)~d(\thpara \setminus \chmass)
-\label{mcMarginalization}
-\end{equation}
-where the notation $\thpara \setminus \chmass$ implies all parameter
-of \eqref{parameterspace} except $\chmass$.  Other parameter and
-higher-dimensional marginalizations follow a similar convention.  In
-practice, the MCMC samples make this integral trivial: since the
-samples are distributed according to the posterior,
-\eqref{mcMarginalization} can be calculated by simply reading off the
-relevant samples in a single parameter, implicitly calculating a
-Monte-Carlo integral over all other parameters.
-
-\subsection{Mass Parameters}
-\label{massSection}
-
-\begin{figure}[h!]
-  \centering \includegraphics[trim=1cm 0cm 2cm 0cm,
-    clip=false,scale=0.63]{1414masses2D.pdf}
- \caption{2D marginalized posterior probability density functions for
-   the mass parameters recovered in typical a
-   $1.4M_{\odot}/1.4M_{\odot}$ system.  The posteriors are plotted in
-   terms of parameters used in the waveform, chirp mass
-   ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual
-   component masses of the binary ($M_1$ and $M_2$).  In the
-   $\chmass$-$q$ space, the posterior would almost resemble a Gaussian if not
-   for the limitation of $q \leq 1$.  The presence of the $q$ cutoff
-   and the convention that $M_1 \geq M_2$ inform the non-Gaussian
-   features present.  When projected as 1D marginalized posteriors,
-   the component masses resemble the posterior PDFs shown in Figure
-   \ref{metaMassPDFs}.}
-  \label{1414masses}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering \includegraphics[trim=1cm 0cm 2cm 0cm,
-    clip=false,scale=0.63]{125masses2D.pdf}
- \caption{Similar to Figure~\ref{1414masses}, but for a typical
-   $1M_{\odot}/2.5M_{\odot}$ system.  The unequal mass ratio displaces
-   the posterior PDFs from the $q \leq 1$ boundary present in the equal-mass
-   case, yielding a Gaussian PDF in both the $\chmass$-$q$ and
-   $M_1$-$M_2$ spaces.}
-  \label{125masses}
-\end{figure}
-
-\begin{figure*}[ht!]
-  \centering \includegraphics[trim=3cm 0cm 2cm 0cm,
-    clip=false,scale=0.75]{newMasses.pdf}
- \caption{Mass PDFs for the four BNS systems, averaged over each of
-   the 40 injections.  The average is reported since, in practice,
-   there was quantitatively no difference between the recovered PDFs
-   for different systems with identical masses and SNRs.  Systems with
-   identical mass ratios but different total masses have
-   quantitatively identical PDFs when normalized to the total
-   mass.  Similarly to Fig. \ref{9dPDF}, we plot the Gaussian kernel density
-   estimates, and reflect $10\%$ of the points across the $q = 1$ and $M_1 = M_2$ boundaries (for the three equal-mass cases).}
-  \label{metaMassPDFs}
-\end{figure*}
-
-Of the nine variables in our parameter space \eqref{parameterspace},
-the mass parameters, $\chmass$ and $q$, or, correspondingly, $M_1$ and
-$M_2$ are the most astrophysically interesting.  The ability of
-Advanced LIGO/Virgo to construct a population of BNS masses will be
-one of the more useful and immediate applications of gravitational-wave astronomy.
-
-We find that there is virtually no difference between the mass PDFs of
-our different injected signals within each mass bin.  While this may
-initially seem disconcerting, it is to be expected for the analysis presented here.
-  Recall that all
-of the BNS signals were injected with a network SNR of 20 into a
-zero-noise detector realization.  Furthermore, note that the mass
-parameters are the only two which directly affect the phase of the
-TaylorF2 waveform \eqref{phase}.  Therefore, as long as the injected
-mass parameters are identical within each mass system, and as long as
-the injected SNR is identical, the amount of recoverable information
-in each mass parameter should be almost identical, and for a
-sufficiently converged MCMC chain, the recovered posterior PDF should
-be identical.
-
-This effect can be summarized as follows: for non-spinning systems,
-the posterior probability of the masses, $p(\chmass, q | s)$, does not
-depend strongly on the recovery of the extrinsic parameters, $\phi_0$
-or $t_c$.  Therefore, systems with identical masses will produce
-identical mass PDFs.  The only noticeable difference will come from
-the specific realization of noise produced by the detector, which we
-address in Section \ref{noiseSection}.
-
-%The ``almost'' in the previous sentence is to draw attention to one critical, neglected fact: while the mass parameters are independent of the injected signals position with respect to the detector network, the other parameters are certainly not.
-Obviously many of the other parameters (i.e.
-sky location, polarization, distance, inclination, and time-of-arrival) all depend on the orientation of the binary with respect to each of the individual detectors.
-Since our 9-dimensional parameter space can be highly correlated, it is entirely reasonable to assume that cross-correlations between the extrinsic parameters and the mass parameters will cause variation in the recovery of the individual injection PDFs.
-
-%In practice, it was found that the cross-correlations between the extrinsic parameters and signal time-of-arrival were several orders of magnitude \carl{[QUANTIFY]} below the uncertainties in $\chmass$ and $q$.
-It should be noted that, in practice, this will \emph{not} be the case: in reality, the noise power-spectral density of each detector varies as a function of time, including both natural variations in sensitivity and detector glitches \carl{[CITE]}.
-In such a case, the base sensitivity of a gravitational-wave detector to even the easiest to recover parameters will vary as a function of position and time.
-
-In Figures~\ref{1414masses} and~\ref{125masses}, we show the
-marginalized 2D posterior PDFs of our mass parameters for prototypical
-equal-mass and unequal-mass binaries.  We include the PDF in both the
-$\chmass$-$q$ space (relevant for the waveform and the MCMC
-algorithm), and the more physically interesting component mass space
-($M_1$-$M_2$).  Although only the $1.4M_{\odot}/1.4M_{\odot}$ system
-is included in Figure \ref{1414masses}, the PDF is qualitatively
-identical to the other equal mass cases, modulo a scaling factor.
-
-To condense the results into a single figure of merit, we average the
-1-dimensional mass PDFs into a single posterior probability for the
-system in Figure~\ref{metaMassPDFs}.  Notice how, when averaged and
-normalized to the injected values, the recovery of the component
-masses depends only on the mass ratio.  Furthermore, for systems with
-equal component masses, the posterior barely extends beyond 15\% of
-the injected values.  If one assumes that the threshold between black
-holes and neutron stars lies at approximately $3M_{\odot}$, then it
-might be naively assumed that the mass recovery would allow one to
-discriminate between black holes and neutron stars.
-
-In practice, there is a physical complication to this claim: we have
-neglected the spin of the binaries, which will be highly correlated to
-the masses.  This coupling means that, in the case where the black hole spins
-are parallel to the orbital angular momentum, a higher-massed spinning black
-hole systems can produce waveforms very similar to non-spinning,
-low-mass systems.  This effect makes it extremely difficult to discern between
-non-spinning neutron stars and spin-aligned, more massive black holes
-\citep{Baird2013,Hannam2013}.  However, the situation is not hopeless:
-if the spins are misaligned, the spin vectors will couple to the
-orientation of the binary (encoded in the three angles $\phi_0$,
-$\iota$, and $\psi$) via relativistic precession.  It remains to be
-seen if using fully spinning waveforms will make it possible for
-Advanced\ LIGO/Virgo to discern binary neutron stars from their
-spinning black hole counterparts.
-
-In Table \ref{ciTableIntrinsic}, we list the 68\% and 95\% credible
-intervals for the mass parameters.  We find that the component masses
-for equal mass systems can be isolated to between 6.4\% and 9\% (10.3\% and 15\%)
-fractional uncertainty at the 68\% (95\%) credible interval.  This value
-drops to less than 1.9\% (3.7\%) for the components of the unequal mass systems.
-Again, this neglects the effects of spin which can substantially
-increase these values.
-
-\subsection{Inclination and Distance}
-\label{idSection}
-
-\begin{figure}[h!]
-  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
-    clip=true,scale=0.75]{distIota2D.pdf}
- \caption{Typical marginalized 2D mass PDFs for luminosity distance
-   $D$ and orbital inclination $\iota$. Notice the bimodal
-   distribution on the first PDF, that can occur when a system is
-   detected nearly ``edge-on'' ($\iota \approx \pi/2$).  In general,
-   the degeneracy between distance and inclination forces the PDF into
-   one of these two paths when the system is not edge-on, as seen in
-   the second and third PDFs.}
- \label{distIotaPDF}
-\end{figure}
-
-Binary neutron star systems (along with neutron star/black hole
-systems) are one of the best candidates for progenitors of short-hard
-gamma-ray bursts \citep[and references therein]{Nakar2007}.  After
-merger, the remnant is believed to emit the burst along the axis of
-orbital angular momentum, making the inclination of the binary system
-of particular interest to gamma-ray astronomy
-\citep{LSCGRB2010,Corsi2012}.  The inclination is detected as a
-relative amplitude difference between the two gravitational-wave
-polarizations, such that to lowest order:
-
-\begin{align}
-h_+(f) &= \frac{1+\cos^2(\iota)}{2 D} \tilde{h}(f) \nonumber
-\\ h_\times(f) &= i \frac{\cos(\iota)}{D}\tilde{h}(f) .
-\end{align}
-
-\noindent It should be apparent that the luminosity distance $D$ and
-the inclination $\iota$ can be highly correlated in any parameter
-estimation recovery.
-
-Given this degeneracy, it should come as no surprise that the 2D
-marginalized posteriors of distance and inclination are the broadest
-of the six physically interesting parameters.  Four typical 2D PDFs
-are presented in Figure~\ref{distIotaPDF}.  Notice the bimodal
-uncertainty present in the top 2D PDF along the $\iota$ axis, due to
-the similarity between the evaluated likelihoods at $\iota$ and $\iota
-+ \pi/2$.  As the majority of the information extracted via parameter
-estimation is from the phase of the signal, the recovery of the
-posterior in $D$-$\iota$ space will be limited, even during the
-Advanced LIGO/Virgo era; however, if a gravitational-wave signal is
-matched to a detected SGRB counterpart (which may occur at the rate of
-$\sim 3 yr^{-1}$ in Advanced LIGO/Virgo, according to
-\cite{Metzger2013}), the optical information about the orbital
-inclination will provide an additional constraint on the D-$\iota$
-space, vastly improving the luminosity distance recovery quoted here.  These results
-qualitatively agree with those of \cite{Nissanke2011}, who studied in detail
-MCMC estimation of $D$-$\iota$ measurements from gravitational-wave detectors with 
-coincident GRB detections.
-
-In Table \ref{ciTableExtrinsic}, we list the averaged 68\% and 95\% credible
-intervals for distance and inclination.  Notice that the uncertainties
-on distance can be extreme, from tens to hundreds of Mpc.  When
-discussing the inclination angle, we elected to use $|\cos(\iota)|$,
-as this maps the occasional bimodal structure into a single PDF, and
-observing a compact merger at $\iota$ and $\iota + \pi/2$ should yield
-identical physics.
-%Since $|\cos(\iota)|$ maps the bi-modal structure in the inclination PDFs seen in Figure \ref{distIotaPDF} to a single
-%mode, the uncertainties in $\iota$ will sufficiently small \carl{[QUANTIFY]} to provide coincident information on
-%GRB beaming angles.
-
-\subsection{Sky Localization}
-\label{skySection}
-
-Unlike the mass parameters, the recovery of the position on the sky is
-highly dependent on the location of the source with respect to the
-detector network in question.  Much of the information about the sky
-position of the source comes from the relative timing of the signals
-in each detector.  For the HLV configuration, timing in the
-three-detector network can only localize signals to one of two points
-in the sky.  That is, when using only time-of-arrival information,
-there is equal support in the probability density functions near true
-location and near the point reflected through the plane formed by the
-three detectors.  See \cite{Fairhurst2011} for a global analysis of
-time-of-arrival accuracy for various network configurations, including
-those considered here.  See also \cite{Prospects2013} for a similar analysis,
-applied to each stage of the advanced detector network.
-
-In practice, however, additional information from the wave
-polarization and the relative difference in SNR between individual
-detectors can break this plane-reflection degeneracy, leading to a
-bi-modal distribution with significantly more support in one mode of
-the PDF.  By fitting for the sky location and the polarization
-simultaneously, the MCMC can often identify the correct mode on the
-sky.  For the four-detector configuration, this concern is irrelevant:
-even with time-of-arrival data alone, the HLVI network can constrain
-any source to a single mode on the sky.  Even then, there are still
-locations on the sky in which two or more detectors are not sensitive
-to the gravitational-wave signal, yielding distorted, non-Gaussian
-PDFs.
-
-The sky location uncertainties for HLV and HLVI are shown in Figures
-\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI} respectively.  We show
-all four mass bins together, since in practice the mass of the signals
-has little effect on the recovery of the sky location for the
-considered BNS systems.  Only the location on the sky, the network
-configuration, and the other extrinsic parameters were found to be
-relevant.  In particular, notice the increase in efficiency between
-the HLV configuration and the HLVI configuration.  In the HLV
-configuration, there exist points on the sky in which the signal was
-injected near the plane of the detector network.  This causes the
-elongated, ``banana-shaped'' PDFs seen in Figure \ref{2525SkyLocHLV}.
-In the HLVI configuration, the plane is no longer relevant, and there
-are substantially fewer regions in which only two detectors see a
-sufficiently strong signal.  For the HLV configuration, we find that
- all of the signals are recovered with
-a solid angle uncertainty of less than 64 $\mathrm{deg}^2$ (136 $\mathrm{deg}^2$)
-at the 68\% (95\%) credible interval, while the HLVI configuration 
-recovers all signals to less than 14 $\mathrm{deg}^2$ (45 $\mathrm{deg}^2$).
-The median quantitative results for the two network configurations show a similar
- benefit with the addition of LIGO India, and are again reported in Table \ref{ciTableExtrinsic}.
-
-Previous studies have considered the increase in sensitivity from the addition of the 
-LIGO India site.  \cite{Nissanke2013} studied the decrease in
-sky-location uncertainties obtained by the inclusion of the LIGO India site
-into the advanced detector network.  Their study also employed an MCMC sampling technique 
- (a modified version of CosmoMC),
-to determine the average parameter estimation uncertainties for a realistic distribution
-of sources.  As the current study is interested in the uncertainties
-of optimal sources at $\text{SNR}_{network}=20$, ignoring the effects of less viable 
-detection candidates, it is useful to compare the $95\%$ credible intervals
-between the two studies.  The cumulative distributions of sky-area uncertainties
-for both network configurations in each study are plotted in Fig. \ref{compSky}.
-
-The difference in uncertainties between the two studies is illustrative.  \cite{Nissanke2013}
-considered a realistic distribution of sources motivated by a local galaxy catalogue for
- sources where $D\leq 200\text{Mpc}$, and homogeneously distributed in co-moving
- volume for sources where $D > 200\text{Mpc}$.  These were then limited to those signals
- where $\text{SNR}_{network} \geq 8.5$ (the \carl{rule-of-thumb} threshold for detection candidates in the
- current LIGO/Virgo matched-filtering framework) for the MCMC parameter estimation.
-   The current study considers a source
- population isotropically distributed on the sky, but at distances such that each signal
- represents an optimal case for parameter estimation.   Fig.\ \ref{compSky} compares
- the sky-area uncertainties that will be available to those considering ``good 
- gravitational-wave events'' (e.g. precision source localization), and the 
- uncertainties that one can gather by considering all gravitational-wave candidates with 
- $\text{SNR}_{network}\geq 8.5$ (e.g. electromagnetic follow-up).  As expected, both source
- populations show a dramatic decrease in parameter estimation uncertainties with the
- addition of the LIGO India site to the advanced detector network.  This holds true even when
- considering the increased number of nominal sources available to the HLVI network 
- configuration in the Nissanke population, where the expansion of the network detection 
- horizon due to LIGO India increases the number of sources to 130, versus 90 in 
- the HLV configuration.  This trend is similar to that observed in \cite{Veitch2012}, contrasting
- the originally proposed four-detector configuration (with two co-located Hanford detectors) to 
- the HLVI configuration.
-
-\begin{figure*}[ht!]
-  \centering \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm
-    0cm]{HLVsky.pdf}
- \caption{The uncertainties on the sky of 160 BNS systems in the HLV
-   detector configuration.  Each region represents a single injection,
-   with the colored central region representing the 68\% uncertainty
-   region on the sphere, and the gray shade representing the 95\%
-   uncertainty region.  The color scheme indicates the total solid
-   angle size of the 68\% region.  Note the similar shape of the
-   uncertainty regions at particular points; this is due to the
-   specific pattern of sensitivity over the sky for the three-detector network.}
- \label{2525SkyLocHLV}
-\end{figure*}
-
-\begin{figure*}[ht!]
-  \centering \includegraphics[angle=0,scale=0.4, trim=5cm 2cm 3cm
-    0cm]{HLVIsky.pdf}
- \caption{The same as Fig \ref{2525SkyLocHLV}, except for the HLVI
-   detector configuration.  Note the substaintally lower average
-   uncertainties on the skies for the majority of the injections.
-   Also note the lack of large, ``banana-shaped'' uncertainties that
-   were recovered by the HLV configuration.  The two improvements are
-   due to the breaking of the plane degeneracy that
-   is facilitated by the transition to a four-detector network.}
- \label{2525SkyLocHLVI}
-\end{figure*}
-
-\begin{figure}[ht!]
-  \centering \includegraphics[angle=0,scale=0.58, trim=0.5cm 1cm 0cm 0cm]{comparitiveSkyAreas.pdf}
-
- \caption{The cumulative fraction of sources found within $deg^2$ at the 95\% credible
- interval.  This plot contains results from two separate studies: the current study, in
- which optimal detection candidates are considered ($\text{SNR}_{network}=20$), 
-and \cite{Nissanke2013}, which employs a separate MCMC code on a
- realistic source population (where $\text{SNR}_{trigger} \geq 8.5$ is employed to determine
- parameter estimation sources).  The optimal detection candidates are constrained
- to substantially smaller solid angles on the sky, as is expected for such ``gold-plated''
- events, while both studies show a substantial decrease in sky-area uncertainties for the HLVI configuration.}
- \label{compSky}
-\end{figure}
-
-\subsection{Varied Noise Realizations}
+\section{Zero-Noise verses Varied Noise Realizations}
 \label{noiseSection}
 
-\begin{figure}[ht!]
-  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
-    clip=true,scale=0.52]{noisePDF.pdf}
+\begin{figure}[b!]
+  \centering \includegraphics[trim=2cm 0cm 0cm 0cm,
+    clip=true,scale=0.52]{noisePDFflat.pdf}
  \caption{The effects of a non-zero noise realization on the recovered
@@
 
-  As a demonstration of this, we injected a single
+     Previous studies have both employed and studied in detail the consequences of this approach.
+   \carl{  In particular, \cite{Nissanke2010} demonstrated that the $n(t)=0$ posterior is equal to the geometric mean over 
+     specific noise realizations of the posterior, while \cite{Sampson2013} performed a numerical experiment to 
+     demonstrate the validity of the assumption.
+We perform a similar numerical experiment here in which we demonstrate that the uncertainties from a $n(t)=0$ posterior are equivalent to the frequentist
+     average over uncertainties from multiple noise realizations. }  We injected a single
 $1M_{\odot}/2.5M_{\odot}$ system, detected in HLVI, into 5 separate
@@
 
-\begin{comment}
-\subsection{Timescale for Parameter Estimation}
-\label{PEtimesSection}
-
-\begin{figure*}[h!]
-  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
-    clip=true,scale=0.65]{HLVRuntimes.pdf}
- \label{HLVRuntimes}
- \caption{Typical Runtimes for the HLV Network Configuration.  Each
-   run was done on the local Northwestern supercomputer}
-\end{figure*}
-
-\begin{figure*}[h!]
-  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
-    clip=true,scale=0.65]{HLVIRuntimes.pdf}
- \label{HLVIRuntimes}
- \caption{\carl{this is superfluous; combine this into one figure with
-     two colors.} }
-\end{figure*}
-
-The parameter estimation techniques described here will be performed
-as a follow-up analysis to the detections returned by various on-line
-analyses in the Advanced LIGO/Virgo era.  While there exist specific
-PE analyses that will be performed in real-time for time sensitive
-signals (i.e. extrinsic parameters for signals with a potential
-optimal counterpart \carl{[CITE PROTO-BEN OR LEO SINGER]}), most PE
-will require several days to weeks to complete the analysis upon a
-single event.  We display the distribution of runtimes for the two
-network configuration in Figures~\ref{HLVRuntimes} and
-~\ref{HLVIRuntimes}
-\end{comment}
-
-\section{Credible Intervals}
-\label{ciSection}
-
-When quoting parameter estimation results, it is often convenient to
-reduce the full parameter space to credible intervals about single
-marginalized parameters..  To that end, we state the averaged 68\% and 95\% credible
-intervals about the single parameters for each of the three
-parameter pairs of interest.  These were already plotted for the sky
-locations in Figures~\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI}.
-
-There are several different ways of computing the width of a credible
-interval in this setup.  If one considers the points in the MCMC as
-random draws from the true posterior, then the $\alpha$-level credible
-interval can be computed by simply ordering the points, removing
-$N(1-\alpha )/2$ points from both sides of the posterior samples
-symmetrically, and measuring the width of the remaining points.  While
-this procedure can prove hazardous for multi-modal distributions, it
-is straightforward and reliable for single-peaked distributions as
-reported here.
-
-In Table~\ref{ciTableIntrinsic}, we list the mean 68\% and 95\% credible
-intervals recovered for the four mass configurations in both network
-configurations. This essentially quantifies the widths of the
-posteriors plotted throughout Section~\ref{resultsSection}.  The
-purpose of Tables~\ref{ciTableIntrinsic} and \ref{ciTableExtrinsic} is
-to provide a quantitative and quotable source for studies seeking to
-determine how well a physical question about BNS systems can be
-answered with the Advanced LIGO/Virgo network.
-
-Given the previous reliance of parameter estimation studies on the Fisher
-Information Matrix, it is informative to compare the credible intervals quoted here 
-to previously reported values in the literature.  We recompute the credible intervals 
-of the chirp mass and the symmetric mass ratio ($\eta \equiv m_1 m_2 / M_{tot}^2$)
-at the 68\% level \carl{NO, FIX ME}(1-$\sigma$) for the $1.4M_{\odot}/1.4M_{\odot}$ system presented 
-here.  We then compare the findings of the MCMC to the Fisher matrix predictions using
-an identical network configuration (HLV), noise curve, and waveform model.  
-We compute the Fisher matrix uncertainties 
-using a code previously described in \cite{Inadequacies}.  We find that the MCMC credible
- intervals \carl{can} vary significantly from
-the estimates of the Fisher matrix, with the Fisher matrix underestimating the 
-fractional uncertainties by as much as a factor of \sout{three} \carl{two}.  See Table~\ref{FIMvsMCMC}.  This 
-result agrees with the conventional wisdom surrounding the Fisher Matrix accuracy,
-as well as results where the Fisher Matrix is computed to higher order \citep{Vitale2010}
-   This disagreement, while 
-   unsurprising, emphasizes the importance of employing the full parameter estimation
-    machinery of an MCMC when making physically relevant claims.
-
-\begin{table*}[h!]
-\centering
-\caption{Median 68\% and 95\% credible intervals for intrinsic parameters for
-  each of the four systems considered.  We report the credible
-  intervals of quantities measured, as well as the component masses
-  and total mass.  Although the results for the HLV and HLVI
-  configurations are quantitatively identical, we report them
-  separately for consistency.}
-  \tabcolsep=0.11cm
-      {\renewcommand{\arraystretch}{1.3} 
-\begin{tabular}{lcccccccccccccccccccc}
-
-\\ HLV\\
-
- \hline\hline System & \vline & \multicolumn{3}{c}{$\Delta \chmass / \chmass$} &
-\vline & \multicolumn{3}{c}{$\Delta M_1 / M_1$} & \vline & \multicolumn{3}{c}{$\Delta M_2 / M_2$} & \vline &
-\multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
-Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
-\hline\hline
-
-$1M_{\odot}-1M_{\odot}$ & \vline &$0.00497\%$ & \vline &$0.0104\%$ & \vline & $7.17\%$ & \vline &$11.9\%$ & \vline & $6.39\%$ & \vline &$10.3\%$ & \vline & $0.643\%$ & \vline &$1.25\%$ & \vline & $0.123$ & \vline &$0.197$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00883\%$ & \vline &$0.0188\%$ & \vline & $7.77\%$ & \vline &$13\%$ & \vline & $6.87\%$ & \vline &$11.1\%$ & \vline & $0.746\%$ & \vline &$1.47\%$ & \vline & $0.132$ & \vline &$0.212$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0176\%$ & \vline &$0.0355\%$ & \vline & $1.86\%$ & \vline &$3.74\%$ & \vline & $1.59\%$ & \vline &$3.23\%$ & \vline & $1.48\%$ & \vline &$2.99\%$ & \vline & $0.0138$ & \vline &$0.028$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.0246\%$ & \vline &$0.0522\%$ & \vline & $9.02\%$ & \vline &$15\%$ & \vline & $7.82\%$ & \vline &$12.6\%$ & \vline & $1.01\%$ & \vline &$1.94\%$ & \vline & $0.149$ & \vline &$0.239$\\
-
-\hline
-\hline
-
-\\HLVI\\
-
- \hline\hline System & \vline & \multicolumn{3}{c}{$\Delta \chmass / \chmass$} &
-\vline & \multicolumn{3}{c}{$\Delta M_1 / M_1$} & \vline & \multicolumn{3}{c}{$\Delta M_2 / M_2$} & \vline &
-\multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
-Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
-\hline\hline
-
-$1M_{\odot}-1M_{\odot}$ & \vline &$0.00497\%$ & \vline &$0.0106\%$ & \vline & $7.15\%$ & \vline &$11.9\%$ & \vline & $6.38\%$ & \vline &$10.4\%$ & \vline & $0.646\%$ & \vline &$1.27\%$ & \vline & $0.123$ & \vline &$0.198$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00884\%$ & \vline &$0.0188\%$ & \vline & $7.67\%$ & \vline &$12.8\%$ & \vline & $6.79\%$ & \vline &$11.1\%$ & \vline & $0.733\%$ & \vline &$1.46\%$ & \vline & $0.13$ & \vline &$0.211$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0176\%$ & \vline &$0.0352\%$ & \vline & $1.85\%$ & \vline &$3.72\%$ & \vline & $1.59\%$ & \vline &$3.2\%$ & \vline & $1.47\%$ & \vline &$2.96\%$ & \vline & $0.0137$ & \vline &$0.0277$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.0243\%$ & \vline &$0.0515\%$ & \vline & $9.03\%$ & \vline &$14.9\%$ & \vline & $7.84\%$ & \vline &$12.6\%$ & \vline & $0.998\%$ & \vline &$1.92\%$ & \vline & $0.149$ & \vline &$0.238$\\
-
-\hline
-\hline
-
-\end{tabular}}
-\label{ciTableIntrinsic}
-\end{table*}
-
-\begin{table*}[h!]
-\centering
-\caption{Median 68\% and 95\% credible intervals of extrinsic parameters for
-  each of the four systems considered.  As expected, there exists a
-  substantial improvement in the sky localization capabilities of the
-  four-detector HLVI configuration over the three-detector HLV
-  configuration.  Note that the solid-angle sky-location credible
-  intervals, $\Delta\Omega$, are calculated directly on the 2D sphere,
-  not by combining the $\alpha$ and $\delta$ uncertainties.}
-
-  \tabcolsep=0.11cm
-      {\renewcommand{\arraystretch}{1.3} 
-\begin{tabular}{lcccccccccccccccccccc}
-
-\\ HLV\\
-
-\hline\hline System & \vline & \multicolumn{3}{c}{$\Delta D$ $(mpc)$} & \vline &
-\multicolumn{3}{c}{$\Delta |\cos(\iota)|$} & \vline & \multicolumn{3}{c}{$\Delta \alpha$ $(deg)$} & \vline &
-\multicolumn{3}{c}{$\Delta \delta$ $(deg)$} & \vline & \multicolumn{3}{c}{$\Delta\Omega$
-$(deg^2)$}\\\hline
-Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
- \hline\hline
-
-$1M_{\odot}-1M_{\odot}$ & \vline &$49.4$ & \vline &$89.9$ & \vline & $0.323$ & \vline &$0.611$ & \vline & $1.73$ & \vline &$4.09$ & \vline & $2.51$ & \vline &$5.52$ & \vline & $5.12$ & \vline &$13.5$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$61.4$ & \vline &$107$ & \vline & $0.314$ & \vline &$0.588$ & \vline & $2.63$ & \vline &$5.42$ & \vline & $2.53$ & \vline &$5.27$ & \vline & $4.12$ & \vline &$11.2$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$68.8$ & \vline &$127$ & \vline & $0.31$ & \vline &$0.549$ & \vline & $2.41$ & \vline &$4.6$ & \vline & $2.77$ & \vline &$6.2$ & \vline & $4.37$ & \vline &$12.1$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$116$ & \vline &$198$ & \vline & $0.349$ & \vline &$0.613$ & \vline & $1.75$ & \vline &$4.51$ & \vline & $2.42$ & \vline &$5.01$ & \vline & $4.62$ & \vline &$12$\\
-
-\hline\hline
-
-\\HLVI\\ 
-\hline\hline System & \vline & \multicolumn{3}{c}{$\Delta D$ $(mpc)$} & \vline &
-\multicolumn{3}{c}{$\Delta |\cos(\iota)|$} & \vline & \multicolumn{3}{c}{$\Delta \alpha$ $(deg)$} & \vline &
-\multicolumn{3}{c}{$\Delta \delta$ $(deg)$} & \vline & \multicolumn{3}{c}{$\Delta\Omega$
-$(deg^2)$}\\\hline
-Credible Level & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% & \vline & 68\% & \vline & 95\% \\
- \hline\hline 
-$1M_{\odot}-1M_{\odot}$ & \vline &$42.7$ & \vline &$76.2$ & \vline & $0.267$ & \vline &$0.455$ & \vline & $1.13$ & \vline &$2.25$ & \vline & $1.48$ & \vline &$3.01$ & \vline & $1.87$ & \vline &$5.37$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$66.6$ & \vline &$121$ & \vline & $0.285$ & \vline &$0.509$ & \vline & $1.27$ & \vline &$2.48$ & \vline & $1.49$ & \vline &$3.01$ & \vline & $2$ & \vline &$5.12$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$73.7$ & \vline &$130$ & \vline & $0.297$ & \vline &$0.499$ & \vline & $1.29$ & \vline &$2.42$ & \vline & $1.42$ & \vline &$2.89$ & \vline & $1.75$ & \vline &$4.87$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$120$ & \vline &$213$ & \vline & $0.301$ & \vline &$0.517$ & \vline & $1.18$ & \vline &$2.34$ & \vline & $1.55$ & \vline &$3.14$ & \vline & $2.25$ & \vline &$5.99$\\ \hline
-
-\end{tabular}}
-\label{ciTableExtrinsic}
-\end{table*}
-
-\begin{table}[h!]
-\centering
-\caption{68\% Credible intervals versus \sout{1-$\sigma$} \carl{$2\sigma$} Fisher matrix uncertainties for mass parameters in each system in the HLV configuration.}
-  \tabcolsep=0.11cm
-    {\renewcommand{\arraystretch}{1.3} 
-\begin{tabular}{lcccccccc}
-
-\hline\hline Parameter & \vline & \multicolumn{3}{c}{$\Delta\mathcal{M}_c / \mathcal{M}_c$} & \vline & \multicolumn{3}{c}{$\Delta \eta / \eta$} \\ \hline \hline
-
-Estimate & \vline & MCMC & \vline & FIM & \vline & MCMC & \vline & FIM \\ \hline
-
-$1M_{\odot}-1M_{\odot}$ & \vline &  0.00497\% & \vline & 0.00396\% & \vline & 0.645\% & \vline & 0.704\% \\
-$1.4M_{\odot}-1.4M_{\odot}$ & \vline &  0.00890\% & \vline & 0.00743\% & \vline & 0.745\% & \vline & 0.866\% \\
-$1M_{\odot}-2.5M_{\odot}$& \vline &  0.0176\% & \vline & 0.00880\% & \vline & 1.475\% & \vline & 0.862\% \\
-$2.5M_{\odot}-2.5M_{\odot}$& \vline &  0.0245\% & \vline & 0.0221\% & \vline & 1.000\% & \vline & 1.299\% \\
-
-\hline\hline
-
-\end{tabular}}
-\label{FIMvsMCMC}
-\end{table}
-
-\section{Conclusion}
-\label{conclusionSection}
-
-In this paper, we performed an MCMC parameter estimation analysis on
-the recoverability of basic information about binary neutron stars,
-using two projected versions of the Advanced LIGO/Virgo network.  We
-focused on the recovery of the two masses, the luminosity distance,
-orbital inclination, and the sky location, as these are the six basic
-parameters of physical interest to the problem.  It should be remembered that these signals were injected at high, 
-but not unrealistic, SNRs \carl{in order to create a reference similar to those found in previous
-Fisher Matrix studies, and to validate the ``$n(t) = 0$ as average'' assumption.
-
- Unlike the Fisher-matrix studies, an MCMC allows us to relax the flawed assumptions of a Gaussian and uni-modal 
- distribtion, and to
-fully explore the relevant parameter space.  Given the highly non-Gaussian nature of the explored 
-parameter space (see Figures \ref{9dPDF}, \ref{1414masses}, \ref{metaMassPDFs}-\ref{2525SkyLocHLVI} ), this exploration is critical to a complete 
-understanding of the gravitational-wave BNS parameter estimation problem}.  
-The results quoted can be thought of as the
-average \carl{lower-bound} uncertainties for an \carl{optimal} \sout{``good''} Advanced LIGO/Virgo detection.
-
-\carl{For the mass parameters,} we found that, neglecting the effects of spin, the component masses can be
-constrained to within 9\% (15\%) of their true value to a credible level of
-68\% (95\%) \carl{for systems with equal-mass neutron stars.
-}  This value drops below 1.9\% (3.7\%) for systems with an asymmetric masses.
-  \carl{It was also found that the fractional uncertainties for equal-mass binary systems are similar at equal SNR.
-Only when the masses are unequal are the fractional errors effected.}
-These results were summarized in Table \ref{ciTableIntrinsic}.  \carl{The current study is the first 
-to quantify neutron star mass measurements in Advanced LIGO/VIRGO  via an MCMC for neutron star masses
-other than $1.4M_{\odot}$.}
-
-We also reported on the ability of the two network configurations to
-constrain the luminosity distance and orbital inclination.  For
-distance, it was found that the uncertainties will average anywhere from
-43 to 120 MPC at 68\% credible levels, and from 76 to 213 MPC at 96\% credible levels,
- making the uncertainties 
-larger than the luminosity distances themselves in many cases.  Furthermore, it was
-found that the cosine of the orbital inclination can be constrained to
-within 0.35 (0.61) at the 68\% (95\%) level on average,
- suggesting that Advanced LIGO/Virgo will not
-be able to offer constraining information on GRB beaming angles in coincidence
-with electromagnetic observations.  Coincidence detections will still be possible, but
-the orbital orientation information from gravitational waves will 
-not provide astrophysically relevant constrains.
-
-Finally, we reported the ability of advanced networks to constrain the
-sky location of \carl{optimal} BNS signals.  It was found that the three-detector
-configuration, consisting of the Washington and Louisiana LIGO sites
-plus the Italian Virgo site, was able to constrain all signals within
-64 $\mathrm{deg}^2$ (136 $\mathrm{deg}^2$) on the sky at the 68\% (95\%) 
-credible level, with
-an average median 68\% (95\%) credible interval of 
-$4.6$ $\mathrm{deg}^2$ (12.2 $\mathrm{deg}^2$).
-Meanwhile, the four-detector configuration, consisting of the
-three-detector sites plus a LIGO India detector, was able to localize
-all the sky locations to within 14 $\mathrm{deg}^2$ (45 $\mathrm{deg}^2$) on the sky at the 68\% (95\%)
-credible interval, with an average median 68\% (95\%) credible interval of 
-2 $\mathrm{deg}^2$ $(5.3$ $\mathrm{deg}^2)$.  These high-SNR results
-were then compared to similar results for a realistic, non-optimal source distribution from
-\cite{Nissanke2013}.
-
-It should be noted that there are two distinct types of systematic
-error, highly relevant to the gravitational-wave parameter estimation
-problem, that we have not addressed in this study.  First, we have
-studied the parameter estimation uncertainties under the assumption
-that the waveform template we use to recover the signal template
-exactly matches the fully relativistic waveforms nature provides.  In
-practice, these waveforms are only approximations to the fully
-general-relativistic physics required to solve the problem.  See
-\cite{BuonannoWaveform} for a better description of the systematic uncertainties
-present in the most common waveform families.  Additionally, there are
-several astrophysical assumptions that can potentially contribute to
-systematic uncertainties in the waveforms, such as the neutron-star
-equation of state, possible modifications to General Relativity,
-eccentricity, etc.
-
-Secondly, as stated above, we have performed our study under idealized
-detector-noise conditions.  In practice the noise levels of Advanced
-LIGO and Advanced Virgo can vary with time and contain occasional
-excursions which are highly non-Gaussian.  Unfortunately, there is no
-reliable way to predict the sort of non-Gaussian detector glitches and
-instrumentation effects that will arise in any advanced
-gravitational-wave detector.  The realization of noise will be a
-major factor in the deflection of signal PDFs from the idealized, \carl{lower-bound} cases
-presented here.
-
-In this study, we have also neglected the effects of spin in the
-parameter space, electing to focus on the absolute basic parameters
-that will be measured routinely in the Advanced Detector era.  Given
-the high degree of coupling between the spin and mass of objects
-in the gravitational-wave parameter space, it remains unclear if the
-mass measurement alone will be sufficient to distinguish non-spinning
-neutron stars from highly-spinning low-mass black holes.  Future work
-will explore this potential mass/spin degeneracy, including the
-effects of orbital precession, with the aim of definitively answering
-this question.
-
-\pagebreak
-
-\section{Acknowledgements}
-
-The authors would like to thank Samaya Nissanke, John Veitch, and Neil Cornish for useful discussions.  We would also like to thank Samaya Nissanke for the 95\% credible regions
-quoted in Fig.
-\ref{compSky}.
-CR and BF were supported by NSF GRFP Fellowships, award DGE-0824162.
-All authors were also partially or fully supported by NSF Gravitational Physics grant PHY-0969820, PI: VK.
-Lastly, VK is grateful to the hospitality of the Aspen Center for Physics while she worked on this study.
-
-\bibliographystyle{apj} \bibliography{paper}{}
-
 \end{document}

### 2013-12-18 doc/Review2Response.txt
fixed everything

@@
 Additionally, we have culled any references to “realistic estimates” from the abstract and introduction.
-By describing the results as “lower-bound average uncertainties”, we believe the information is still physically interesting, while not misleading the reader.
+By describing the results as “averaged lower-bound uncertainties”, we believe the information is still physically interesting, while not misleading to the reader.
 
@@
 
-Of course, the true prior should be the true mass distribution for binary neutron stars, combined with a distance/sky-location prior based on the distribution of baryonic matter in the local universe.
+The reviewer is correct that our priors are not astrophysical in nature.
 In practice, the observed distribution of neutron star masses from pulsar measurements isn’t sufficiently strong to noticeably influence our recovered posteriors.
-[DE-SARCASTIC THIS]
+As such, we elected to employ an agnostic prior on our neutron star masses.
 
-The zero-spin assumption is NOT physical, though in practice the maximum possible spin of a neutron star (assuming a reasonable equation of state) is insufficient to induce a large effect in the waveform.
+The zero-spin assumption is not physical, though in practice the maximum possible spin of a neutron star (assuming a reasonable equation of state) is insufficient to induce a large effect in our parameter estimation,
 
@@
 At a wall in the parameter space (e.g.
-q=1), the KDE drops artificially, since the value at q=1 is missing support from points where q>1.
-To fix this, it is customary to reflect some of the points across the boundary, so that the KDE resembles the histogram.
-As long as dp(x)/dx = 0 at the boundary, this estimator is unbiased.
-We elected to use 10% of the points, as it was the minimum number required to get the smooth KDE to match the binned histograms.
-[SHORTEN THIS AND INSERT IN THE TEXT]
+q=1), the KDE (which is only employed when generating the plots in Figure 1) needs to be artificially increased so that the smoothing near q=1 does not artificially drop due to the lack of points where q>1.
+This was done purely so the smoothed plots would agree with the binned histograms of the same data.
+We have clarified the text describing the figure.
 
@@
 
-We have added a mention that this is a simplification in the text. [ADD IT]
+We have modified the text to describe this as a simplification
 

### 2013-12-18 doc/paper.tex
fixed everything

@@
 \item uniform in component masses from $0.8M_{\odot} \leq M_{1,2} \leq
-  30M_{\odot}$, with a minimum chirp mass (see Eq.~\eqref{eqRatioCM})
+  30M_{\odot}$, with a minimum chirp mass (see Eq.~\eqref{parameterspace})
   of 0.6 $M_{\odot}$ 
@@
   Figure~\ref{1414masses}.  The plots here represent the Gaussian kernel density
-  estimator of each PDF.  The estimate for $q$ was 
-  computed by reflecting the highest $10\%$ of samples across the $q=1$ boundary.  
-  This was done to avoid a false decrease in estimated probability density near
-  the boundary.}
+  estimator of each PDF.  The \sout{estimate} \carl{plot} for $q$ was 
+  computed by reflecting the highest $10\%$ of samples across the $q=1$ boundary, \carl{in order
+  for the smoothed plot to agree with the binned histograms.}
+  \sout{This was done to avoid a false decrease in estimated probability density near
+  the boundary.}}
 \end{figure*}
@@
 of the chirp mass and the symmetric mass ratio ($\eta \equiv m_1 m_2 / M_{tot}^2$)
-at the 68\% level \carl{NO, FIX ME}(1-$\sigma$) for the $1.4M_{\odot}/1.4M_{\odot}$ system presented 
+at the 68\% level ($2\times\sigma$) for the $1.4M_{\odot}/1.4M_{\odot}$ system presented 
 here.  We then compare the findings of the MCMC to the Fisher matrix predictions using
@@
 \centering
-\caption{68\% Credible intervals versus \sout{1-$\sigma$} \carl{$2\sigma$} Fisher matrix uncertainties for mass parameters in each system in the HLV configuration.}
+\caption{68\% Credible intervals versus \carl{$2\times\sigma$} Fisher matrix uncertainties for mass parameters in each system in the HLV configuration.}
   \tabcolsep=0.11cm
@@
 mass, $M_{tot}\equiv M_1+M_2$, it is convenient to work with the mass
-ratio and chirp mass, defined by
-\begin{equation}
-  q\equiv M_2/M_1~~~~\text{and}~~~~\chmass = (M_1 M_2)^{3/5}
-  M_{tot}^{-1/5},
-  \label{eqRatioCM}
-\end{equation}
-respectively.  Note that most gravitational-wave literature instead uses
+ratio and chirp mass, defined in \ref{parameterspace}.
+  Note that most gravitational-wave literature instead uses
   the \textit{symmetric mass ratio}, defined as $\eta \equiv M_1 M_2 /
